### 2020-08-20 Paper/main.tex
8-20 latex

\documentclass{bioinfo}
\copyrightyear{2015} \pubyear{2015}

\access{Advance Access Publication Date: Day Month Year}
\appnotes{Manuscript Category}

\begin{document}
\firstpage{1}

\subtitle{Subject Section}

\title[short Title]{This is a title}
\author[Sample \textit{et~al}.]{Corresponding Author\,$^{\text{\sfb 1,}*}$, Co-Author\,$^{\text{\sfb 2}}$ and Co-Author\,$^{\text{\sfb 2,}*}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
$^{\text{\sf 2}}$Department, Institution, City, Post Code,
Country.}

\corresp{$^\ast$To whom correspondence should be addressed.}

\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

\editor{Associate Editor: XXXXXXX}

\abstract{\textbf{Motivation:}  Text
Text Text Text Text Text.\\
\textbf{Results:} Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text\\
\textbf{Availability:} Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text Text  Text\\
\textbf{Contact:} \href{name@bio.com}{name@bio.com}\\
\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}
online.}

\maketitle

\section{Introduction}

Clustered regularly interspaced short palindromic repeats (CRISPR) / CRIPSR-associated  protein 9 (Cas9) systems is preferred over other biological research and human medicine technologies now, beacuse of it's efficiency, 
 robustness and programmability.  Cas9 nucleases can be directed by short guide RNAs (sgRNAs) to introduce site-specific DNA double-stranded breaks in target, 
 so to enable editing site-specific within the mammalian genome \citep{jinek2012a,cong2013multiplex,mali2013rnaguided}. CRISPR / Cas9, to a large extent, has developed genetic therapies at the cellular level, 
 while there are still severe medical disadvantage even now which has greatly hindered the further clinical application of the CRISPR/Cas9 systems. 
 One of these disadvantage is due to point mutations caused by off-target effects \citep{rubeis2018risks,kang2016introducing,ishii2017reproductive,liang2015crispr/cas9-mediated}. 
 To overcome this disadvantage, a solution is to engineer CRISPR/Cas9 with higher specificities. 
 That's why more and more higher specificities Cas9 variants, such as enhanced SpCas9 (eSpCas9(1.1)), 
 Cas9-High Fidelity (SpCas9-HF1) \citep{ishii2017reproductive,slaymaker2016rationally}, hyper-accurate Cas9 (HypaCas9) \citep{kleinstiver2016high-fidelity}, 
 been developed and bring a significant volume of experimental data, that is to say researchers have to face the difficulty of analyzing such huge and heterogeneous data.

\section{Approach}

Equation~(\ref{eq:01}) Text Text Text Text Text Text  Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
.....

{\ldots}{\ldots} text follows.
\begin{equation}
\sum \text{\it x}+ \text{\it y} =\text{\it Z}\label{eq:01}\vspace*{-10pt}
\end{equation}

%\enlargethispage{12pt}
\begin{methods}
\section{Methods}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text
text\vspace*{1pt}

\begin{itemize}
\item for bulleted list, use itemize
\item for bulleted list, use itemize
\item for bulleted list, use itemize\vspace*{1pt}
\end{itemize}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
 might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text Text Text Text Text Text Text Text Text Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text\vadjust{\newpage}.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text Text Text Text Text Text Text Text Text Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\subsection{This is subheading}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text
text. Text Text Text Text Text Text  Text Text Text Text Text Text
Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\subsubsection{This is subsubheading}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text\break
text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text
textText Text Text Text Text Text  Text Text Text Text Text Text
Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\enlargethispage{6pt}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\begin{table}[!t]
\processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}\toprule head1 &
head2 & head3 & head4\\\midrule
row1 & row1 & row1 & row1\\
row2 & row2 & row2 & row2\\
row3 & row3 & row3 & row3\\
row4 & row4 & row4 & row4\\\botrule
\end{tabular}}{This is a footnote}
\end{table}

\end{methods}

\begin{figure}[!tpb]%figure1
\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{235pt} \vbox to 100pt{\vfill\hbox to
235pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
\end{minipage}}
%\centerline{\includegraphics{fig01.eps}}
\caption{Caption, caption.}\label{fig:01}
\end{figure}

%\begin{figure}[!tpb]%figure2
%%\centerline{\includegraphics{fig02.eps}}
%\caption{Caption, caption.}\label{fig:02}
%\end{figure}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\subsection{Test1}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\section{Discussion}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text.

Table~\ref{Tab:01} shows that Text Text Text Text Text  Text Text
Text Text Text Text. Figure~2\vphantom{\ref{fig:02}} shows that
the above method Text Text. Text Text Text  Text Text Text Text
Text Text. Figure~2\vphantom{\ref{fig:02}} shows that the above
method Text Text. Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     please remove the " % " symbol from \centerline{\includegraphics{fig01.eps}}
%     as it may ignore the figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

(Table~\ref{Tab:01}) Text Text Text Text Text Text  Text Text Text
Text Text Text Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\begin{enumerate}
\item this is item, use enumerate
\item this is item, use enumerate
\item this is item, use enumerate
\end{enumerate}

Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows\vadjust{\pagebreak} that the
above method  Text Text Text Text Text Text Text Text Text Text
Text Text.  \citealp{Boffelli03} might want to know about text
text text text Text Text Text Text Text Text  Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text\break Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text\vspace*{-10pt}

\section*{Acknowledgements}

Text Text Text Text Text Text  Text Text.  \citealp{jinek2012a} might want to know about  text
text text text\vspace*{-12pt}

\section*{Funding}

This work has been supported by the\cite{Liu2019}... Text Text  Text Text.\vspace*{-12pt}

\bibliographystyle{natbib}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{bioinformatics}
%
%\bibliographystyle{plain}
%
\bibliography{bibtex}

\end{document}

### 2020-08-22 Paper/main.tex
8-22 paper

@@
 
-Clustered regularly interspaced short palindromic repeats (CRISPR) / CRIPSR-associated  protein 9 (Cas9) systems is preferred over other biological research and human medicine technologies now, beacuse of it's efficiency,
+Clustered regularly interspaced short palindromic repeats (CRISPR)/CRIPSR-associated  protein 9 (Cas9) systems is preferred over other biological research and human medicine technologies now, beacuse of it's efficiency,
  robustness and programmability.  Cas9 nucleases can be directed by short guide RNAs (sgRNAs) to introduce site-specific DNA double-stranded breaks in target, 
  so to enable editing site-specific within the mammalian genome \citep{jinek2012a,cong2013multiplex,mali2013rnaguided}.
-CRISPR / Cas9, to a large extent, has developed genetic therapies at the cellular level,
+CRISPR/Cas9, to a large extent, has developed genetic therapies at the cellular level,
  while there are still severe medical disadvantage even now which has greatly hindered the further clinical application of the CRISPR/Cas9 systems. 
@@
  been developed and bring a significant volume of experimental data, that is to say researchers have to face the difficulty of analyzing such huge and heterogeneous data.
+
+The activity of chosen sgRNA sequence determines the success of genome editing, however distinctly fluctuant behaviors have been observed for the performance of different sgRNAs, even in the same Cas9 system.
+ Some optimum sgRNAs can hit almost all targers alleles, while anothers don't even show activity \citep{wang2019optimized}.
+ This fact indicates that it's meaningful to explore an efficient approaches to guide sgRNA design. 
+ In practice, there have been a number of application and toolkit applied in this task. In the earlier studies, methods in silico are categorized into three types: 
+ (1) alignment-based, (2) hypothesis-driven and (3) learning-based \citep{chuai2018deepcrispr}. 
+ Recently we noticed that the last type of method seems to be getting more attention because of huger and huger data set \citep{liu2019computational}.
+
+Learning-based method, which designed to predict the activity of sgRNAs, is essentially a computational model built by machine learning algorithm, not only conventional machine learning but also deep learning algorithm.
+ Some studies on HT\_ABE and HT\_CBE have shown that deep learning based models often outperformed conventional machine learning, when the number of sgRNAs in the data set reached a certain level \citep{Song2020,kim2018deep,kim2019spcas9}.
+ Per contra, conventional machine learning algorithms, such as linear regression, logistic regression and the decision tree, are often more interpretable due to the fewer parameters and clearer mathematical assumptions.
+ In short, what was needed for developer is to trade-off accuracy and interpretability. 
+ Muhammad Rafidet al.
+consider deep-learning-based models as black boxs and believe they lack interpretability, motivated by the empirical assertion, they turn to build a model based conventional machine learning to compete with state of the art deep learning models \citep{MuhammadRafid2020}.
+ On the other hand, input perturbation based feature importance analysis become a preferred components to reveal the importance of features in deep learning models.
+Liu et al.
+use a sliding window of length 2 to extract dimeric as input and rank the position of dimeric by contribution to final output \citep{Liu2019}.
+ One regret is that subject to the processing of the input sgRNA sequence, their analysis can not exactly on the nucleotide class.
+Further, SHAP, one of the most prominent of model explain techniques, has been widely used to understand the decision made by the model.
+ Wang et al. develope DeepHF, a deep learning based model, and use Deep SHAP to revealed nucleotide contributions \citep{wang2019optimized}. 
+ Deep SHAP is a compositional approximation of SHAP values since it is challenged to computate SHAP values exactly, especially for a complex deep neural networks \citep{lundberg2017a}. 
+ In our understanding, the method based on input perturbation often requires better generalization ability of the model (even for artificial ridiculous noise data). 
+ Moreover, recent work indicates that model explain techniques, which based post hoc explanations techniques and input perturbations, could be fooled to generate meaningless explanations instead of reflecting the underlying biases \citep{slack2019fooling}, in other word, they could be unreliable and misleading, even on model with excellent performance.
+ In light of the above, we believe it is essential to develope a model which can not only match deep learning based model in performance, but also be comparable to conventional machine learning algorithms in interpretability.
 
@@
 \citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
+
 Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
@@
 Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-
 Text Text Text Text Text Text  Text Text Text Text Text Text Text
@@
 %
-\bibliography{bibtex}
+\bibliography{document}
 

### 2020-08-22 pretrainRNN.py
8_22 pretrain RNN

@@ -1,0 +1,198 @@
+import math
+import pickle
+import numpy as np
+######
+pkl = open('alldata.pkl','rb')
+x_onehot =  pickle.load(pkl)
+x_biofeat = pickle.load(pkl)
+y = pickle.load(pkl)
+x_seq = pickle.load(pkl)
+import os
+os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
+
+from sklearn.metrics import  mean_squared_error, r2_score
+from sklearn.model_selection import train_test_split
+
+random_state=40
+test_size = 0.15
+
+x_train_onehot, x_test_onehot, y_train, y_test = train_test_split(x_onehot, y, test_size=test_size, random_state=random_state)
+x_train_biofeat, x_test_biofeat, y_train, y_test = train_test_split(x_biofeat, y, test_size=test_size, random_state=random_state)
+def get_spearman(model):
+    y_test_pred = model.predict([x_test_onehot,x_test_biofeat])
+    return sp.stats.spearmanr(y_test, y_test_pred)[0]  
+def get_score_at_test(model):
+    y_test_pred = model.predict([x_test_onehot,x_test_biofeat])
+    mse = mean_squared_error(y_test, y_test_pred)
+    spearmanr = sp.stats.spearmanr(y_test, y_test_pred)[0]    
+    r2 = r2_score(y_test, y_test_pred)
+    return 'MES:' + str(mse),'Spearman:' + str(spearmanr) , 'r2:' + str(r2)
+
+
+
+from hyperopt import fmin, tpe, hp, STATUS_OK, Trials
+params = {
+    'train_batch_size':1024,
+    'train_epochs_num':200,
+    'train_base_learning_rate':0.001,
+    'rnn_fc_dropout':0.5868,
+    #'rnn_embedding_dropout':0.4872,
+    #'rnn_dropout':0.5608,
+    'bio_fc_dropout':0.6433,
+    #'rnn_recurrent_dropout':0.4310,
+    
+    'embedding_output':48,
+    'rnn_head_unit_num':94,
+    'rnn_tail_unit_num':400,
+
+    'rnn_fc_hidden_layer_num':2,
+    'rnn_fc_hidden_layer_units_num':300,
+    'bio_fc_hidden_layer_num':1,
+    'bio_fc_hidden_layer_units_num':67
+    }
+params_range = {
+    'embedding_output':[20,500],
+    'rnn_head_unit_num':[20,500],
[…]

### 2020-08-23 Paper/main.tex
8-23 latex

@@
 \documentclass{bioinfo}
+
 \copyrightyear{2015} \pubyear{2015}
@@
  This fact indicates that it's meaningful to explore an efficient approaches to guide sgRNA design.
+
 In practice, there have been a number of application and toolkit applied in this task. In the earlier studies, methods in silico are categorized into three types: 
@@
  In light of the above, we believe it is essential to develope a model which can not only match deep learning based model in performance, but also be comparable to conventional machine learning algorithms in interpretability.
+
+Deep neural network has shown its power in the study of CRISPR/Cas9 and its improved Systems \citep{liu2019computational}. 
+ Most of the deep neural network existing are the combination of recurrent neural network (RNN), convolutional neural network (CNN), fully connected neural network(FNN), and their variants. 
+ We found that the deep learning models used in sgRNA on-target activity (even for off-target effect) prediction tasks in recent years can be divided into the following two categories according to the encoding approach of the sgRNA sequence (sgRNA-DNA sequence pair, for off-target effect prediction):
+
+(1) Methods in spatial domain. 
+ Some previous studies have used model based CNN to predict gRNA on-target activity or off-target effects \citep{lin2018off-target,kim2018deep,chuai2018deepcrispr}. 
+ They process sgRNA base sequence inputs with the help of one-hot encoding idea. 
+ In other words, they regard it as two-dimensional image data, and use convolution layer to extracte potential features in spatial domain, 
+ It is worth noting that Zhang et al. adds bidirectional gated recurrent unit (BGRU, in short), a RNN variant, after pooling layer of classic CNN network \citep{zhang2020c-rnncrispr:}. 
+ Our explanation is that BGRU assists CNN to extract spatial features in one dimension, under this belief it belong to this category.
+
+(2) Methods in temporal domain. 
+ Although RNN-based network have been shown effective to improve the performance of the model with temporal sequential input, especially in natural language processing and sequential recommendation\citep{huang2018improving},
+ RNN be not used for gRNA activity prediction, until recently \citep{wang2019optimized,liu2020deep,Liu2019}. 
+ They consider the nucleotides(can also dimer or polymer) in the sgRNA sequence as word, and the sgRNA sequence itself as a sentence (from 5' to 3'), then a trainable matrix (could be either supervised or unsupervised) is used to project the word to the dense real-valued space.
+ This technology is called embedding, which generates the base embedding. RNN further encoding the base embedding into a sequence of hidden state vector. 
+ Specially, Liu et al. use RNN and CNN in parallel to extract features in base embedding \citep{Liu2019}. 
+ However, base embedding is not spatially interpretable (different from one-hot encode), and they have no way to further explore the correlation between CNN and RNN output.
+Almost all RNN based models used in sgRNA on-target activity or off-target effect flatten the hidden state vector into a one-dimensional vector as the input of the fully connected layer.
+ It is a pity that the temporal sequential dependency of hidden state vector are rarely noticed.
+To summarise, RNN has limited representation power in capturing spatial feature.
+Furthermore, hidden state vector representation is usually hard to understand and explain.
 
@@
 Text Text Text Text Text Text Text Text Text Text Text.
- might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
-Text Text Text Text Text Text Text Text Text Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
 
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
-Text Text Text Text Text Text Text Text Text Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
 
@@
 \citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text
-text. Text Text Text Text Text Text  Text Text Text Text Text Text
-Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
 
@@
 Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
+
 Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
+\citealp{Boffelli03} might want to know about  text text text.
 Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text
-textText Text Text Text Text Text  Text Text Text Text Text Text
-Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
+\citealp{Boffelli03} might want to know about Text Text  Text Text Text Text Text Text.
 
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
 
@@
 \citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
 
@@
 \citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text.
+Text Text Text Text Text Text  Text Text Text Text Text Text Text.
 
@@
 Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
 Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text

### 2020-08-24 Paper/main.tex
8-24 paper

@@
 \documentclass{bioinfo}
-
 \copyrightyear{2015} \pubyear{2015}
@@
 
-\abstract{\textbf{Motivation:}  Text
+\abstract{\textbf{Motivation:} Text Text Text Text Text Text Text Text Text Text Text Text Text
+Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
+Text Text Text Text Text Text
 Text Text Text Text Text.\\
@@
 Text Text Text Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text\\
-\textbf{Availability:} Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text
-Text Text Text Text Text Text Text Text Text Text Text Text Text Text  Text\\
-\textbf{Contact:} \href{name@bio.com}{name@bio.com}\\
+\textbf{Availability:} The example code are available at \href{https://github.com/South-Walker/AttCRISPR}{https://github.com/South-Walker/AttCRISPR}\\
+\textbf{Contact:} \href{xlm@xiaoliming96.com}{xlm@xiaoliming96.com}\\
 \textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}
@@
 
-Clustered regularly interspaced short palindromic repeats (CRISPR)/CRIPSR-associated  protein 9 (Cas9) systems is preferred over other biological research and human medicine technologies now, beacuse of it's efficiency,
+Clustered regularly interspaced short palindromic repeats (CRISPR)/CRIPSR associated protein 9 (Cas9) systems is preferred over other biological research and human medicine technologies now, beacuse of it's efficiency,
  robustness and programmability.  Cas9 nucleases can be directed by short guide RNAs (sgRNAs) to introduce site-specific DNA double-stranded breaks in target, 
@@
  In short, what was needed for developer is to trade-off accuracy and interpretability. 
- Muhammad Rafidet al.
-consider deep-learning-based models as black boxs and believe they lack interpretability, motivated by the empirical assertion, they turn to build a model based conventional machine learning to compete with state of the art deep learning models \citep{MuhammadRafid2020}.
+ \citeauthor{MuhammadRafid2020} consider deep-learning-based models as black boxs and believe they lack interpretability, 
+ motivated by the empirical assertion, they turn to build a model based conventional machine learning to compete with state of the art deep learning models \citep{MuhammadRafid2020}. 
  On the other hand, input perturbation based feature importance analysis become a preferred components to reveal the importance of features in deep learning models. 
-Liu et al.
-use a sliding window of length 2 to extract dimeric as input and rank the position of dimeric by contribution to final output \citep{Liu2019}.
+ \citeauthor{Liu2019} use a sliding window of length 2 to extract dimeric as input and rank the position of dimeric by contribution to final output \citep{Liu2019}. 
  One regret is that subject to the processing of the input sgRNA sequence, their analysis can not exactly on the nucleotide class.
 Further, SHAP, one of the most prominent of model explain techniques, has been widely used to understand the decision made by the model.
- Wang et al. develope DeepHF, a deep learning based model, and use Deep SHAP to revealed nucleotide contributions \citep{wang2019optimized}. 
+ \citeauthor{wang2019optimized} develope DeepHF, a deep learning based model, and use Deep SHAP to revealed nucleotide contributions \citep{wang2019optimized}. 
  Deep SHAP is a compositional approximation of SHAP values since it is challenged to computate SHAP values exactly, especially for a complex deep neural networks \citep{lundberg2017a}. 
@@
 Deep neural network has shown its power in the study of CRISPR/Cas9 and its improved Systems \citep{liu2019computational}. 
- Most of the deep neural network existing are the combination of recurrent neural network (RNN), convolutional neural network (CNN), fully connected neural network(FNN), and their variants. 
+ Most of the deep neural network existing are the combination of recurrent neural network (RNN), convolutional neural network (CNN), fully connected neural network (FNN), and their variants. 
  We found that the deep learning models used in sgRNA on-target activity (even for off-target effect) prediction tasks in recent years can be divided into the following two categories according to the encoding approach of the sgRNA sequence (sgRNA-DNA sequence pair, for off-target effect prediction):
 
-(1) Methods in spatial domain. 
+\begin{enumerate}
+    \item Methods in spatial domain. 
     Some previous studies have used model based CNN to predict gRNA on-target activity or off-target effects \citep{lin2018off-target,kim2018deep,chuai2018deepcrispr}. 
@@
     In other words, they regard it as two-dimensional image data, and use convolution layer to extracte potential features in spatial domain, 
- It is worth noting that Zhang et al. adds bidirectional gated recurrent unit (BGRU, in short), a RNN variant, after pooling layer of classic CNN network \citep{zhang2020c-rnncrispr:}. 
+    It is worth noting that \citeauthor{zhang2020c-rnncrispr:} adds bidirectional gated recurrent unit (BGRU, in short), a RNN variant, after pooling layer of classic CNN network \citep{zhang2020c-rnncrispr:}.
     Our explanation is that BGRU assists CNN to extract spatial features in one dimension, under this belief it belong to this category. 
-
-(2) Methods in temporal domain. 
+    \item Methods in temporal domain. 
     Although RNN-based network have been shown effective to improve the performance of the model with temporal sequential input, especially in natural language processing and sequential recommendation\citep{huang2018improving},
@@
     This technology is called embedding, which generates the base embedding. RNN further encoding the base embedding into a sequence of hidden state vector. 
- Specially, Liu et al. use RNN and CNN in parallel to extract features in base embedding \citep{Liu2019}. 
+    Specially, \citeauthor{Liu2019} use RNN and CNN in parallel to extract features in base embedding \citep{Liu2019}. 
     However, base embedding is not spatially interpretable (different from one-hot encode), and they have no way to further explore the correlation between CNN and RNN output.
@@
     It is a pity that the temporal sequential dependency of hidden state vector are rarely noticed. 
-To summarise, RNN has limited representation power in capturing spatial feature.
-Furthermore, hidden state vector representation is usually hard to understand and explain.
+    To summarise, RNN has limited representation power in capturing spatial feature. Furthermore, hidden state vector representation is usually hard to understand and explain.
+\end{enumerate}
+
+Attention mechanism has demonstrated its power in Natural Language Processing, Statistical Learning, Speech and Computer Vision \citep{chaudhari2019an}. 
+ It makes model tends to focus selectively on parts of the input which is help in performing the task effectively. 
+ Previous observation have shown that Cas9 preferentially binds sgRNAs containing purines but not pyrimidines \citep{wang2014genetic} and multiple thymine in the spacer impairing sgRNA activity \citep{wu2014genome-wide},
+ that is to say some specific nucleotide and base position need more attention compared to others. 
+ The above is the premise of introducing attention mechanism. Strictly speaking, we are not the first to bring attention mechanisms into this field. 
+ The most similar approach to ours is the work based on transformer by \citeauthor{Liu2019}. 
+ They use transformer, a components based on attention mechanism, instead of RNN to improve the ability of temporal feature extraction, hence, enhance the performance of their model \citep{Liu2019,vaswani2017attention}.
+ In our work,the interpretability benefit from attention mechanism is more focused.
+
+In this paper, our main contributions are as follows:\vspace*{1pt}
+
+\begin{itemize}
+    \item Present a novel deep-learning-based model, which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
+    It doesn't belong to any of the above categories of existing approaches.
+    \item Introduce attention mechanism into our model. 
+    As a result, It does not need post hoc explanations techniques based on input perturbation to explain itself. 
+    It is intrinsic interpretable at the nucleotide level in the temporal and spatial domains. 
+    The model we built could be approximated with a linear regression model, thus, it is transformed from a black box to an intrinsically interpretable model with the performance of deep learning based model.
+    This seems to has something in common with the idea of two-layer additive models, built by \citeauthor{DBLP:phd/basesearch/Chen20d}. 
+    He uses linear modeling with positive coefficients for feature, but inserts (interpretable) nonlinearities in several places to make the model more flexible and accurate \citep{DBLP:phd/basesearch/Chen20d}.
+    \item Throught abation analysis and testing a series of possible network structure, 
+    we find there are multiple components and strategy can improve the performance of our model and constructed AttCRISPR, 
+    which could outperform the current state-of-the-art tool on deepHF dataset.\vspace*{1pt}
+\end{itemize}
 
@@
 \citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text
 text\vspace*{1pt}
@@
 \citealp{Boffelli03} might want to know about  text text text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text\break
-text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about Text Text  Text Text Text Text Text Text.
 
@@
 Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
 
@@
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
 Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
@@
 
-Text Text Text Text Text Text  Text Text.  \citealp{jinek2012a} might want to know about  text
+Text Text Textext
 text text text\vspace*{-12pt}
@@
 
-This work has been supported by the\cite{Liu2019}... Text Text  Text Text.\vspace*{-12pt}
+This work has beenText  Text Text.\vspace*{-12pt}
 

### 2020-09-07 AttCRISPR.py
9-7

@@ -1,297 +1,0 @@
-import math
-import pickle
-import numpy as np
-######
-pkl = open('alldata.pkl','rb')
-x_onehot =  pickle.load(pkl)
-x_biofeat = pickle.load(pkl)
-y = pickle.load(pkl)
-x_seq = pickle.load(pkl)
-
-
-from sklearn.metrics import  mean_squared_error, r2_score
-from sklearn.model_selection import train_test_split
-import os
-os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
-random_state=40
-test_size = 0.15
-validate_size = 0.1
-x_train_validate_onehot, x_test_onehot, y_train_validate, y_test = train_test_split(x_onehot, y, test_size=test_size, random_state=random_state)
-x_train_validate_biofeat, x_test_biofeat, y_train_validate, y_test = train_test_split(x_biofeat, y, test_size=test_size, random_state=random_state)
-x_train_onehot, x_validate_onehot,y_train, y_validate = train_test_split(x_train_validate_onehot, y_train_validate, test_size=validate_size, random_state=random_state)
-x_train_biofeat, x_validate_biofeat,y_train, y_validate = train_test_split(x_train_validate_biofeat, y_train_validate, test_size=validate_size, random_state=random_state)
-def get_spearman(model):
-    y_test_pred = model.predict([x_test_onehot,x_test_biofeat])
-    return sp.stats.spearmanr(y_test, y_test_pred)[0]  
-def get_score_at_test(model):
-    y_test_pred = model.predict([x_test_onehot,x_test_biofeat])
-    mse = mean_squared_error(y_test, y_test_pred)
-    spearmanr = sp.stats.spearmanr(y_test, y_test_pred)[0]    
-    r2 = r2_score(y_test, y_test_pred)
-    return 'MES:' + str(mse),'Spearman:' + str(spearmanr) , 'r2:' + str(r2)
-
-
-
-
-from random import randint
-import copy
-l_x_train_onehot = x_train_onehot.tolist()
-l_x_train_biofeat = x_train_biofeat.tolist()
-l_y_train = y_train.tolist()
-
-x=0
-for i in range(len(l_x_train_onehot)):
-    if randint(0,100) < 32:
-        j = randint(4,16)
-        for k in range(4):
-            if l_x_train_onehot[i][j][k][0] == 1:
-                x = k
-        offset = randint(1,4)
-        noise_x = (x+offset)%4
[…]

### 2020-09-07 Ensemble.py

@@ -1,161 +1,27 @@
-import math
-import pickle
-import numpy as np
-######
-pkl = open('alldata.pkl','rb')
-x_onehot =  pickle.load(pkl)
-x_biofeat = pickle.load(pkl)
-y = pickle.load(pkl)
-x_seq = pickle.load(pkl)
-
-best = -1
-from sklearn.metrics import  mean_squared_error, r2_score
-from sklearn.model_selection import train_test_split
-import os
-os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
-random_state=40
-test_size = 0.15
-validate_size = 0.1
-x_train_validate_onehot, x_test_onehot, y_train_validate, y_test = train_test_split(x_onehot, y, test_size=test_size, random_state=random_state)
-x_train_validate_biofeat, x_test_biofeat, y_train_validate, y_test = train_test_split(x_biofeat, y, test_size=test_size, random_state=random_state)
-x_train_onehot, x_validate_onehot,y_train, y_validate = train_test_split(x_train_validate_onehot, y_train_validate, test_size=validate_size, random_state=random_state)
-x_train_biofeat, x_validate_biofeat,y_train, y_validate = train_test_split(x_train_validate_biofeat, y_train_validate, test_size=validate_size, random_state=random_state)
-def get_spearman(model):
-    y_test_pred = model.predict([x_test_onehot,x_test_biofeat])
-    return sp.stats.spearmanr(y_test, y_test_pred)[0]  
-def get_score_at_test(model):
-    y_test_pred = model.predict([x_test_onehot,x_test_biofeat])
-    mse = mean_squared_error(y_test, y_test_pred)
-    spearmanr = sp.stats.spearmanr(y_test, y_test_pred)[0]    
-    r2 = r2_score(y_test, y_test_pred)
-    global best
-    if best<spearmanr:
-        best = spearmanr
-        model.save('./bestEnsemble.h5')
-        print('save')
-    return 'MES:' + str(mse),'Spearman:' + str(spearmanr) , 'r2:' + str(r2), 'best:' + str(best)
-
-
-
-
-from random import randint
-import copy
-l_x_train_onehot = x_train_onehot.tolist()
-l_x_train_biofeat = x_train_biofeat.tolist()
-l_y_train = y_train.tolist()
-
-x=0
-for i in range(len(l_x_train_onehot)):
-    if randint(0,100) < 32:
-        j = randint(4,16)
-        for k in range(4):
-            if l_x_train_onehot[i][j][k][0] == 1:
-                x = k
[…]

### 2020-09-07 GetModelAttention.py

@@ -1,222 +1,0 @@
-from keras.models import load_model
-import math
-import pickle
-import numpy as np
-from keras.models import *
-import scipy as sp
-from sklearn.model_selection import train_test_split
-import os
-os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
-
-pkl = open('alldata.pkl','rb') 
-x_onehot =  pickle.load(pkl)
-x_biofeat = pickle.load(pkl)
-y = pickle.load(pkl)
-x_seq = pickle.load(pkl)
-
-random_state=40
-test_size = 0.15
-x_train_onehot, x_test_onehot, y_train, y_test = train_test_split(x_onehot, y, test_size=test_size, random_state=random_state)
-x_train_biofeat, x_test_biofeat, y_train, y_test = train_test_split(x_biofeat, y, test_size=test_size, random_state=random_state)
-x_train_seq, x_test_seq, y_train, y_test = train_test_split(x_seq, y, test_size=test_size, random_state=random_state)
-
-
-def getscore(model,y):
-    y_pre = model.predict([x_test_onehot,x_test_biofeat,x_test_seq]).reshape(-1)
-
-    return float(sp.stats.spearmanr(y, y_pre)[0])
-
-from keras.callbacks import Callback
-from keras.callbacks import LambdaCallback
-x_attention_onehot = x_train_onehot
-x_attention_biofeat = x_train_biofeat
-x_attention_seq = x_train_seq
-y_attention = y_train
-def get_temporal_attention(model,usebiofeat=True):
-    temporal_layer_model = Model(
-        inputs=load_model.input, outputs=model.get_layer('rnn_embedding').output)
-    if usebiofeat:
-        input = [x_attention_onehot,x_attention_biofeat,x_attention_seq]
-    else:
-        input = [x_attention_onehot,x_attention_seq]
-    temporal_value = temporal_layer_model.predict(input)
-    weights = [0 for x in range(0,21)]
-    for w in range(len(temporal_value)):
-        for i in range(21):
-            weights[i] += temporal_value[w][i]*y_attention[w]
-    total = 0
-    for i in range(21):
-        total += weights[i]
-    for i in range(21):
-        weights[i] = weights[i] / total
-    return weights;
[…]

### 2020-09-07 HyperParametersSearch.py

@@ -1,18 +1,0 @@
-from hyperopt import fmin, tpe, hp, STATUS_OK, Trials
-import AttCRISPR
-from AttCRISPR import train_with
-space = {
-    'cnn_fc_hidden_layer_num':hp.choice('cnn_fc_hidden_layer_num', [2,3,4]),
-    'cnn_filters_num':hp.choice('cnn_filters_num', [20,25]),
-    'cnn_fc_hidden_layer_units_num':hp.uniform('cnn_fc_hidden_layer_units_num',0,1),
-    'rnn_embedding_output':hp.uniform('rnn_embedding_output',0,1),
-    'rnn_unit_num':hp.uniform('rnn_unit_num',0,1),
-    'rnn_fc_hidden_layer_num':hp.choice('rnn_fc_hidden_layer_num', [1,2,3]),
-    'rnn_fc_hidden_layer_units_num':hp.uniform('rnn_fc_hidden_layer_units_num',0,1),
-    'bio_fc_hidden_layer_num':hp.choice('bio_fc_hidden_layer_num', [0,1]),
-    'bio_fc_hidden_layer_units_num':hp.uniform('bio_fc_hidden_layer_units_num',0,1),
-    }
-trials = Trials()
-best = fmin(train_with, space, algo=tpe.suggest, max_evals=150, trials=trials)
-print('best: ')
-print(best)

### 2020-09-07 LearnUtil.py

@@ -1,0 +1,42 @@
+best = -1
+from sklearn.metrics import  mean_squared_error, r2_score
+import scipy as sp
+def get_score_at_test(model,input,label,issave=True,savepath=None):
+    pred_label = model.predict(input)
+    mse = mean_squared_error(label, pred_label)
+    spearmanr = sp.stats.spearmanr(label, pred_label)[0]    
+    r2 = r2_score(label, pred_label)
+    global best
+    if best<spearmanr:
+        best = spearmanr
+        if issave:
+            model.save(savepath)
+        print('best')
+    return 'MES:' + str(mse),'Spearman:' + str(spearmanr) , 'r2:' + str(r2), 'best:' + str(best)
+
+
+import keras
+from keras.layers import Input, Dense, BatchNormalization
+from keras.layers.core import *
+def mlp(inputs,output_layer_activation,output_dim,output_use_bias,
+        hidden_layer_num,hidden_layer_units_num,hidden_layer_activation,dropout,
+        name=None,output_regularizer=None):
+    if output_layer_activation == 'sigmoid' or output_layer_activation == 'tanh':
+        hidden_layer_num-=1
+    x = inputs
+    for l in range(hidden_layer_num):
+        x = Dense(hidden_layer_units_num, activation=hidden_layer_activation)(inputs)
+        x = Dropout(dropout)(x)
+    if output_layer_activation == 'sigmoid' or output_layer_activation == 'tanh':
+        x = Dense(hidden_layer_units_num)(x)
+        
+        x = keras.layers.concatenate([x,inputs])
+        x = Activation(hidden_layer_activation)(x)
+        x = Dense(output_dim,use_bias=output_use_bias,
+                  kernel_regularizer='l2',activity_regularizer=output_regularizer)(x)
+        x = Activation(output_layer_activation,name=name)(x)
+        return x
+    x = Dense(output_dim,activation=output_layer_activation,
+              kernel_regularizer='l2',activity_regularizer=output_regularizer,
+              use_bias=output_use_bias,name=name)(x)
+    return x

### 2020-09-07 ParamsUtil.py

@@ -1,0 +1,37 @@
+import math
+import numpy as np
+import pandas as pd
+
+from WTConst import Params as params
+
+from sklearn.model_selection import train_test_split
+def SplitData(onehot,biofeat,label):    
+    random_state=40
+    test_size = 0.15
+    validate_size = 0.1
+    x_train_validate_onehot, x_test_onehot, y_train_validate, y_test = train_test_split(onehot, label, test_size=test_size, random_state=random_state)
+    x_train_validate_biofeat, x_test_biofeat, _, _ = train_test_split(biofeat, label, test_size=test_size, random_state=random_state)
+    
+    x_train_onehot, x_validate_onehot, y_train, y_validate = train_test_split(x_train_validate_onehot, y_train_validate, test_size=validate_size, random_state=random_state)
+    x_train_biofeat, x_validate_biofeat, _, _ = train_test_split(x_train_validate_biofeat, y_train_validate, test_size=validate_size, random_state=random_state)
+    data = {'input':
+            {'train':{'onehot':x_train_onehot,'biofeat':x_train_biofeat},
+             'validate':{'onehot':x_validate_onehot,'biofeat':x_validate_biofeat},
+             'test':{'onehot':x_test_onehot,'biofeat':x_test_biofeat}
+             },
+            'label':
+            {'train':y_train,
+             'validate':y_validate,
+             'test':y_test
+             }
+            }
+    return data
+
+import pickle
+def Read_Data():
+    pkl = open(params['data_file'],'rb')
+    x_onehot = pickle.load(pkl)
+    x_biofeat = pickle.load(pkl)
+    label = pickle.load(pkl)
+    x_seq = pickle.load(pkl)
+    return SplitData(x_onehot,x_biofeat,label)

### 2020-09-07 TestH5.py

@@ -1,0 +1,18 @@
+from sklearn.metrics import  mean_squared_error, r2_score
+import scipy as sp
+def get_score_at_test(model,input,label,issave=True,savepath=None):
+    pred_label = model.predict(input)
+    mse = mean_squared_error(label, pred_label)
+    spearmanr = sp.stats.spearmanr(label, pred_label)[0]    
+    r2 = r2_score(label, pred_label)
+    return 'MES:' + str(mse),'Spearman:' + str(spearmanr) , 'r2:' + str(r2)
+
+from ParamsUtil import *
+data = Read_Data()
+from keras.models import load_model
+model = load_model('WTBestCNN.h5')
+print(get_score_at_test(model,
+                        data['input']['test']['onehot'],data['label']['test']))
+model = load_model('WTBestRNN.h5')
+print(get_score_at_test(model,
+                        data['input']['test']['onehot'],data['label']['test']))

### 2020-09-07 WTConst.py

@@ -1,0 +1,39 @@
+CNNParams = {
+    'train_batch_size':16,
+    'train_epochs_num':75,
+    'train_base_learning_rate':0.00002,
+    'cnn_save_file':'WTBestCNN.h5',
+    'cnn_fc_hidden_layer_num':2,
+    'cnn_fc_hidden_layer_units_num':421,
+    'cnn_fc_dropout':0.5,
+    'cnn_filters_num':50,
+    'cnn_conv_num':3,
+    'cnn_last_layer_units_num':60
+    }
+RNNParams = {
+    'train_batch_size':128,
+    'train_epochs_num':75,
+    'train_base_learning_rate':0.001,
+    'rnn_save_file':'WTBestRNN.h5',
+    'rnn_embedding_output':97,
+    'rnn_unit_num':99,
+    'rnn_fc_hidden_layer_num':1,
+    'rnn_fc_hidden_layer_units_num':166
+    }
+EnsembleParams = {
+    'cnn_load_file':'WTBestCNN.h5',
+    'rnn_load_file':'WTBestRNN.h5',
+    'ensemble_save_file':'WTEnsemble.h5',
+    'train_batch_size':128,
+    'train_epochs_num':75,
+    'train_base_learning_rate':0.00016,
+    'bio_fc_hidden_layer_num':1,
+    'bio_fc_hidden_layer_units_num':87,
+    'bio_fc_dropout':0.05
+    }
+Params = {
+    'data_file':'alldata.pkl',
+    'CNNParams':CNNParams,
+    'RNNParams':RNNParams,
+    'EnsembleParams':EnsembleParams
+    }

### 2020-09-07 pretrainCNN.py

@@ -1,204 +1,63 @@
-import math
-import pickle
-import numpy as np
-######
-pkl = open('alldata.pkl','rb')
-x_onehot =  pickle.load(pkl)
-x_biofeat = pickle.load(pkl)
-y = pickle.load(pkl)
-x_seq = pickle.load(pkl)
-
-best = -1
-from sklearn.metrics import  mean_squared_error, r2_score
-from sklearn.model_selection import train_test_split
-import os
-#os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
-random_state=40
-test_size = 0.15
-validate_size = 0.1
-x_train_validate_onehot, x_test_onehot, y_train_validate, y_test = train_test_split(x_onehot, y, test_size=test_size, random_state=random_state)
-x_train_validate_biofeat, x_test_biofeat, y_train_validate, y_test = train_test_split(x_biofeat, y, test_size=test_size, random_state=random_state)
-x_train_onehot, x_validate_onehot,y_train, y_validate = train_test_split(x_train_validate_onehot, y_train_validate, test_size=validate_size, random_state=random_state)
-x_train_biofeat, x_validate_biofeat,y_train, y_validate = train_test_split(x_train_validate_biofeat, y_train_validate, test_size=validate_size, random_state=random_state)
-def get_spearman(model):
-    y_test_pred = model.predict([x_test_onehot,x_test_biofeat])
-    return sp.stats.spearmanr(y_test, y_test_pred)[0]  
-def get_score_at_test(model):
-    y_test_pred = model.predict([x_test_onehot,x_test_biofeat])
-    mse = mean_squared_error(y_test, y_test_pred)
-    spearmanr = sp.stats.spearmanr(y_test, y_test_pred)[0]    
-    r2 = r2_score(y_test, y_test_pred)
-    global best
-    if best<spearmanr:
-        best = spearmanr
-        model.save('./bestCNN.h5')
-        print('save')
-    return 'MES:' + str(mse),'Spearman:' + str(spearmanr) , 'r2:' + str(r2), 'best:' + str(best)
-
-
-
-
-from random import randint
-import copy
-l_x_train_onehot = x_train_onehot.tolist()
-l_x_train_biofeat = x_train_biofeat.tolist()
-l_y_train = y_train.tolist()
-
-x=0
-for i in range(len(l_x_train_onehot)):
-    if randint(0,100) < 32:
-        j = randint(4,16)
-        for k in range(4):
-            if l_x_train_onehot[i][j][k][0] == 1:
[…]

### 2020-09-08 ESPConst.py
9-8

@@ -2,7 +2,7 @@ CNNParams = {
     'train_batch_size':16,
     'train_epochs_num':75,
     'train_base_learning_rate':0.00002,
-    'cnn_save_file':'WTBestCNN.h5',
+    'cnn_save_file':'ESPBestCNN.h5',
     'cnn_fc_hidden_layer_num':2,
     'cnn_fc_hidden_layer_units_num':421,
     'cnn_fc_dropout':0.5,
@@ -14,16 +14,16 @@ RNNParams = {
     'train_batch_size':128,
     'train_epochs_num':75,
     'train_base_learning_rate':0.001,
-    'rnn_save_file':'WTBestRNN.h5',
+    'rnn_save_file':'ESPBestRNN.h5',
     'rnn_embedding_output':97,
     'rnn_unit_num':99,
     'rnn_fc_hidden_layer_num':1,
     'rnn_fc_hidden_layer_units_num':166
     }
 EnsembleParams = {
-    'cnn_load_file':'WTBestCNN.h5',
-    'rnn_load_file':'WTBestRNN.h5',
-    'ensemble_save_file':'WTEnsemble.h5',
+    'cnn_load_file':'ESPBestCNN.h5',
+    'rnn_load_file':'ESPBestRNN.h5',
+    'ensemble_save_file':'ESPEnsemble.h5',
     'train_batch_size':16,
     'train_epochs_num':75,
     'train_base_learning_rate':0.00002,
@@ -32,19 +32,19 @@ EnsembleParams = {
     'bio_fc_dropout':0.05
     }
 FineTuning = {
-    'cnn_load_file':'WTBestCNN.h5',
-    'rnn_load_file':'WTBestRNN.h5',
-    'ensemble_load_file':'WTEnsemble.h5',
-    'ensemble_save_file':'WTFineTuning.h5',
-    'train_batch_size':16,
+    'cnn_load_file':'ESPBestCNN.h5',
+    'rnn_load_file':'ESPBestRNN.h5',
+    'ensemble_load_file':'ESPEnsemble.h5',
+    'ensemble_save_file':'ESPFineTuning.h5',
+    'train_batch_size':64,
     'train_epochs_num':300,
-    'train_base_learning_rate':0.00002,
+    'train_base_learning_rate':0.001,
     'bio_fc_hidden_layer_num':1,
     'bio_fc_hidden_layer_units_num':87,
     'bio_fc_dropout':0.05
     }
 Params = {
[…]

### 2020-09-08 Ensemble.py

@@ -1,6 +1,6 @@
 import keras
 from keras.preprocessing import text,sequence
-from keras.layers import Input
+from keras.layers import Input, BatchNormalization, Softmax
 from keras.layers.core import *
 from keras.models import *
 from keras.callbacks import Callback,LambdaCallback
@@ -9,13 +9,13 @@ import keras.backend as K
 from hyperopt import fmin, tpe, hp, STATUS_OK, Trials
 from LearnUtil import *
 
-def model(params):
+def model(params,cnn_trainable=False,rnn_trainable=False,load_weight=False):
     onehot_input = Input(name='onehot_input', shape = (21,4, 1,))
     biological_input = Input(name='bio_input', shape = (11,))
     cnnmodel = load_model(params['cnn_load_file'])
     rnnmodel = load_model(params['rnn_load_file'])
-    cnnmodel.trainable = False
-    rnnmodel.trainable = False
+    cnnmodel.trainable = cnn_trainable
+    rnnmodel.trainable = rnn_trainable
     x_cnn = cnnmodel(onehot_input)
     x_rnn = rnnmodel(onehot_input)
     x = keras.layers.concatenate([x_rnn,x_cnn])
@@ -26,21 +26,22 @@ def model(params):
                 hidden_layer_activation='relu',dropout=params['bio_fc_dropout'],
                 name='biofeat_embedding')
     output = keras.layers.concatenate([x,x_bio])
-    output = mlp(output,
-                output_layer_activation='linear',output_dim=1,output_use_bias=True,
-                hidden_layer_num=0,hidden_layer_units_num=0,
-                hidden_layer_activation='relu',dropout=0,output_regularizer='l2')
+    output = Dense(units=1,kernel_initializer=keras.initializers.RandomNormal(mean=0.3, stddev=0.05),bias_initializer='zero')(output)
     model = Model(inputs=[onehot_input, biological_input],
                  outputs=[output])
+    if load_weight:
+        model.load_weights(params['ensemble_load_file']) 
     return model
 
 def train(params,
           train_input,train_biofeat,train_label,
           validate_input,validate_biofeat,validate_label,
-          test_input,test_biofeat,test_label):
+          test_input,test_biofeat,test_label,
+          cnn_trainable=False,rnn_trainable=False,load_weight=False):
     global best
     best = -1
-    m = model(params)
+    m = model(params,
+              cnn_trainable=cnn_trainable,rnn_trainable=rnn_trainable,load_weight=load_weight)
[…]

### 2020-09-08 GetModelAttention.py

@@ -1,0 +1,180 @@
+from keras.models import load_model
+import math
+import pickle
+import numpy as np
+from keras.models import *
+import scipy as sp
+from sklearn.model_selection import train_test_split
+import os
+os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
+
+pkl = open('alldata.pkl','rb') 
+x_onehot =  pickle.load(pkl)
+x_biofeat = pickle.load(pkl)
+y = pickle.load(pkl)
+x_seq = pickle.load(pkl)
+
+random_state=40
+test_size = 0.15
+x_train_onehot, x_test_onehot, y_train, y_test = train_test_split(x_onehot, y, test_size=test_size, random_state=random_state)
+x_train_biofeat, x_test_biofeat, y_train, y_test = train_test_split(x_biofeat, y, test_size=test_size, random_state=random_state)
+x_train_seq, x_test_seq, y_train, y_test = train_test_split(x_seq, y, test_size=test_size, random_state=random_state)
+
+from keras.callbacks import Callback
+from keras.callbacks import LambdaCallback
+x_attention_onehot = x_train_onehot
+x_attention_biofeat = x_train_biofeat
+x_attention_seq = x_train_seq
+y_attention = y_train
+def get_temporal_attention(model,usebiofeat=True):
+    return 1
+def get_spatial_attention(model,usebiofeat=True):
+    spatial_layer_model = Model(
+        inputs=model.inputs[0], outputs=model.get_layer('spatial_attention_result').output)
+    spatial_value = spatial_layer_model.predict(x_attention_onehot)
+    spatial_value = spatial_value.reshape((spatial_value.shape[0],21,4))
+    spatial_value = spatial_value * y_attention.reshape((spatial_value.shape[0],1,1))
+    spatial_value = np.mean(spatial_value, axis=0)
+    spatial_sum = np.sum(spatial_value, axis=1)
+    for i in range(len(spatial_value)):
+        t = spatial_sum[i]/4
+        if i == 0:
+            t*=2
+        for j in range(len(spatial_value[0])):
+            spatial_value[i][j] -= t
+    spatial_value[0][1]=0
+    spatial_value[0][3]=0
+    return spatial_value.T
+
[…]

### 2020-09-08 Pipeline.py

@@ -4,9 +4,9 @@ from ParamsUtil import *
 
 best = -1
 import os
-#os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
+os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
 
-def AddNoise(onehot,biofeat,label,rate=32,intensity=0.25):
+def AddNoise(onehot,biofeat,label,rate=50,intensity=0.30):
     from random import randint
     import copy
     t_onehot = onehot.tolist()
@@ -21,10 +21,10 @@ def AddNoise(onehot,biofeat,label,rate=32,intensity=0.25):
             if onehot[i][j][k][0] == 1:
                x = k
         offset = randint(1,4)
-        noise_x = (x+offset)%4
+        noise = intensity/3
         newx = copy.deepcopy(onehot[i])
-        newx[j][x][0] = 1-intensity
-        newx[j][noise_x][0] = intensity
+        for k in range(4):
+            newx[j][k][0] = (1-intensity) if x==k else noise
         t_onehot.append(newx)
         t_biofeat.append(copy.deepcopy(t_biofeat[i]))
         t_label.append(copy.deepcopy(t_label[i]))
@@ -52,23 +52,35 @@ def Pipeline(pretrainCNN=False,pretrainRNN=False,ensemble=False):
     data = Read_Data()
     input = data['input']
     label = data['label']
-    
+    global best
+    best = -1
     if pretrainCNN:
+        input_train_onehot = input['train']['onehot']
+        y_train = label['train']
         input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
-                                                                  label['train'],rate=32,intensity=0.25)
+                                                                  label['train'],rate=50,intensity=0.3)
         CNN(params['CNNParams'],input_train_onehot,y_train,
              input['validate']['onehot'],label['validate'],
              input['test']['onehot'],label['test'])
+    best = -1
     if pretrainRNN:
         input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
-                                                                  label['train'],rate=32,intensity=0.1)
+                                                                  label['train'],rate=50,intensity=0.3)
         RNN(params['RNNParams'],input_train_onehot,y_train,
              input['validate']['onehot'],label['validate'],
              input['test']['onehot'],label['test'])
+    best = -1
     if ensemble:
[…]

### 2020-09-08 pretrainCNN.py

@@ -16,8 +16,8 @@ def model(params):
     maxpooling_spatial = Lambda(lambda inp: K.max(inp,axis=3,keepdims=True))(conv_0)
     attention_spatial = keras.layers.concatenate([maxpooling_spatial,avgpooling_spatial],axis=3)
     attention_spatial = BatchNormalization()(attention_spatial)
-    attention_spatial = Conv2D(1, (3, 2), padding='same', activation='sigmoid')(attention_spatial)
-    conv_output = Lambda(lambda inp: inp[0]*inp[1])( [onehot_input,attention_spatial])
+    attention_spatial = Conv2D(1, (3, 2), padding='same', activation='sigmoid',name='spatial_attention')(attention_spatial)
+    conv_output = Lambda(lambda inp: inp[0]*inp[1],name='spatial_attention_result')( [onehot_input,attention_spatial])
 
     convs = []
     for i in range(params['cnn_conv_num']):
@@ -32,10 +32,7 @@ def model(params):
                           hidden_layer_num=params['cnn_fc_hidden_layer_num'],hidden_layer_units_num=params['cnn_fc_hidden_layer_units_num'],
                           hidden_layer_activation='relu',dropout=params['cnn_fc_dropout'],
                           name='cnn_embedding')
-    output = mlp(onehot_embedded,
-            output_layer_activation='linear',output_dim=1,output_use_bias=False,
-            hidden_layer_num=0,hidden_layer_units_num=0,
-            hidden_layer_activation='relu',dropout=0)
+    output = Dense(units=1,kernel_regularizer='l2',name='spatial_score')(onehot_embedded)
     model = Model(inputs=[onehot_input],
                  outputs=[output],name='cnn')
     return model

### 2020-09-08 pretrainRNN.py

@@ -50,7 +50,7 @@ def model(params):
                 Softmax(axis=-1)(dot([encoderat[j],decoderat[i]],axes=-1))
                 )
         aat.append(
-            Reshape((21,1,))(keras.layers.concatenate(atat))
+            Reshape((21,1,),name='temporal_attention_'+str(i))(keras.layers.concatenate(atat))
             )
         
     ctat = []
@@ -75,14 +75,11 @@ def model(params):
                                      hidden_layer_num=params['rnn_fc_hidden_layer_num'],hidden_layer_units_num=params['rnn_fc_hidden_layer_units_num'],
                                      hidden_layer_activation='relu',dropout=0,
                                      name='rnn_output_at_'+str(i))
-    rnn_embedded = keras.layers.concatenate(time_rnn_embeddedat,name='rnn_embedding')
+    rnn_embedded = keras.layers.concatenate(time_rnn_embeddedat,name='temporal_pos_score')
     rnn_embedded = Dropout(rate=0.05)(rnn_embedded)
-    x_rnn = mlp(rnn_embedded,
-            output_layer_activation='linear',output_dim=1,output_use_bias=False,
-            hidden_layer_num=0,hidden_layer_units_num=0,
-            hidden_layer_activation='relu',dropout=0)
+    output = Dense(units=1,kernel_regularizer='l2',name='temporal_score')(rnn_embedded)
     model = Model(inputs=[onehot_input],
-                 outputs=[x_rnn])
+                 outputs=[output],name='rnn')
     return model
 
 def train(params,train_input,train_label,validate_input,validate_label,test_input,test_label):

### 2020-09-09 ESPConst.py
9-9 pipeline

@@ -16,7 +16,7 @@ RNNParams = {
     'train_base_learning_rate':0.001,
     'rnn_save_file':'ESPBestRNN.h5',
     'rnn_embedding_output':97,
-    'rnn_unit_num':99,
+    'rnn_unit_num':45,
     'rnn_fc_hidden_layer_num':1,
     'rnn_fc_hidden_layer_units_num':166
     }
@@ -36,17 +36,32 @@ FineTuning = {
     'rnn_load_file':'ESPBestRNN.h5',
     'ensemble_load_file':'ESPEnsemble.h5',
     'ensemble_save_file':'ESPFineTuning.h5',
-    'train_batch_size':64,
+    'train_batch_size':16,
     'train_epochs_num':300,
-    'train_base_learning_rate':0.001,
+    'train_base_learning_rate':0.00002,
     'bio_fc_hidden_layer_num':1,
     'bio_fc_hidden_layer_units_num':87,
     'bio_fc_dropout':0.05
     }
+ParamsRanges = {
+    'CNNParams':
+    {
+        'cnn_fc_hidden_layer_units_num':[200,600],
+        'cnn_filters_num':[30,70],
+        'cnn_last_layer_units_num':[10,110]
+    },
+    'RNNParams':
+    {
+        'rnn_embedding_output':[40,140],
+        'rnn_unit_num':[30,130],
+        'rnn_fc_hidden_layer_units_num':[66,266],
+    }
+    }
 Params = {
-    'data_file':'espalldata.pkl',
+    'data_file':'ESPData.pkl',
     'CNNParams':CNNParams,
     'RNNParams':RNNParams,
     'EnsembleParams':EnsembleParams,
-    'FineTuning':FineTuning
+    'FineTuning':FineTuning,
+    'ParamsRanges':ParamsRanges
     }

### 2020-09-09 Ensemble.py

@@ -38,8 +38,7 @@ def train(params,
           validate_input,validate_biofeat,validate_label,
           test_input,test_biofeat,test_label,
           cnn_trainable=False,rnn_trainable=False,load_weight=False):
-    global best
-    best = -1
+    result = Result()
     m = model(params,
               cnn_trainable=cnn_trainable,rnn_trainable=rnn_trainable,load_weight=load_weight)
     batch_size = params['train_batch_size']
@@ -49,7 +48,7 @@ def train(params,
     
     batch_end_callback = LambdaCallback(on_epoch_end=
                                         lambda batch,logs: 
-                                        print(get_score_at_test(m,[test_input,test_biofeat],test_label,
+                                        print(get_score_at_test(m,[test_input,test_biofeat],result,test_label,
                                                                 issave=True,savepath=params['ensemble_save_file'])))
     m.fit([train_input,train_biofeat],train_label,
           batch_size=batch_size,
@@ -57,5 +56,6 @@ def train(params,
           verbose=2,
           validation_data=([validate_input,validate_biofeat],validate_label),
           callbacks=[batch_end_callback])
-    return {'loss': -1*best, 'status': STATUS_OK}
+    return {'loss': -1*result.Best, 'status': STATUS_OK}
+
 

### 2020-09-09 GetModelAttention.py

@@ -26,9 +26,17 @@ x_attention_onehot = x_train_onehot
 x_attention_biofeat = x_train_biofeat
 x_attention_seq = x_train_seq
 y_attention = y_train
-def get_temporal_attention(model,usebiofeat=True):
-    return 1
-def get_spatial_attention(model,usebiofeat=True):
+def get_temporal_attention(model):
+    temporal_layer_models = []
+    temporal_values = []
+    for i in range(21):
+        print(i)
+        temporal_layer_model = Model(inputs=model.inputs[0], outputs=model.get_layer('temporal_attention_'+str(i)).output)
+        temporal_values.append(
+            np.mean(temporal_layer_model.predict(x_attention_onehot), axis=0)
+            )
+    return temporal_values
+def get_spatial_attention(model):
     spatial_layer_model = Model(
         inputs=model.inputs[0], outputs=model.get_layer('spatial_attention_result').output)
     spatial_value = spatial_layer_model.predict(x_attention_onehot)
@@ -83,8 +91,6 @@ def bezier(t,points,pointsnum):
     return r
 
 def Plot3D(spatial_attention):
-    base_code_dict = {'T': 1, 'A': 2, 'C': 3, 'G': 4} 
-    code_base_dict = {1: 'T', 2: 'A', 3: 'C', 4: 'G'}
     from matplotlib import pyplot as plt
     from mpl_toolkits.mplot3d import Axes3D
 
@@ -92,8 +98,8 @@ def Plot3D(spatial_attention):
     ax1 = plt.axes(projection='3d')
 
     import numpy as np
-    xstep = 0.2
-    ystep = 0.1
+    xstep = 0.5
+    ystep = 0.2
     xbegin = 1.0
     ybegin = 0.0
     xend = 4.0001
@@ -111,10 +117,10 @@ def Plot3D(spatial_attention):
         
         u = float(nowposy)/float(yend-ybegin)
 
-        point0 = bezier(u,spatial_attention[0],21)
-        point1 = bezier(u,spatial_attention[1],21)
-        point2 = bezier(u,spatial_attention[2],21)
-        point3 = bezier(u,spatial_attention[3],21)
+        point0 = bezier(u,spatial_attention[3],21)
+        point1 = bezier(u,spatial_attention[0],21)
+        point2 = bezier(u,spatial_attention[1],21)
+        point3 = bezier(u,spatial_attention[2],21)
         print(u)
 
[…]

### 2020-09-09 HyperParametersSearch.py

@@ -1,0 +1,43 @@
+import ParamsUtil
+from ParamsUtil import *
+from hyperopt import fmin, tpe, hp, STATUS_OK, Trials
+from Pipeline import Pipeline
+######
+
+params['CNNParams']['train_epochs_num'] = 50
+params['RNNParams']['train_epochs_num'] = 50
+params['EnsembleParams']['train_epochs_num'] = 50
+params['FineTuning']['train_epochs_num'] = 50
+
+
+
+def HyperParametersSearch(hyperparameters):
+    nonSearch = hyperparameters['nonSearch']
+    paramsRange = nonSearch['Range']
+    paramsSetName = nonSearch['ParamsSetName']
+    name2params = lambda name: int(
+        hyperparameters[name]*(paramsRange[name][1]-paramsRange[name][0])
+        +paramsRange[name][0]
+        )
+    for i in hyperparameters.keys():
+        if i == 'nonSearch':
+            continue
+        params[paramsSetName][i] = name2params(i)
+    return Pipeline(pretrainCNN=True,pretrainRNN=False,ensemble=False,fineTuning=False)
+def HyperParameters(paramsRange,paramsSetName):
+    space = {
+        'nonSearch':
+        {
+            'Range':paramsRange[paramsSetName],
+            'ParamsSetName':paramsSetName
+            }
+        }
+    for i in paramsRange[paramsSetName].keys():
+        space.update({i:hp.uniform(i,0,1)})
+    trials = Trials()
+    result = fmin(HyperParametersSearch, space, algo=tpe.suggest, max_evals=25, trials=trials)
+    print('best: ')
+    print(result)
+
+if __name__ == "__main__":
+    HyperParameters(params['ParamsRanges'],'RNNParams')

### 2020-09-09 LearnUtil.py

@@ -1,18 +1,19 @@
-best = -1
+class Result(object):
+    Best = -1
 from sklearn.metrics import  mean_squared_error, r2_score
 import scipy as sp
-def get_score_at_test(model,input,label,issave=True,savepath=None):
+def get_score_at_test(model,input,result,label,issave=True,savepath=None):
     pred_label = model.predict(input)
     mse = mean_squared_error(label, pred_label)
     spearmanr = sp.stats.spearmanr(label, pred_label)[0]    
     r2 = r2_score(label, pred_label)
-    global best
-    if best<spearmanr:
-        best = spearmanr
+    
+    if result.Best<spearmanr:
+        result.Best = spearmanr
         if issave:
             model.save(savepath)
         print('best')
-    return 'MES:' + str(mse),'Spearman:' + str(spearmanr) , 'r2:' + str(r2), 'best:' + str(best)
+    return 'MES:' + str(mse),'Spearman:' + str(spearmanr) , 'r2:' + str(r2), 'best:' + str(result.Best)
 
 
 import keras

### 2020-09-09 ParamsUtil.py

@@ -4,6 +4,8 @@ import pandas as pd
 
 from WTConst import Params as params
 
+import os
+#os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
 from sklearn.model_selection import train_test_split
 def SplitData(onehot,biofeat,label):    
     random_state=40

### 2020-09-09 Pipeline.py

@@ -2,10 +2,6 @@ import ParamsUtil
 from ParamsUtil import *
 ######
 
-best = -1
-import os
-os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
-
 def AddNoise(onehot,biofeat,label,rate=50,intensity=0.30):
     from random import randint
     import copy
@@ -43,44 +39,41 @@ def AddNoise(onehot,biofeat,label,rate=50,intensity=0.30):
 
     return onehot,biofeat,label
 
-
+from pretrainRNN import train as RNN
 from PretrainCNN import train as CNN
-from PretrainRNN import train as RNN
 from Ensemble import train as Ensemble
 
-def Pipeline(pretrainCNN=False,pretrainRNN=False,ensemble=False):
+def Pipeline(pretrainCNN=False,pretrainRNN=False,ensemble=False,fineTuning=False):
     data = Read_Data()
     input = data['input']
     label = data['label']
-    global best
-    best = -1
+    r = None
     if pretrainCNN:
         input_train_onehot = input['train']['onehot']
         y_train = label['train']
         input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
                                                                   label['train'],rate=50,intensity=0.3)
-        CNN(params['CNNParams'],input_train_onehot,y_train,
+        r = CNN(params['CNNParams'],input_train_onehot,y_train,
              input['validate']['onehot'],label['validate'],
              input['test']['onehot'],label['test'])
-    best = -1
     if pretrainRNN:
         input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
                                                                   label['train'],rate=50,intensity=0.3)
-        RNN(params['RNNParams'],input_train_onehot,y_train,
+        r = RNN(params['RNNParams'],input_train_onehot,y_train,
              input['validate']['onehot'],label['validate'],
              input['test']['onehot'],label['test'])
-    best = -1
     if ensemble:
-        Ensemble(params['EnsembleParams'],
+        r = Ensemble(params['EnsembleParams'],
                  input['train']['onehot'],input['train']['biofeat'],label['train'],
                  input['validate']['onehot'],input['validate']['biofeat'],label['validate'],
                  input['test']['onehot'],input['test']['biofeat'],label['test'],
                  cnn_trainable=False,rnn_trainable=False)
-    best = -1
[…]

### 2020-09-09 WTConst.py

@@ -16,7 +16,7 @@ RNNParams = {
     'train_base_learning_rate':0.001,
     'rnn_save_file':'WTBestRNN.h5',
     'rnn_embedding_output':97,
-    'rnn_unit_num':99,
+    'rnn_unit_num':45,
     'rnn_fc_hidden_layer_num':1,
     'rnn_fc_hidden_layer_units_num':166
     }
@@ -43,10 +43,25 @@ FineTuning = {
     'bio_fc_hidden_layer_units_num':87,
     'bio_fc_dropout':0.05
     }
+ParamsRanges = {
+    'CNNParams':
+    {
+        'cnn_fc_hidden_layer_units_num':[200,600],
+        'cnn_filters_num':[30,70],
+        'cnn_last_layer_units_num':[10,110]
+    },
+    'RNNParams':
+    {
+        'rnn_embedding_output':[40,140],
+        'rnn_unit_num':[30,130],
+        'rnn_fc_hidden_layer_units_num':[66,266],
+    }
+    }
 Params = {
-    'data_file':'alldata.pkl',
+    'data_file':'WTData.pkl',
     'CNNParams':CNNParams,
     'RNNParams':RNNParams,
     'EnsembleParams':EnsembleParams,
-    'FineTuning':FineTuning
+    'FineTuning':FineTuning,
+    'ParamsRanges':ParamsRanges
     }

### 2020-09-09 pretrainCNN.py

@@ -38,8 +38,7 @@ def model(params):
     return model
 
 def train(params,train_input,train_label,validate_input,validate_label,test_input,test_label):
-    global best
-    best = -1
+    result = Result()
     m = model(params)
     batch_size = params['train_batch_size']
     learningrate = params['train_base_learning_rate']
@@ -48,7 +47,7 @@ def train(params,train_input,train_label,validate_input,validate_label,test_inpu
 
     batch_end_callback = LambdaCallback(on_epoch_end=
                                         lambda batch,logs: 
-                                        print(get_score_at_test(m,test_input,test_label,
+                                        print(get_score_at_test(m,test_input,result,test_label,
                                                                 issave=True,savepath=params['cnn_save_file'])))
 
     m.fit(train_input,train_label,
@@ -57,4 +56,4 @@ def train(params,train_input,train_label,validate_input,validate_label,test_inpu
           verbose=2,
           validation_data=([validate_input],validate_label), 
           callbacks=[batch_end_callback])
-    return {'loss': -1*best, 'status': STATUS_OK}
+    return {'loss': -1*result.Best, 'status': STATUS_OK}

### 2020-09-09 pretrainRNN.py

@@ -47,11 +47,9 @@ def model(params):
         atat = []
         for j in range(21):
             atat.append(
-                Softmax(axis=-1)(dot([encoderat[j],decoderat[i]],axes=-1))
+                dot([encoderat[j],decoderat[i]],axes=-1)
                 )
-        aat.append(
-            Reshape((21,1,),name='temporal_attention_'+str(i))(keras.layers.concatenate(atat))
-            )
+        aat.append(Reshape((21,1,),name='temporal_attention_'+str(i))(keras.layers.concatenate(atat)))
         
     ctat = []
     for i in range(21):
@@ -61,7 +59,7 @@ def model(params):
             Reshape((1,params['rnn_unit_num'],))(weightavg)
             )
     rnn_output = keras.layers.concatenate(ctat,axis=-2)
-    rnn_output = keras.layers.concatenate([rnn_output,decoder_output])
+    #rnn_output = keras.layers.concatenate([rnn_output,decoder_output])
 
     time_rnn_embeddedat = []
     for i in range(21):
@@ -83,8 +81,7 @@ def model(params):
     return model
 
 def train(params,train_input,train_label,validate_input,validate_label,test_input,test_label):
-    global best
-    best = -1
+    result = Result()
     m = model(params)
     batch_size = params['train_batch_size']
     learningrate = params['train_base_learning_rate']
@@ -93,7 +90,7 @@ def train(params,train_input,train_label,validate_input,validate_label,test_inpu
 
     batch_end_callback = LambdaCallback(on_epoch_end=
                                         lambda batch,logs: 
-                                        print(get_score_at_test(m,test_input,test_label,
+                                        print(get_score_at_test(m,test_input,result,test_label,
                                                                 issave=True,savepath=params['rnn_save_file'])))
 
     m.fit(train_input,train_label,
@@ -102,4 +99,4 @@ def train(params,train_input,train_label,validate_input,validate_label,test_inpu
           verbose=2,
           validation_data=([validate_input],validate_label), 
           callbacks=[batch_end_callback])
-    return {'loss': -1*best, 'status': STATUS_OK}
+    return {'loss': -1*result.Best, 'status': STATUS_OK}

### 2020-09-09 Paper/main.tex

@@
 \documentclass{bioinfo}
-\copyrightyear{2015} \pubyear{2015}
+\copyrightyear{2020} \pubyear{2020}
 
@@
 
-\subtitle{Subject Section}
+\subtitle{Genome analysis}
 
-\title[short Title]{This is a title}
+\title[short Title]{AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction
+}
 \author[Sample \textit{et~al}.]{Corresponding Author\,$^{\text{\sfb 1,}*}$, Co-Author\,$^{\text{\sfb 2}}$ and Co-Author\,$^{\text{\sfb 2,}*}$}
@@
  Moreover, recent work indicates that model explain techniques, which based post hoc explanations techniques and input perturbations, could be fooled to generate meaningless explanations instead of reflecting the underlying biases \citep{slack2019fooling}, in other word, they could be unreliable and misleading, even on model with excellent performance.
+ In addition, as far as we know, all the interpretable deep learning models today can only analyze the preference of on-target activity (or off-target probability) on specific nucleotide species and position (for example, the guanine (G) adjacent to PAM has a positive effect on sgRNA activity), which we'll call the first-order preference in our paper.
+ However they didn't analyzed the preference for sgRNA at the overall level, which we'll call the second-order preference in our paper (for example, could a thymine (T) at 2 bases upstream of the G adjacent to PAM affect the degree of preference for the G?)
+ We agree that base on the first-order influence and Bayesian formula can obtain the second-order preference in a statistical sense.
+However, it is obviously time-consuming task with exponential time complexity.
  In light of the above, we believe it is essential to develope a model which can not only match deep learning based model in performance, but also be comparable to conventional machine learning algorithms in interpretability.
@@
     \item Present a novel deep-learning-based model, which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
+    Finally, the ensemble learning method is used to combine the two to achieve better performance.
     It doesn't belong to any of the above categories of existing approaches.
@@
     As a result, It does not need post hoc explanations techniques based on input perturbation to explain itself. 
-    It is intrinsic interpretable at the nucleotide level in the temporal and spatial domains. 
-    The model we built could be approximated with a linear regression model, thus, it is transformed from a black box to an intrinsically interpretable model with the performance of deep learning based model.
-    This seems to has something in common with the idea of two-layer additive models, built by \citeauthor{DBLP:phd/basesearch/Chen20d}. 
-    He uses linear modeling with positive coefficients for feature, but inserts (interpretable) nonlinearities in several places to make the model more flexible and accurate \citep{DBLP:phd/basesearch/Chen20d}.
+    It is intrinsic interpretable in both temporal and spatial domains.
+    In the spatial domain it's at the nucleotide level, in our word, first-order interpretable, 
+    while at the overall level in the temporal domain, in our word, second-order interpretable. 
+    Thus, it is transformed from a black box to an intrinsically interpretable model with the performance of deep learning based model. 
     \item Throught abation analysis and testing a series of possible network structure, 

### 2020-09-10 Paper/main.tex
9-10

@@
 
-\subtitle{Genome analysis}
+\subtitle{Sequence analysis}
 
@@
 
-\abstract{\textbf{Motivation:} Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text
-Text Text Text Text Text.\\
-\textbf{Results:} Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text
-Text Text Text Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text\\
+\abstract{\textbf{Motivation:} More and more higher specificities Cas9 variants are developed to avoid the off-target effect, which bring a significant volume of experimental data. 
+Conventional machine learning performance poorly on these datasets, while model based on deep learning are often lack of interpretability, which makes it difficult for researchers to understand its decisions.
+Moreover, neither the deep learning based model with existing structure can not satisfy enough precision at such huge datasets.\\
+\textbf{Results:} To overcome it, we design and implement AttCRISPR, a deep learning based model to predict the on-target activity. 
+Our model was trained and tested on the biggest dataset, DeepHF dataset, as far as we know for performance evaluation. 
+AttCRISPR achieves the best performance on DeepHF dataset, yielding an average spearman value of 0.99\%, 0.99\%, 0.99\% (corresponding to WT-SpCas9, eSpCas9(1.1), SpCas9-HF1) under tenfold shuffled validation.
+In addition, another advantage of AttCRISPR over other well-perform methods is that it is intrinsic interpretable and does not rely on other post hoc explanations techniques. 
+In this paper, We design a set of algorithm to reveal the biological significance of the decision maked by AttCRISPR from the global and local perspectives at sgRNA overall level and nucleotide level.\\
 \textbf{Availability:} The example code are available at \href{https://github.com/South-Walker/AttCRISPR}{https://github.com/South-Walker/AttCRISPR}\\
@@
 
-Clustered regularly interspaced short palindromic repeats (CRISPR)/CRIPSR associated protein 9 (Cas9) systems is preferred over other biological research and human medicine technologies now, beacuse of it's efficiency,
+Clustered regularly interspaced short palindromic repeats (CRISPR) / CRIPSR associated protein 9 (Cas9) systems is preferred over other biological research and human medicine technologies now, beacuse of it's efficiency,
  robustness and programmability.  Cas9 nucleases can be directed by short guide RNAs (sgRNAs) to introduce site-specific DNA double-stranded breaks in target, 
@@
 
+\begin{figure}[!tpb]%figure2
+    \centerline{\includegraphics[scale=0.5]{category.png}}
+    \caption{Two categories of the deep learning models used in sgRNA related task. 
+    (a) Model work in spatial domain. (b) Model work in temporal domain.}\label{fig:01}
+\end{figure}
+
 Deep neural network has shown its power in the study of CRISPR/Cas9 and its improved Systems \citep{liu2019computational}. 
@@
     \item Present a novel deep-learning-based model, which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
-    Finally, the ensemble learning method is used to combine the two to achieve better performance.
+    Finally, the ensemble learning method is used to combine the two to achieve better performance than other models.
     It doesn't belong to any of the above categories of existing approaches.
@@
 
-\section{Approach}
+\section{Materials and methods}
 
-Equation~(\ref{eq:01}) Text Text Text Text Text Text  Text Text
-Text Text Text Text Text Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-.....
+\subsection{Sequence and biological features embedding}
+
+Text Text Text Text Text Text  Text Text Text Text Text Text Text
+Text Text  Text Text Text Text Text Text.
+
+\subsubsection{Spatial sequence embedding}
+
+Text  Text
+
+\subsubsection{Temporal sequence embedding}
+
+Text
+
+\subsubsection{biological features embedding}
+
+Text
+
+\subsection{Neural network architecture}
+
+Text
+
+\subsubsection{Attention module and model in spatial domain}
+
+Text
+
+\subsubsection{Attention module and model in temporal domain}
+
+Text
+
+\subsubsection{Ensemble method boosting model}
+
+Text
+
+\subsection{Datasets and current prediction algorithms}
+
+text
+
+\subsection{Experiments}
+
+text
 
@@
 \begin{methods}
-\section{Methods}
+\section{Results}
 
@@
 
-\begin{itemize}
-\item for bulleted list, use itemize
-\item for bulleted list, use itemize
-\item for bulleted list, use itemize\vspace*{1pt}
-\end{itemize}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
-Text Text Text Text Text Text Text Text Text Text Text.
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text\vadjust{\newpage}.
 Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
@@
 \end{minipage}}
-%\centerline{\includegraphics{fig01.eps}}
-\caption{Caption, caption.}\label{fig:01}
+%\centerline{\includegraphics[scale=0.6]{category.png}}
+\caption{Caption, caption.}\label{fig:02}
 \end{figure}
-
-%\begin{figure}[!tpb]%figure2
-%%\centerline{\includegraphics{fig02.eps}}
-%\caption{Caption, caption.}\label{fig:02}
-%\end{figure}
 
@@
 \citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
+Text
 
@@
 
-Text Text Textext
+Text
 text text text\vspace*{-12pt}

### 2020-09-10 ESPConst.py

@@ -4,21 +4,21 @@ CNNParams = {
     'train_base_learning_rate':0.00002,
     'cnn_save_file':'ESPBestCNN.h5',
     'cnn_fc_hidden_layer_num':2,
-    'cnn_fc_hidden_layer_units_num':421,
+    'cnn_fc_hidden_layer_units_num':289,
     'cnn_fc_dropout':0.5,
-    'cnn_filters_num':50,
+    'cnn_filters_num':69,
     'cnn_conv_num':3,
-    'cnn_last_layer_units_num':60
+    'cnn_last_layer_units_num':37
     }
 RNNParams = {
     'train_batch_size':128,
     'train_epochs_num':75,
     'train_base_learning_rate':0.001,
     'rnn_save_file':'ESPBestRNN.h5',
-    'rnn_embedding_output':97,
-    'rnn_unit_num':45,
+    'rnn_embedding_output':62,
+    'rnn_unit_num':38,
     'rnn_fc_hidden_layer_num':1,
-    'rnn_fc_hidden_layer_units_num':166
+    'rnn_fc_hidden_layer_units_num':119
     }
 EnsembleParams = {
     'cnn_load_file':'ESPBestCNN.h5',

### 2020-09-10 HyperParametersSearch.py

@@ -23,7 +23,10 @@ def HyperParametersSearch(hyperparameters):
         if i == 'nonSearch':
             continue
         params[paramsSetName][i] = name2params(i)
-    return Pipeline(pretrainCNN=True,pretrainRNN=False,ensemble=False,fineTuning=False)
+    if paramsSetName == 'RNNParams':
+        return Pipeline(pretrainCNN=False,pretrainRNN=True)
+    if paramsSetName == 'CNNParams':
+        return Pipeline(pretrainCNN=True,pretrainRNN=False)
 def HyperParameters(paramsRange,paramsSetName):
     space = {
         'nonSearch':
@@ -35,7 +38,7 @@ def HyperParameters(paramsRange,paramsSetName):
     for i in paramsRange[paramsSetName].keys():
         space.update({i:hp.uniform(i,0,1)})
     trials = Trials()
-    result = fmin(HyperParametersSearch, space, algo=tpe.suggest, max_evals=25, trials=trials)
+    result = fmin(HyperParametersSearch, space, algo=tpe.suggest, max_evals=5, trials=trials)
     print('best: ')
     print(result)
 

### 2020-09-10 SPConst.py

@@ -4,21 +4,21 @@ CNNParams = {
     'train_base_learning_rate':0.00002,
     'cnn_save_file':'SPBestCNN.h5',
     'cnn_fc_hidden_layer_num':2,
-    'cnn_fc_hidden_layer_units_num':421,
+    'cnn_fc_hidden_layer_units_num':315,
     'cnn_fc_dropout':0.5,
-    'cnn_filters_num':50,
+    'cnn_filters_num':65,
     'cnn_conv_num':3,
-    'cnn_last_layer_units_num':60
+    'cnn_last_layer_units_num':74
     }
 RNNParams = {
     'train_batch_size':128,
     'train_epochs_num':75,
     'train_base_learning_rate':0.001,
     'rnn_save_file':'SPBestRNN.h5',
-    'rnn_embedding_output':97,
-    'rnn_unit_num':45,
+    'rnn_embedding_output':117,
+    'rnn_unit_num':124,
     'rnn_fc_hidden_layer_num':1,
-    'rnn_fc_hidden_layer_units_num':166
+    'rnn_fc_hidden_layer_units_num':120
     }
 EnsembleParams = {
     'cnn_load_file':'SPBestCNN.h5',

### 2020-09-10 WTConst.py

@@ -4,21 +4,21 @@ CNNParams = {
     'train_base_learning_rate':0.00002,
     'cnn_save_file':'WTBestCNN.h5',
     'cnn_fc_hidden_layer_num':2,
-    'cnn_fc_hidden_layer_units_num':421,
+    'cnn_fc_hidden_layer_units_num':600,
     'cnn_fc_dropout':0.5,
-    'cnn_filters_num':50,
+    'cnn_filters_num':61,
     'cnn_conv_num':3,
-    'cnn_last_layer_units_num':60
+    'cnn_last_layer_units_num':54
     }
 RNNParams = {
-    'train_batch_size':128,
+    'train_batch_size':64,
     'train_epochs_num':75,
-    'train_base_learning_rate':0.001,
+    'train_base_learning_rate':0.0001,
     'rnn_save_file':'WTBestRNN.h5',
-    'rnn_embedding_output':97,
-    'rnn_unit_num':45,
+    'rnn_embedding_output':77,
+    'rnn_unit_num':125,
     'rnn_fc_hidden_layer_num':1,
-    'rnn_fc_hidden_layer_units_num':166
+    'rnn_fc_hidden_layer_units_num':140
     }
 EnsembleParams = {
     'cnn_load_file':'WTBestCNN.h5',

### 2020-09-10 pretrainRNN.py

@@ -38,9 +38,9 @@ def model(params):
                 Cropping1D(cropping=(i,21-1-i))(decoder_output)
                 )
             )
-
-    for i in range(21):
-        decoderat[i] = Dense(params['rnn_unit_num'], activation=None,use_bias=False)(decoderat[i])
+    #could be removed
+    #for i in range(21):
+        #decoderat[i] = Dense(params['rnn_unit_num'], activation=None,use_bias=False)(decoderat[i])
 
     aat = []
     for i in range(21):
@@ -49,25 +49,19 @@ def model(params):
             atat.append(
                 dot([encoderat[j],decoderat[i]],axes=-1)
                 )
-        aat.append(Reshape((21,1,),name='temporal_attention_'+str(i))(keras.layers.concatenate(atat)))
+        at = keras.layers.concatenate(atat)
+        at = Softmax()(at)
+        aat.append(Reshape((21,1,),name='temporal_attention_'+str(i))(at))
         
     ctat = []
     for i in range(21):
         weightavg = Lambda(lambda inp: inp[0]*inp[1])([encoder_output ,aat[i]])
-        weightavg = Lambda(lambda inp: K.sum(inp,axis=-2,keepdims=False))(weightavg)
         ctat.append(
-            Reshape((1,params['rnn_unit_num'],))(weightavg)
+            Lambda(lambda inp: K.sum(inp,axis=-2,keepdims=False)+decoderat[i])(weightavg)
             )
-    rnn_output = keras.layers.concatenate(ctat,axis=-2)
-    #rnn_output = keras.layers.concatenate([rnn_output,decoder_output])
 
-    time_rnn_embeddedat = []
+    time_rnn_embeddedat = ctat
     for i in range(21):
-        time_rnn_embeddedat.append(
-            Flatten(name='rnn_flatten_'+str(i))(
-                Cropping1D(cropping=(i,21-1-i))(rnn_output)
-                )
-            )
         time_rnn_embeddedat[i] = mlp(time_rnn_embeddedat[i],
                                      output_layer_activation='tanh',output_dim=1,output_use_bias=False,
                                      hidden_layer_num=params['rnn_fc_hidden_layer_num'],hidden_layer_units_num=params['rnn_fc_hidden_layer_units_num'],

### 2020-09-11 Train/Faker.py
9-11 fix RNN

@@ -2,6 +2,9 @@ import ParamsUtil
 from ParamsUtil import *
 ######
 
+import os
+os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
+
 def AddNoise(onehot,biofeat,label,rate=50,intensity=0.30):
     from random import randint
     import copy
@@ -38,42 +41,55 @@ def AddNoise(onehot,biofeat,label,rate=50,intensity=0.30):
     label=t_label[index]
 
     return onehot,biofeat,label
-
-from TrainRNN import train as RNN
-from TrainCNN import train as CNN
+def faker(data,rate=5):    
+    from random import randint
+    import copy
+    input = data['input']
+    onehot = input['train']['onehot'].tolist()
+    biofeat = input['train']['biofeat'].tolist()
+    label = data['label']['train'].tolist()
+    x=0
+    for i in range(len(input['test']['onehot'])):
+        if randint(0,100) > rate:
+            continue
+        onehot.append(input['test']['onehot'][i])
+        biofeat.append(input['test']['biofeat'][i])
+        label.append(data['label']['test'][i])
+    
+    onehot = np.array(onehot).reshape(-1,21,4,1)
+    biofeat = np.array(biofeat).reshape(-1,11)
+    label = np.array(label).reshape(-1)
+    return onehot,biofeat,label
+from PretrainCNN import train as CNN
+from PretrainRNN import train as RNN
 from Ensemble import train as Ensemble
 
-def Pipeline(pretrainCNN=False,pretrainRNN=False,ensemble=False,fineTuning=False):
+def Pipeline(pretrainCNN=False,pretrainRNN=False,ensemble=False):
     data = Read_Data()
     input = data['input']
     label = data['label']
-    r = None
     if pretrainCNN:
         input_train_onehot = input['train']['onehot']
         y_train = label['train']
-        input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
-                                                                  label['train'],rate=50,intensity=0.3)
-        r = CNN(params['CNNParams'],input_train_onehot,y_train,
+        input_train_onehot,input_train_biofeat,y_train = faker(data,rate=5)
+        CNN(params['CNNParams'],input_train_onehot,y_train,
              input['validate']['onehot'],label['validate'],
              input['test']['onehot'],label['test'])
     if pretrainRNN:
-        input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
[…]

### 2020-09-11 Train/SPConst.py

@@ -52,9 +52,9 @@ ParamsRanges = {
     },
     'RNNParams':
     {
-        'rnn_embedding_output':[40,140],
-        'rnn_unit_num':[30,130],
-        'rnn_fc_hidden_layer_units_num':[66,266],
+        'rnn_embedding_output':[10,210],
+        'rnn_unit_num':[10,210],
+        'rnn_fc_hidden_layer_units_num':[20,520],
     }
     }
 Params = {

### 2020-09-11 Train/TrainRNN.py

@@ -1,5 +1,5 @@
 import keras
-from keras.layers import Softmax,Input, Conv2D, Flatten, BatchNormalization, Multiply,Cropping1D,dot, Bidirectional
+from keras.layers import Softmax,GlobalAveragePooling1D,Input, Conv2D, Flatten, BatchNormalization, Multiply,Cropping1D,dot, Bidirectional
 from keras.layers.core import *
 from keras.layers.recurrent import LSTM,GRU
 from keras.models import *
@@ -14,34 +14,32 @@ def model(params):
     embedded = Conv2D(params['rnn_embedding_output'], (1, 4),strides=(1,4), padding='Valid', activation=None)(onehot_input)
     embedded = Reshape((21,params['rnn_embedding_output'],))(embedded)
 
+    ######encoder&decoder######
     encoder = LSTM(params['rnn_unit_num'],return_sequences=True,return_state=False,unroll=True)
-    encoder = Bidirectional(encoder,merge_mode='sum',name='encoder_output')
+    encoder = Bidirectional(encoder,merge_mode='sum',name='encoder')
     encoder_output = encoder(embedded)
-    
-    encoderat = []
-    for i in range(21):
-        encoderat.append(
-            Flatten()(
-                Cropping1D(cropping=(i,21-1-i))(encoder_output)
-                )
-            )
+
     decoder_input = keras.layers.concatenate([embedded,encoder_output])
     decoder = LSTM(params['rnn_unit_num'],dropout=0.25,recurrent_dropout=0.25,
-                     return_sequences=True,return_state=False,name='last_gru_output',unroll=True)
-    decoder = Bidirectional(decoder,merge_mode='sum',name='last_bgru_output')
-    decoder_output = decoder(decoder_input)
+                     return_sequences=True,return_state=True,unroll=True)
+    decoder = Bidirectional(decoder,merge_mode='sum',name='decoder')
+    decoder_output,_,c_1,_,c_2 = decoder(decoder_input)
     
+
+    encoderat = []
     decoderat = []
     for i in range(21):
+        encoderat.append(
+            Flatten()(Cropping1D(cropping=(i,21-1-i))(encoder_output)))
         decoderat.append(
-            Flatten()(
-                Cropping1D(cropping=(i,21-1-i))(decoder_output)
-                )
-            )
-    #could be removed
-    #for i in range(21):
[…]

### 2020-09-11 Train/WTConst.py

@@ -11,14 +11,14 @@ CNNParams = {
     'cnn_last_layer_units_num':54
     }
 RNNParams = {
-    'train_batch_size':64,
+    'train_batch_size':128,
     'train_epochs_num':75,
-    'train_base_learning_rate':0.0001,
+    'train_base_learning_rate':0.001,
     'rnn_save_file':'WTBestRNN.h5',
-    'rnn_embedding_output':77,
-    'rnn_unit_num':125,
+    'rnn_embedding_output':97,
+    'rnn_unit_num':45,
     'rnn_fc_hidden_layer_num':1,
-    'rnn_fc_hidden_layer_units_num':140
+    'rnn_fc_hidden_layer_units_num':166
     }
 EnsembleParams = {
     'cnn_load_file':'WTBestCNN.h5',
@@ -52,9 +52,9 @@ ParamsRanges = {
     },
     'RNNParams':
     {
-        'rnn_embedding_output':[40,140],
-        'rnn_unit_num':[30,130],
-        'rnn_fc_hidden_layer_units_num':[66,266],
+        'rnn_embedding_output':[10,210],
+        'rnn_unit_num':[10,210],
+        'rnn_fc_hidden_layer_units_num':[20,520],
     }
     }
 Params = {

### 2020-09-11 Paper/main.tex
9-11 fix RNN

@@
 
+\subsection{Sequence encoding}
+
+Text
+
 \subsection{Sequence and biological features embedding}
@@
 
-\subsection{Neural network architecture}
+\subsubsection{Spatial attention module}
 
@@
 
-\subsubsection{Attention module and model in spatial domain}
+\subsubsection{Temporal attention module}
 
@@
 
-\subsubsection{Attention module and model in temporal domain}
+\subsection{Neural network architecture}
 
-Text
+\begin{figure}[!tpb]%figure2
+    \centerline{\includegraphics[scale=0.5]{category.png}}
+    \caption{The overview of AttCRISPR. 
+    It consists of two components, namely CNNs and RNNs. 
+    The CNN component is used to capture spatial nucleotide preference, 
+    while the RNN component is used to capture temporal nucleotide preference. 
+    Finally, a weighted average method with trainable weight is used to predict activity.}\label{fig:02}
+\end{figure}
 

### 2020-09-11 Train/TrainRNN.py

@@ -8,8 +8,21 @@ from keras.optimizers import *
 import keras.backend as K
 from hyperopt import fmin, tpe, hp, STATUS_OK, Trials
 from LearnUtil import *
+import math
 
+
+def GaussianKernelBuffer(windowsize=3):
+    gaussian = lambda d: math.exp( -(d*d)*2/windowsize/windowsize ) if abs(d)<=windowsize else 0
+    result = []
+    for i in range(21):
+        resultat = []
+        for j in range(21):
+            resultat.append(gaussian(i-j))
+        result.append(resultat)
+    return result
 def model(params):
+    GaussianBuffer = GaussianKernelBuffer()
+
     onehot_input = Input(name = 'onehot_input', shape = (21,4, 1,))
     embedded = Conv2D(params['rnn_embedding_output'], (1, 4),strides=(1,4), padding='Valid', activation=None)(onehot_input)
     embedded = Reshape((21,params['rnn_embedding_output'],))(embedded)
@@ -36,24 +49,24 @@ def model(params):
 
     #context = Lambda(lambda inp: inp[0]+inp[1])([c_1,c_2])
     context = GlobalAveragePooling1D()(encoder_output)
-    for i in range(21):
-        decoderat[i] = Dense(params['rnn_unit_num'], kernel_initializer='zeros', activation=None,use_bias=False)(decoderat[i])
-    
+
     ######attention######
     aat = []
     for i in range(21):
         atat = []
         for j in range(21):
+            align = dot([encoderat[j],decoderat[i]],axes=-1)
             atat.append(
-                dot([encoderat[j],decoderat[i]],axes=-1)
+                Lambda(lambda inp: inp*GaussianBuffer[i][j])(align)
                 )
         at = keras.layers.concatenate(atat)
-        at = Softmax()(at)
+        #at = Softmax()(at)
         aat.append(Reshape((21,1,),name='temporal_attention_'+str(i))(at))
     rnn_output = []
     for i in range(21):
         weightavg = Lambda(lambda inp: inp[0]*inp[1])([encoder_output ,aat[i]])
         weightavg = Lambda(lambda inp: K.sum(inp,axis=-2,keepdims=False))(weightavg)
+        #weightavg = Lambda(lambda inp: (inp[0]+inp[1])/2)([weightavg,encoderat[i]])
         rnn_output.append(keras.layers.concatenate([context,weightavg,decoderat[i]]))
     time_rnn_embeddedat = rnn_output 
     for i in range(21):

### 2020-09-12 Train/GetModelAttention.py
9-12 fixRNN

@@ -8,7 +8,7 @@ from sklearn.model_selection import train_test_split
 import os
 os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
 
-pkl = open('alldata.pkl','rb') 
+pkl = open('WTData.pkl','rb') 
 x_onehot =  pickle.load(pkl)
 x_biofeat = pickle.load(pkl)
 y = pickle.load(pkl)
@@ -27,15 +27,10 @@ x_attention_biofeat = x_train_biofeat
 x_attention_seq = x_train_seq
 y_attention = y_train
 def get_temporal_attention(model):
-    temporal_layer_models = []
-    temporal_values = []
-    for i in range(21):
-        print(i)
-        temporal_layer_model = Model(inputs=model.inputs[0], outputs=model.get_layer('temporal_attention_'+str(i)).output)
-        temporal_values.append(
-            np.mean(temporal_layer_model.predict(x_attention_onehot), axis=0)
-            )
-    return temporal_values
+    temporal_layer_model = Model(inputs=model.inputs[0], outputs=model.get_layer('temporal_attention').output)
+    temporal_attention = temporal_layer_model.predict(x_attention_onehot)
+    temporal_value = np.mean(temporal_attention, axis=0)
+    return temporal_value
 def get_spatial_attention(model):
     spatial_layer_model = Model(
         inputs=model.inputs[0], outputs=model.get_layer('spatial_attention_result').output)
@@ -169,7 +164,7 @@ load_model = load_model('./WTBestRNN.h5')
 
 load_model.summary()
 #cnn_model = load_model.get_layer('cnn')
-cnn_model = load_model
+#cnn_model = load_model
 #rnn_model = load_model.get_layer('rnn')
 rnn_model = load_model
 temporal_attention = get_temporal_attention(rnn_model)

### 2020-09-12 Train/SPConst.py

@@ -25,7 +25,7 @@ EnsembleParams = {
     'rnn_load_file':'SPBestRNN.h5',
     'ensemble_save_file':'SPEnsemble.h5',
     'train_batch_size':16,
-    'train_epochs_num':75,
+    'train_epochs_num':10,
     'train_base_learning_rate':0.00002,
     'bio_fc_hidden_layer_num':1,
     'bio_fc_hidden_layer_units_num':87,

### 2020-09-12 Train/TrainRNN.py

@@ -11,14 +11,16 @@ from LearnUtil import *
 import math
 
 
-def GaussianKernelBuffer(windowsize=3):
-    gaussian = lambda d: math.exp( -(d*d)*2/windowsize/windowsize ) if abs(d)<=windowsize else 0
+def GaussianKernelBuffer(windowsize=8):
+    gaussian = lambda d: math.exp( -(d*d)*2/windowsize/windowsize ) if abs(d)<=windowsize/2 else 0
     result = []
     for i in range(21):
         resultat = []
         for j in range(21):
             resultat.append(gaussian(i-j))
-        result.append(resultat)
+        nresultat = np.array(resultat)
+        result.append(nresultat)
+    return np.array(result)
     return result
 def model(params):
     GaussianBuffer = GaussianKernelBuffer()
@@ -47,9 +49,10 @@ def model(params):
         decoderat.append(
             Flatten()(Cropping1D(cropping=(i,21-1-i))(decoder_output)))
 
-    #context = Lambda(lambda inp: inp[0]+inp[1])([c_1,c_2])
-    context = GlobalAveragePooling1D()(encoder_output)
-
+    context = Lambda(lambda inp: inp[0]+inp[1])([c_1,c_2])
+    #context = GlobalAveragePooling1D()(encoder_output)
+    for i in range(21):
+        decoderat[i] = Dense(params['rnn_unit_num'],activation=None,use_bias=False)(decoderat[i])
     ######attention######
     aat = []
     for i in range(21):
@@ -57,24 +60,27 @@ def model(params):
         for j in range(21):
             align = dot([encoderat[j],decoderat[i]],axes=-1)
             atat.append(
-                Lambda(lambda inp: inp*GaussianBuffer[i][j])(align)
+                align
                 )
         at = keras.layers.concatenate(atat)
-        #at = Softmax()(at)
-        aat.append(Reshape((21,1,),name='temporal_attention_'+str(i))(at))
-    rnn_output = []
+        at = Softmax()(at)
+        at = Reshape((1,21,))(at)
+        aat.append(at)
+    m = keras.layers.concatenate(aat,axis=-2)
+    weight = Lambda(lambda inp: K.constant(GaussianBuffer)*inp ,name = 'temporal_attention')(m)
+    weightavg = Lambda(lambda inp: K.batch_dot(inp[0],inp[1]),name='weight_avg')([weight,encoder_output])
+    rnn_output = (keras.layers.concatenate([weightavg,decoder_output]))
[…]

### 2020-09-12 Train/WTConst.py

@@ -12,11 +12,11 @@ CNNParams = {
     }
 RNNParams = {
     'train_batch_size':128,
-    'train_epochs_num':75,
-    'train_base_learning_rate':0.001,
+    'train_epochs_num':100,
+    'train_base_learning_rate':0.0005,
     'rnn_save_file':'WTBestRNN.h5',
     'rnn_embedding_output':97,
-    'rnn_unit_num':45,
+    'rnn_unit_num':99,
     'rnn_fc_hidden_layer_num':1,
     'rnn_fc_hidden_layer_units_num':166
     }
@@ -25,7 +25,7 @@ EnsembleParams = {
     'rnn_load_file':'WTBestRNN.h5',
     'ensemble_save_file':'WTEnsemble.h5',
     'train_batch_size':16,
-    'train_epochs_num':75,
+    'train_epochs_num':10,
     'train_base_learning_rate':0.00002,
     'bio_fc_hidden_layer_num':1,
     'bio_fc_hidden_layer_units_num':87,

### 2020-09-25 Paper/main.tex
paper

@@
 
-Learning-based method, which designed to predict the activity of sgRNAs, is essentially a computational model built by machine learning algorithm, not only conventional machine learning but also deep learning algorithm.
+Learning-based method, which designed to predict the on-target activity (or off-target probability) of sgRNAs, 
+ is essentially a computational model built by machine learning algorithm, not only conventional machine learning but also deep learning algorithm. 
+ In general, the single or multiple base sequences (vary according to the task) and biological features are represented as a multi-dimensional vector $X\in\mathbb{R}^d$, 
+ and $d=l+b$, where $l$ refers to the length of base sequences and $b$ refers to the number of biological features, these methods can be represented as
+\begin{equation}
+\text{\it y}=Score(\it X)\label{eq:01}\vspace*{-10pt}
+\end{equation}\\
+ where $Score(\cdot)$ depends on the algorithm being selected, and $y$ denotes the predicted value.
  Some studies on HT\_ABE and HT\_CBE have shown that deep learning based models often outperformed conventional machine learning, when the number of sgRNAs in the data set reached a certain level \citep{Song2020,kim2018deep,kim2019spcas9}.
@@
  In our understanding, the method based on input perturbation often requires better generalization ability of the model (even for artificial ridiculous noise data). 
- Moreover, recent work indicates that model explain techniques, which based post hoc explanations techniques and input perturbations, could be fooled to generate meaningless explanations instead of reflecting the underlying biases \citep{slack2019fooling}, in other word, they could be unreliable and misleading, even on model with excellent performance.
- In addition, as far as we know, all the interpretable deep learning models today can only analyze the preference of on-target activity (or off-target probability) on specific nucleotide species and position (for example, the guanine (G) adjacent to PAM has a positive effect on sgRNA activity), which we'll call the first-order preference in our paper.
- However they didn't analyzed the preference for sgRNA at the overall level, which we'll call the second-order preference in our paper (for example, could a thymine (T) at 2 bases upstream of the G adjacent to PAM affect the degree of preference for the G?)
- We agree that base on the first-order influence and Bayesian formula can obtain the second-order preference in a statistical sense.
-However, it is obviously time-consuming task with exponential time complexity.
- In light of the above, we believe it is essential to develope a model which can not only match deep learning based model in performance, but also be comparable to conventional machine learning algorithms in interpretability.
+ Moreover, recent work indicates that model explain techniques, which based post hoc explanations techniques and input perturbations, could be fooled to generate meaningless explanations instead of reflecting the underlying biases \citep{slack2019fooling},
+ in other word, they could be unreliable and misleading, even on model with excellent performance. 
+ In addition, as far as we know, all the interpretable deep learning models today can only analyze the preference of on-target activity (or off-target probability) on specific nucleotide species and position
+ for example, the G adjacent to PAM has a positive effect on sgRNA activity as \citeauthor{wang2019optimized} report, 
+ which we'll call the first-order preference in our paper, due to it's similar to the total differential of $y$ in Equation \ref{eq:01} as following
+\begin{equation}
+dy = \sum^{d}_ia_idx_i\label{eq:02}\vspace*{-10pt}
+\end{equation}
+\begin{equation}
+a_i=\frac{\partial}{\partial x_i} Score(X)\label{eq:03}\vspace*{-10pt}
+\end{equation}\\
+ where $x_i$ denotes the $i$-th dimension of the vector $X$, 
+ $a_i$ indicates how dramatically the function changes as $x_i$ changes in a neighborhood of $X$. 
+ Similarly the first-order preference indicates how dramatically the function changes as $x_i$ changes, in other word, the importance of $x_i$.
+ However they didn't analyzed the preference for position $i$ nucleotide at the overall level, 
+ which we'll call the second-order preference in our paper due to its calculation is based on first-order preference, 
+ Specifically, we use a vector $A_i$ to build the first-order preference at position $i$ within sgRNA sequence, then
+\begin{equation}
+y=\sum_i^lW_iA_i\cdot X_i\label{eq:04}\vspace*{-10pt}
+\end{equation}\\
+ where $W$ denotes a non-negative weight matrix, $W_i$ denotes the weight of the $i$-th position, $X_i$ denotes the embedding vector of the nucleotide at $i$-th position.
+ We linearly combine the first-order preference vector of base sequence as following
+\begin{equation}
+\widetilde{A}=BA\label{eq:05}\vspace*{-10pt}
+\end{equation}\\
+ where the weight matrix $B$ is learned through attention mechanism, and we define $A$ as the first-order original preference matrix, 
+ $\widetilde{A}$ as the first-order combine preference matrix (or just first-order preference) to differentiate them.
+ In other words, we build a additive model for the first-order preference, 
+ which means that the first-order preference of the $i$-th position $\widetilde{A_i}$ can be calculated as
+\begin{equation}
+\widetilde{A}_i=\sum_j^lB_{ij}A_i\label{eq:06}\vspace*{-10pt}
+\end{equation}\\
+ Suppose that in Equation \ref{eq:06} the first-order original preference at each position is relatively independent and weight matrix B is independent of any first-order original preference, 
+ then the total differential of the first-order preference at $i$-th position could be written as
+\begin{equation}
+d\widetilde{A}_i=\sum_j^lB_{ij}EdA_j\label{eq:07}\vspace*{-10pt}
+\end{equation}\\
+ where $E$ is the identity matrix, and we define $B$ as the second-order preference matrix, 
+ it can explain how a particular pattern containing two nucleotides affects the base sequence, 
+ for example, how does the degree of preference for the G adjacent to PAM be affected by a T at 2 bases upstream?
+ The previous work (even based on conventional machine learning algorithms with high interpretability) 
+ was limited to dimers which can only work on the adjacent base pairs \citep{Liu2019} 
+ or have to perform complex feature engineering \citep{MuhammadRafid2020}.
+ In light of the above, we believe it is essential to develope a model which can not only match deep learning based model in performance, 
+ but also be comparable to conventional machine learning algorithms in interpretability.
 
 \begin{figure}[!tpb]%figure2
-    \centerline{\includegraphics[scale=0.5]{category.png}}
+\centerline{\includegraphics[scale=0.4]{category.png}}
 \caption{Two categories of the deep learning models used in sgRNA related task. 
@@
 In this paper, our main contributions are as follows:\vspace*{1pt}
-
 \begin{itemize}
@@
     It is intrinsic interpretable in both temporal and spatial domains.
-    In the spatial domain it's at the nucleotide level, in our word, first-order interpretable, 
-    while at the overall level in the temporal domain, in our word, second-order interpretable. 
+    In the spatial domain it's at the nucleotide level, in our word, first-order preference, 
+    while at the overall level in the temporal domain, in our word, second-order preference. 
     Thus, it is transformed from a black box to an intrinsically interpretable model with the performance of deep learning based model. 
@@
     we find there are multiple components and strategy can improve the performance of our model and constructed AttCRISPR, 
-    which could outperform the current state-of-the-art tool on deepHF dataset.\vspace*{1pt}
+    which could outperform the current state-of-the-art tool on DeepHF dataset.\vspace*{1pt}
 \end{itemize}
@@
 
+Equation \ref{eq:01} is the inventory flow formula.
 Text
@@
 \begin{equation}
-\sum \text{\it x}+ \text{\it y} =\text{\it Z}\label{eq:01}\vspace*{-10pt}
+\sum \text{\it x}+ \text{\it y} =\text{\it Z}\label{eq:0}\vspace*{-10pt}
+\end{equation}
+
+{\ldots}{\ldots} text follows.
+
+{\ldots}{\ldots} text follows.
+\begin{equation}
+    \partial y = \sum^{len}_ia_i\partial x_i\label{eq:02}\vspace*{-10pt}
 \end{equation}

### 2020-09-25 Train/GetModelAttention.py

@@ -7,7 +7,7 @@ from keras.models import *
 import scipy as sp
 from sklearn.model_selection import train_test_split
 import os
-os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
+#os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
 
 pkl = open('WTData.pkl','rb') 
 x_onehot =  pickle.load(pkl)
@@ -56,6 +56,7 @@ def get_local_temporal_attention(model):
 def get_temporal_attention(model):
     temporal_layer_model = Model(inputs=model.inputs[0], outputs=model.get_layer('temporal_attention').output)
     temporal_score_model = Model(inputs=model.inputs[0], outputs=model.get_layer('last_score').output)
+    temporal_perpos_score_weight = model.get_layer('temporal_score').get_weights()
     last_layer_weight = model.get_layer('temporal_score').get_weights()[0]
     temporal_attention = temporal_layer_model.predict(x_attention_onehot)
     temporal_value = np.mean(temporal_attention, axis=0)
@@ -64,18 +65,24 @@ def get_temporal_attention(model):
     for i in range(21):
         sum = 0
         count = 0
-        ##zscore?
+        ##normalize
         for j in range(21):
             sum += temporal_value[i][j]
-            count += 1 if temporal_value[i][j]!=0 else 0
-        avg = sum / count
-        sumx_2 = 0
         for j in range(21):
-            sumx_2 += (temporal_value[i][j]-avg)*(temporal_value[i][j]-avg) if temporal_value[i][j]!=0 else 0
-        sigma = math.sqrt(sumx_2 / count)
-        for j in range(21):
-            temporal_value[i][j] = (temporal_value[i][j]-avg) / sigma if temporal_value[i][j]!=0 else 0
-            temporal_value[i][j] = temporal_value[i][j]/temporal_score[i]
+            temporal_value[i][j] = temporal_value[i][j]/sum
+            #temporal_value[i][j] = temporal_value[i][j]/temporal_score[i]
+        ##zscore
+        #for j in range(21):
+            #sum += temporal_value[i][j]
+            #count += 1 if temporal_value[i][j]!=0 else 0
+        #avg = sum / count
+        #sumx_2 = 0
+        #for j in range(21):
[…]

### 2020-09-25 Train/TrainRNN.py

@@ -59,6 +59,7 @@ def model(params):
             Flatten()(Cropping1D(cropping=(i,21-1-i))(decoder_output)))
     ######attention######
     aat = []
+    sqrtd = math.sqrt(params['rnn_unit_num'])
     for i in range(21):
         atat = []
         for j in range(21):
@@ -67,22 +68,21 @@ def model(params):
             atat.append(
                 align
                 )
+        ## add l2 regular
         at = keras.layers.concatenate(atat)
-        at = Softmax()(at)
+        #l2(0.00001) is opt while 0.001 is best
+        at = Dense(21,activation='softmax',use_bias=True,activity_regularizer=keras.regularizers.l2(0.00001))(at)
         #at[j] important of pos[j] in scoring pos[i]
+
         at = Reshape((1,21,))(at)
         aat.append(at)
     #aat[i][j] important of pos[j] in scoring pos[i]
     m = keras.layers.concatenate(aat,axis=-2)
     weight = Lambda(lambda inp: K.constant(GaussianBuffer)*inp ,name = 'temporal_attention')(m)
     weightavg = Lambda(lambda inp: K.batch_dot(inp[0],inp[1]),name='weight_avg')([weight,encoder_output])
-    context = Dense(params['rnn_unit_num'],activation='tanh',use_bias=True)(context)
+    context = Dense(params['rnn_unit_num'],activation='tanh', use_bias=True)(context)
     context = Lambda(lambda inp: K.repeat(inp,21))(context)
 
-    #equal to matrix mul!!! since len(embedded.shape)==3 count(weight)==len(embedded.shape[-1])
-    #embedded = Dense(params['rnn_last_score_num'],activation=None,use_bias=False)(embedded)
-    #weightavg = Dense(params['rnn_last_score_num'],activation=None,use_bias=False)(weightavg)
-    #context = Dense(params['rnn_last_score_num'],activation=None,use_bias=False)(context)
     context = BatchNormalization()(context)
     weightavg = BatchNormalization()(weightavg)
     
@@ -90,7 +90,7 @@ def model(params):
     rnn_embedded = Lambda(lambda inp: K.sum(inp, axis=-1, keepdims=False),name='last_score')(score)
     #magic
     rnn_embedded = Dropout(rate=0.05)(rnn_embedded)
[…]

### 2020-09-25 Train/WTConst.py

@@ -12,7 +12,7 @@ CNNParams = {
     }
 RNNParams = {
     'train_batch_size':128,
-    'train_epochs_num':400,
+    'train_epochs_num':75,
     'train_base_learning_rate':0.001,
     'rnn_save_file':'WTBestRNN.h5',
     ##from 30

### 2020-09-26 Paper/main.tex
paper

@@
  One of these disadvantage is due to point mutations caused by off-target effects \citep{rubeis2018risks,kang2016introducing,ishii2017reproductive,liang2015crispr/cas9-mediated}. 
- To overcome this disadvantage, a solution is to engineer CRISPR/Cas9 with higher specificities. 
+ To overcome this disadvantage, a solution is to engineer CRISPR / Cas9 with higher specificities. 
  That's why more and more higher specificities Cas9 variants, such as enhanced SpCas9 (eSpCas9(1.1)), 
@@
  for example, the G adjacent to PAM has a positive effect on sgRNA activity as \citeauthor{wang2019optimized} report, 
- which we'll call the first-order preference in our paper, due to it's similar to the total differential of $y$ in Equation \ref{eq:01} as following
+ which we'll call the first-order preference in our paper, due to it's similar to the total differential of $y$ in Equation~(\ref{eq:01}) as following
 \begin{equation}
@@
  In other words, we build a additive model for the first-order preference, 
- which means that the first-order preference of the $i$-th position $\widetilde{A_i}$ can be calculated as
+ which means that the first-order preference of the $i$-th position $\widetilde{A}_i$ can be calculated as
 \begin{equation}
-\widetilde{A}_i=\sum_j^lB_{ij}A_i\label{eq:06}\vspace*{-10pt}
+\widetilde{A}_i=\sum_j^lB_{ij}A_j\label{eq:06}\vspace*{-10pt}
 \end{equation}\\
- Suppose that in Equation \ref{eq:06} the first-order original preference at each position is relatively independent and weight matrix B is independent of any first-order original preference, 
+ Assume that in Equation~(\ref{eq:06}) the first-order original preference at each position is relatively independent and weight matrix B is independent of any first-order original preference, 
  then the total differential of the first-order preference at $i$-th position could be written as
@@
 \begin{figure}[!tpb]%figure2
-\centerline{\includegraphics[scale=0.4]{category.png}}
+\centerline{\includegraphics[scale=0.45]{category.png}}
 \caption{Two categories of the deep learning models used in sgRNA related task. 
@@
  Most of the deep neural network existing are the combination of recurrent neural network (RNN), convolutional neural network (CNN), fully connected neural network (FNN), and their variants. 
+ As Figure~1\vphantom{\ref{fig:01}} show,  
  We found that the deep learning models used in sgRNA on-target activity (even for off-target effect) prediction tasks in recent years can be divided into the following two categories according to the encoding approach of the sgRNA sequence (sgRNA-DNA sequence pair, for off-target effect prediction):
@@
 
-\subsection{Sequence encoding}
+\subsection{Sequence encoding and embedding}
 
-Equation \ref{eq:01} is the inventory flow formula.
-Text
+For encoding process, we use the complementary base to represent the original base in sgRNA, as others do. 
+Further, we use one-hot encode strategy, which's is to say, we encoding each base in sgRNA into a four-dimensional vector 
+(encode A,T,G,C into [1,0,0,0], [0,1,0,0], [0,0,1,0], [0,0,0,1], respectively), called one-hot vector. 
+Then a sgRNA can be considered as a matrix $X_{oh}\in\mathbb{R}^{L\times 4} $, named one-hot matrix (a little sparse, since an one-hot vector is zero in all but one dimension). 
+We believe it is meaningful to regard $X_{oh}$ as a binary image, 
+therefore, it is used as an input of convolutional neural network, which performs well in the image field.
+Meanwhile, as mentioned above, one-hot matrix is a little sparse.
 
-\subsection{Sequence and biological features embedding}
+To facilitate the training process, we can mapping each one-hot vector into a dense real-valued high-dimensional space, which is called embedding. 
+Concretely speaking, at the matrix level, the formula is as follows
+\begin{equation}
+X_e=X_{oh}E_m\label{eq:08}\vspace*{-10pt}
+\end{equation}\\
+where $X_e$ named embedding matrix, $E_m\in\mathbb{R}^{4\times m}$ is a trainable transformational matrix, $m$ refers to the dimension of embedding space. 
+We believe it is also meaningful to regard nucleotides in the sgRNA sequence as word, and the sgRNA sequence itself as a sentence, 
+Guided by this belief $E_m$ is the word embedding matrix and $X_e$ is the sentence embedding in natural language processing (NLP).
+Therefore, $X_e$ is used as an input of recurrent neural network (or its variant), which performs well in the NLP field.
+In the area of NLP, there have been many methods based on pre-training and unsupervised learning been developed to determine the $E_m$. 
+However, we believe that sgRNA sequence is not a natural language in the true sense, the method above does not apply to it. 
+So $E_m$ will be trained along with the model as a whole.
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
+Due to each element of $X_{oh}$ is interpretable (representing whether there is a corresponding nucleotide type at the corresponding location), 
+we call $X_{oh}$ the spatial input, and the convolutional neural network work on $X_{oh}$ is method in spatial domain. 
+In other hand, different from $X_{oh}$, $X_e$ can only be explained in the first dimension (representing the embedding vector of corresponding nucleotide type), 
+and embedding vector is difficult for humans to understand. 
+That's why we call $X_e$ the temporal input, and the recurrent neural network (or its variant) work on $X_e$ is method in temporal domain.
 
-\subsubsection{Spatial sequence embedding}
+\subsection{Neural network architecture}
 
-Text  Text
+Based on the categorization above, we assume that method in spatial domain and in temporal domain are heterogeneous, 
+which can satisfy the diversity premise of ensemble learning. 
+Based on assumption above and ensemble learning, we follow the stacking strategy to develop AttCRISPR 
+which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
+Further, we use attention mechanisms in both spatial and temporal domain respectively to enhance the interpretability of AttCRISPR.
 
-\subsubsection{Temporal sequence embedding}
+\subsubsection{Method and attention in spatial domain}
 
@@
 
-\subsubsection{biological features embedding}
+\subsubsection{Method and attention in temporal domain}
 
@@
 
-\subsubsection{Spatial attention module}
+\subsubsection{Model ensemble following stacking strategy}
 
@@
 
-\subsubsection{Temporal attention module}
-
-Text
-
-\subsection{Neural network architecture}
-
-\begin{figure}[!tpb]%figure2
-    \centerline{\includegraphics[scale=0.5]{category.png}}
-    \caption{The overview of AttCRISPR. 
-    It consists of two components, namely CNNs and RNNs. 
-    The CNN component is used to capture spatial nucleotide preference, 
-    while the RNN component is used to capture temporal nucleotide preference. 
-    Finally, a weighted average method with trainable weight is used to predict activity.}\label{fig:02}
-\end{figure}
-
-\subsubsection{Ensemble method boosting model}
-
-Text
-
-\subsection{Datasets and current prediction algorithms}
+\subsection{Datasets and current prediction method}
 
@@
 
-{\ldots}{\ldots} text follows.
-\begin{equation}
-\sum \text{\it x}+ \text{\it y} =\text{\it Z}\label{eq:0}\vspace*{-10pt}
-\end{equation}
-
-{\ldots}{\ldots} text follows.
-
-{\ldots}{\ldots} text follows.
-\begin{equation}
-    \partial y = \sum^{len}_ia_i\partial x_i\label{eq:02}\vspace*{-10pt}
-\end{equation}
-
-%\enlargethispage{12pt}
-\begin{methods}
 \section{Results}
@@
 Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-text\vspace*{1pt}
-
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-
-\subsection{This is subheading}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-\subsubsection{This is subsubheading}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text.
+Text Text  Text Text Text Text Text
 
@@
 Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
 
@@
 
-\end{methods}
-
 \begin{figure}[!tpb]%figure1
-\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{235pt} \vbox to 100pt{\vfill\hbox to
-235pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
+\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{200pt} \vbox to 100pt{\vfill\hbox to
+200pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
 \end{minipage}}
-%\centerline{\includegraphics[scale=0.6]{category.png}}
 \caption{Caption, caption.}\label{fig:02}
@@
 Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text
 
@@
 Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
+Text Text  Text
 
@@
 Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text.
-
-Table~\ref{Tab:01} shows that Text Text Text Text Text  Text Text
-Text Text Text Text. Figure~2\vphantom{\ref{fig:02}} shows that
-the above method Text Text. Text Text Text  Text Text Text Text
-Text Text. Figure~2\vphantom{\ref{fig:02}} shows that the above
-method Text Text. Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
-Text.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%     please remove the " % " symbol from \centerline{\includegraphics{fig01.eps}}
-%     as it may ignore the figures.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Text
 
@@
 Text Text Text Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
 
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-\begin{enumerate}
-\item this is item, use enumerate
-\item this is item, use enumerate
-\item this is item, use enumerate
-\end{enumerate}
 
@@
 above method  Text Text Text Text Text Text Text Text Text Text
-Text Text.  \citealp{Boffelli03} might want to know about text
-text text text Text Text Text Text Text Text  Text Text Text Text
-Text Text Text Text Text Text Text Text Text Text Text.
 Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
 Text Text Text Text Text Text Text\break Text.

### 2020-09-27 PaperDrawer/Assets/CurveDrawer.cs
9-27 not drawer now

@@ -1,81 +1,0 @@
-﻿using System.Collections;
-using System.Collections.Generic;
-using UnityEngine;
-
-[RequireComponent(typeof(LineRenderer))]
-[ExecuteInEditMode]
-public class CurveDrawer : MonoBehaviour
-{
-    public int segmentNum;
-    public GameObject[] ControlObject;
-    private Curver curver;
-    private LineRenderer lineRenderer;
-    // Start is called before the first frame update
-    void Start()
-    {
-        curver = new Bezier();
-        lineRenderer = GetComponent<LineRenderer>();
-    }
-
-    // Update is called once per frame
-    void Update()
-    {
-        if (curver == null)
-            curver = new Bezier();
-        List<Vector3> position = new List<Vector3>();
-        for (int i = 0; i < ControlObject.Length; i++)
-        {
-            position.Add(ControlObject[i].transform.position);
-        }
-        curver.SetControlPoint(position);
-        var segments = curver.GetPosition(segmentNum);
-        lineRenderer.positionCount = segments.Count;
-        lineRenderer.SetPositions(segments.ToArray());
-    }
-}
-public abstract class Curver
-{
-    public abstract void SetControlPoint(IEnumerable<Vector3> controlpoints);
-    public abstract List<Vector3> GetPosition(int segmentNum);
-}
-//order = 3
-public class Bezier : Curver
-{
-    private Vector3[] controlPoints = new Vector3[4];
-    private List<Vector3> lastSegment;
-    private int lastSegmentNum;
-    private bool hasChangedAfterLast = true;
-    public override List<Vector3> GetPosition(int segmentNum)
-    {
-        if (segmentNum == lastSegmentNum && !hasChangedAfterLast)
-            return lastSegment;
-        List<Vector3> r = new List<Vector3>();
-        float t = 0;
-        float dt = 1.0f / segmentNum;
-        Vector3 now;
-        for (int i = 0; i < segmentNum; i++) 
-        {
-            now = (1 - t) * (1 - t) * (1 - t) * controlPoints[0] +
-                3 * t * (1 - t) * (1 - t) * controlPoints[1] +
-                3 * t * t * (1 - t) * controlPoints[2] +
-                t * t * t * controlPoints[3];
-            r.Add(now);
-            t += dt;
-        }
-        lastSegmentNum = segmentNum;
-        hasChangedAfterLast = false;
-        return r;
-    }
-
[…]

### 2020-09-27 PaperDrawer/Assets/Script/BlendCamera.cs

@@ -1,46 +1,0 @@
-﻿using System.Collections;
-using System.Collections.Generic;
-using UnityEngine;
-using UnityEngine.Rendering;
-[ExecuteInEditMode]
-[RequireComponent(typeof(Camera))]
-public class BlendCamera : MonoBehaviour
-{
-    public RenderTexture rt_posteff;
-    public Camera posteffCam;
-    public Shader blend;
-    private Material m_blend;
-
-    private int camwidth, camheight;
-    private Camera mainCam;
-    // Start is called before the first frame update
-    void Awake()
-    {
-        mainCam = GetComponent<Camera>();
-        camwidth = mainCam.pixelWidth;
-        camheight = mainCam.pixelHeight;
-        rt_posteff = new RenderTexture(camwidth, camheight, 0);
-        posteffCam.targetTexture = rt_posteff;
-    }
-    private void OnRenderImage(RenderTexture source, RenderTexture destination)
-    {
-        if (m_blend == null)
-        {
-            m_blend = new Material(blend);
-        }
-        m_blend.SetTexture("_PosteffTex", rt_posteff);
-        m_blend.SetTexture("_SourceTex", source);
-        Graphics.Blit(source, destination, m_blend);
-    }
-    // Update is called once per frame
-    void Update()
-    {
-        if (mainCam.pixelHeight != camheight || mainCam.pixelWidth != camwidth)
-        {
-            camwidth = mainCam.pixelWidth;
-            camheight = mainCam.pixelHeight;
-            rt_posteff = new RenderTexture(camwidth, camheight, 0);
-            posteffCam.targetTexture = rt_posteff;
-        }
-    }
-}

### 2020-09-27 PaperDrawer/Assets/Script/BlendOP.cs

@@ -1,56 +1,0 @@
-﻿using System.Collections;
-using System.Collections.Generic;
-using UnityEngine;
-
-[ExecuteInEditMode]
-[RequireComponent(typeof(Camera))]
-public class BlendOP : MonoBehaviour
-{
-    public RenderTexture rt_posteff;
-    public Camera posteffCam;
-    public Shader blend;
-    private Vector4 rt_posteff_st;
-    [Range(-1, 1)]
-    public float offset_x;
-    [Range(-1, 1)]
-    public float offset_y;
-    private Material m_blend;
-
-    private int camwidth, camheight;
-    private Camera mainCam;
-    // Start is called before the first frame update
-    void Awake()
-    {
-        mainCam = GetComponent<Camera>();
-        camwidth = mainCam.pixelWidth;
-        camheight = mainCam.pixelHeight;
-        rt_posteff = new RenderTexture(camwidth, camheight,0);
-        posteffCam.targetTexture = rt_posteff;
-    }
-    private void OnRenderImage(RenderTexture source, RenderTexture destination)
-    {
-        if (m_blend == null)
-        {
-            m_blend = new Material(blend);
-        }
-        rt_posteff_st.z = offset_x;
-        rt_posteff_st.w = offset_y;
-        rt_posteff_st.x = 1;// - offset_x;
-        rt_posteff_st.y = 1;// - offset_y;
-        m_blend.SetTexture("_PosteffTex", rt_posteff);
-        m_blend.SetVector("_PosteffTex_ST", rt_posteff_st);
-        m_blend.SetTexture("_SourceTex", source);
-        Graphics.Blit(source, destination, m_blend);
-    }
-    // Update is called once per frame
-    void Update()
-    {
-        if (mainCam.pixelHeight != camheight || mainCam.pixelWidth != camwidth)
-        {
-            camwidth = mainCam.pixelWidth;
-            camheight = mainCam.pixelHeight;
-            rt_posteff = new RenderTexture(camwidth, camheight, 0);
-            posteffCam.targetTexture = rt_posteff;
-        }
-    }
-}

### 2020-09-27 PaperDrawer/Assets/Script/ConnectRect.cs

@@ -1,56 +1,0 @@
-﻿using System.Collections;
-using System.Collections.Generic;
-using UnityEngine;
-
-[ExecuteInEditMode]
-public class ConnectRect : MonoBehaviour
-{
-    public GameObject cude1,cude2;
-    public Camera cam1, cam2, maincam;
-    public Vector2 offset1;
-    public Material mat;
-    private Vector2 cude1FrontTopRightinScreen;
-    private Vector2 cude1FrontBottomRightinScreen;
-    private Vector2 cude2FrontTopLeftScreen;
-    private Vector2 cude2FrontBottomLeftScreen;
-
-    // Start is called before the first frame update
-    void Start()
-    {
-        cude1FrontTopRightinScreen = GetScreenPos(new Vector4(0.5f, 0.5f, 0.5f, 1), cude1, cam1, offset1);
-        cude1FrontBottomRightinScreen = GetScreenPos(new Vector4(0.5f, -0.5f, 0.5f, 1), cude1, cam1, offset1);
-        cude2FrontTopLeftScreen = GetScreenPos(new Vector4(-0.5f, 0.5f, 0.5f, 1), cude2, cam2);
-        cude2FrontBottomLeftScreen = GetScreenPos(new Vector4(-0.5f, -0.5f, 0.5f, 1), cude2, cam2);
-    }
-    private void OnGUI()
-    {
-        GUI.Button(new Rect(cude1FrontBottomRightinScreen.x, maincam.pixelHeight - cude1FrontBottomRightinScreen.y, 100, 100),"hi");
-    }
-    private void OnPostRender()
-    {
-        GL.PushMatrix();
-        GL.LoadOrtho();
-        GL.Color(Color.white);
-        mat.SetPass(0);
-        GL.Begin(GL.LINES);
-
-        GL.Vertex3(cude1FrontTopRightinScreen.x / maincam.pixelWidth, 1-cude1FrontTopRightinScreen.y / maincam.pixelHeight, -9);
-        GL.Vertex3(0, 0, 9);
-        //GL.Vertex3(cude2FrontTopLeftScreen.x / maincam.pixelWidth, 1-cude2FrontTopLeftScreen.y / maincam.pixelHeight,-9);
-        GL.End();
-        GL.PopMatrix();
-    }
-    
-    Vector2 GetScreenPos(Vector4 objectpos, GameObject game, Camera cam)
-    {
-        return GetScreenPos(objectpos, game, cam, Vector2.zero);
-    }
[…]

### 2020-09-27 PaperDrawer/Assets/Script/EdgeDetectNormalsAndDepth.cs

@@ -1,46 +1,0 @@
-﻿using UnityEngine;
-using System.Collections;
-
-public class EdgeDetectNormalsAndDepth : PostEffectsBase {
-
-	public Shader edgeDetectShader;
-	private Material edgeDetectMaterial = null;
-	public Material material {  
-		get {
-			edgeDetectMaterial = CheckShaderAndCreateMaterial(edgeDetectShader, edgeDetectMaterial);
-			return edgeDetectMaterial;
-		}  
-	}
-
-	[Range(0.0f, 1.0f)]
-	public float edgesOnly = 0.0f;
-
-	public Color edgeColor = Color.black;
-
-	public Color backgroundColor = Color.white;
-
-	public float sampleDistance = 1.0f;
-
-	public float sensitivityDepth = 1.0f;
-
-	public float sensitivityNormals = 1.0f;
-	
-	void OnEnable() {
-		GetComponent<Camera>().depthTextureMode |= DepthTextureMode.DepthNormals;
-	}
-
-	[ImageEffectOpaque]
-	void OnRenderImage (RenderTexture src, RenderTexture dest) {
-		if (material != null) {
-			material.SetFloat("_EdgeOnly", edgesOnly);
-			material.SetColor("_EdgeColor", edgeColor);
-			material.SetColor("_BackgroundColor", backgroundColor);
-			material.SetFloat("_SampleDistance", sampleDistance);
-			material.SetVector("_Sensitivity", new Vector4(sensitivityNormals, sensitivityDepth, 0.0f, 0.0f));
-
-			Graphics.Blit(src, dest, material);
-		} else {
-			Graphics.Blit(src, dest);
-		}
-	}
-}

### 2020-09-27 PaperDrawer/ConvolutionTexture/ConvolutionTexture/Program.cs

@@ -1,123 +1,0 @@
-﻿using System;
-using System.Collections.Generic;
-using System.Linq;
-using System.Text;
-using System.IO;
-using System.Threading.Tasks;
-using System.Drawing;
-using System.Runtime.InteropServices;
-
-namespace ConvolutionTexture
-{
-    class Program
-    {
-        static StringBuilder rootPath { get { return new StringBuilder(@"../../../../DrawerData/"); } }
-        static string sgRNADirectory = rootPath.Append("Convolution/").ToString();
-        static string allinput = rootPath.Append("Convolution/singleall.out").ToString();
-        static string outputPath = rootPath.Append("convolution{0}.png").ToString();
-        static void Main(string[] args)
-        {
-            double[,,] datas = new double[21, 4, 60];
-            using (FileStream fs = new FileStream(allinput, FileMode.Open, FileAccess.Read))
-            {
-                StreamReader sr = new StreamReader(fs);
-                var ss = sr.ReadToEnd().Split(',');
-                int ssindex = 0;
-                for (int i = 0; i < datas.GetLength(0); i++)
-                {
-                    for (int j = 0; j < datas.GetLength(1); j++)
-                    {
-                        for (int k = 0; k < datas.GetLength(2); k++)
-                        {
-                            datas[i, j, k] = Convert.ToDouble(ss[ssindex++]);  
-                        }
-                    }
-                }
-            }
-            for (int k = 0; k < datas.GetLength(2); k++)
-            {
-                double max = double.MinValue;
-                double min = double.MaxValue;
-                for (int i = 0; i < datas.GetLength(0); i++)
-                {
-                    for (int j = 0; j < datas.GetLength(1); j++)
-                    {
-                        max = (max > datas[i, j, k]) ? max : datas[i, j, k];
-                        min = (min > datas[i, j, k]) ? datas[i, j, k] : min;
-                    }
-                }
-                double scale = (max - min);
-                for (int i = 0; i < datas.GetLength(0); i++)
-                {
-                    for (int j = 0; j < datas.GetLength(1); j++)
-                    {
-                        datas[i, j, k] += min;
-                        if (scale == 0)
-                            datas[i, j, k] = 0.5;
-                        else
-                            datas[i, j, k] /= scale;
-                    }
-                }
-            }
-            CudeTexture(datas, 3, 20);
-        }
-        /// <summary>
-        /// 
-        /// </summary>
[…]

### 2020-09-27 PaperDrawer/ConvolutionTexture/ConvolutionTexture/Properties/AssemblyInfo.cs

@@ -1,36 +1,0 @@
-﻿using System.Reflection;
-using System.Runtime.CompilerServices;
-using System.Runtime.InteropServices;
-
-// 有关程序集的一般信息由以下
-// 控制。更改这些特性值可修改
-// 与程序集关联的信息。
-[assembly: AssemblyTitle("ConvolutionTexture")]
-[assembly: AssemblyDescription("")]
-[assembly: AssemblyConfiguration("")]
-[assembly: AssemblyCompany("")]
-[assembly: AssemblyProduct("ConvolutionTexture")]
-[assembly: AssemblyCopyright("Copyright ©  2020")]
-[assembly: AssemblyTrademark("")]
-[assembly: AssemblyCulture("")]
-
-// 将 ComVisible 设置为 false 会使此程序集中的类型
-//对 COM 组件不可见。如果需要从 COM 访问此程序集中的类型
-//请将此类型的 ComVisible 特性设置为 true。
-[assembly: ComVisible(false)]
-
-// 如果此项目向 COM 公开，则下列 GUID 用于类型库的 ID
-[assembly: Guid("bc93552d-e8dc-45ce-89bd-654f49ffd7fb")]
-
-// 程序集的版本信息由下列四个值组成: 
-//
-//      主版本
-//      次版本
-//      生成号
-//      修订号
-//
-//可以指定所有这些值，也可以使用“生成号”和“修订号”的默认值
-//通过使用 "*"，如下所示:
-// [assembly: AssemblyVersion("1.0.*")]
-[assembly: AssemblyVersion("1.0.0.0")]
-[assembly: AssemblyFileVersion("1.0.0.0")]

### 2020-09-27 PaperDrawer/EmbeddingTexture/EmbeddingTexture/Program.cs

@@ -1,340 +1,0 @@
-﻿using System;
-using System.IO;
-using System.Collections.Generic;
-using System.Linq;
-using System.Text;
-using System.Threading.Tasks;
-using System.Drawing;
-
-namespace EmbeddingTexture
-{
-    struct HSI
-    {
-        public double H, S, I;
-        private double agreeH { get { return 180 * H / Math.PI; } }
-        public Color toRGBA()
-        {
-            double r = 0,
-                g = 0,
-                b = 0;
-            if (agreeH < 120)
-            {
-                b = I * (1 - S);
-                r = I * (1 +
-                    (
-                    S * Math.Cos(H) / Math.Cos(60.0 / 180.0 * Math.PI - H)
-                    ));
-                g = 3 * I - (r + b);
-            }
-            else if (agreeH < 240)
-            {
-                double newH = H - 120.0 / 180.0 * Math.PI;
-                r = I * (1 - S);
-                g = I * (1 +
-                    (
-                    S * Math.Cos(newH) / Math.Cos(60.0 / 180.0 * Math.PI - newH)
-                    ));
-                b = 3 * I - (r + g);
-            }
-            else
-            {
-                double newH = H - 240.0 / 180.0 * Math.PI;
-                g = I * (1 - S);
-                b = I * (1 +
-                    (
-                    S * Math.Cos(newH) / Math.Cos(60.0 / 180.0 * Math.PI - newH)
-                    ));
-                r = 3 * I - (g + b);
-            }
-            return Color.FromArgb((int)(r * 256), (int)(g * 256), (int)(b * 256));
-        }
-        static public HSI fromRGBA(Color color)
-        {
-            return fromRGBA(color.R, color.G, color.B);
-        }
-        static public HSI fromRGBA(int R, int G, int B)
-        {
-            double r = (double)R / 256.0;
-            double g = (double)G / 256.0;
-            double b = (double)B / 256.0;
-            HSI hsi = new HSI();
-            double theta = Math.Acos(
-                ((r-g)+(r-b))/2.0
-                / Math.Sqrt((r-g)*(r-g)+(r-b)*(g-b))
-                );
-            hsi.H = (b <= g) ? theta : 2 * Math.PI - theta;
-            hsi.I = (double)(r + g + b) / 3;
-            double minrgb = Math.Min(r, Math.Min(g, b));
-            hsi.S = 1 -
-                3 / (r + g + b) * minrgb;
-            return hsi;
-        }
-    }
[…]

### 2020-09-27 PaperDrawer/EmbeddingTexture/EmbeddingTexture/Properties/AssemblyInfo.cs

@@ -1,36 +1,0 @@
-﻿using System.Reflection;
-using System.Runtime.CompilerServices;
-using System.Runtime.InteropServices;
-
-// 有关程序集的一般信息由以下
-// 控制。更改这些特性值可修改
-// 与程序集关联的信息。
-[assembly: AssemblyTitle("EmbeddingTexture")]
-[assembly: AssemblyDescription("")]
-[assembly: AssemblyConfiguration("")]
-[assembly: AssemblyCompany("")]
-[assembly: AssemblyProduct("EmbeddingTexture")]
-[assembly: AssemblyCopyright("Copyright ©  2020")]
-[assembly: AssemblyTrademark("")]
-[assembly: AssemblyCulture("")]
-
-// 将 ComVisible 设置为 false 会使此程序集中的类型
-//对 COM 组件不可见。如果需要从 COM 访问此程序集中的类型
-//请将此类型的 ComVisible 特性设置为 true。
-[assembly: ComVisible(false)]
-
-// 如果此项目向 COM 公开，则下列 GUID 用于类型库的 ID
-[assembly: Guid("99353c49-b279-4685-8847-8d61e2da6406")]
-
-// 程序集的版本信息由下列四个值组成: 
-//
-//      主版本
-//      次版本
-//      生成号
-//      修订号
-//
-//可以指定所有这些值，也可以使用“生成号”和“修订号”的默认值
-//通过使用 "*"，如下所示:
-// [assembly: AssemblyVersion("1.0.*")]
-[assembly: AssemblyVersion("1.0.0.0")]
-[assembly: AssemblyFileVersion("1.0.0.0")]

### 2020-09-27 PaperDrawer/OneHotTexture/OneHotTexture/Program.cs

@@ -1,46 +1,0 @@
-﻿using System;
-using System.Collections.Generic;
-using System.Linq;
-using System.Text;
-using System.Threading.Tasks;
-using System.Drawing;
-
-namespace OneHotTexture
-{
-    class Program
-    {
-        static char[] sgRNA = "GTTGAGAAGGACCGCCACAAC".ToCharArray();
-        static Dictionary<char, int[]> base2onehot = new Dictionary<char, int[]>
-        {
-            {'A',new int[4]{1,0,0,0} },
-            {'T',new int[4]{0,1,0,0} },
-            {'G',new int[4]{0,0,1,0} },
-            {'C',new int[4]{0,0,0,1} }
-
-        };
-        static string outputpath = @"./onehot.png";
-        static void Main(string[] args)
-        {
-            Bitmap img = new Bitmap(1024, 1024);
-            int[,] onehot = new int[21, 4];
-            for (int i = 0; i < onehot.GetLength(0); i++)
-            {
-                var nowonehot = base2onehot[sgRNA[i]];
-                for (int j = 0; j < onehot.GetLength(1); j++)
-                {
-                    onehot[i, j] = nowonehot[j];
-                }
-            }
-            for (int w = 0; w < img.Width; w++)
-            {
-                for (int h = 0; h < img.Height; h++)
-                {
-                    int i = w * onehot.GetLength(0) / (img.Width + 1);
-                    int j = h * onehot.GetLength(1) / (img.Height + 1);
-                    img.SetPixel(h, w, (onehot[i, j] == 0) ? Color.Black : Color.White);
-                }
-            }
-            img.Save(outputpath);
-        }
-    }
-}

### 2020-09-27 PaperDrawer/OneHotTexture/OneHotTexture/Properties/AssemblyInfo.cs

@@ -1,36 +1,0 @@
-﻿using System.Reflection;
-using System.Runtime.CompilerServices;
-using System.Runtime.InteropServices;
-
-// 有关程序集的一般信息由以下
-// 控制。更改这些特性值可修改
-// 与程序集关联的信息。
-[assembly: AssemblyTitle("OneHotTexture")]
-[assembly: AssemblyDescription("")]
-[assembly: AssemblyConfiguration("")]
-[assembly: AssemblyCompany("")]
-[assembly: AssemblyProduct("OneHotTexture")]
-[assembly: AssemblyCopyright("Copyright ©  2020")]
-[assembly: AssemblyTrademark("")]
-[assembly: AssemblyCulture("")]
-
-// 将 ComVisible 设置为 false 会使此程序集中的类型
-//对 COM 组件不可见。如果需要从 COM 访问此程序集中的类型
-//请将此类型的 ComVisible 特性设置为 true。
-[assembly: ComVisible(false)]
-
-// 如果此项目向 COM 公开，则下列 GUID 用于类型库的 ID
-[assembly: Guid("9267e348-025c-4e54-95c0-e48ce7d11ad9")]
-
-// 程序集的版本信息由下列四个值组成: 
-//
-//      主版本
-//      次版本
-//      生成号
-//      修订号
-//
-//可以指定所有这些值，也可以使用“生成号”和“修订号”的默认值
-//通过使用 "*"，如下所示:
-// [assembly: AssemblyVersion("1.0.*")]
-[assembly: AssemblyVersion("1.0.0.0")]
-[assembly: AssemblyFileVersion("1.0.0.0")]

### 2020-09-28 Paper/main.tex
paper
9-28 cnn

@@
 which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
-Further, we use attention mechanisms in both spatial and temporal domain respectively to enhance the interpretability of AttCRISPR.
+Further, we apply attention mechanisms in both spatial and temporal domain respectively to enhance the interpretability of AttCRISPR.
 
@@
 
-Text
+\begin{figure}[!tpb]%figure2
+    \centerline{\includegraphics[scale=0.15]{newcnn.png}}
+    \caption{Two categories of the deep learning models used in sgRNA related task. 
+    (a) Model work in spatial domain. (b) Model work in temporal domain.}\label{fig:02}
+\end{figure}
+As Figure~1\vphantom{\ref{fig:02}} show,
 

### 2020-09-30 Paper/main.tex
9-30 paper

@@
 (encode A,T,G,C into [1,0,0,0], [0,1,0,0], [0,0,1,0], [0,0,0,1], respectively), called one-hot vector. 
-Then a sgRNA can be considered as a matrix $X_{oh}\in\mathbb{R}^{L\times 4} $, named one-hot matrix (a little sparse, since an one-hot vector is zero in all but one dimension). 
+Then a sgRNA can be considered as a matrix $X_{oh}\in\mathbb{R}^{l\times4} $, named one-hot matrix (a little sparse, since an one-hot vector is zero in all but one dimension). 
 We believe it is meaningful to regard $X_{oh}$ as a binary image, 
@@
 \begin{figure}[!tpb]%figure2
-    \centerline{\includegraphics[scale=0.15]{newcnn.png}}
-    \caption{Two categories of the deep learning models used in sgRNA related task. 
-    (a) Model work in spatial domain. (b) Model work in temporal domain.}\label{fig:02}
+    \centerline{\includegraphics[scale=0.15]{CNNv2.png}}
+    \caption{The architecture of spatial domain method in AttCRISPR. 
+    The input of the method is encoded sgRNA sequence, a $21\times 4$ one-hot matrix. 
+    Then refine it through a spatial attention module, which could tell us the importance of a specific matrix element (or just say, pixel).
+    Finally, a simple convolutional neural network is applied.}\label{fig:02}
 \end{figure}
-As Figure~1\vphantom{\ref{fig:02}} show,
+As Figure~2\vphantom{\ref{fig:02}} show, method in spatial domain relies on the convolutional neural network. 
+As previously mentioned, sgRNA sequence has been encoded into a $21\times 4$ one-hot matrix $X_{oh}$, and we regard $X_{oh}$ as a binary image. 
+Then, convolution kernels with different size are used to extract potential spatial features just like what other do in computer vision. 
+According to the foregoing, the Spatial Attention Module proposed by \citeauthor{woo2018cbam:} can be applied in our method in spatial domain, 
+which was used to improve the performance of CNN in vision tasks.
+
+\begin{figure}[!tpb]%figure3
+    \centerline{\includegraphics[scale=0.37]{spatialmodule.png}}
+    \caption{Details of spatial attention module. A convolution layer is used to generate multi-channel map from $X_{oh}$.
+    Then concatenated the output of both max-pooling and average-pooling method and forward it to the last convolution layer.
+    A sigmoid is used to map the final result to a range of zero to one.
+    }\label{fig:03}
+\end{figure}
+
+As Figure~3\vphantom{\ref{fig:03}} show, Given an one-hot map $X_{oh}$, spatial attention module generating spatial attention matrix 
+$M_s\in\mathbb{R}^{l\times 4}$ with the same as $X_{oh}$ in shape. 
+Each element of $M_s$ is constrained to a range of zero to one, implemented by a sigmoid function, which reflects the importance of the corresponding elements of $X_{oh}$.
+The overall spatial attention process can be summarized as:
+\begin{equation}
+X_{mc} = f^{3\times4}(X_{oh})\label{eq:09}\vspace*{-10pt}
+\end{equation}
+
+\begin{equation}
+M_s = \sigma(f^{3\times2}([AvgPool(X_{mc});MaxPool(X_{mc})]))\label{eq:10}\vspace*{-10pt}
+\end{equation}
+
+\begin{equation}
+X_{rf} = M_s\otimes X_{oh}\label{eq:11}\vspace*{-10pt}
+\end{equation}\\
+
+where $f^{p\times q}$ represents a convolution operation with the filter size of $p\times q$, 
+$p,q\in\mathbb{Z}^{+}$, $X_{mc}$ is a multi-channel map generated by $X_{oh}$, $\sigma$ denotes the sigmoid function, 
+AvgPool denotes the average-pooling operation, MaxPool denotes the max-pooling operation, $\otimes$ denotes element-wise multiplication.
+
+Spatial attention matrix $M_s$ formally conforms to our proposed definition of first-order preference (each element of $X_{oh}$ is multiplied by the corresponding element of $M_s$), 
+in other word, element of $M_s$ reveal how important the corresponding elements in $X_{oh}$ is. 
+We think it can reveal the preference of the scoring function at each position. 
+For instance, follow the encoding rules above, train spatial domain part of AttCRISPR with the WT-SpCas9 dataset. 
+Then take the average of all spatial attention matrix, and the element in the first row and third column are closer to 1, which means when calculate the final score, 
+G typically may have a important contribution at first position within sgRNA sequence. 
+In fact, this corresponds to some early studies concerning the Human (hU6) promoter, which is believed to require G as the first nucleotide of its transcript \citep{cong2013multiplex,jinek2012a,mali2013rnaguided}.
 
@@
 
-Text
+\begin{figure}[!tpb]%figure4
+    \centerline{\includegraphics[scale=0.15]{CNNv2.png}}
+    \caption{The architecture of temporal domain method in AttCRISPR. 
+    The input of the method is embedding sgRNA sequence, a $21\times e$ embedding matrix, where $e$ is the dimension of a nucleotide embedding vector. 
+    }\label{fig:04}
+\end{figure}
+As Figure~4\vphantom{\ref{fig:04}} show, method in temporal domain relies on the recurrent neural network (or its variant). 
+As previously mentioned, we mapping each one-hot vector into a dense real-valued high-dimensional space follow the Equation~(\ref{eq:08}), which generates the embedded matrix $X_e$.
+And we regard $X_{e}$ as a sequential data, or temporal data.
+Recurrent neural network (or its variant) has showed outstanding performance in the tasks with temporal data (for instance, natural language processing, sequential recommendation). 
+That's why we prefer to use it to extract potential temporal features.
 
@@
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text
+Text
 
@@
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
+Text
 
@@
 \end{table}
-
-\begin{figure}[!tpb]%figure1
-\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{200pt} \vbox to 100pt{\vfill\hbox to
-200pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
-\end{minipage}}
-\caption{Caption, caption.}\label{fig:02}
-\end{figure}
 

### 2020-10-03 Paper/main.tex
10-3 paper

@@
 \end{equation}\\
- where $W$ denotes a non-negative weight matrix, $W_i$ denotes the weight of the $i$-th position, $X_i$ denotes the embedding vector of the nucleotide at $i$-th position.
+ where $W$ denotes a non-negative weight vector, $W_i$ denotes the weight of the $i$-th position, $X_i$ denotes the embedding vector of the nucleotide at $i$-th position.
  We linearly combine the first-order preference vector of base sequence as following
 \begin{equation}
-\widetilde{A}=BA\label{eq:05}\vspace*{-10pt}
+\tilde{A}=BA\label{eq:05}\vspace*{-10pt}
 \end{equation}\\
  where the weight matrix $B$ is learned through attention mechanism, and we define $A$ as the first-order original preference matrix, 
- $\widetilde{A}$ as the first-order combine preference matrix (or just first-order preference) to differentiate them.
+ $\tilde{A}$ as the first-order combine preference matrix (or just first-order preference) to differentiate them.
  In other words, we build a additive model for the first-order preference, 
- which means that the first-order preference of the $i$-th position $\widetilde{A}_i$ can be calculated as
+ which means that the first-order preference of the $i$-th position $\tilde{A}_i$ can be calculated as
 \begin{equation}
-\widetilde{A}_i=\sum_j^lB_{ij}A_j\label{eq:06}\vspace*{-10pt}
+\tilde{A}_i=\sum_j^lB_{ij}A_j\label{eq:06}\vspace*{-10pt}
 \end{equation}\\
@@
 \begin{equation}
-d\widetilde{A}_i=\sum_j^lB_{ij}EdA_j\label{eq:07}\vspace*{-10pt}
+d\tilde{A}_i=\sum_j^lB_{ij}EdA_j\label{eq:07}\vspace*{-10pt}
 \end{equation}\\
@@
 \begin{equation}
-X_{mc} = f^{3\times4}(X_{oh})\label{eq:09}\vspace*{-10pt}
+X_{mc} = f^{3\times4}(X_{oh})\label{eq:09}
 \end{equation}
-
 \begin{equation}
-M_s = \sigma(f^{3\times2}([AvgPool(X_{mc});MaxPool(X_{mc})]))\label{eq:10}\vspace*{-10pt}
+M_s = \sigma(f^{3\times2}([AvgPool(X_{mc});MaxPool(X_{mc})]))\label{eq:10}
 \end{equation}
-
 \begin{equation}
@@
 \end{figure}
-As Figure~4\vphantom{\ref{fig:04}} show, method in temporal domain relies on the recurrent neural network (or its variant). 
+As Figure~4\vphantom{\ref{fig:04}} show, temporal domain part of AttCRISPR relies on the recurrent neural network (or its variant). 
 As previously mentioned, we mapping each one-hot vector into a dense real-valued high-dimensional space follow the Equation~(\ref{eq:08}), which generates the embedded matrix $X_e$.
@@
 That's why we prefer to use it to extract potential temporal features. 
+To be precise, we prefer the architecture of encoder-decoder which has been proven to be effective in Seq2Seq task. 
+Two main differences we have to face are that sgRNA is not a natural language in the traditional sense, and we don't have to translate it to other sequence. 
+To accommodate them, the embedded matrix $X_e$ is used as input of both the encoder and decoder, and the sequence of decoder is to build the first-order preference of sgRNA sequence $\tilde{A}$. 
+As mentioned above, the predicted value $y$ should satisfy the following equation
+\begin{equation}
+y=\sum_i^lW_i\tilde{A}_i\cdot {X_e}_i\label{eq:12}\vspace*{-10pt}
+\end{equation}\\
+where $W$ denotes a non-negative weight vector acquired through a full connection layer, $W_i$ denotes the $i$-th dimension of the vector $W$. 
+Equation~(\ref{eq:12}) is the same formally as Equation~(\ref{eq:04}). 
+On this basis, we apply the idea of attention mechanism which has been widely used in natural language processing tasks to AttCRISPR in the method of temporal domain, 
+and name it Temporal Attention Module \citep{vaswani2017attention,luong2015effective,bahdanau2014neural}.
+As the idea of \citeauthor{vaswani2017attention}, Temporal Attention Module satisfies the following equation
+\begin{equation}
+Attention(Q,K,V)=align(Q,K)V\label{eq:12}\vspace*{-10pt}
+\end{equation}\\
+where the $align(\cdot)$ is put forward by \citeauthor{luong2015effective}. 
+$Q$, $K$, $V$ are queries, keys and values matrix accordingly in the paper of \citeauthor{vaswani2017attention}. 
+Specifically, in our attention module they are calculated by the following equation
+\begin{equation}
+K_i=Encoder({X_e}_i,\theta_E,K_{i-1})\label{eq:13}
+\end{equation}
+\begin{equation}
+Q_i=Decoder({X_e}_i,\theta_D,Q_{i-1})\label{eq:14}
+\end{equation}
+\begin{equation}
+V=K\label{eq:15}\vspace*{-10pt}
+\end{equation}\\
+where vector $K_i$, $Q_i$ denotes the $i$-th row of the matrix $K$ and $Q$ accordingly, $Encoder(\cdot)$ and $Decoder(\cdot)$ are independent GRU units, $\theta_E$ and $\theta_D$ denote all the related parameters of GRU networks accordingly.
+In the actual implementation, we apply the bidirectional GRU networks for better performance, and for the sake of conciseness, we show a conventional GRU network here. 
+The function $align()$ is as follows
+\begin{equation}
+B=align(Q,K)\label{eq:16}
+\end{equation}
+\begin{equation}
+B_i=softmax(Q_iK^T)\otimes G_i\label{eq:17}
+\end{equation}
+\begin{equation}
+G_{ij}=\left\{\begin{matrix}
+exp(\frac{(i-j)^2}{-2\sigma})&,\left | i-j \right |\leqslant \sigma
+\\ 0&,\left | i-j \right |>  \sigma
+\end{matrix}\right.\label{eq:18}\vspace*{-10pt}
+\end{equation}\\
+where the matrix $B\in\mathbb{R}^{l\times l}$ is the second-order preference we need, and vector $B_i$ denotes the $i$-th row of the matrix $B$. 
+In our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in a biological sense.
 

### 2020-10-03 Train/ESPConst.py

@@ -12,12 +12,13 @@ CNNParams = {
     }
 RNNParams = {
     'train_batch_size':128,
-    'train_epochs_num':50,
-    'train_base_learning_rate':0.001,
-    'rnn_save_file':'WTBestRNN.h5',
-    'rnn_embedding_output':30,
-    'rnn_unit_num':140,
-    'rnn_last_score_num':250
+    'train_epochs_num':100,
+    'train_base_learning_rate':0.0005,
+    'rnn_save_file':'ESPBestRNN.h5',
+    'rnn_window_size':4,
+    'rnn_embedding_output':75,
+    'rnn_last_activation':'sigmoid',
+    'rnn_unit_num':100
     }
 EnsembleParams = {
     'cnn_load_file':'ESPBestCNN.h5',

### 2020-10-03 Train/SPConst.py

@@ -12,12 +12,13 @@ CNNParams = {
     }
 RNNParams = {
     'train_batch_size':128,
-    'train_epochs_num':50,
-    'train_base_learning_rate':0.001,
-    'rnn_save_file':'WTBestRNN.h5',
-    'rnn_embedding_output':30,
-    'rnn_unit_num':140,
-    'rnn_last_score_num':250
+    'train_epochs_num':400,
+    'train_base_learning_rate':0.0005,
+    'rnn_save_file':'SPBestRNN.h5',
+    'rnn_window_size':4,
+    'rnn_embedding_output':75,
+    'rnn_last_activation':'sigmoid',
+    'rnn_unit_num':100
     }
 EnsembleParams = {
     'cnn_load_file':'SPBestCNN.h5',

### 2020-10-03 Train/TrainCNN.py

@@ -65,6 +65,6 @@ if __name__ == "__main__":
     label = data['label']
     input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
                                                               label['train'],rate=0,intensity=0)
-    train(params['RNNParams'],input_train_onehot,y_train,
+    train(params['CNNParams'],input_train_onehot,y_train,
           input['validate']['onehot'],label['validate'],
           input['test']['onehot'],label['test'])

### 2020-10-03 Train/TrainRNN.py

@@ -11,7 +11,7 @@ from LearnUtil import *
 import math
 
 
-def GaussianKernelBuffer(windowsize=8):
+def GaussianKernelBuffer(windowsize):
     gaussian = lambda d: math.exp( -(d*d)*2/windowsize/windowsize ) if abs(d)<=windowsize/2 else 0
     result = []
     for i in range(21):
@@ -30,26 +30,22 @@ def GaussianKernelBuffer(windowsize=8):
             result[i][j]*=time
     return np.array(result)
 def model(params):
-    GaussianBuffer = GaussianKernelBuffer()
-
+    GaussianBuffer = GaussianKernelBuffer(params['rnn_window_size'])
     onehot_input = Input(name = 'onehot_input', shape = (21,4, 1,))
     embedded = Conv2D(params['rnn_embedding_output'], (1, 4),strides=(1,4), padding='Valid', activation=None)(onehot_input)
     embedded = Reshape((21,params['rnn_embedding_output'],))(embedded)
     embedded = SpatialDropout1D(0.25)(embedded)
     ######encoder&decoder######
-    encoder = GRU(params['rnn_unit_num'],return_sequences=True,return_state=False,unroll=True)
+    encoder = GRU(params['rnn_unit_num'],return_sequences=True,return_state=True,unroll=True)
     encoder = Bidirectional(encoder,merge_mode='sum',name='encoder')
-    encoder_output = encoder(embedded)
+    encoder_output,ec1,ec2 = encoder(embedded)
 
-    decoder_input = keras.layers.concatenate([embedded,encoder_output])
-    #decoder_input = encoder_output
+    decoder_input = embedded
     decoder = GRU(params['rnn_unit_num'],return_sequences=True,return_state=True,unroll=True,
-                  dropout=0.25,kernel_regularizer='l2',recurrent_regularizer='l2',recurrent_dropout=0.25)
+                  kernel_regularizer=keras.regularizers.l2(0.01),
+                  recurrent_regularizer=keras.regularizers.l2(0.01))
     decoder = Bidirectional(decoder,merge_mode='sum',name='decoder')
-    decoder_output,_,context = decoder(decoder_input)
-    #context = Lambda(lambda inp: inp[1]+inp[0],name='context')([c1,c2])
-    
-
+    decoder_output,dc1,dc2 = decoder(decoder_input)
     encoderat = []
     decoderat = []
     for i in range(21):
@@ -63,34 +59,39 @@ def model(params):
     for i in range(21):
         atat = []
         for j in range(21):
[…]

### 2020-10-03 Train/WTConst.py

@@ -12,14 +12,13 @@ CNNParams = {
     }
 RNNParams = {
     'train_batch_size':128,
-    'train_epochs_num':75,
+    'train_epochs_num':500,
     'train_base_learning_rate':0.001,
     'rnn_save_file':'WTBestRNN.h5',
-    ##from 30
-    'rnn_embedding_output':100,
-    ##from 140
-    'rnn_unit_num':100,
-    'rnn_last_score_num':250
+    'rnn_window_size':8,
+    'rnn_embedding_output':60,
+    'rnn_last_activation':'sigmoid',
+    'rnn_unit_num':100
     }
 EnsembleParams = {
     'cnn_load_file':'WTBestCNN.h5',

### 2020-10-03 Paper/main.tex
10-3 paper

@@
 In our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in a biological sense. 
-
+G is the damping matrix base on Gaussian function. 
+Since a simple belief that the closer the base is to the $i$-th position, the more it affects the $i$-th position normally, we use the damping matrix G to constrain the network learning. 
+$\sigma$ represents a threshold of length, any base over this length from the position $i$ is not considered to be affected.
 \subsubsection{Model ensemble following stacking strategy}

### 2020-10-04 Paper/main.tex
10-4 fix paper

@@
 \end{equation}\\
-where $W$ denotes a non-negative weight vector acquired through a full connection layer, $W_i$ denotes the $i$-th dimension of the vector $W$. 
+where $W\in\mathbb{R}^l$ denotes a non-negative weight vector acquired through a full connection layer, $W_i$ denotes the $i$-th dimension of the vector $W$. 
 Equation~(\ref{eq:12}) is the same formally as Equation~(\ref{eq:04}). 
@@
 $Q$, $K$, $V$ are queries, keys and values matrix accordingly in the paper of \citeauthor{vaswani2017attention}. 
-Specifically, in our attention module they are calculated by the following equation
+As Figure~5\vphantom{\ref{fig:05}} show, in our attention module they are calculated by the following equation
 \begin{equation}
@@
 In the actual implementation, we apply the bidirectional GRU networks for better performance, and for the sake of conciseness, we show a conventional GRU network here. 
-The function $align()$ is as follows
+The function $align(\cdot)$ is as follows
 \begin{equation}
@@
 where the matrix $B\in\mathbb{R}^{l\times l}$ is the second-order preference we need, and vector $B_i$ denotes the $i$-th row of the matrix $B$. 
-In our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in a biological sense. 
-G is the damping matrix base on Gaussian function. 
+In our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in the biological sense. 
+$G\in\mathbb{R}^{l\times l}$ is the damping matrix base on Gaussian function. 
 Since a simple belief that the closer the base is to the $i$-th position, the more it affects the $i$-th position normally, we use the damping matrix G to constrain the network learning. 

### 2020-10-04 Train/SPConst.py
10-4 train

@@ -17,7 +17,7 @@ RNNParams = {
     'rnn_save_file':'SPBestRNN.h5',
     'rnn_window_size':4,
     'rnn_embedding_output':75,
-    'rnn_last_activation':'sigmoid',
+    'rnn_last_activation':'linear',
     'rnn_unit_num':100
     }
 EnsembleParams = {

### 2020-10-04 Train/TrainRNN.py

@@ -43,9 +43,9 @@ def model(params):
     decoder_input = embedded
     decoder = GRU(params['rnn_unit_num'],return_sequences=True,return_state=True,unroll=True,
                   kernel_regularizer=keras.regularizers.l2(0.01),
-                  recurrent_regularizer=keras.regularizers.l2(0.01))
+                  recurrent_regularizer=keras.regularizers.l2(0.01),dropout=0.25,recurrent_dropout=0.25)
     decoder = Bidirectional(decoder,merge_mode='sum',name='decoder')
-    decoder_output,dc1,dc2 = decoder(decoder_input)
+    decoder_output,dc1,dc2 = decoder(decoder_input,initial_state=[ec1,ec2])
     encoderat = []
     decoderat = []
     for i in range(21):
@@ -91,7 +91,8 @@ def model(params):
     rnn_embedded = score
     #magic
     rnn_embedded = Dropout(rate=0.05)(rnn_embedded)
-    output = Dense(units=1,kernel_regularizer=keras.regularizers.l2(0.001),kernel_constraint=keras.constraints.NonNeg(),name='temporal_score',activation=params['rnn_last_activation'],use_bias=False)(rnn_embedded)
+    output = Dense(units=1,kernel_regularizer=keras.regularizers.l2(0.001),kernel_constraint=keras.constraints.NonNeg(),
+                   name='temporal_score',activation=params['rnn_last_activation'],use_bias=False)(rnn_embedded)
     model = Model(inputs=[onehot_input],
                  outputs=[output],name='rnn')
     return model
@@ -124,23 +125,10 @@ if __name__ == "__main__":
     label = data['label']
     input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
                                                               label['train'],rate=0,intensity=0)
-    train(params['RNNParams'],input_train_onehot,y_train,
-          input['validate']['onehot'],label['validate'],
-          input['test']['onehot'],label['test'])
-
-
     scores = []
-
-    embedding_output = [30,70,100,200]
-    unit_num = [30,100,200,300]
-    for i in range(4):
-        for j in range(4):
-            print('embedding: '+str(embedding_output[i]))
-            print('unit_num: '+str(unit_num[j]))
-            params['RNNParams']['rnn_embedding_output'] = embedding_output[i]
-            params['RNNParams']['rnn_unit_num'] = unit_num[j]
-            thisbest = train(params['RNNParams'],input_train_onehot,y_train,
[…]

### 2020-10-05 Paper/main.tex

@@
 \begin{equation}
-Attention(Q,K,V)=align(Q,K)V\label{eq:12}\vspace*{-10pt}
+Attention(Q,K,V)=align(Q,K)V\label{eq:13}\vspace*{-10pt}
 \end{equation}\\
@@
 \begin{equation}
-K_i=Encoder({X_e}_i,\theta_E,K_{i-1})\label{eq:13}
-\end{equation}
-\begin{equation}
-Q_i=Decoder({X_e}_i,\theta_D,Q_{i-1})\label{eq:14}
-\end{equation}
-\begin{equation}
-V=K\label{eq:15}\vspace*{-10pt}
+\left\{\begin{matrix}
+K_i=Encoder({X_e}_i,\theta_E,K_{i-1})
+\\ Q_i=Decoder({X_e}_i,\theta_D,Q_{i-1})
+\\V=K 
+\end{matrix}\right.\label{eq:14}\vspace*{-10pt}
 \end{equation}\\
@@
 where the matrix $B\in\mathbb{R}^{l\times l}$ is the second-order preference we need, and vector $B_i$ denotes the $i$-th row of the matrix $B$. 
-In our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in the biological sense. 
 $G\in\mathbb{R}^{l\times l}$ is the damping matrix base on Gaussian function. 
@@
 $\sigma$ represents a threshold of length, any base over this length from the position $i$ is not considered to be affected.
+Further, if we think of the values matrix as a vector form of the first-order preference $A$ in Equation~(\ref{eq:05}), we can reach the following equation
+\begin{equation}
+\tilde{A}=BV\label{eq:19}\vspace*{-10pt}
+\end{equation}\\
+according to above, values matrix $V$ comes from the hidden states of a bidirectional GRU networks, which is usually hard to understand and explain.
+While $B$ is the second-order preference matrix obtained by the attention mechanism, in our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in the biological sense.
 \subsubsection{Model ensemble following stacking strategy}

### 2020-10-06 Paper/main.tex
10-6 paper

@@
 \begin{equation}
-\text{\it y}=Score(\it X)\label{eq:01}\vspace*{-10pt}
-\end{equation}\\
+\text{\it y}=Score(\it X)\label{eq:01}
+\end{equation}
  where $Score(\cdot)$ depends on the algorithm being selected, and $y$ denotes the predicted value.
@@
 \begin{equation}
-dy = \sum^{d}_ia_idx_i\label{eq:02}\vspace*{-10pt}
+dy = \sum^{d}_ia_idx_i\label{eq:02}
 \end{equation}
 \begin{equation}
-a_i=\frac{\partial}{\partial x_i} Score(X)\label{eq:03}\vspace*{-10pt}
-\end{equation}\\
+a_i=\frac{\partial}{\partial x_i} Score(X)\label{eq:03}
+\end{equation}
  where $x_i$ denotes the $i$-th dimension of the vector $X$, 
@@
 \begin{equation}
-y=\sum_i^lW_iA_i\cdot X_i\label{eq:04}\vspace*{-10pt}
-\end{equation}\\
+y=\sum_i^lW_iA_i\cdot X_i\label{eq:04}
+\end{equation}
  where $W$ denotes a non-negative weight vector, $W_i$ denotes the weight of the $i$-th position, $X_i$ denotes the embedding vector of the nucleotide at $i$-th position.
@@
 \begin{equation}
-\tilde{A}=BA\label{eq:05}\vspace*{-10pt}
-\end{equation}\\
+\tilde{A}=BA\label{eq:05}
+\end{equation}
  where the weight matrix $B$ is learned through attention mechanism, and we define $A$ as the first-order original preference matrix, 
@@
 \begin{equation}
-\tilde{A}_i=\sum_j^lB_{ij}A_j\label{eq:06}\vspace*{-10pt}
-\end{equation}\\
+\tilde{A}_i=\sum_j^lB_{ij}A_j\label{eq:06}
+\end{equation}
  Assume that in Equation~(\ref{eq:06}) the first-order original preference at each position is relatively independent and weight matrix B is independent of any first-order original preference, 
@@
 \begin{equation}
-d\tilde{A}_i=\sum_j^lB_{ij}EdA_j\label{eq:07}\vspace*{-10pt}
-\end{equation}\\
+d\tilde{A}_i=\sum_j^lB_{ij}EdA_j\label{eq:07}
+\end{equation}
+
+\begin{figure}[!tpb]%figure2
+    \centerline{\includegraphics[width=86mm]{category.png}}
+    \caption{Two categories of the deep learning models used in sgRNA related task. 
+    (a) Model work in spatial domain. 
+    In spatial domain, the base sequence is encoded into a binary matrix (or a binary image). 
+    Since convolution has great advantages in extracting spatial features, the convolutional neural network is an excellent tool in spatial domain. 
+    (b) Model work in temporal domain. 
+    In temporal domain, the base sequence (represented by the binary matrix) is embedded into a sequance of high-dimensional vector, 
+    in which the recurrent neural network perform better.
+    In addition, we note that the last layers of neural network are usually full connection structure (not necessarily), 
+    which greatly increases the difficulty of understanding the decisions of model.
+    }\label{fig:01}
+\end{figure}
+
  where $E$ is the identity matrix, and we define $B$ as the second-order preference matrix, 
@@
  but also be comparable to conventional machine learning algorithms in interpretability.
-
-\begin{figure}[!tpb]%figure2
-\centerline{\includegraphics[scale=0.45]{category.png}}
-\caption{Two categories of the deep learning models used in sgRNA related task. 
-(a) Model work in spatial domain. (b) Model work in temporal domain.}\label{fig:01}
-\end{figure}
 
@@
  The most similar approach to ours is the work based on transformer by \citeauthor{Liu2019}. 
- They use transformer, a components based on attention mechanism, instead of RNN to improve the ability of temporal feature extraction, hence, enhance the performance of their model \citep{Liu2019,vaswani2017attention}.
+ They use transformer, a components based on attention mechanism, instead of RNN to improve the ability of temporal feature extraction, 
+ hence, enhance the performance of their model \citep{Liu2019,vaswani2017attention}. 
  In our work,the interpretability benefit from attention mechanism is more focused.
-
  In this paper, our main contributions are as follows:\vspace*{1pt}
@@
 \begin{equation}
-X_e=X_{oh}E_m\label{eq:08}\vspace*{-10pt}
-\end{equation}\\
+X_e=X_{oh}E_m\label{eq:08}
+\end{equation}
 where $X_e$ named embedding matrix, $E_m\in\mathbb{R}^{4\times m}$ is a trainable transformational matrix, $m$ refers to the dimension of embedding space. 
@@
 \begin{figure}[!tpb]%figure2
-    \centerline{\includegraphics[scale=0.15]{CNNv2.png}}
+    \centerline{\includegraphics[width=86mm]{CNNv2.png}}
     \caption{The architecture of spatial domain method in AttCRISPR. 
@@
 \begin{figure}[!tpb]%figure3
-    \centerline{\includegraphics[scale=0.37]{spatialmodule.png}}
+    \centerline{\includegraphics[width=86mm]{spatialmodule.png}}
     \caption{Details of spatial attention module. A convolution layer is used to generate multi-channel map from $X_{oh}$.
@@
 As Figure~3\vphantom{\ref{fig:03}} show, Given an one-hot map $X_{oh}$, spatial attention module generating spatial attention matrix 
-$M_s\in\mathbb{R}^{l\times 4}$ with the same as $X_{oh}$ in shape. 
-Each element of $M_s$ is constrained to a range of zero to one, implemented by a sigmoid function, which reflects the importance of the corresponding elements of $X_{oh}$.
+$A_s\in\mathbb{R}^{l\times 4}$ with the same as $X_{oh}$ in shape. 
+Each element of $A_s$ is constrained to a range of zero to one, implemented by a sigmoid function, which reflects the importance of the corresponding elements of $X_{oh}$.
 The overall spatial attention process can be summarized as:
 \begin{equation}
-X_{mc} = f^{3\times4}(X_{oh})\label{eq:09}
+\left\{\begin{matrix}
+X_{mc} = f^{3\times4}(X_{oh})
+\\A_s = \sigma(f^{3\times2}([AvgPool(X_{mc});MaxPool(X_{mc})]))
+\\X_{rf} = A_s\otimes X_{oh}
+\end{matrix}\right.\label{eq:11}
 \end{equation}
-\begin{equation}
-M_s = \sigma(f^{3\times2}([AvgPool(X_{mc});MaxPool(X_{mc})]))\label{eq:10}
-\end{equation}
-\begin{equation}
-X_{rf} = M_s\otimes X_{oh}\label{eq:11}\vspace*{-10pt}
-\end{equation}\\
-
 where $f^{p\times q}$ represents a convolution operation with the filter size of $p\times q$, 
@@
 
-Spatial attention matrix $M_s$ formally conforms to our proposed definition of first-order preference (each element of $X_{oh}$ is multiplied by the corresponding element of $M_s$), 
-in other word, element of $M_s$ reveal how important the corresponding elements in $X_{oh}$ is. 
+Spatial attention matrix $A_s$ formally conforms to our proposed definition of first-order preference (each element of $X_{oh}$ is multiplied by the corresponding element of $A_s$), 
+in other word, element of $A_s$ reveal how important the corresponding elements in $X_{oh}$ is. 
 We think it can reveal the preference of the scoring function at each position. 
@@
 \subsubsection{Method and attention in temporal domain}
-
 \begin{figure}[!tpb]%figure4
-    \centerline{\includegraphics[scale=0.15]{CNNv2.png}}
+    \centerline{\includegraphics[width=86mm]{temporalmodule.png}}
     \caption{The architecture of temporal domain method in AttCRISPR. 
@@
 \begin{equation}
-y=\sum_i^lW_i\tilde{A}_i\cdot {X_e}_i\label{eq:12}\vspace*{-10pt}
-\end{equation}\\
+y=\sum_i^lW_i\tilde{A}_i\cdot {X_e}_i\label{eq:12}
+\end{equation}
 where $W\in\mathbb{R}^l$ denotes a non-negative weight vector acquired through a full connection layer, $W_i$ denotes the $i$-th dimension of the vector $W$. 
@@
 \begin{equation}
-Attention(Q,K,V)=align(Q,K)V\label{eq:13}\vspace*{-10pt}
-\end{equation}\\
+Attention(Q,K,V)=align(Q,K)V\label{eq:13}
+\end{equation}
 where the $align(\cdot)$ is put forward by \citeauthor{luong2015effective}. 
@@
 \\V=K 
-\end{matrix}\right.\label{eq:14}\vspace*{-10pt}
-\end{equation}\\
+\end{matrix}\right.\label{eq:14}
+\end{equation}
 where vector $K_i$, $Q_i$ denotes the $i$-th row of the matrix $K$ and $Q$ accordingly, $Encoder(\cdot)$ and $Decoder(\cdot)$ are independent GRU units, $\theta_E$ and $\theta_D$ denote all the related parameters of GRU networks accordingly.
@@
 \\ 0&,\left | i-j \right |>  \sigma
-\end{matrix}\right.\label{eq:18}\vspace*{-10pt}
-\end{equation}\\
+\end{matrix}\right.\label{eq:18}
+\end{equation}
 where the matrix $B\in\mathbb{R}^{l\times l}$ is the second-order preference we need, and vector $B_i$ denotes the $i$-th row of the matrix $B$. 
@@
 \begin{equation}
-\tilde{A}=BV\label{eq:19}\vspace*{-10pt}
-\end{equation}\\
+\tilde{A}=BV\label{eq:19}
+\end{equation}
 according to above, values matrix $V$ comes from the hidden states of a bidirectional GRU networks, which is usually hard to understand and explain.
@@
 
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows\vadjust{\pagebreak} that the
-above method  Text Text Text Text Text Text Text Text Text Text
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text\break Text.
-
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text\vspace*{-10pt}
-
 \section*{Acknowledgements}

### 2020-10-07 Paper/main.tex
10-7 paper

@@
  which we'll call the second-order preference in our paper due to its calculation is based on first-order preference,
- Specifically, we use a vector $A_i$ to build the first-order preference at position $i$ within sgRNA sequence, then
+
+ Specifically, we use a vector $A_i$ to build the first-order original preference at position $i$ within sgRNA sequence, then
+ define $\tilde{A}$ as the first-order combine preference matrix (or just first-order preference), which means $\tilde{A}$ can be expressed linearly by $A$ as follow
 \begin{equation}
-y=\sum_i^lW_iA_i\cdot X_i\label{eq:04}
+\tilde{A}=BA\label{eq:04}
 \end{equation}
- where $W$ denotes a non-negative weight vector, $W_i$ denotes the weight of the $i$-th position, $X_i$ denotes the embedding vector of the nucleotide at $i$-th position.
- We linearly combine the first-order preference vector of base sequence as following
+where the weight matrix $B\in\mathbb{R}^{l\times l}$ is learned through attention mechanism. 
+Then the predicted value can be expressed as
 \begin{equation}
-\tilde{A}=BA\label{eq:05}
+y=\sum_i^lW_i\tilde{A}_i\cdot {X_e}_i\label{eq:05}
 \end{equation}
- where the weight matrix $B$ is learned through attention mechanism, and we define $A$ as the first-order original preference matrix, 
- $\tilde{A}$ as the first-order combine preference matrix (or just first-order preference) to differentiate them.
- In other words, we build a additive model for the first-order preference, 
- which means that the first-order preference of the $i$-th position $\tilde{A}_i$ can be calculated as
-\begin{equation}
-\tilde{A}_i=\sum_j^lB_{ij}A_j\label{eq:06}
-\end{equation}
- Assume that in Equation~(\ref{eq:06}) the first-order original preference at each position is relatively independent and weight matrix B is independent of any first-order original preference, 
- then the total differential of the first-order preference at $i$-th position could be written as
+ where $W\in\mathbb{R}^l$ denotes a non-negative weight vector, $W_i$ denotes the weight of the $i$-th position, ${X_e}_i$ denotes the embedding vector of the nucleotide at $i$-th position.
+ Assume that in Equation~(\ref{eq:04}) the first-order original preference at each position is relatively independent and weight matrix $B$ is independent of any first-order original preference, 
+ then the total differential of the first-order preference at $i$-th position $\tilde{A}_i$ could be written as
 \begin{equation}
@@
 \end{equation}
+where $E$ is the identity matrix, and we call $B$ as the second-order preference matrix, 
+it can explain how a particular pattern containing two nucleotides affects the base sequence, 
+for example, how does the degree of preference for the G adjacent to PAM be affected by a T at 2 bases upstream?
 
@@
 \end{figure}
-
- where $E$ is the identity matrix, and we define $B$ as the second-order preference matrix, 
- it can explain how a particular pattern containing two nucleotides affects the base sequence, 
- for example, how does the degree of preference for the G adjacent to PAM be affected by a T at 2 bases upstream?
  The previous work (even based on conventional machine learning algorithms with high interpretability) 
@@
 AvgPool denotes the average-pooling operation, MaxPool denotes the max-pooling operation, $\otimes$ denotes element-wise multiplication.
-
+\begin{figure}[!tpb]%figure4
+    \centerline{\includegraphics[width=86mm]{temporalmodule.png}}
+    \caption{The architecture of temporal domain method in AttCRISPR. 
+    The input of the method is embedding sgRNA sequence, a $21\times e$ embedding matrix, where $e$ is the dimension of a nucleotide embedding vector. 
+    }\label{fig:04}
+\end{figure}
 Spatial attention matrix $A_s$ formally conforms to our proposed definition of first-order preference (each element of $X_{oh}$ is multiplied by the corresponding element of $A_s$), 
@@
 In fact, this corresponds to some early studies concerning the Human (hU6) promoter, which is believed to require G as the first nucleotide of its transcript \citep{cong2013multiplex,jinek2012a,mali2013rnaguided}.
-
 \subsubsection{Method and attention in temporal domain}
-\begin{figure}[!tpb]%figure4
-    \centerline{\includegraphics[width=86mm]{temporalmodule.png}}
-    \caption{The architecture of temporal domain method in AttCRISPR. 
-    The input of the method is embedding sgRNA sequence, a $21\times e$ embedding matrix, where $e$ is the dimension of a nucleotide embedding vector. 
-    }\label{fig:04}
-\end{figure}
 As Figure~4\vphantom{\ref{fig:04}} show, temporal domain part of AttCRISPR relies on the recurrent neural network (or its variant). 
@@
 To accommodate them, the embedded matrix $X_e$ is used as input of both the encoder and decoder, and the sequence of decoder is to build the first-order preference of sgRNA sequence $\tilde{A}$. 
-As mentioned above, the predicted value $y$ should satisfy the following equation
-\begin{equation}
-y=\sum_i^lW_i\tilde{A}_i\cdot {X_e}_i\label{eq:12}
-\end{equation}
-where $W\in\mathbb{R}^l$ denotes a non-negative weight vector acquired through a full connection layer, $W_i$ denotes the $i$-th dimension of the vector $W$. 
-Equation~(\ref{eq:12}) is the same formally as Equation~(\ref{eq:04}). 
+As mentioned above, the predicted value $y$ should satisfy Equation~(\ref{eq:05}). 
 On this basis, we apply the idea of attention mechanism which has been widely used in natural language processing tasks to AttCRISPR in the method of temporal domain, 
@@
 
+\subsection{Test1}
+
+Text Text  Text
+
+\section{Discussion}
+
+Text
+
+\section{Conclusion}
+
+(Table~\ref{Tab:01}) Text Text Text Text Text Text  Text Text Text
+Text Text Text Text Text Text  Text Text Text Text Text Text.
+
+\section*{Acknowledgements}
+
+Text
 \begin{table}[!t]
@@
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-
-\subsection{Test1}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text
-
-\section{Discussion}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text
-
-\section{Conclusion}
-
-(Table~\ref{Tab:01}) Text Text Text Text Text Text  Text Text Text
-Text Text Text Text Text Text  Text Text Text Text Text Text.
-
-\section*{Acknowledgements}
-
-Text
-text text text\vspace*{-12pt}
+\vspace*{-12pt}
 

### 2020-10-09 Train/SPConst.py
10-9 train

@@ -12,12 +12,13 @@ CNNParams = {
     }
 RNNParams = {
     'train_batch_size':128,
-    'train_epochs_num':400,
+    'train_epochs_num':40,
     'train_base_learning_rate':0.0005,
     'rnn_save_file':'SPBestRNN.h5',
     'rnn_window_size':4,
     'rnn_embedding_output':75,
     'rnn_last_activation':'linear',
+    'rnn_use_context_state':True,
     'rnn_unit_num':100
     }
 EnsembleParams = {

### 2020-10-09 Train/TrainRNN.py

@@ -45,7 +45,10 @@ def model(params):
                   kernel_regularizer=keras.regularizers.l2(0.01),
                   recurrent_regularizer=keras.regularizers.l2(0.01),dropout=0.25,recurrent_dropout=0.25)
     decoder = Bidirectional(decoder,merge_mode='sum',name='decoder')
-    decoder_output,dc1,dc2 = decoder(decoder_input,initial_state=[ec1,ec2])
+    if params['rnn_use_context_state']:
+        decoder_output,dc1,dc2 = decoder(decoder_input,initial_state=[ec1,ec2])  
+    else:
+        decoder_output,dc1,dc2 = decoder(decoder_input)
     encoderat = []
     decoderat = []
     for i in range(21):
@@ -92,7 +95,8 @@ def model(params):
     #magic
     rnn_embedded = Dropout(rate=0.05)(rnn_embedded)
     output = Dense(units=1,kernel_regularizer=keras.regularizers.l2(0.001),kernel_constraint=keras.constraints.NonNeg(),
-                   name='temporal_score',activation=params['rnn_last_activation'],use_bias=False)(rnn_embedded)
+                   name='temporal_score',activation=params['rnn_last_activation'],
+                   use_bias=params['rnn_last_use_bias'])(rnn_embedded)
     model = Model(inputs=[onehot_input],
                  outputs=[output],name='rnn')
     return model
@@ -103,7 +107,8 @@ def train(params,train_input,train_label,validate_input,validate_label,test_inpu
     batch_size = params['train_batch_size']
     learningrate = params['train_base_learning_rate']
     epochs = params['train_epochs_num']
-    m.compile(loss='mse', optimizer=Adam(lr=learningrate))
+    optimizer = params['optimizer']
+    m.compile(loss='mse', optimizer=optimizer(lr=learningrate))
 
     batch_end_callback = LambdaCallback(on_epoch_end=
                                         lambda batch,logs: 
@@ -125,8 +130,9 @@ if __name__ == "__main__":
     label = data['label']
     input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
                                                               label['train'],rate=0,intensity=0)
+
     scores = []
-    for i in range(20):
+    for i in range(3,4):
         thisbest = train(params['RNNParams'],input_train_onehot,y_train,
                     input['validate']['onehot'],label['validate'],
                     input['test']['onehot'],label['test'])['loss']

### 2020-10-09 Train/WTConst.py

@@ -10,14 +10,18 @@ CNNParams = {
     'cnn_conv_num':3,
     'cnn_last_layer_units_num':54
     }
+from keras.optimizers import *
 RNNParams = {
     'train_batch_size':128,
-    'train_epochs_num':40,
-    'train_base_learning_rate':0.001,
+    'train_epochs_num':2000,
+    'train_base_learning_rate':0.0001,
+    'optimizer':Adamax,
     'rnn_save_file':'WTBestRNN.h5',
     'rnn_window_size':8,
     'rnn_embedding_output':60,
     'rnn_last_activation':'sigmoid',
+    'rnn_use_context_state':True,
+    'rnn_last_use_bias':False,
     'rnn_unit_num':100
     }
 EnsembleParams = {

### 2020-10-09 Train/TrainRNN.py
10-9 fix rnn

@@ -25,7 +25,7 @@ def GaussianKernelBuffer(windowsize):
         sum=0
         for j in range(21):
             sum+=result[i][j]
-        time=42/sum
+        time=21/sum
         for j in range(21):
             result[i][j]*=time
     return np.array(result)

### 2020-10-09 Paper/main.tex

@@
 \subsubsection{Method and attention in temporal domain}
+
+\begin{figure}[!tpb]%figure3
+    \centerline{\includegraphics[width=86mm]{temporalattentionmodule.png}}
+    \caption{wait2write
+    }\label{fig:03}
+\end{figure}
 As Figure~4\vphantom{\ref{fig:04}} show, temporal domain part of AttCRISPR relies on the recurrent neural network (or its variant). 

### 2020-10-09 Paper/main.tex
10-9 paper

@@
 While $B$ is the second-order preference matrix obtained by the attention mechanism, in our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in the biological sense.
+
 \subsubsection{Model ensemble following stacking strategy}
 
-Text
+As \citeauthor{wang2019optimized,Li2016ProteinSS,Wang2016ProteinSS} have shown, some indirect sgRNA features, which can't be obtained directly by deep learning, including position accessibilities of secondary structure, stem–loop of secondary structure, melting temperature, and GC content are strongly associated with sgRNA activity.
+And we use a simple full connection network to extract the indirect features, and call the output of fully connection network $y_{bio}$. 
+As mentioned above, we assume that method in spatial domain and in temporal domain are heterogeneous, which can satisfy the diversity premise of ensemble learning.
+That's why we follow the stacking strategy, integrate the methods in time domain and space domain. 
+Specifically, the $y_{bio}$, the spatial output $y_{s}$ and the temporal output $y_{t}$ we got earlier are concatenated and then weighted averaging is performed through a full connection layer as follow
+\begin{equation}
+y=W[y_{bio};y_s;y_t]\label{eq:20}
+\end{equation}
+where, $y$ is the final prediction value of AttCRISPR, $W$ is the weight learned by the full connection network. 
+In the actual implementation, we freeze the network in the spatial domain and temporal domain at first, in order to make our network focused on learning the weight $w$.
+Later in the process, in the fine tuning of AttCRISPR, the parameters of the entire network are adjusted.
 

### 2020-10-10 Paper/main.tex
10-10 paper

@@
 As \citeauthor{wang2019optimized,Li2016ProteinSS,Wang2016ProteinSS} have shown, some indirect sgRNA features, which can't be obtained directly by deep learning, including position accessibilities of secondary structure, stem–loop of secondary structure, melting temperature, and GC content are strongly associated with sgRNA activity.
-And we use a simple full connection network to extract the indirect features, and call the output of fully connection network $y_{bio}$. 
+It's worth noting that in the work of \citeauthor{wang2019optimized}, hand-crafted biological features didn't be normalized. 
+Since the wide range of data distribution, we believe it makes sense to normalize it, and we preprocess they based on the standard score (Z-Score).
+Then we use a simple full connection network to extract the indirect features, and call the output of fully connection network $y_{bio}$. 
 As mentioned above, we assume that method in spatial domain and in temporal domain are heterogeneous, which can satisfy the diversity premise of ensemble learning.
@@
 where, $y$ is the final prediction value of AttCRISPR, $W$ is the weight learned by the full connection network. 
-In the actual implementation, we freeze the network in the spatial domain and temporal domain at first, in order to make our network focused on learning the weight $w$.
+In the actual implementation, we freeze the network in the spatial domain and temporal domain at first, in order to make our network focused on learning the weight $W$.
 Later in the process, in the fine tuning of AttCRISPR, the parameters of the entire network are adjusted.
@@
 
-text
+The dataset we used for training, validation and testing is built by \citeauthor{wang2019optimized} \citep{wang2019optimized}. 
+We extracted 55604, 58617, 56888 sgRNAs with activity (represented by insertion/deletion (indel)) for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively, from its source data.
 

### 2020-10-10 Paper/main.tex
10-10 paper

@@
 We extracted 55604, 58617, 56888 sgRNAs with activity (represented by insertion/deletion (indel)) for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively, from its source data. 
+As far as we know, the best performance on this dataset is the DeepHF of \citeauthor{wang2019optimized} currently, which base on deep learning and bidirectional LSTM architecture. 
+DeepHF achieved Spearman correlation coefficients of 0.867, 0.862 and 0.860 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively. 
+Another tool worth noting is CRISPRpred(SEQ), which is based on conventional machine learning and need complicated human feature engineering exercise \cite{MuhammadRafid2020}. 
+They also test their tool with this dataset and achieved Spearman correlation coefficients of 0.838, 0.830 and 0.821 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively (without any hyperparameter tuning).
 

### 2020-10-10 Train/Ensemble.py
10-10 train

@@ -26,7 +26,8 @@ def model(params,cnn_trainable=False,rnn_trainable=False,load_weight=False):
                 hidden_layer_activation='relu',dropout=params['bio_fc_dropout'],
                 name='biofeat_embedding')
     output = keras.layers.concatenate([x,x_bio])
-    output = Dense(units=1,kernel_initializer=keras.initializers.RandomNormal(mean=0.3, stddev=0.05),bias_initializer='zero')(output)
+    output = Dense(units=1,kernel_initializer=keras.initializers.RandomNormal(mean=0.3, stddev=0.05),
+                   use_bias=False,bias_initializer='zero',name='last_weight_avg')(output)
     model = Model(inputs=[onehot_input, biological_input],
                  outputs=[output])
     if load_weight:
@@ -56,6 +57,9 @@ def train(params,
           verbose=2,
           validation_data=([validate_input,validate_biofeat],validate_label),
           callbacks=[batch_end_callback])
+
+    weight = m.get_layer('last_weight_avg').get_weights()
+    print(weight)
     return {'loss': -1*result.Best, 'status': STATUS_OK}
 
 

### 2020-10-10 Train/ParamsUtil.py

@@ -2,7 +2,7 @@ import math
 import numpy as np
 import pandas as pd
 
-from ESPConst import Params as params
+from WTConst import Params as params
 
 import os
 #os.environ["CUDA_VISIBLE_DEVICES"] = "-1"

### 2020-10-10 Train/SPConst.py

@@ -10,16 +10,19 @@ CNNParams = {
     'cnn_conv_num':3,
     'cnn_last_layer_units_num':74
     }
+from keras.optimizers import *
 RNNParams = {
     'train_batch_size':128,
-    'train_epochs_num':40,
-    'train_base_learning_rate':0.0005,
+    'train_epochs_num':2000,
+    'train_base_learning_rate':0.0001,
+    'optimizer':Adamax,
     'rnn_save_file':'SPBestRNN.h5',
-    'rnn_window_size':4,
+    'rnn_window_size':8,
     'rnn_embedding_output':75,
-    'rnn_last_activation':'linear',
+    'rnn_last_activation':'sigmoid',
     'rnn_use_context_state':True,
-    'rnn_unit_num':100
+    'rnn_last_use_bias':False,
+    'rnn_unit_num':200
     }
 EnsembleParams = {
     'cnn_load_file':'SPBestCNN.h5',

### 2020-10-10 Train/TrainRNN.py

@@ -130,7 +130,8 @@ if __name__ == "__main__":
     label = data['label']
     input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
                                                               label['train'],rate=0,intensity=0)
-
+    params['RNNParams']['rnn_embedding_output'] = 150
+    params['RNNParams']['rnn_unit_num'] = 100
     scores = []
     for i in range(3,4):
         thisbest = train(params['RNNParams'],input_train_onehot,y_train,

### 2020-10-11 Paper/main.tex
10-11 paper

@@
     \caption{The architecture of spatial domain method in AttCRISPR. 
-    The input of the method is encoded sgRNA sequence, a $21\times 4$ one-hot matrix. 
+    The input of the method is encoded sgRNA sequence $X_{oh}$, a $21\times 4$ one-hot matrix. 
     Then refine it through a spatial attention module, which could tell us the importance of a specific matrix element (or just say, pixel).
-    Finally, a simple convolutional neural network is applied.}\label{fig:02}
+    A simple convolutional neural network followed is applied to extract potential feature representation of sgRNA sequence.
+    In the last step, we flatten the output of convolutional neural network into a one dimensional vector and 
+    use a multilayer perceptron with sigmoid activation function to achieve the spatial output $y_s$.}\label{fig:02}
 \end{figure}
@@
     Then concatenated the output of both max-pooling and average-pooling method and forward it to the last convolution layer.
-    A sigmoid is used to map the final result to a range of zero to one.
+    A sigmoid function is used to map the final result to a range of zero to one at last, 
+    which generates the spatial attention matrix $A_s$.
     }\label{fig:03}
@@
     \caption{The architecture of temporal domain method in AttCRISPR. 
-    The input of the method is embedding sgRNA sequence, a $21\times e$ embedding matrix, where $e$ is the dimension of a nucleotide embedding vector. 
+    The input of the method is embedding sgRNA sequence $X_e$, a $21\times e$ embedding matrix, where $e$ is the dimension of a nucleotide embedding vector. 
+    Then Keys $K$, Values $V$ and Queries $Q$ is generated through a classic encoder-decoder structure which is need for temporal attention module.
     }\label{fig:04}
@@
 \subsubsection{Method and attention in temporal domain}
-
-\begin{figure}[!tpb]%figure3
-    \centerline{\includegraphics[width=86mm]{temporalattentionmodule.png}}
-    \caption{wait2write
-    }\label{fig:03}
-\end{figure}
 As Figure~4\vphantom{\ref{fig:04}} show, temporal domain part of AttCRISPR relies on the recurrent neural network (or its variant). 
@@
 
+\begin{figure}[!tpb]%figure3
+    \centerline{\includegraphics[width=86mm]{temporalattentionmodule.png}}
+    \caption{wait2write
+    }\label{fig:03}
+\end{figure}
 \subsubsection{Model ensemble following stacking strategy}
@@
 DeepHF achieved Spearman correlation coefficients of 0.867, 0.862 and 0.860 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively. 
-Another tool worth noting is CRISPRpred(SEQ), which is based on conventional machine learning and need complicated human feature engineering exercise \cite{MuhammadRafid2020}. 
+Another tool worth noting is CRISPRpred(SEQ), which is based on conventional machine learning and need complicated human feature engineering exercise \citep{MuhammadRafid2020}. 
 They also test their tool with this dataset and achieved Spearman correlation coefficients of 0.838, 0.830 and 0.821 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively (without any hyperparameter tuning).
+\citeauthor{wang2019optimized} implemente a tenfold shuffled validation to evaluate the stability of the performance of DeepHF.
+To be more specific, each set is shuffled and divided into three parts, 76.5\%, 15\% and 8.5\% of the relevant data was used as the training, test and validation set respectively in a single experiment.
+The experiment is repeated ten times with the results recorded and averaged finally.
+In order to make the comparison apples to apples, we will follow this strategy to design experiments.
 
@@
 text
+
+\begin{table}[!t]
+    \processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}\toprule head1 &
+    head2 & head3 & head4\\\midrule
+    row1 & row1 & row1 & row1\\
+    row2 & row2 & row2 & row2\\
+    row3 & row3 & row3 & row3\\
+    row4 & row4 & row4 & row4\\\botrule
+    \end{tabular}}{This is a footnote}
+\end{table}
 
@@
 Text
-\begin{table}[!t]
-    \processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}\toprule head1 &
-    head2 & head3 & head4\\\midrule
-    row1 & row1 & row1 & row1\\
-    row2 & row2 & row2 & row2\\
-    row3 & row3 & row3 & row3\\
-    row4 & row4 & row4 & row4\\\botrule
-    \end{tabular}}{This is a footnote}
-\end{table}
 

### 2020-10-12 Paper/main.tex
10-12 paper

@@
  \citeauthor{MuhammadRafid2020} consider deep-learning-based models as black boxs and believe they lack interpretability, 
- motivated by the empirical assertion, they turn to build a model based conventional machine learning to compete with state of the art deep learning models \citep{MuhammadRafid2020}. 
+ motivated by the empirical assertion, they turn to build a model based conventional machine learning to compete with state-of-the-art deep learning models \citep{MuhammadRafid2020}. 
  On the other hand, input perturbation based feature importance analysis become a preferred components to reveal the importance of features in deep learning models. 
@@
     Thus, it is transformed from a black box to an intrinsically interpretable model with the performance of deep learning based model. 
-    \item Throught abation analysis and testing a series of possible network structure, 
+    \item Throught ablation analysis and testing a series of possible network structure, 
     we find there are multiple components and strategy can improve the performance of our model and constructed AttCRISPR, 
@@
     A sigmoid function is used to map the final result to a range of zero to one at last, 
-    which generates the spatial attention matrix $A_s$.
+    which generates the spatial first-order preference matrix $A_s$.
     }\label{fig:03}
@@
 AvgPool denotes the average-pooling operation, MaxPool denotes the max-pooling operation, $\otimes$ denotes element-wise multiplication.
-\begin{figure}[!tpb]%figure4
-    \centerline{\includegraphics[width=86mm]{temporalmodule.png}}
-    \caption{The architecture of temporal domain method in AttCRISPR. 
-    The input of the method is embedding sgRNA sequence $X_e$, a $21\times e$ embedding matrix, where $e$ is the dimension of a nucleotide embedding vector. 
-    Then Keys $K$, Values $V$ and Queries $Q$ is generated through a classic encoder-decoder structure which is need for temporal attention module.
-    }\label{fig:04}
-\end{figure}
 Spatial attention matrix $A_s$ formally conforms to our proposed definition of first-order preference (each element of $X_{oh}$ is multiplied by the corresponding element of $A_s$), 
@@
 As mentioned above, the predicted value $y$ should satisfy Equation~(\ref{eq:05}).
+
 On this basis, we apply the idea of attention mechanism which has been widely used in natural language processing tasks to AttCRISPR in the method of temporal domain, 
@@
 $Q$, $K$, $V$ are queries, keys and values matrix accordingly in the paper of \citeauthor{vaswani2017attention}.
+
 As Figure~5\vphantom{\ref{fig:05}} show, in our attention module they are calculated by the following equation
@@
 While $B$ is the second-order preference matrix obtained by the attention mechanism, in our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in the biological sense.
-
+\begin{figure}[!tpb]%figure4
+    \centerline{\includegraphics[width=86mm]{temporalmodule.png}}
+    \caption{The architecture of temporal domain method in AttCRISPR. 
+    The input of the method is embedding sgRNA sequence $X_e$, a $21\times e$ embedding matrix, where $e$ is the dimension of a nucleotide embedding vector. 
+    Then Keys $K$, Values $V$ and Queries $Q$ is generated through a classic encoder-decoder structure which is need for temporal attention module.
+    Next, the temporal attention module generates the first-order preference $\tilde{A}$, a $21\times e$ matrix (or a vector set). 
+    Each of the row vectors in matrix $\tilde{A}$ represents the base preference of sgRNA at the corresponding position, we use their dot product with the corresponding row vector in embedded $X_e$ to build the score of corresponding position.
+    Hence, a full connection layer is used to weighted average them and achieve the temporal output $y_t$.
+    }\label{fig:04}
+\end{figure}
 \begin{figure}[!tpb]%figure3
     \centerline{\includegraphics[width=86mm]{temporalattentionmodule.png}}
-    \caption{wait2write
-    }\label{fig:03}
+    \caption{
+        Details of temporal attention module. 
+        To generate the first order preference vector in the $i$ position of sgRNA $\tilde{A}_i$. 
+        First, the $i$-th row vector of the querys matrix $Q_i$ is multiplied by the transpose of the keys mateix $K^T$, and apply a softmax function to obtain a preliminary weights vector on the values.
+        Second, to favor the alignment points near $i$, the weights vector obtained is multiplied element-by-element by the $i$-th row vector of the damping matrix $G$, as Equation~(\ref{eq:17}) has shown.
+        $G_{ij}$ can be regarded as the result of place a Gaussian distribution centered around $i$, then sampling the position $j$ (a scaling factor is used to ensure the sum of $G_I$ is $l$). 
+        Then we achieve the second-order preference matrix $B$, it is also a weights matrix on the values.
+So the first-order preference matrix $\tilde{A}$ come from the product of $B$ and values matrix $V$.
+        Although it's not shown above, it is also worth noting that, a full connection layer with L2 constraints is used to generates a transformation matrix in order to ensure $\tilde{A}_i$ and ${X_e} _i$ are in the same vector space.
+        Temporal attention module generates the temporal first-order preference matrix $\tilde{A}$ and the temporal second-order preference matrix $B$.
+    }\label{fig:05}
 \end{figure}
@@
 Since the wide range of data distribution, we believe it makes sense to normalize it, and we preprocess they based on the standard score (Z-Score).
+
 Then we use a simple full connection network to extract the indirect features, and call the output of fully connection network $y_{bio}$. 
@@
 DeepHF achieved Spearman correlation coefficients of 0.867, 0.862 and 0.860 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively.
+
 Another tool worth noting is CRISPRpred(SEQ), which is based on conventional machine learning and need complicated human feature engineering exercise \citep{MuhammadRafid2020}. 
 They also test their tool with this dataset and achieved Spearman correlation coefficients of 0.838, 0.830 and 0.821 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively (without any hyperparameter tuning).
+
 \citeauthor{wang2019optimized} implemente a tenfold shuffled validation to evaluate the stability of the performance of DeepHF.
@@
 
-text
+Two different sets of experiments are carried out in our work. 
+The first one is designed for ablation analysis of AttCRISPR. 
+We compare the performance of method in both spatial and temporal domain (without any hand-crafted biological features). 
+Furthermore, we test the ensemble method based on the same strategy, which proved that the ensemble of method in both spatial and temporal domain can significantly improve the performance.
+
+The second experiment is designed to compare the performance of AttCRISPR and other current prediction method. 
+In order to make the comparison apples to apples, we reduce the dimensionality of the same hand-crafted biological features as DeepHF's, 
+which has been shown to enhance the predictability of a deep-learning model greatly, with a multilayer perceptron. 
+Then follow the Equation~(\ref{eq:20}) to achieve the final prediction value. 
+AttCRISPR (with the hand-crafted biological features) performs better on all three data sets than DeepHF, the current state-of-the-art.
+
+Our baselines have a comprehensive coverage of the methods tested in these datasets.
+
+In Table~\ref{Tab:01}, we annotate some properties of these baselines (with/without neural models, with/without hand-crafted feature)
 
 \begin{table}[!t]
-    \processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}\toprule head1 &
-    head2 & head3 & head4\\\midrule
-    row1 & row1 & row1 & row1\\
-    row2 & row2 & row2 & row2\\
-    row3 & row3 & row3 & row3\\
-    row4 & row4 & row4 & row4\\\botrule
+    \processtable{
+    The naming convention code and brief description of the methods compared in our work\label{Tab:01}} 
+    {\begin{tabular}{@{}lllll@{}}\toprule 
+        Method & Code & Neural & Hand-crafted Feature & Description\\\midrule
+        Linear$^*$ & row1 & No & No & row1\\
+        Ridge$^*$ & row4 & No & No & row4\\
+        XGBoost$^*$ & row1 & No & No & row1\\
+        MLP$^*$ & row1 & Yes & No & row1\\
+        DeepHF$^*$ & row1 & Yes & Yes & row1\\
+        CRISPRpred(SEQ)$^{\#}$ & row1 & No & Yes & row1\\
+        \botrule
     \end{tabular}}{This is a footnote}
 \end{table}
-
 \section{Results}
@@
 
-Text Text  Text
+Text
 
@@
 
-(Table~\ref{Tab:01}) Text Text Text Text Text Text  Text Text Text
-Text Text Text Text Text Text  Text Text Text Text Text Text.
+Text
 
@@
 
-This work has beenText  Text Text.\vspace*{-12pt}
+ text.\vspace*{-12pt}
 

### 2020-10-14 Paper/main.tex
10-14 paper

@@
  In short, what was needed for developer is to trade-off accuracy and interpretability. 
- \citeauthor{MuhammadRafid2020} consider deep-learning-based models as black boxs and believe they lack interpretability, 
+ \citeauthor{MuhammadRafid2020} consider deep-learning models as black boxs and believe they lack interpretability, 
  motivated by the empirical assertion, they turn to build a model based conventional machine learning to compete with state-of-the-art deep learning models \citep{MuhammadRafid2020}. 
@@
 \begin{itemize}
-    \item Present a novel deep-learning-based model, which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
+    \item Present a novel deep-learning model, which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
     Finally, the ensemble learning method is used to combine the two to achieve better performance than other models.
@@
     }\label{fig:04}
-\end{figure}
-\begin{figure}[!tpb]%figure3
 \centerline{\includegraphics[width=86mm]{temporalattentionmodule.png}}
@@
 \end{figure}
+
 \subsubsection{Model ensemble following stacking strategy}
@@
 The first one is designed for ablation analysis of AttCRISPR. 
-We compare the performance of method in both spatial and temporal domain (without any hand-crafted biological features). 
+We compare the performance of end2end method (without any hand-crafted biological features) in both spatial and temporal domain. 
 Furthermore, we test the ensemble method based on the same strategy, which proved that the ensemble of method in both spatial and temporal domain can significantly improve the performance.
@@
 
+\begin{table}[!tpb]
+    \processtable{The methods compared in our work and brief description of these methods\label{Tab:01}} 
+    {\begin{tabular}{@{}lllp{3.5cm}l@{}}\toprule
+        Method & Neural & End2end & Description\\\midrule
+        CNN$^*$ & Yes & Yes & Naive convolutional neural network\\
+        RNN$^*$ & Yes & Yes & Bidirectional long short-term memory neural network\\
+        XGBoost$^*$ & No & Yes & Extreme Gradient Boosting regression tree\\
+        MLP$^*$ & Yes & Yes & Multilayer perceptron\\
+        DeepHF$^*$ & Yes & No & Bidirectional long short-term memory neural network (with hand-crafted biological features)\\
+        CRISPRpred(SEQ)$^{\#}$ & No & No & A conventional machine learning pipeline\\
+        SpAC & Yes & Yes & Spatial AttCRISPR\\
+        TAC & Yes & Yes & Temporal AttCRISPR\\
+        EnAC & Yes & Yes & Ensemble AttCRISPR (without hand-crafted biological features)\\
+        StAC & Yes & No & Standard AttCRISPR\\
+        \botrule
+    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: The method with superscript of $^*$ and $^{\#}$ is reported by \citeauthor{wang2019optimized} and \citeauthor{MuhammadRafid2020} respectively.
+We use the conclusion of corresponding paper as the performance indicators of the model directly. 
+Specially, CRISPRpred(SEQ) take another set of hand-crafted sequence-based feature to improve performance.}
+\end{table}
+
 Our baselines have a comprehensive coverage of the methods tested in these datasets. 
+In Table~\ref{Tab:01}, we annotate some properties of these baselines (is/isn't neural models, is/isn't end2end models)
+All the experiments were carried out in Python 3.6 using Keras 2.2.4 and one GeForce RTX 2080Ti Super was used for training and testing if needed.
 
-In Table~\ref{Tab:01}, we annotate some properties of these baselines (with/without neural models, with/without hand-crafted feature)
+\section{Results}
 
-\begin{table}[!t]
-    \processtable{
-    The naming convention code and brief description of the methods compared in our work\label{Tab:01}} 
-    {\begin{tabular}{@{}lllll@{}}\toprule 
-        Method & Code & Neural & Hand-crafted Feature & Description\\\midrule
-        Linear$^*$ & row1 & No & No & row1\\
-        Ridge$^*$ & row4 & No & No & row4\\
-        XGBoost$^*$ & row1 & No & No & row1\\
-        MLP$^*$ & row1 & Yes & No & row1\\
-        DeepHF$^*$ & row1 & Yes & Yes & row1\\
-        CRISPRpred(SEQ)$^{\#}$ & row1 & No & Yes & row1\\
-        \botrule
-    \end{tabular}}{This is a footnote}
-\end{table}
-\section{Results}
+We designed experiments to address the following questions:
+\begin{itemize}
+    \item 
+    Whether the stacking of method in spatial domain and temporal domain can get better performance then use these method alone? 
+    $\rightarrow$ Section~\ref{section:stacking}
+    \item 
+    How does AttCRISPR perform compared to current state-of-the-art methods, covering both conventional machine learning and deep-learning models? 
+    $\rightarrow$ Section~\ref{section:comparison}
+    \item 
+    How can researcher understand the decisions make by AttCRISPR locally and globally, based on attention mechanisms? 
+    $\rightarrow$ Section~\ref{section:interpretability}
+    \vspace*{1pt}
+\end{itemize}
+
+\subsection{Model building and stacking}\label{section:stacking}
 
@@
 
-\enlargethispage{6pt}
+\subsection{Comparison to current methods}\label{section:comparison}
 
@@
 
-\subsection{Test1}
+\subsection{Interpretability of the AttCRISPR}\label{section:interpretability}
 

### 2020-10-14 Train/Ensemble.py
10-14 validation

@@ -9,7 +9,7 @@ import keras.backend as K
 from hyperopt import fmin, tpe, hp, STATUS_OK, Trials
 from LearnUtil import *
 
-def model(params,cnn_trainable=False,rnn_trainable=False,load_weight=False):
+def model(params,withbiofeature=True,cnn_trainable=False,rnn_trainable=False,load_weight=False):
     onehot_input = Input(name='onehot_input', shape = (21,4, 1,))
     biological_input = Input(name='bio_input', shape = (11,))
     cnnmodel = load_model(params['cnn_load_file'])
@@ -19,26 +19,28 @@ def model(params,cnn_trainable=False,rnn_trainable=False,load_weight=False):
     x_cnn = cnnmodel(onehot_input)
     x_rnn = rnnmodel(onehot_input)
     x = keras.layers.concatenate([x_rnn,x_cnn])
-    ######Biofeat######
-    x_bio = mlp(biological_input,
-                output_layer_activation='tanh',output_dim=1,output_use_bias=True,
-                hidden_layer_num=params['bio_fc_hidden_layer_num'],hidden_layer_units_num=params['bio_fc_hidden_layer_units_num'],
-                hidden_layer_activation='relu',dropout=params['bio_fc_dropout'],
-                name='biofeat_embedding')
-    output = keras.layers.concatenate([x,x_bio])
-    output = Dense(units=1,kernel_initializer=keras.initializers.RandomNormal(mean=0.3, stddev=0.05),
+    if withbiofeature:
+        ######Biofeat######
+        x_bio = mlp(biological_input,
+                    output_layer_activation='tanh',output_dim=1,output_use_bias=True,
+                    hidden_layer_num=params['bio_fc_hidden_layer_num'],hidden_layer_units_num=params['bio_fc_hidden_layer_units_num'],
+                    hidden_layer_activation='relu',dropout=params['bio_fc_dropout'],
+                    name='biofeat_embedding')
+        output = keras.layers.concatenate([x,x_bio])
+    else :
+        output = x
+    output = Dense(units=1,kernel_initializer=keras.initializers.RandomNormal(mean=0.4, stddev=0.05),
                    use_bias=False,bias_initializer='zero',name='last_weight_avg')(output)
     model = Model(inputs=[onehot_input, biological_input],
-                 outputs=[output])
+                  outputs=[output])
     if load_weight:
         model.load_weights(params['ensemble_load_file']) 
     return model
 
 def train(params,
[…]

### 2020-10-14 Train/ParamsUtil.py

@@ -2,8 +2,16 @@ import math
 import numpy as np
 import pandas as pd
 
-from WTConst import Params as params
-
+def GetParams(dataset):
+    if dataset == 'WT':
+        from WTConst import Params as params
+    elif dataset == 'ESP':
+        from ESPConst import Params as params
+    elif dataset == 'SP':
+        from SPConst import Params as params
+    else:
+        raise Exception('No this dataset!')
+    return params
 import os
 #os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
 from sklearn.model_selection import train_test_split
@@ -20,30 +28,59 @@ def ZScore(biofeat):
         for j in range(len(biofeat)):
             biofeat[j][i] = (biofeat[j][i]-avg) / sigma
 
+#### the same as method of Wang et al. ####
+def load_data_kf(X,X_biofeat,y):
+    from sklearn.model_selection import ShuffleSplit
+    train_test_data = []
+    kf = ShuffleSplit(n_splits=10, test_size=0.15, random_state=33)
+    for train_index, test_index in kf.split(X):
+        X_train, X_train_biofeat, X_test, X_test_biofeat = X[train_index],X_biofeat[train_index], X[test_index],X_biofeat[test_index]
+        y_train, y_test = y[train_index], y[test_index]
+        
+        train_test_data.append((X_train,X_train_biofeat,X_test,X_test_biofeat,y_train,y_test))
+    return train_test_data
+def ReadValidationData(dataset):
+    params = GetParams(dataset)
+    pkl = open(params['data_file'],'rb')
+    x_onehot = pickle.load(pkl)
+    x_biofeat = pickle.load(pkl)
+    ZScore(x_biofeat)
+    label = pickle.load(pkl)
+    x_seq = pickle.load(pkl)
+    dataslist = load_data_kf(x_onehot,x_biofeat,label)
+    datas = []
+    for d in dataslist:
+        data = {'input':
+                {'train':{'onehot':d[0],'biofeat':d[1]},
+                 'test':{'onehot':d[2],'biofeat':d[3]}
+                },
+                'label':
+                {'train':d[4],
+                'test':d[5]
+                }
+                }
+        datas.append(data)
+    return datas
 def SplitData(onehot,biofeat,label):    
     random_state=40
     test_size = 0.15
     validate_size = 0.1
-    x_train_validate_onehot, x_test_onehot, y_train_validate, y_test = train_test_split(onehot, label, test_size=test_size, random_state=random_state)
[…]

### 2020-10-14 Train/Pipeline.py

@@ -6,38 +6,30 @@ from TrainRNN import train as RNN
 from TrainCNN import train as CNN
 from Ensemble import train as Ensemble
 
-def Pipeline(pretrainCNN=False,pretrainRNN=False,ensemble=False,fineTuning=False):
-    data = Read_Data()
+def Pipeline(dataset,pretrainCNN=False,pretrainRNN=False,ensemble=False,fineTuning=False):
+    data = ReadData(dataset)
+    params = GetParams(dataset)
     input = data['input']
     label = data['label']
     r = None
     if pretrainCNN:
-        input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
-                                                                  label['train'],rate=0,intensity=0)
-        r = CNN(params['CNNParams'],input_train_onehot,y_train,
-             input['validate']['onehot'],label['validate'],
+        r = CNN(params['CNNParams'],input['train']['onehot'],label['train'],
              input['test']['onehot'],label['test'])
     if pretrainRNN:
-        input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
-                                                                  label['train'],rate=0,intensity=0)
-        r = RNN(params['RNNParams'],input_train_onehot,y_train,
+        r = RNN(params['CNNParams'],input['train']['onehot'],label['train'],
              input['validate']['onehot'],label['validate'],
              input['test']['onehot'],label['test'])
     if ensemble:
-        #input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],
-        #                                                          label['train'],rate=50,intensity=10)
         input_train_onehot,input_train_biofeat,y_train = input['train']['onehot'],input['train']['biofeat'],label['train']
         r = Ensemble(params['EnsembleParams'],
-                 input_train_onehot,input_train_biofeat,y_train,
-                 input['validate']['onehot'],input['validate']['biofeat'],label['validate'],
+                 input['train']['onehot'],input['train']['biofeat'],label['train'],
                  input['test']['onehot'],input['test']['biofeat'],label['test'],
                  cnn_trainable=False,rnn_trainable=False)
     if fineTuning:
         r = Ensemble(params['FineTuning'],
                 input['train']['onehot'],input['train']['biofeat'],label['train'],
[…]

### 2020-10-14 Train/TestH5.py

@@ -8,7 +8,7 @@ def get_score_at_test(model,input,label,issave=True,savepath=None):
     return 'MES:' + str(mse),'Spearman:' + str(spearmanr) , 'r2:' + str(r2)
 
 from ParamsUtil import *
-data = Read_Data()
+data = ReadData()
 from keras.models import load_model
 model = load_model('WTBestCNN.h5')
 print(get_score_at_test(model,

### 2020-10-14 Train/TrainCNN.py

@@ -37,7 +37,7 @@ def model(params):
                  outputs=[output],name='cnn')
     return model
 
-def train(params,train_input,train_label,validate_input,validate_label,test_input,test_label):
+def train(params,train_input,train_label,test_input,test_label,issave=True):
     result = Result()
     m = model(params)
     batch_size = params['train_batch_size']
@@ -48,19 +48,21 @@ def train(params,train_input,train_label,validate_input,validate_label,test_inpu
     batch_end_callback = LambdaCallback(on_epoch_end=
                                         lambda batch,logs: 
                                         print(get_score_at_test(m,test_input,result,test_label,
-                                                                issave=True,savepath=params['cnn_save_file'])))
+                                                                issave=issave,savepath=params['cnn_save_file'])))
 
     m.fit(train_input,train_label,
           batch_size=batch_size,
           epochs=epochs,
           verbose=2,
-          validation_data=([validate_input],validate_label), 
+          validation_split=0.1,
           callbacks=[batch_end_callback])
     return {'loss': -1*result.Best, 'status': STATUS_OK}
 if __name__ == "__main__":
     import ParamsUtil
     from ParamsUtil import *
-    data = Read_Data()
+    dataset = 'WT'
+    data = ReadData(dataset)
+    params = GetParams(dataset)
     input = data['input']
     label = data['label']
     input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],

### 2020-10-14 Train/TrainRNN.py

@@ -101,7 +101,7 @@ def model(params):
                  outputs=[output],name='rnn')
     return model
 
-def train(params,train_input,train_label,validate_input,validate_label,test_input,test_label):
+def train(params,train_input,train_label,test_input,test_label,issave=True):
     result = Result()
     m = model(params)
     batch_size = params['train_batch_size']
@@ -113,19 +113,21 @@ def train(params,train_input,train_label,validate_input,validate_label,test_inpu
     batch_end_callback = LambdaCallback(on_epoch_end=
                                         lambda batch,logs: 
                                         print(get_score_at_test(m,test_input,result,test_label,
-                                                                issave=True,savepath=params['rnn_save_file'])))
+                                                                issave=issave,savepath=params['rnn_save_file'])))
 
     m.fit(train_input,train_label,
           batch_size=batch_size,
           epochs=epochs,
           verbose=2,
-          validation_data=([validate_input],validate_label), 
+          validation_split=0.1, 
           callbacks=[batch_end_callback])
     return {'loss': -1*result.Best, 'status': STATUS_OK}
 if __name__ == "__main__":
     import ParamsUtil
     from ParamsUtil import *
-    data = Read_Data()
+    dataset = 'WT'
+    data = ReadData(dataset)
+    params = GetParams(dataset)
     input = data['input']
     label = data['label']
     input_train_onehot,input_train_biofeat,y_train = AddNoise(input['train']['onehot'],input['train']['biofeat'],

### 2020-10-14 Train/Validation.py

@@ -1,0 +1,27 @@
+import ParamsUtil
+from ParamsUtil import *
+######
+
+from TrainRNN import train as RNN
+from TrainCNN import train as CNN
+from Ensemble import train as Ensemble
+
+def ValidateCNN(dataset):
+    datas = ReadValidationData(dataset)
+    result = []
+    time = 0
+    for data in datas:
+        time+=1
+        params = GetParams(dataset)
+        params['cnn_save_file'] = params['cnn_save_file']+'_'+str(time)
+        input = data['input']
+        label = data['label']
+        r = None
+        r = CNN(params['CNNParams'],input['train']['onehot'],label['train'],
+             input['test']['onehot'],label['test'],issave=True)
+        result.append(r.best)
+
+        print(result)
+if __name__ == "__main__":
+    ValidateCNN('WT')
+

### 2020-10-15 Train/Faker.py
10-15 del faker which never use

@@ -1,95 +1,0 @@
-import ParamsUtil
-from ParamsUtil import *
-######
-
-import os
-os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
-
-def AddNoise(onehot,biofeat,label,rate=50,intensity=0.30):
-    from random import randint
-    import copy
-    t_onehot = onehot.tolist()
-    t_biofeat = biofeat.tolist()
-    t_label = label.tolist()
-    x=0
-    for i in range(len(onehot)):
-        if randint(0,100) > rate:
-            continue
-        j = randint(4,16)
-        for k in range(4):
-            if onehot[i][j][k][0] == 1:
-               x = k
-        offset = randint(1,4)
-        noise = intensity/3
-        newx = copy.deepcopy(onehot[i])
-        for k in range(4):
-            newx[j][k][0] = (1-intensity) if x==k else noise
-        t_onehot.append(newx)
-        t_biofeat.append(copy.deepcopy(t_biofeat[i]))
-        t_label.append(copy.deepcopy(t_label[i]))
-
-
-    index=np.arange(len(t_onehot))
-    np.random.shuffle(index)
-    
-    t_onehot = np.array(t_onehot).reshape(-1,21,4,1)
-    t_biofeat = np.array(t_biofeat).reshape(-1,11)
-    t_label = np.array(t_label).reshape(-1)
-
-    onehot=t_onehot[index,:,:,:]
-    biofeat=t_biofeat[index,:] 
-    label=t_label[index]
-
-    return onehot,biofeat,label
-def faker(data,rate=5):    
-    from random import randint
-    import copy
-    input = data['input']
-    onehot = input['train']['onehot'].tolist()
-    biofeat = input['train']['biofeat'].tolist()
-    label = data['label']['train'].tolist()
-    x=0
-    for i in range(len(input['test']['onehot'])):
-        if randint(0,100) > rate:
-            continue
-        onehot.append(input['test']['onehot'][i])
-        biofeat.append(input['test']['biofeat'][i])
-        label.append(data['label']['test'][i])
-    
-    onehot = np.array(onehot).reshape(-1,21,4,1)
-    biofeat = np.array(biofeat).reshape(-1,11)
-    label = np.array(label).reshape(-1)
-    return onehot,biofeat,label
-from PretrainCNN import train as CNN
-from PretrainRNN import train as RNN
-from Ensemble import train as Ensemble
-
[…]

### 2020-10-15 Train/AttCRISPRDemo.py
10-15 code

@@ -1,0 +1,6 @@
+from Pipeline import Pipeline as train
+import sys
+if __name__ == "__main__":
+    assert len(sys.argv)==2
+    assert sys.argv[1] in ['WT','ESP','SP']
+    train(sys.argv[1],pretrainCNN=True,pretrainRNN=True,ensemble=True,fineTuning=True) 

### 2020-10-15 Train/niceRNN.py

@@ -1,127 +1,0 @@
-import keras
-from keras.layers import Softmax,Input, Conv2D, Flatten, BatchNormalization, Multiply,Cropping1D,dot, Bidirectional
-from keras.layers.core import *
-from keras.layers.recurrent import LSTM,GRU
-from keras.models import *
-from keras.callbacks import EarlyStopping, Callback,LambdaCallback
-from keras.optimizers import *
-import keras.backend as K
-from hyperopt import fmin, tpe, hp, STATUS_OK, Trials
-from LearnUtil import *
-import math
-def GaussianKernelBuffer(windowsize=8):
-    gaussian = lambda d: math.exp( -(d*d)*2/windowsize/windowsize ) if abs(d)<=windowsize/2 else 0
-    result = []
-    for i in range(21):
-        resultat = []
-        for j in range(21):
-            resultat.append(gaussian(i-j))
-        nresultat = np.array(resultat)
-        result.append(nresultat)
-    for i in range(21):
-        sum=0
-        for j in range(21):
-            sum+=result[i][j]
-        time=21/sum
-        for j in range(21):
-            result[i][j]*=time
-    return np.array(result)
-def model(params):
-    GaussianBuffer = GaussianKernelBuffer()
-    onehot_input = Input(name = 'onehot_input', shape = (21,4, 1,))
-    embedded = Conv2D(params['rnn_embedding_output'], (1, 4),strides=(1,4), padding='Valid', activation=None)(onehot_input)
-    embedded = Reshape((21,params['rnn_embedding_output'],))(embedded)
-
-    encoder = LSTM(params['rnn_unit_num'],return_sequences=True,return_state=False,unroll=True)
-    encoder = Bidirectional(encoder,merge_mode='sum',name='encoder_output')
-    encoder_output = encoder(embedded)
-    
-    encoderat = []
-    for i in range(21):
-        encoderat.append(
-            Flatten()(
-                Cropping1D(cropping=(i,21-1-i))(encoder_output)
-                )
-            )
-    decoder_input = keras.layers.concatenate([embedded,encoder_output])
-    decoder = LSTM(params['rnn_unit_num'],dropout=0.25,recurrent_dropout=0.25,
-                     return_sequences=True,return_state=False,name='last_gru_output',unroll=True)
-    decoder = Bidirectional(decoder,merge_mode='sum',name='last_bgru_output')
-    decoder_output = decoder(decoder_input)
-    
-    decoderat = []
-    for i in range(21):
-        decoderat.append(
-            Flatten()(
[…]

### 2020-10-15 Train/testModule.py

@@ -1,22 +1,0 @@
-
-import pickle
-def Read_Data(filename):
-    pkl = open(filename,'rb')
-    x_onehot = pickle.load(pkl)
-    x_biofeat = pickle.load(pkl)
-    ZScore(x_biofeat)
-    label = pickle.load(pkl)
-    x_seq = pickle.load(pkl)
-    return SplitData(x_onehot,x_biofeat,label)
-
-dataset = []
-dataset.append('WTData.pkl')
-dataset.append('ESPData.pkl')
-dataset.append('SPData.pkl')
-for f in dataset:
-    pkl = open(f,'rb')
-    x_onehot = pickle.load(pkl)
-    x_biofeat = pickle.load(pkl)
-    label = pickle.load(pkl)
-    x_seq = pickle.load(pkl)
-    print(len(x_onehot))

### 2020-10-17 Train/ESPConst.py
10-17 train

@@ -13,7 +13,7 @@ CNNParams = {
 from keras.optimizers import *
 RNNParams = {
     'train_batch_size':128,
-    'train_epochs_num':2000,
+    'train_epochs_num':1000,
     'train_base_learning_rate':0.0001,
     'optimizer':Adamax,
     'rnn_save_file':'ESPBestRNN.h5',
@@ -22,16 +22,17 @@ RNNParams = {
     'rnn_last_activation':'linear',
     'rnn_last_use_bias':True,
     'rnn_use_context_state':True,
-    'rnn_unit_num':200
+    'rnn_unit_num':200,
+    'rnn_last_dropout':0.40
     }
 
 EnsembleParams = {
     'cnn_load_file':'ESPBestCNN.h5',
     'rnn_load_file':'ESPBestRNN.h5',
     'ensemble_save_file':'ESPEnsemble.h5',
-    'train_batch_size':16,
-    'train_epochs_num':75,
-    'train_base_learning_rate':0.00002,
+    'train_batch_size':128,
+    'train_epochs_num':20,
+    'train_base_learning_rate':0.00005,
     'bio_fc_hidden_layer_num':1,
     'bio_fc_hidden_layer_units_num':87,
     'bio_fc_dropout':0.05

### 2020-10-17 Train/Ensemble.py

@@ -36,13 +36,16 @@ def model(params,withbiofeature=True,cnn_trainable=False,rnn_trainable=False,loa
     if load_weight:
         model.load_weights(params['ensemble_load_file']) 
     return model
+    if load_weight:
+        model.load_weights(params['ensemble_load_file']) 
+    return model
 
 def train(params,
           train_input,train_biofeat,train_label,
-          test_input,test_biofeat,test_label,
+          test_input,test_biofeat,test_label,withbiofeature,
           cnn_trainable=False,rnn_trainable=False,load_weight=False,issave=True):
     result = Result()
-    m = model(params,
+    m = model(params,withbiofeature=withbiofeature,
               cnn_trainable=cnn_trainable,rnn_trainable=rnn_trainable,load_weight=load_weight)
     batch_size = params['train_batch_size']
     learningrate = params['train_base_learning_rate']

### 2020-10-17 Train/Pipeline.py

@@ -32,4 +32,4 @@ def Pipeline(dataset,pretrainCNN=False,pretrainRNN=False,ensemble=False,fineTuni
                 cnn_trainable=True,rnn_trainable=True,load_weight=True)
     return r
 if __name__ == "__main__":
-    Pipeline('WT',pretrainCNN=False,pretrainRNN=False,ensemble=True,fineTuning=False) 
+    Pipeline('WT',pretrainCNN=False,pretrainRNN=False,ensemble=False,fineTuning=True) 

### 2020-10-17 Train/Plot.py

@@ -1,0 +1,25 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+fig, axes = plt.subplots(figsize=(12, 5))
+
+all_data = [np.random.normal(0, std, 10) for std in range(6, 10)]
+
+axes.violinplot(all_data,
+                   showmeans=False,
+                   showmedians=True
+                   )
+axes.set_title('violin plot')
+
+# adding horizontal grid lines
+
+axes.yaxis.grid(True)
+axes.set_xticks([y + 1 for y in range(len(all_data))], )
+axes.set_xlabel('xlabel')
+axes.set_ylabel('ylabel')
+
+plt.setp(axes, xticks=[y + 1 for y in range(len(all_data))],
+         xticklabels=['x1', 'x2', 'x3', 'x4'],
+         )
+
+plt.show()

### 2020-10-17 Train/SPConst.py

@@ -13,7 +13,7 @@ CNNParams = {
 from keras.optimizers import *
 RNNParams = {
     'train_batch_size':128,
-    'train_epochs_num':2000,
+    'train_epochs_num':1000,
     'train_base_learning_rate':0.0001,
     'optimizer':Adamax,
     'rnn_save_file':'SPBestRNN.h5',
@@ -22,7 +22,8 @@ RNNParams = {
     'rnn_last_activation':'sigmoid',
     'rnn_use_context_state':True,
     'rnn_last_use_bias':False,
-    'rnn_unit_num':200
+    'rnn_unit_num':200,
+    'rnn_last_dropout':0.50
     }
 EnsembleParams = {
     'cnn_load_file':'SPBestCNN.h5',

### 2020-10-17 Train/TestH5.py

@@ -8,11 +8,18 @@ def get_score_at_test(model,input,label,issave=True,savepath=None):
     return 'MES:' + str(mse),'Spearman:' + str(spearmanr) , 'r2:' + str(r2)
 
 from ParamsUtil import *
-data = ReadData()
+
+dataset = 'WT'
+datas = ReadValidationData(dataset)
 from keras.models import load_model
-model = load_model('WTBestCNN.h5')
-print(get_score_at_test(model,
-                        data['input']['test']['onehot'],data['label']['test']))
-model = load_model('WTBestRNN.h5')
-print(get_score_at_test(model,
-                        data['input']['test']['onehot'],data['label']['test']))
+params = GetParams(dataset)
+filename = params['CNNParams']['cnn_save_file']
+time=0
+for data in datas:
+    time+=1
+    model = load_model('WTBestCNN.h5'+'_'+str(time))
+    print(get_score_at_test(model,
+                            data['input']['test']['onehot'],data['label']['test']))
+    #model = load_model('WTBestRNN.h5')
+    #print(get_score_at_test(model,
+                        #data['input']['test']['onehot'],data['label']['test']))

### 2020-10-17 Train/TrainRNN.py

@@ -93,7 +93,7 @@ def model(params):
     
     rnn_embedded = score
     #magic
-    rnn_embedded = Dropout(rate=0.05)(rnn_embedded)
+    rnn_embedded = Dropout(rate=params['rnn_last_dropout'])(rnn_embedded)
     output = Dense(units=1,kernel_regularizer=keras.regularizers.l2(0.001),kernel_constraint=keras.constraints.NonNeg(),
                    name='temporal_score',activation=params['rnn_last_activation'],
                    use_bias=params['rnn_last_use_bias'])(rnn_embedded)

### 2020-10-17 Train/Validation.py

@@ -6,22 +6,79 @@ from TrainRNN import train as RNN
 from TrainCNN import train as CNN
 from Ensemble import train as Ensemble
 
-def ValidateCNN(dataset):
+def ValidateCNN(dataset,validateall=True,validateat=0):
     datas = ReadValidationData(dataset)
     result = []
     time = 0
+    params = GetParams(dataset)
+    filename = params['CNNParams']['cnn_save_file']
     for data in datas:
-        time+=1
-        params = GetParams(dataset)
-        params['cnn_save_file'] = params['cnn_save_file']+'_'+str(time)
+        time += 1
+        if not validateall:
+            if validateat > time:
+                continue
+            elif validateat < time:
+                break
+        params['CNNParams']['cnn_save_file'] = filename + '_'+str(time)
         input = data['input']
         label = data['label']
         r = None
         r = CNN(params['CNNParams'],input['train']['onehot'],label['train'],
              input['test']['onehot'],label['test'],issave=True)
-        result.append(r.best)
+        result.append(r['loss'])
 
         print(result)
+def ValidateRNN(dataset,validateall=True,validateat=0):
+    datas = ReadValidationData(dataset)
+    result = []
+    time = 0
+    params = GetParams(dataset)
+    filename = params['RNNParams']['rnn_save_file']
+    for data in datas:
+        time += 1
+        if not validateall:
+            if validateat > time:
+                continue
+            elif validateat < time:
+                break
+        params['RNNParams']['rnn_save_file'] = filename + '_'+str(time)
+        input = data['input']
+        label = data['label']
+        r = None
+        r = RNN(params['RNNParams'],input['train']['onehot'],label['train'],
+             input['test']['onehot'],label['test'],issave=True)
+        result.append(r['loss'])
+        print(result)
+def ValidateEnsemble(dataset,withbiofeature=False,validateall=True,validateat=0):
+    datas = ReadValidationData(dataset)
+    result = []
+    time = 0
+    params = GetParams(dataset)
+    cnnfilename = params['EnsembleParams']['cnn_load_file']
+    rnnfilename = params['EnsembleParams']['rnn_load_file']
+    ensemblefilename = params['EnsembleParams']['ensemble_save_file']
+    for data in datas:
+        time += 1
+        if not validateall:
+            if validateat > time:
+                continue
+            elif validateat < time:
+                break
[…]

### 2020-10-17 Train/WTConst.py

@@ -13,7 +13,7 @@ CNNParams = {
 from keras.optimizers import *
 RNNParams = {
     'train_batch_size':128,
-    'train_epochs_num':2000,
+    'train_epochs_num':1000,
     'train_base_learning_rate':0.0001,
     'optimizer':Adamax,
     'rnn_save_file':'WTBestRNN.h5',
@@ -22,15 +22,16 @@ RNNParams = {
     'rnn_last_activation':'sigmoid',
     'rnn_use_context_state':True,
     'rnn_last_use_bias':False,
-    'rnn_unit_num':100
+    'rnn_unit_num':100,
+    'rnn_last_dropout':0.05
     }
 EnsembleParams = {
     'cnn_load_file':'WTBestCNN.h5',
     'rnn_load_file':'WTBestRNN.h5',
     'ensemble_save_file':'WTEnsemble.h5',
     'train_batch_size':128,
-    'train_epochs_num':10,
-    'train_base_learning_rate':0.001,
+    'train_epochs_num':20,
+    'train_base_learning_rate':0.00005,
     'bio_fc_hidden_layer_num':1,
     'bio_fc_hidden_layer_units_num':87,
     'bio_fc_dropout':0.05

### 2020-10-18 Paper/main.tex
10-17 data
10-18 paper

@@
 \begin{equation}
-\left\{\begin{matrix}
+\left\{\begin{array}{l}
 X_{mc} = f^{3\times4}(X_{oh})
@@
 \\X_{rf} = A_s\otimes X_{oh}
-\end{matrix}\right.\label{eq:11}
+\end{array}\right.\label{eq:11}
 \end{equation}
@@
 \begin{equation}
-\left\{\begin{matrix}
+\left\{\begin{array}{l}
 K_i=Encoder({X_e}_i,\theta_E,K_{i-1})
@@
 \\V=K 
-\end{matrix}\right.\label{eq:14}
+\end{array}\right.\label{eq:14}
 \end{equation}
@@
 \section{Results}
-
+\begin{figure*}[!tpb]%figure4
+    \centerline{\includegraphics[width=178mm]{baselinewithoutbiofeat.eps}}
+    \caption{wait2write}\label{fig:06}
+    \end{figure*}
 We designed experiments to address the following questions:
@@
     \item 
-    Whether the stacking of method in spatial domain and temporal domain can get better performance then use these method alone? 
+    In the absence of hand-crafted biological features, whether the stacking of method in spatial domain and temporal domain can get better performance then use these method alone? 
     $\rightarrow$ Section~\ref{section:stacking}
@@
 Text
+\begin{table}[!tpb]
+    \processtable{wait2write\label{Tab:02}} 
+    {\begin{tabular}{@{}llll@{}}\toprule
+        Method & WT-SpCas9 & eSpCas9(1.1) & SpCas9-HF1\\\midrule
+        XGBoost & 0.845 & 0.831 & 0.818\\
+        MLP & 0.842 & 0.846 & 0.844\\
+        CNN & 0.846 & 0.831 & 0.834\\
+        RNN & 0.856 & 0.849 & 0.851\\
+        TAC & 0.857 & 0.844 & 0.851\\
+        SpAC & 0.862 & 0.854 & 0.857\\
+        \textbf{EnAC} & \textbf{0.868} & \textbf{0.859} & \textbf{0.862}\\
+        CRISPRpred(SEQ) & 0.838 & 0.830 & 0.821\\
+        \botrule
+    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: wait2write}
+\end{table}
 

### 2020-10-19 Paper/main.tex
10-19 paper

@@
 
-Text
+In Table~\ref{Tab:02}, we list the performance of methods in spatial or temporal domain and the stacking of methods. 
+Temporal AttCRISPR, TAC for short, achieved Spearman correlation coefficients of 0.857, 0.844, 0.851 in above three dataset. 
+Spatial AttCRISPR, SpAC for short, corresponds to 0.862, 0.854, 0.857. In the absence of hand-crafted biological features. 
+Ensemble AttCRISPR achieve the best performance of our knowledge, corresponds to 0.868, 0.859, 0.862. 
 \begin{table}[!tpb]
@@
 
-Text
+text
 

### 2020-10-19 Paper/main.tex
10-19 paper

@@
 Ensemble AttCRISPR achieve the best performance of our knowledge, corresponds to 0.868, 0.859, 0.862.
+
+In addition, in Table~\ref{Tab:02}, the performance of other methods without using hand-crafted biological features, are also recorded. 
+Regardless of the method we developed, RNN reported by \citeauthor{wang2019optimized}, which can be categorized as the method in temporal domain, 
+is the most predictive with Spearman correlation coefficients of 0.856, 0.849, 0.851. 
+It's obvious that the ensemble AttCRISPR is better at prediction (Figure~6\vphantom{\ref{fig:06}}a-c). 
+Furthermore, the prediction ability of models could be boosted by addition of other hand-crafted biological features, which can't be obtained directly by sequence information.
+
+Hence, the second experiment is designed to compare the performance of standard AttCRISPR (hand-crafted biological features are used to improve performance of ensemble AttCRISPR)
+ and current state-of-the-art method, DeepHF (the RNN mentioned above integrated with hand-crafted biological features).
 \begin{table}[!tpb]

### 2020-10-19 Train/ESPConst.py
10-19 code

@@ -31,10 +31,10 @@ EnsembleParams = {
     'rnn_load_file':'ESPBestRNN.h5',
     'ensemble_save_file':'ESPEnsemble.h5',
     'train_batch_size':128,
-    'train_epochs_num':20,
+    'train_epochs_num':30,
     'train_base_learning_rate':0.00005,
-    'bio_fc_hidden_layer_num':1,
-    'bio_fc_hidden_layer_units_num':87,
+    'bio_fc_hidden_layer_num':2,
+    'bio_fc_hidden_layer_units_num':150,
     'bio_fc_dropout':0.05
     }
 FineTuning = {
@@ -42,11 +42,11 @@ FineTuning = {
     'rnn_load_file':'ESPBestRNN.h5',
     'ensemble_load_file':'ESPEnsemble.h5',
     'ensemble_save_file':'ESPFineTuning.h5',
-    'train_batch_size':16,
-    'train_epochs_num':300,
+    'train_batch_size':128,
+    'train_epochs_num':100,
     'train_base_learning_rate':0.00002,
-    'bio_fc_hidden_layer_num':1,
-    'bio_fc_hidden_layer_units_num':87,
+    'bio_fc_hidden_layer_num':2,
+    'bio_fc_hidden_layer_units_num':150,
     'bio_fc_dropout':0.05
     }
 ParamsRanges = {

### 2020-10-19 Train/SPConst.py

@@ -29,11 +29,11 @@ EnsembleParams = {
     'cnn_load_file':'SPBestCNN.h5',
     'rnn_load_file':'SPBestRNN.h5',
     'ensemble_save_file':'SPEnsemble.h5',
-    'train_batch_size':16,
-    'train_epochs_num':10,
-    'train_base_learning_rate':0.00002,
-    'bio_fc_hidden_layer_num':1,
-    'bio_fc_hidden_layer_units_num':87,
+    'train_batch_size':128,
+    'train_epochs_num':20,
+    'train_base_learning_rate':0.00005,
+    'bio_fc_hidden_layer_num':2,
+    'bio_fc_hidden_layer_units_num':150,
     'bio_fc_dropout':0.05
     }
 FineTuning = {
@@ -41,11 +41,11 @@ FineTuning = {
     'rnn_load_file':'SPBestRNN.h5',
     'ensemble_load_file':'SPEnsemble.h5',
     'ensemble_save_file':'SPFineTuning.h5',
-    'train_batch_size':16,
-    'train_epochs_num':300,
+    'train_batch_size':128,
+    'train_epochs_num':100,
     'train_base_learning_rate':0.00002,
-    'bio_fc_hidden_layer_num':1,
-    'bio_fc_hidden_layer_units_num':87,
+    'bio_fc_hidden_layer_num':2,
+    'bio_fc_hidden_layer_units_num':150,
     'bio_fc_dropout':0.05
     }
 ParamsRanges = {

### 2020-10-19 Train/Validation.py

@@ -78,7 +78,38 @@ def ValidateEnsemble(dataset,withbiofeature=False,validateall=True,validateat=0)
              withbiofeature=withbiofeature)
         result.append(r['loss'])
         print(result)
+
+def ValidateFineTuning(dataset,validateall=True,validateat=0):
+    datas = ReadValidationData(dataset)
+    result = []
+    time = 0
+    params = GetParams(dataset)
+    cnnfilename = params['FineTuning']['cnn_load_file']
+    rnnfilename = params['FineTuning']['rnn_load_file']
+    ensemblefilename = params['FineTuning']['ensemble_load_file']
+    finetuningfilename = params['FineTuning']['ensemble_save_file']
+    for data in datas:
+        time += 1
+        if not validateall:
+            if validateat > time:
+                continue
+            elif validateat < time:
+                break
+        input = data['input']
+        label = data['label']
+        params['FineTuning']['cnn_load_file'] = cnnfilename+'_'+str(time)
+        params['FineTuning']['rnn_load_file'] = rnnfilename+'_'+str(time)
+        params['FineTuning']['ensemble_load_file'] = ensemblefilename+'_'+str(time)
+        params['FineTuning']['ensemble_save_file'] = finetuningfilename+'_'+str(time)
+        r = None
+        r = Ensemble(params['FineTuning'],input['train']['onehot'],input['train']['biofeat'],label['train'],
+             input['test']['onehot'],input['test']['biofeat'],label['test'],issave=True,
+             withbiofeature=True,rnn_trainable=True,cnn_trainable=True)
+        result.append(r['loss'])
+        print(result)
 if __name__ == "__main__":
     #ValidateRNN('ESP',validateall=False,validateat=1)
     #ValidateCNN('ESP',validateall=True)
-    ValidateEnsemble('WT',withbiofeature=False,validateall=True)
+    #ValidateEnsemble('WT',withbiofeature=False,validateall=True)
+    #ValidateEnsemble('WT',withbiofeature=True,validateall=True)
+    ValidateFineTuning('WT',validateall=True,validateat=0)

### 2020-10-19 Train/WTConst.py

@@ -30,10 +30,10 @@ EnsembleParams = {
     'rnn_load_file':'WTBestRNN.h5',
     'ensemble_save_file':'WTEnsemble.h5',
     'train_batch_size':128,
-    'train_epochs_num':20,
+    'train_epochs_num':10,
     'train_base_learning_rate':0.00005,
-    'bio_fc_hidden_layer_num':1,
-    'bio_fc_hidden_layer_units_num':87,
+    'bio_fc_hidden_layer_num':2,
+    'bio_fc_hidden_layer_units_num':200,
     'bio_fc_dropout':0.05
     }
 FineTuning = {
@@ -41,11 +41,11 @@ FineTuning = {
     'rnn_load_file':'WTBestRNN.h5',
     'ensemble_load_file':'WTEnsemble.h5',
     'ensemble_save_file':'WTFineTuning.h5',
-    'train_batch_size':16,
-    'train_epochs_num':300,
+    'train_batch_size':128,
+    'train_epochs_num':100,
     'train_base_learning_rate':0.00002,
-    'bio_fc_hidden_layer_num':1,
-    'bio_fc_hidden_layer_units_num':87,
+    'bio_fc_hidden_layer_num':2,
+    'bio_fc_hidden_layer_units_num':200,
     'bio_fc_dropout':0.05
     }
 ParamsRanges = {

### 2020-10-21 Paper/main.tex
10-21 paper

@@
 \copyrightyear{2020} \pubyear{2020}
+\usepackage{booktabs}
 
@@
     \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: The method with superscript of $^*$ and $^{\#}$ is reported by \citeauthor{wang2019optimized} and \citeauthor{MuhammadRafid2020} respectively.
-We use the conclusion of corresponding paper as the performance indicators of the model directly. 
 Specially, CRISPRpred(SEQ) take another set of hand-crafted sequence-based feature to improve performance.}
@@
 \section{Results}
-\begin{figure*}[!tpb]%figure4
-    \centerline{\includegraphics[width=178mm]{baselinewithoutbiofeat.eps}}
-    \caption{wait2write}\label{fig:06}
-    \end{figure*}
+\begin{figure}[!tpb]%figure4
+    \centerline{\includegraphics[width=86mm]{baselinewithoutbiofeat.eps}}
+    \caption{In the absence of hand-crafted biological features, performance of different algorithms for sgRNA activity prediction. 
+    (a)-(c) The performance of Temporal AttCRISPR, Spatial AttCRISPR and Ensemble AttCRISPR. 
+    The half-violin plots show the mean and distribution of the Spearman correlation coefficient between predicted and measured sgRNA activity scores over all tests. 
+    (e)-(g) In the absence of hand-crafted biological features, the performance of all prediction methods in these datasets as far as we know. 
+    The $mean \pm s.d.$ of the Spearman correlation coefficient between predicted and measured sgRNA activity scores are shown in the bar plots.}\label{fig:06}
+\end{figure}
 We designed experiments to address the following questions:
@@
 is the most predictive with Spearman correlation coefficients of 0.856, 0.849, 0.851. 
-It's obvious that the ensemble AttCRISPR is better at prediction (Figure~6\vphantom{\ref{fig:06}}a-c). 
+It's obvious that the ensemble AttCRISPR is better at prediction (Figure~6\vphantom{\ref{fig:06}} a-c). 
 Furthermore, the prediction ability of models could be boosted by addition of other hand-crafted biological features, which can't be obtained directly by sequence information.
@@
 \begin{table}[!tpb]
-    \processtable{wait2write\label{Tab:02}} 
-    {\begin{tabular}{@{}llll@{}}\toprule
+    \processtable{
+    Performance comparisons for different methods in the absence of hand-crafted biological features 
+    (take Spearman correlation coefficient as evaluation index)\label{Tab:02}} 
+    {\begin{tabular}{@{}lccc@{}}\toprule
         Method & WT-SpCas9 & eSpCas9(1.1) & SpCas9-HF1\\\midrule
-        XGBoost & 0.845 & 0.831 & 0.818\\
-        MLP & 0.842 & 0.846 & 0.844\\
-        CNN & 0.846 & 0.831 & 0.834\\
-        RNN & 0.856 & 0.849 & 0.851\\
+        XGBoost$^*$ & 0.845 & 0.831 & 0.818\\
+        MLP$^*$ & 0.842 & 0.846 & 0.844\\
+        CNN$^*$ & 0.846 & 0.831 & 0.834\\
+        RNN$^*$ & 0.856 & 0.849 & 0.851\\
         TAC & 0.857 & 0.844 & 0.851\\
         SpAC & 0.862 & 0.854 & 0.857\\
-        \textbf{EnAC} & \textbf{0.868} & \textbf{0.859} & \textbf{0.862}\\
-        CRISPRpred(SEQ) & 0.838 & 0.830 & 0.821\\
+        EnAC & \textbf{0.868} & \textbf{0.859} & \textbf{0.862}\\
+        CRISPRpred(SEQ)$^{\#}$ & 0.838 & 0.830 & 0.821\\
         \botrule
-    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: wait2write}
+    \end{tabular}}{}
+    \processtable{
+    Performance comparisons for methods before and after integrating with hand-crafted biological features
+(take Spearman correlation coefficient as evaluation index)\label{Tab:03}} 
+    {\begin{tabular}{lcccccc}\toprule
+        & \multicolumn{2}{c}{WT-SpCas9} & \multicolumn{2}{c}{eSpCas9(1.1)} & \multicolumn{2}{c}{SpCas9-HF} \\ 
+        \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \noalign{\smallskip} 
+        Method & Mean  & \begin{tabular}[c]{@{}l@{}}Std Dev\\ ($\times 10^{-3}$)\end{tabular} & Mean & \begin{tabular}[c]{@{}l@{}}Std Dev\\ ($\times 10^{-3}$)\end{tabular} & Mean & \begin{tabular}[c]{@{}l@{}}Std Dev\\ ($\times 10^{-3}$)\end{tabular} \\ \hline
+        RNN$^*$ & 0.856 & 3.33 & 0.849 & 5.00 & 0.851 & 4.11 \\
+        EnAC   & 0.868 & 2.66 & 0.859 & 4.66 & 0.862 & 3.19 \\
+        DeepHF$^*$ & 0.867 & \textbf{2.37} & 0.862 & 4.24 & 0.860 & 3.21 \\
+        StAC   & \textbf{0.872} & 2.55 & \textbf{0.867} & \textbf{3.71} & \textbf{0.867} & \textbf{2.65} \\
+     \botrule
+\end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: 
+The method with superscript of $^*$ and $^{\#}$ is reported by \citeauthor{wang2019optimized} and \citeauthor{MuhammadRafid2020} respectively. 
+In the tables, we use the results reported in the relevant paper as the performance of the method directly.}
 \end{table}
@@
 
-text
+In order to make the comparison apples to apples, 
+we follow Equation~(\ref{eq:20}) to modify the ensemble method and design the control experiment using the same strategy to validate the conclusion that integrating with hand-crafted biological features can improve the predictive performance of methods.
+What's more, we compare the standard AttCRISPR and current state-of-the-art method, DeepHF, and show the results in Table~\ref{Tab:03}.
+
+As shown in Table~\ref{Tab:03}, in the absence of hand-crafted biological features, AttCRISPR has significant advantages over DeepHF in predictability. 
+Further, integration with the hand-crafted biological features can also improve the performance of AttCRISPR, and achieve Spearman correlation coefficients of 0.872, 0.867 and 0.867 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively.
+Meanwhile, current state-of-the-art method, DeepHF achieve 0.867, 0.862 and 0.860 respectively.
+After integrating with biological features, the performance gap between AttCRISPR and DeepHF is shortened, while AttCRISPR still has better performance.
+In addition, we also compare the standard deviation of data obtained in ten tests, which are shown in Table~\ref{Tab:03}.
+It reveal that AttCRISPR is more stable than DeepHF.
+
+\begin{figure}[!tpb]%figure4
+    \centerline{\includegraphics[width=86mm]{baselinewithbiofeat.eps}}
+    \caption{wait2write}\label{fig:07}
+\end{figure}
 
@@
 
-Text
-
-\vspace*{-12pt}
+Text\vspace*{-12pt}
 
@@
 \bibliographystyle{natbib}
-%\bibliographystyle{achemnat}
-%\bibliographystyle{plainnat}
-%\bibliographystyle{abbrv}
-%\bibliographystyle{bioinformatics}
-%
-%\bibliographystyle{plain}
-%
 \bibliography{document}

### 2020-10-22 Paper/main.tex
10-22 paper

@@
     \centerline{\includegraphics[width=86mm]{baselinewithbiofeat.eps}}
-    \caption{wait2write}\label{fig:07}
+    \caption{
+Performance comparisons for methods before and after integrating with hand-crafted biological features, 
+where DeepHF is the RNN integrated with hand-crafted biological features, 
+and StAC is the EnAC integrated with hand-crafted biological features. 
+The box plot show the mean and distribution of Spearman correlation coefficient between predicted and measured sgRNA activity scores over all tests.
+}\label{fig:07}
 \end{figure}

### 2020-10-23 Paper/main.tex
10-23 paper

@@
 
+To some extent, the attention module in the AttCRISPR can help us to understand the decisions it makes. 
+In the following sections, we will analyze the insight into activity of sgRNA bring through the attention mechanism at both global and local levels.
+
+In the following content, when we use the word, global, we are referring to rules thats are common throughout the data set. 
+If assumed the method with strong generalization ability, it might mean that these rules is common in the corresponding Cas9 system.
+On the other hand, local refers to the rules applicable to a certain sgRNA. 
+We believe that the locally interpretable is very helpful in the design and optimization of sgRNA.
+\begin{figure*}[!tpb]%figure4
+    \centerline{\includegraphics[width=178mm]{spatialattention.eps}}
+    \caption{wait2write}\label{fig:06}
+\end{figure*}
+
+\subsubsection{Globally interpretable}
+
+At global level, a important question we want AttCRISPR to answer is which nucleotide it prefers at each position on the sequence. 
+In fact, \citeauthor{wang2019optimized} has already answered this question in detail with the DeepSHAP method.
+Leaving aside nucleotides, just consider the importance of each position, the method of \citeauthor{Liu2019} goes some way to answering this question.
+
+\subsubsection{Locally interpretable}
+
 Text

### 2020-10-24 Paper/main.tex
10-24 paper

@@
     which greatly increases the difficulty of understanding the decisions of model.
-    }\label{fig:01}
+    }\label{fig:category}
 \end{figure}
@@
  Most of the deep neural network existing are the combination of recurrent neural network (RNN), convolutional neural network (CNN), fully connected neural network (FNN), and their variants. 
- As Figure~1\vphantom{\ref{fig:01}} show,  
+ As Figure~\ref{fig:category} show,  
  We found that the deep learning models used in sgRNA on-target activity (even for off-target effect) prediction tasks in recent years can be divided into the following two categories according to the encoding approach of the sgRNA sequence (sgRNA-DNA sequence pair, for off-target effect prediction):
@@
     In the last step, we flatten the output of convolutional neural network into a one dimensional vector and 
-    use a multilayer perceptron with sigmoid activation function to achieve the spatial output $y_s$.}\label{fig:02}
+    use a multilayer perceptron with sigmoid activation function to achieve the spatial output $y_s$.}\label{fig:CNN}
 \end{figure}
-As Figure~2\vphantom{\ref{fig:02}} show, method in spatial domain relies on the convolutional neural network. 
+As Figure~\ref{fig:CNN} show, method in spatial domain relies on the convolutional neural network. 
 As previously mentioned, sgRNA sequence has been encoded into a $21\times 4$ one-hot matrix $X_{oh}$, and we regard $X_{oh}$ as a binary image. 
@@
     which generates the spatial first-order preference matrix $A_s$.
-    }\label{fig:03}
+    }\label{fig:spatialmodule}
 \end{figure}
 
-As Figure~3\vphantom{\ref{fig:03}} show, Given an one-hot map $X_{oh}$, spatial attention module generating spatial attention matrix 
+As Figure~\ref{fig:spatialmodule} show, Given an one-hot map $X_{oh}$, spatial attention module generating spatial attention matrix 
 $A_s\in\mathbb{R}^{l\times 4}$ with the same as $X_{oh}$ in shape. 
@@
 \subsubsection{Method and attention in temporal domain}
-As Figure~4\vphantom{\ref{fig:04}} show, temporal domain part of AttCRISPR relies on the recurrent neural network (or its variant). 
+As Figure~\ref{fig:04} show, temporal domain part of AttCRISPR relies on the recurrent neural network (or its variant). 
 As previously mentioned, we mapping each one-hot vector into a dense real-valued high-dimensional space follow the Equation~(\ref{eq:08}), which generates the embedded matrix $X_e$.
@@
 
-As Figure~5\vphantom{\ref{fig:05}} show, in our attention module they are calculated by the following equation
+As Figure~\ref{fig:05} show, in our attention module they are calculated by the following equation
 \begin{equation}
@@
     }\label{fig:04}
+\end{figure}
+\begin{figure}[!tpb]
 \centerline{\includegraphics[width=86mm]{temporalattentionmodule.png}}
@@
 \begin{table}[!tpb]
-    \processtable{The methods compared in our work and brief description of these methods\label{Tab:01}} 
+    \processtable{The methods compared in our work and brief description of these methods\label{Tab:baseline}} 
     {\begin{tabular}{@{}lllp{3.5cm}l@{}}\toprule
@@
 Our baselines have a comprehensive coverage of the methods tested in these datasets. 
-In Table~\ref{Tab:01}, we annotate some properties of these baselines (is/isn't neural models, is/isn't end2end models)
+In Table~\ref{Tab:baseline}, we annotate some properties of these baselines (is/isn't neural models, is/isn't end2end models)
 All the experiments were carried out in Python 3.6 using Keras 2.2.4 and one GeForce RTX 2080Ti Super was used for training and testing if needed.
@@
 \section{Results}
-\begin{figure}[!tpb]%figure4
+\begin{figure}[!tpb]
     \centerline{\includegraphics[width=86mm]{baselinewithoutbiofeat.eps}}
@@
     The half-violin plots show the mean and distribution of the Spearman correlation coefficient between predicted and measured sgRNA activity scores over all tests. 
-    (e)-(g) In the absence of hand-crafted biological features, the performance of all prediction methods in these datasets as far as we know. 
+    (d)-(f) In the absence of hand-crafted biological features, the performance of all prediction methods in these datasets as far as we know. 
     The $mean \pm s.d.$ of the Spearman correlation coefficient between predicted and measured sgRNA activity scores are shown in the bar plots.}\label{fig:06}
@@
 
-In Table~\ref{Tab:02}, we list the performance of methods in spatial or temporal domain and the stacking of methods. 
+In Table~\ref{Tab:withoutbiofeature}, we list the performance of methods in spatial or temporal domain and the stacking of methods. 
 Temporal AttCRISPR, TAC for short, achieved Spearman correlation coefficients of 0.857, 0.844, 0.851 in above three dataset. 
@@
 
-In addition, in Table~\ref{Tab:02}, the performance of other methods without using hand-crafted biological features, are also recorded. 
+In addition, in Table~\ref{Tab:withoutbiofeature}, the performance of other methods without using hand-crafted biological features, are also recorded. 
 Regardless of the method we developed, RNN reported by \citeauthor{wang2019optimized}, which can be categorized as the method in temporal domain, 
 is the most predictive with Spearman correlation coefficients of 0.856, 0.849, 0.851. 
-It's obvious that the ensemble AttCRISPR is better at prediction (Figure~6\vphantom{\ref{fig:06}} a-c). 
+It's obvious that the ensemble AttCRISPR is better at prediction (Figure~\ref{fig:06} a-c). 
 Furthermore, the prediction ability of models could be boosted by addition of other hand-crafted biological features, which can't be obtained directly by sequence information.
@@
     Performance comparisons for different methods in the absence of hand-crafted biological features 
-    (take Spearman correlation coefficient as evaluation index)\label{Tab:02}} 
+    (take Spearman correlation coefficient as evaluation index)\label{Tab:withoutbiofeature}} 
     {\begin{tabular}{@{}lccc@{}}\toprule
@@
     Performance comparisons for methods before and after integrating with hand-crafted biological features
-(take Spearman correlation coefficient as evaluation index)\label{Tab:03}} 
+(take Spearman correlation coefficient as evaluation index)\label{Tab:withbiofeature}} 
     {\begin{tabular}{lcccccc}\toprule
@@
 we follow Equation~(\ref{eq:20}) to modify the ensemble method and design the control experiment using the same strategy to validate the conclusion that integrating with hand-crafted biological features can improve the predictive performance of methods.
-What's more, we compare the standard AttCRISPR and current state-of-the-art method, DeepHF, and show the results in Table~\ref{Tab:03}.
+What's more, we compare the standard AttCRISPR and current state-of-the-art method, DeepHF, and show the results in Table~\ref{Tab:withbiofeature}.
 
-As shown in Table~\ref{Tab:03}, in the absence of hand-crafted biological features, AttCRISPR has significant advantages over DeepHF in predictability. 
+As shown in Table~\ref{Tab:withbiofeature}, in the absence of hand-crafted biological features, AttCRISPR has significant advantages over DeepHF in predictability. 
 Further, integration with the hand-crafted biological features can also improve the performance of AttCRISPR, and achieve Spearman correlation coefficients of 0.872, 0.867 and 0.867 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively.
@@
 After integrating with biological features, the performance gap between AttCRISPR and DeepHF is shortened, while AttCRISPR still has better performance.
-In addition, we also compare the standard deviation of data obtained in ten tests, which are shown in Table~\ref{Tab:03}.
+In addition, we also compare the standard deviation of data obtained in ten tests, which are also shown in Table~\ref{Tab:withbiofeature}.
 It reveal that AttCRISPR is more stable than DeepHF.
@@
 On the other hand, local refers to the rules applicable to a certain sgRNA. 
-We believe that the locally interpretable is very helpful in the design and optimization of sgRNA.
-\begin{figure*}[!tpb]%figure4
+We believe that the local interpretability is very helpful in the design and optimization of sgRNA.
+\begin{figure*}[!tpb]
     \centerline{\includegraphics[width=178mm]{spatialattention.eps}}
-    \caption{wait2write}\label{fig:06}
+    \caption{Preference for each position-dependent nucleotide on the sgRNA sequence. 
+(a)-(c) Bars show the score of preference after standardization, and the higher the number, the more positive it is for activity of sgRAN. 
+The numbers below indicated the position of the nucleotides on-target DNA. 
+(d)-(f) Preference surfaces for each position-dependent nucleotide fitted with Bézier surfaces. 
+Each position-dependent nucleotide is a control point. 
+The coordinates of the control points on the vertical axis represent the degree of preference, 
+and the higher the position-dependent nucleotide corresponding to the control point is, the more positive it is for the activity of sgRAN.
+The contour plots at the bottom show the area of position-dependent nucleotides which have different contribution to the activity of sgRNA. 
+}\label{fig:spatialattention}
 \end{figure*}
 
-\subsubsection{Globally interpretable}
+\subsubsection{Global interpretability}
 
@@
 In fact, \citeauthor{wang2019optimized} has already answered this question in detail with the DeepSHAP method.
-Leaving aside nucleotides, just consider the importance of each position, the method of \citeauthor{Liu2019} goes some way to answering this question.
+Leaving aside nucleotides, just consider the importance of each position, the method of \citeauthor{Liu2019} have gone some way too. 
+While our method is not based on the post hoc explanations techniques and input perturbations, the only work we need to do is to get the first-order preference $A$ generated by the attention module.
+Specifically, we use the first-order preference $A_s$ generated by the spatial attention module instead of  $\tilde{A}$ generated by the temporal attention module. 
+The latter is in a higher dimensional dense space which make it difficult to understand. 
+In practice, we input every sgRNA into the spatial AttCRISPR, in order to obtain the $A_s$ from the spatial attention module and take its mean value. 
+Then we rescale it through Z-score to obtain a standardization value and the final result is shown in Figure~\ref{fig:spatialattention}.
 
-\subsubsection{Locally interpretable}
+As shown in Figure~\ref{fig:spatialattention}, we captured the preference for each position-dependent nucleotide on the sgRNA sequence. 
+The result revealed that A and G typically have a positive contribution to the activity of sgRNA, while T typically have a negative contribution. 
+It is agree with the previous conlusion that when Cas9 is binding sgRNA, it prefer the one containing purines to pyrimidines \citep{wang2014genetic}. 
+In addition, global interpretability also pointed out that distinct from other nucleotides, G is strongly favored at position 20. 
+This is consistent with the conclusions of several other reports \citep{Wong2015,Doench2014}.
+
+Furthermore, the preference of the nucleotide at the same position doesn't change dramatically with the Cas9 nucleases, 
+while we still notice that compared with the other two datasets, 
+C makes a more positive contribution to the activity of sgRNA with the SpCas9-HF1 especially in the position 5, which is evident in Figure~\ref{fig:spatialattention} d-f.
+
+The above discussion shows that, in the task of sgRNA activity prediction, 
+attention mechanism can help us understand the decision made by AttCRISPR and reveal the insight into activity of sgRNA. 
+Some of them are consistent with the conclusion accepted current.
+
+\subsubsection{Local interpretability}
 
@@
 
-Text\vspace*{-12pt}
+Text
+\vspace*{-12pt}
 
@@
 
- text.\vspace*{-12pt}
+Text
+\vspace*{-12pt}
 

### 2020-10-26 Train/GetModelAttention.py
10-26 paper&attention code

@@ -9,81 +9,67 @@ from sklearn.model_selection import train_test_split
 import os
 #os.environ["CUDA_VISIBLE_DEVICES"] = "-1"
 
-pkl = open('WTData.pkl','rb') 
-x_onehot =  pickle.load(pkl)
-x_biofeat = pickle.load(pkl)
-y = pickle.load(pkl)
-x_seq = pickle.load(pkl)
-
-random_state=40
-test_size = 0.15
-x_train_onehot, x_test_onehot, y_train, y_test = train_test_split(x_onehot, y, test_size=test_size, random_state=random_state)
-x_train_biofeat, x_test_biofeat, y_train, y_test = train_test_split(x_biofeat, y, test_size=test_size, random_state=random_state)
-x_train_seq, x_test_seq, y_train, y_test = train_test_split(x_seq, y, test_size=test_size, random_state=random_state)
 
 from keras.callbacks import Callback
 from keras.callbacks import LambdaCallback
-x_attention_onehot = x_train_onehot
-x_attention_biofeat = x_train_biofeat
-x_attention_seq = x_train_seq
-y_attention = y_train
-def get_local_temporal_attention(model):
-    temporal_layer_model = Model(inputs=model.inputs[0],outputs=model.get_layer('temporal_attention').output)
-    temporal_attention = temporal_layer_model.predict(x_attention_onehot)
-    temporal_value = np.mean(temporal_attention, axis=0)
-    ##normalize
-    for i in range(21):
-        sum = 0
-        for j in range(21):
-            sum+=temporal_value[i][j]
-        for j in range(21):
-            temporal_value[i][j] = temporal_value[i][j]/sum
-    answer = []
-    sums = []
-    for i in range(21):
-        sum = 0
-        for j in range(21):
-            sum += temporal_value[i][j]
-        sums.append(sum)
-    for i in range(21):
-        preanswer = []
-        for k in range(21):
-            time = 10*temporal_value[i][k]/sums[i]+0.5
-            time = int(time)
-            for t in range(time):
-                answer.append('A'+str(i)+','+'B'+str(k))
-    return answer
+x_attention_onehot = None
+x_attention_biofeat = None
+x_attention_seq = None
+y_attention = None
+def ReadData(dataset):
[…]

### 2020-10-27 Train/GetModelAttention.py
10-27 data

@@ -47,19 +47,15 @@ def get_local_temporal_attention(model,index):
     #second = second_layer_model.predict(onehot)
     second = second_layer_model.predict(onehot)
     second = np.mean(second,axis=0)
-    baseline = np.matmul(baseline,second)
+    for j in range(second.shape[1]):
+        sum = 0
+        for i in range(second.shape[0]):
+            sum+=second[i][j]
+        for i in range(second.shape[0]):
+            second[i][j] = second[i][j]/sum
+    np.savetxt(str(index)+'_second.csv',second,fmt='%.5f',delimiter=',')
     np.savetxt(str(index)+'.csv',baseline,fmt='%.5f',delimiter=',')
-    return None
 def get_temporal_attention(model):
-    
-    second_layer_model = Model(
-        inputs=model.inputs[0],outputs=model.get_layer('temporal_attention').output)
-    #second = second_layer_model.predict(onehot)
-    second = second_layer_model.predict(x_attention_onehot)
-    second = np.mean(second,axis=0)
-    scale = np.sum(second)/21
-
-
     last_layer_weight = model.get_layer('temporal_score').get_weights()[0].reshape((-1))
     temporal_layer_model = Model(
         inputs=model.inputs[0], outputs=model.get_layer('score_at_each_position').output)
@@ -67,9 +63,7 @@ def get_temporal_attention(model):
     score_at_each_position = temporal_layer_model.predict(x_attention_onehot)
     baseline = np.mean(score_at_each_position, axis=0)
     baseline = np.multiply(baseline,last_layer_weight)
-    baseline = baseline * scale
     np.savetxt('baseline.csv',baseline,fmt='%.5f',delimiter=',')
-    return None
 def get_spatial_attention(model):
     spatial_layer_model = Model(
         inputs=model.inputs[0], outputs=model.get_layer('spatial_attention_result').output)
@@ -204,8 +198,8 @@ cnnmodeldict = {'WT':'WTBestCNN.h5','ESP':'ESPBestCNN.h5','SP':'SPBestCNN.h5'}
 dataname = 'WT'
 ReadData(dataname)
 rnn_model = load_model('./'+rnnmodeldict[dataname])
-get_local_temporal_attention(rnn_model,7882)
 get_temporal_attention(rnn_model)
+get_local_temporal_attention(rnn_model,7882)
 
 
 cnn_model = load_model('./'+cnnmodeldict[dataname])

### 2020-10-28 Paper/main.tex
10-26 paper&attention code
10-28 paper

@@
 \begin{equation}
-y=\sum_i^lW_i\tilde{A}_i\cdot {X_e}_i\label{eq:05}
+y=W \cdot \tilde{A} {X_e}^{T}\label{eq:05}
 \end{equation}
- where $W\in\mathbb{R}^l$ denotes a non-negative weight vector, $W_i$ denotes the weight of the $i$-th position, ${X_e}_i$ denotes the embedding vector of the nucleotide at $i$-th position.
+ where $W\in\mathbb{R}^l$ denotes a non-negative weight vector. 
  Assume that in Equation~(\ref{eq:04}) the first-order original preference at each position is relatively independent and weight matrix $B$ is independent of any first-order original preference, 
@@
 
+\begin{table}[!tpb]
+    \processtable{Three sgRNA and their activity \label{Tab:optimum}} 
+    {\begin{tabular}{@{}lll@{}}\toprule
+        Index & sgRNA & Activity \\\midrule
+        8493 & ACATGACTTTGGATTTCCCCAGG & 0.831\\
+        8492 & ACATGACTTTGGATTCCCCCAGG & 0.869\\
+        8491 & ACATGACTTTGGACTTCCCCAGG & 0.861\\
+        \botrule
+    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{
+\emph{Index} represents its index in the source data (Supplementary Data 1), 
+\emph{Activity} represents its activity reported in WT-SpCas9 dataset. }
+\end{table}
+\begin{figure}[!tpb]
+    \centerline{\includegraphics[width=86mm]{local0.eps}}
+    \caption{
+The scores of sgRNA with index of 8493 obtained by the temporal AttCRISPR. 
+The bar plot reveals the score at each position at local level, while the line of dashes reveals the scores at global level. 
+At global level we calculated the scores of all sgRNA, then average the scores at each position to obtain the global level which can be used as base line and is helpful to judge the relative height of the scores.
+}\label{fig:opt}
+\end{figure}
+\begin{figure}[!tpb]
+    \centerline{\includegraphics[width=86mm]{secondorder.eps}}
+    \caption{wait2write}\label{fig:heatmap}
+\end{figure}
 Text

### 2020-10-28 Paper/main.tex
10-28 paper

@@
 
+At local level, we will analyze a case (consisting of three sgRNAs as Table~\ref{Tab:optimum} show), then answer two imortant question based on the local interpretability. 
+First, how to optimize a sgRNA with local interpretability to make it have more on-target activity. 
+Second, in the eyes of AttCRISPR, what are the reasons for the low activity of the sgRNA.
+
+For the first question, we input the least-active sgRNA in Table~\ref{Tab:optimum} (with the index of 8493 and the activity of 0.831, call source sgRNA for convenience) into the temporal AttCRISPR. 
+The score of each position is obtained based on Equation~(\ref{eq:05}) (the calculated symbol with $W$ is Hadamard product instead of dot product, in order to achieve the result in vector form), 
+and the results are shown in Figure~\ref{fig:opt}. 
+Acording to Figure~\ref{fig:opt}, scores at position 14 and 16 of source sgRNA are significantly below the base line 
+(in fact, the scores at position 6 and 11 is also noteworthy, however, we don't find sgRNA in the dataset for comparison). 
+If replaced the T at position 14 with C, would generate the same sgRNA as the one with index of 8491, which is with a activity value of 0.861. 
+If replaced the T at position 16 with C, would generate the same sgRNA as the one with index of 8492, which is with a activity value of 0.869. 
+Therefore, we could conclude that the local interpretability is helpful for us to optimize the sgRNA without exhaustively search.
+
 \begin{table}[!tpb]
@@
 \end{figure}
+
+Next,
+
 \begin{figure}[!tpb]
@@
 \end{figure}
-Text
 

### 2020-10-28 Paper/main.tex
10-28 paper

@@
 
-Next,
+The second question we want AttCRISPR to answer is why it give two low scores at position 14 and 16. 
+In practice, we will try to answer this question with second-order preference. 
+Let AttCRISPR output the second-order preference matrix $B$ corresponding to the source sgRNA, and show it in Figure~\ref{fig:heatmap}. 
+It is obvious that a few unusual bright spots appear in the red box in Figure~\ref{fig:heatmap}. 
+We believe that tells us the nucleotide at position 15 has a great effect on the score of position 14 andd 16 (instead of position 13 or 17, which corresponding position are relatively dim in color). 
+As shown in Table~\ref{Tab:optimum}, in source sgRNA there are three consecutive Ts at position 14, 15 and 16, and this may reveal that multiple consecutive Us on sgRNA would leads to low on-target activity of sgRNA, which is consistent with earlier report \citep{wu2014genome-wide}.
 
@@
     \centerline{\includegraphics[width=86mm]{secondorder.eps}}
-    \caption{wait2write}\label{fig:heatmap}
+    \caption{The visualization of second-order preference matrix $B$, 
+the elements in the $i$-th row and the $j$-th column represent the influence of nucleotide at position $j$ when generate the first-order preference $\tilde{A}$ at position $i$. 
+The warmer the color, the more important it is. 
+In the red box, a few unusual bright spots appear. 
+To be more specific, the nucleotide at position 15 has a great effect on the first-order preference at positon 14 and 16.
+}\label{fig:heatmap}
 \end{figure}

### 2020-10-29 Paper/main.tex
10-29 paper

@@
 
-\subsubsection{Local interpretability}
+\subsubsection{Local interpretability}\label{section:local}
 
@@
 
-Text
+In this article, we have introduced a new prediction methods, called AttCRISPR for the activity of sgRNA. 
+For the first time, we take the ensemble of both spatial and temporal domain to predict the on-target activity of sgRNA. 
+Throught ablation analysis and testing a series of possible network structure, we demonstrate that the ensemble method performs better than other methods on this task. 
+In addition, we apply attention modules in both the spatial and temporal parts of AttCRISPR, 
+and design two experiments combined with some early reports to prove that attention mechanisms can help researcher understand the decisions made by model which make it easy to optimize low activity sgRNA without exhaustively search.
+
+In Section~\ref{section:stacking}, we have tested both spatial and temporal domain AttCRISPR, and CNN (method in spatial domain), RNN (method in temporal domain) which reported by \citeauthor{wang2019optimized} in the absence of hand-crafted biological features.
+A worth noticing point is that there is a gap between spatial AttCRISPR and CNN, though the performance of temporal AttCRISPR is basically the same as that of RNN. 
+We suspect there are two possible reasons. 
+One is that attention modules can significantly improve the performance of the model, which is short of experimental validation, 
+and the other is the performance of the method in spatial domain is underestimated.
+
+In Section~\ref{section:comparison}, also integrating with hand-srafted biological features to improve the predictive performance, the performance gap between AttCRISPR and DeepHF is shortened, while AttCRISPR still has better performance.
+This may be a natural belief that with the primary biological sequence we can predict the functional and structural information. 
+Therefore, there is a limit to the improvement of the performance by integrating with hand-srafed biological features.
+
+In Figure~\ref{fig:heatmap} of Section~\ref{section:local}, we note that the brightness at coordinates (14, 15) and (16, 15) exceeds (14, 13) and (16, 17). 
+In other words, there are two unusual bright spots at coordinates (14, 15) and (16, 15). 
+This could explain that the nucleotide trimer at position 14, 15, 16 has a great influence on the decision made by AttCRISPR. 
+We believe that we can use a carefully designed $3\times 3$ convolution kernel, and move it along the diagonal of the second-order preference matrix $B$, 
+in order to find all kind of nucleotide trimer that have a great influence on the decision made by AttCRISPR. 
+However, due to the lack of validation method, we don't implement it in our work.
+
+The current architecture of AttCRISPR focuses on predicting the on-target activity of conventional sgRNA which have a PAM based on NGG. 
+However it can be extended to other Cas9 species, variants or off-target task easily.
 
@@
 
-Text
-
-\section*{Acknowledgements}
-
-Text
-\vspace*{-12pt}
-
-\section*{Funding}
-
-Text
-\vspace*{-12pt}
+In this paper, all the existing prediction method of sgRNA on-target activity are categorized as encoding-based spatial domain method and embedding-based temporal domain method, 
+according to the processing method of input sgRNA. 
+Then, we develop AttCRISPR, a ensemble method of both spatial method and temporal method follow the stacking strategy with strong interpretability. 
+AttCRISPR prove that the ensemble method have a better performance in the datasets of DeepHF
+and can compete with the current state-of-the-art method. 
+In addition, AttCRISPR apply attention mechanisms in both the temporal and spatial part, 
+and we explain the decisions made by AttCRISPR through the attention module which is consistent with earlier reports. 
+Further, we also point out that the output of the attention module can be used to optimize the low-activity sgRNA without exhaustively search, 
+and our optimization results are verified with available experimental data. 
+To our knowledge, this is the first time that the attentional mechanim is used to reveal the reasons influencing on-target activity of sgRNA, and assist sgRNA design.
 

### 2020-11-02 Paper/main.tex
11-2 paper

@@
  \citeauthor{wang2019optimized} develope DeepHF, a deep learning based model, and use Deep SHAP to revealed nucleotide contributions \citep{wang2019optimized}. 
- Deep SHAP is a compositional approximation of SHAP values since it is challenged to computate SHAP values exactly, especially for a complex deep neural networks \citep{lundberg2017a}. 
+ Deep SHAP is a compositional approximation of SHAP values since it is challenged to computate SHAP values exactly, especially for a complex deep neural networks. 
  In our understanding, the method based on input perturbation often requires better generalization ability of the model (even for artificial ridiculous noise data).
- Moreover, recent work indicates that model explain techniques, which based post hoc explanations techniques and input perturbations, could be fooled to generate meaningless explanations instead of reflecting the underlying biases \citep{slack2019fooling},
- in other word, they could be unreliable and misleading, even on model with excellent performance. 
+
+ wait2write
+
  In addition, as far as we know, all the interpretable deep learning models today can only analyze the preference of on-target activity (or off-target probability) on specific nucleotide species and position
@@
     \item Methods in temporal domain. 
-    Although RNN-based network have been shown effective to improve the performance of the model with temporal sequential input, especially in natural language processing and sequential recommendation\citep{huang2018improving},
+    Although RNN-based network have been shown effective to improve the performance of the model with temporal sequential input, especially in natural language processing and sequential recommendation,
     RNN be not used for gRNA activity prediction, until recently \citep{wang2019optimized,liu2020deep,Liu2019}. 
@@
 
-Attention mechanism has demonstrated its power in Natural Language Processing, Statistical Learning, Speech and Computer Vision \citep{chaudhari2019an}. 
+Attention mechanism has demonstrated its power in Natural Language Processing, Statistical Learning, Speech and Computer Vision. 
  It makes model tends to focus selectively on parts of the input which is help in performing the task effectively. 
@@
 On this basis, we apply the idea of attention mechanism which has been widely used in natural language processing tasks to AttCRISPR in the method of temporal domain, 
-and name it Temporal Attention Module \citep{vaswani2017attention,luong2015effective,bahdanau2014neural}.
+and name it Temporal Attention Module \citep{vaswani2017attention,luong2015effective}.
 As the idea of \citeauthor{vaswani2017attention}, Temporal Attention Module satisfies the following equation
@@
 
-As \citeauthor{wang2019optimized,Li2016ProteinSS,Wang2016ProteinSS} have shown, some indirect sgRNA features, which can't be obtained directly by deep learning, including position accessibilities of secondary structure, stem–loop of secondary structure, melting temperature, and GC content are strongly associated with sgRNA activity.
+As \citeauthor{wang2019optimized,Wang2016ProteinSS} have shown, some indirect sgRNA features, which can't be obtained directly by deep learning, including position accessibilities of secondary structure, stem–loop of secondary structure, melting temperature, and GC content are strongly associated with sgRNA activity.
 It's worth noting that in the work of \citeauthor{wang2019optimized}, hand-crafted biological features didn't be normalized. 

### 2020-11-02 Paper/main.tex
11-2 paper

@@
 
-\title[short Title]{AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction
+\title[short Title]{AttCRISPR : an spacetime interpretable model for on-target activity of sgRNA prediction
 }
-\author[Sample \textit{et~al}.]{Corresponding Author\,$^{\text{\sfb 1,}*}$, Co-Author\,$^{\text{\sfb 2}}$ and Co-Author\,$^{\text{\sfb 2,}*}$}
-\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
-$^{\text{\sf 2}}$Department, Institution, City, Post Code,
-Country.}
+\author[Xiao \textit{et~al}.]{Liming Xiao\,$^{\text{\sfb 1}}$, Yunqi Wan\,$^{\text{\sfb 1}}$ and Zhenran Jiang\,$^{\text{\sfb 1,}*}$}
+\address{$^{\text{\sf 1}}$Department of Computer Science \& Technology, East China Normal University, Shanghai, 200062, China.}
 

### 2020-11-05 Paper/main.tex

@@
 
-\title[short Title]{AttCRISPR : an spacetime interpretable model for on-target activity of sgRNA prediction
-}
+\title[short Title]{AttCRISPR : a spacetime interpretable model for prediction of sgRNA on-target activity}
 \author[Xiao \textit{et~al}.]{Liming Xiao\,$^{\text{\sfb 1}}$, Yunqi Wan\,$^{\text{\sfb 1}}$ and Zhenran Jiang\,$^{\text{\sfb 1,}*}$}
@@
 \abstract{\textbf{Motivation:} More and more higher specificities Cas9 variants are developed to avoid the off-target effect, which bring a significant volume of experimental data. 
-Conventional machine learning performance poorly on these datasets, while model based on deep learning are often lack of interpretability, which makes it difficult for researchers to understand its decisions.
+Conventional machine learning performance poorly on these datasets, while model based on deep learning are often lack of interpretability, which makes it difficult for researchers to understand its decisions,
+not to mention to design high-activity sgRNA with the insights brought by the model. 
 Moreover, neither the deep learning based model with existing structure can not satisfy enough precision at such huge datasets.\\
-\textbf{Results:} To overcome it, we design and implement AttCRISPR, a deep learning based model to predict the on-target activity. 
-Our model was trained and tested on the biggest dataset, DeepHF dataset, as far as we know for performance evaluation. 
-AttCRISPR achieves the best performance on DeepHF dataset, yielding an average spearman value of 0.99\%, 0.99\%, 0.99\% (corresponding to WT-SpCas9, eSpCas9(1.1), SpCas9-HF1) under tenfold shuffled validation.
-In addition, another advantage of AttCRISPR over other well-perform methods is that it is intrinsic interpretable and does not rely on other post hoc explanations techniques. 
-In this paper, We design a set of algorithm to reveal the biological significance of the decision maked by AttCRISPR from the global and local perspectives at sgRNA overall level and nucleotide level.\\
+\textbf{Results:} To overcome these, we design and implement AttCRISPR, a intrinsic interpretable method based on deep learning to predict the on-target activity. 
+In this paper, we find that based on the preprocessing of the input base sequence, the deep learning models can be divided into two categories, 
+methods in spatial domain with the input of encoded base sequence and in temporal domain with the input of embedded base sequence. 
+Based on the categorization above, we assume that spatial and temporal method are heterogeneous, and use a full connection layer to stack them, which achieve a better performance. 
+Our model was trained and tested on the biggest dataset, the same dataset as DeepHF used, as far as we know for performance evaluation. 
+In addition, benefits from two attention modules, spatial and temporal attention modules, AttCRISPR has strong interpretability. 
+Through them, we can understand the decisions made by AttCRISPR at both global and local levels without other post hoc explanations techniques. 
+Further, interpretability can be used to help us design and optimize sgRNA activity without exhaustively search. 
+AttCRISPR can compete with state-of-the-art method in these datasets, and achieves an average spearman value of 0.872, 0.867, 0.867 (corresponding to WT-SpCas9, eSpCas9(1.1), SpCas9-HF1) under tenfold shuffled validation.
+\\
 \textbf{Availability:} The example code are available at \href{https://github.com/South-Walker/AttCRISPR}{https://github.com/South-Walker/AttCRISPR}\\
@@
  Some optimum sgRNAs can hit almost all targers alleles, while anothers don't even show activity \citep{wang2019optimized}.
- This fact indicates that it's meaningful to explore an efficient approaches to guide sgRNA design.
+ This fact indicates that it's meaningful to explore an efficient approaches to predict sgRNA activity and even guide sgRNA design.
 
@@
 \begin{equation}
-\text{\it y}=Score(\it X)\label{eq:01}
+ y=Score( X)\label{eq:01}
 \end{equation}
@@
 
- wait2write
-
- In addition, as far as we know, all the interpretable deep learning models today can only analyze the preference of on-target activity (or off-target probability) on specific nucleotide species and position
- for example, the G adjacent to PAM has a positive effect on sgRNA activity as \citeauthor{wang2019optimized} report, 
- which we'll call the first-order preference in our paper, due to it's similar to the total differential of $y$ in Equation~(\ref{eq:01}) as following
-\begin{equation}
-dy = \sum^{d}_ia_idx_i\label{eq:02}
-\end{equation}
-\begin{equation}
-a_i=\frac{\partial}{\partial x_i} Score(X)\label{eq:03}
-\end{equation}
- where $x_i$ denotes the $i$-th dimension of the vector $X$, 
- $a_i$ indicates how dramatically the function changes as $x_i$ changes in a neighborhood of $X$. 
- Similarly the first-order preference indicates how dramatically the function changes as $x_i$ changes, in other word, the importance of $x_i$.
- However they didn't analyzed the preference for position $i$ nucleotide at the overall level, 
- which we'll call the second-order preference in our paper due to its calculation is based on first-order preference,
-
- Specifically, we use a vector $A_i$ to build the first-order original preference at position $i$ within sgRNA sequence, then
- define $\tilde{A}$ as the first-order combine preference matrix (or just first-order preference), which means $\tilde{A}$ can be expressed linearly by $A$ as follow
-\begin{equation}
-\tilde{A}=BA\label{eq:04}
-\end{equation}
-where the weight matrix $B\in\mathbb{R}^{l\times l}$ is learned through attention mechanism. 
-Then the predicted value can be expressed as
-\begin{equation}
-y=W \cdot \tilde{A} {X_e}^{T}\label{eq:05}
-\end{equation}
- where $W\in\mathbb{R}^l$ denotes a non-negative weight vector. 
- Assume that in Equation~(\ref{eq:04}) the first-order original preference at each position is relatively independent and weight matrix $B$ is independent of any first-order original preference, 
- then the total differential of the first-order preference at $i$-th position $\tilde{A}_i$ could be written as
-\begin{equation}
-d\tilde{A}_i=\sum_j^lB_{ij}EdA_j\label{eq:07}
-\end{equation}
-where $E$ is the identity matrix, and we call $B$ as the second-order preference matrix, 
-it can explain how a particular pattern containing two nucleotides affects the base sequence, 
-for example, how does the degree of preference for the G adjacent to PAM be affected by a T at 2 bases upstream?
+ Beyond that, existing analysis of the models interpretability are all at global level, and result is a general pattern in the datasets. 
+For example, which position has a great impact on the final decision of the model and which position-dependent nucleotide has a positive impact on the activity. 
+Lack of analysis at local level. 
+For example, which structure causes the low activity of a certain nucleotide sequence and how to improve its activity with a few modification. 
+In light of the above, we believe it is essential to develope a model which can not only match deep learning based model in performance, 
+but also with strong interpretability that can be comparable to conventional machine learning method.
 
@@
 \end{figure}
- The previous work (even based on conventional machine learning algorithms with high interpretability) 
- was limited to dimers which can only work on the adjacent base pairs \citep{Liu2019} 
- or have to perform complex feature engineering \citep{MuhammadRafid2020}.
- In light of the above, we believe it is essential to develope a model which can not only match deep learning based model in performance, 
- but also be comparable to conventional machine learning algorithms in interpretability.
 
@@
     It is intrinsic interpretable in both temporal and spatial domains.
-    In the spatial domain it's at the nucleotide level, in our word, first-order preference, 
-    while at the overall level in the temporal domain, in our word, second-order preference. 
+    In the spatial domain it's at global level, while at local level in the temporal domain. 
     Thus, it is transformed from a black box to an intrinsically interpretable model with the performance of deep learning based model. 
@@
 Further, we apply attention mechanisms in both spatial and temporal domain respectively to enhance the interpretability of AttCRISPR.
+
+\subsubsection{First-order preference and second-order preference}
+
+Before introducing the neural network architecture of AttCRISPR, Let's define first-order preference and second-order preference for convenience. 
+Taking a simple linear regression model as an example, for input $X$ in Equation~(\ref{eq:01}), $y$ in Equation~(\ref{eq:01}) is as following
+ \begin{equation}
+y = AX\label{eq:linear}
+\end{equation}
+where $A \in\mathbb{R}^d$, the total differential of $y$ in Equation~(\ref{eq:linear}) is as following
+ \begin{equation}
+dy = \sum^{d}_iA_idX_i\label{eq:02}
+\end{equation}
+where $A_i$ and $X_i$ denotes the $i$-th dimension of the vector $X$ and $A$, 
+$A_i$ indicates how dramatically the function changes as $X_i$ changes in a neighborhood of $X$, 
+in other word, the importance of $X_i$. 
+That's why we'll call $A$ first-order preference in our paper. 
+Specifically, we use a vector $A_i$ to build the first-order original preference at position $i$ within sgRNA sequence, 
+and $X_i$ is an embeddedness of the $i$-th feature, then $A$ and $X$ are two matrix. 
+Further, the final result can be weighted by a trainable non-negative weight vector $W\in\mathbb{R}^l$, as follow
+\begin{equation}
+y=W \cdot AX^{T}\label{eq:superlinear}
+\end{equation}
+then we define $\tilde{A}$ as the first-order combine preference matrix (or just first-order preference), which means $\tilde{A}$ can be expressed linearly by $A$ as follow
+\begin{equation}
+\tilde{A}=BA\label{eq:04}
+\end{equation}
+where the weight matrix $B\in\mathbb{R}^{l\times l}$ is learned through attention mechanism, 
+which we'll call the second-order preference matrix in our paper due to its calculation is based on first-order preference, 
+it can explain how a particular pattern containing two nucleotides affects the base sequence. 
+Then the predicted value can be expressed as
+\begin{equation}
+y=W \cdot \tilde{A} {X_e}^{T}\label{eq:05}
+\end{equation}
 
@@
 In fact, this corresponds to some early studies concerning the Human (hU6) promoter, which is believed to require G as the first nucleotide of its transcript \citep{cong2013multiplex,jinek2012a,mali2013rnaguided}.
+
 \subsubsection{Method and attention in temporal domain}
@@
 $\sigma$ represents a threshold of length, any base over this length from the position $i$ is not considered to be affected.
-Further, if we think of the values matrix as a vector form of the first-order preference $A$ in Equation~(\ref{eq:05}), we can reach the following equation
+Further, if we think of the values matrix as a vector form of the first-order preference $A$ in Equation~(\ref{eq:04}), we can reach the following equation
 \begin{equation}

### 2020-11-05 Paper/main.tex
11-5 paper

@@
 
-\abstract{\textbf{Motivation:} More and more higher specificities Cas9 variants are developed to avoid the off-target effect, which bring a significant volume of experimental data. 
-Conventional machine learning performance poorly on these datasets, while model based on deep learning are often lack of interpretability, which makes it difficult for researchers to understand its decisions,
+\abstract{\textbf{Motivation:} More and more Cas9 variants with higher specificities are developed to avoid the off-target effect, which bring a significant volume of experimental data. 
+Conventional machine learning performs poorly on these datasets, while model based on deep learning are often lack of interpretability, which makes it difficult for researchers to understand its decisions,
 not to mention to design high-activity sgRNA with the insights brought by the model. 
@@
 Through them, we can understand the decisions made by AttCRISPR at both global and local levels without other post hoc explanations techniques. 
-Further, interpretability can be used to help us design and optimize sgRNA activity without exhaustively search. 
+Further, interpretability AttCRISPR can be used to guide researcher to design sgRNA with higher activity, in order to reduce the experimental cost. 
 AttCRISPR can compete with state-of-the-art method in these datasets, and achieves an average spearman value of 0.872, 0.867, 0.867 (corresponding to WT-SpCas9, eSpCas9(1.1), SpCas9-HF1) under tenfold shuffled validation.
@@
 \textbf{Availability:} The example code are available at \href{https://github.com/South-Walker/AttCRISPR}{https://github.com/South-Walker/AttCRISPR}\\
-\textbf{Contact:} \href{xlm@xiaoliming96.com}{xlm@xiaoliming96.com}\\
+\textbf{Contact:} \href{zrjiang@cs.ecnu.edu.cn}{zrjiang@cs.ecnu.edu.cn}\\
 \textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}
@@
 
-Clustered regularly interspaced short palindromic repeats (CRISPR) / CRIPSR associated protein 9 (Cas9) systems is preferred over other biological research and human medicine technologies now, beacuse of it's efficiency,
- robustness and programmability.  Cas9 nucleases can be directed by short guide RNAs (sgRNAs) to introduce site-specific DNA double-stranded breaks in target, 
- so to enable editing site-specific within the mammalian genome \citep{jinek2012a,cong2013multiplex,mali2013rnaguided}.
+Clustered regularly interspaced short palindromic repeats (CRISPR) / CRIPSR associated protein 9 (Cas9) systems is preferred over other biological research and human medicine technologies now, 
+beacuse of it's efficiency, robustness and programmability. 
+Cas9 nucleases can be directed by short guide RNAs (sgRNAs) to introduce site-specific DNA double-stranded breaks in target, 
+so to enable editing site-specific regions within the mammalian genome \citep{jinek2012a,cong2013multiplex,mali2013rnaguided}. 
 CRISPR/Cas9, to a large extent, has developed genetic therapies at the cellular level, 
- while there are still severe medical disadvantage even now which has greatly hindered the further clinical application of the CRISPR/Cas9 systems. 
- One of these disadvantage is due to point mutations caused by off-target effects \citep{rubeis2018risks,kang2016introducing,ishii2017reproductive,liang2015crispr/cas9-mediated}. 
+while there are still severe medical disadvantages even now which has greatly hindered the further clinical application of the CRISPR/Cas9 systems. 
+One of these disadvantages is due to point mutations caused by off-target effect \citep{rubeis2018risks,kang2016introducing,ishii2017reproductive,liang2015crispr/cas9-mediated}. 
 To overcome this disadvantage, a solution is to engineer CRISPR / Cas9 with higher specificities. 
@@
 
-The activity of chosen sgRNA sequence determines the success of genome editing, however distinctly fluctuant behaviors have been observed for the performance of different sgRNAs, even in the same Cas9 system.
- Some optimum sgRNAs can hit almost all targers alleles, while anothers don't even show activity \citep{wang2019optimized}.
- This fact indicates that it's meaningful to explore an efficient approaches to predict sgRNA activity and even guide sgRNA design.
+The activity of chosen sgRNA sequence determines the efficiency of genome editing, 
+however distinctly fluctuant behaviors have been observed for the performance of different sgRNAs, even in the same Cas9 system. 
+This fact indicates that it's meaningful to explore an efficient approach to predict sgRNA activity and even guide sgRNA design.
 
@@
 (1) alignment-based, (2) hypothesis-driven and (3) learning-based \citep{chuai2018deepcrispr}. 
- Recently we noticed that the last type of method seems to be getting more attention because of huger and huger data set \citep{liu2019computational}.
+Recently we noticed that the last type of method seems to be getting more attention because of huger and huger datasets \citep{liu2019computational}.
 
@@
  where $Score(\cdot)$ depends on the algorithm being selected, and $y$ denotes the predicted value.
- Some studies on HT\_ABE and HT\_CBE have shown that deep learning based models often outperformed conventional machine learning, when the number of sgRNAs in the data set reached a certain level \citep{Song2020,kim2018deep,kim2019spcas9}.
+ Some studies on HT\_ABE and HT\_CBE (two gene editing tools grew out of CRISPR) have shown that deep learning based models often outperformed conventional machine learning, when the number of sgRNAs in the dataset reached a certain level \citep{Song2020,kim2018deep,kim2019spcas9}.
  Per contra, conventional machine learning algorithms, such as linear regression, logistic regression and the decision tree, are often more interpretable due to the fewer parameters and clearer mathematical assumptions.
@@
 \begin{figure}[!tpb]%figure2
-    \centerline{\includegraphics[width=86mm]{category.png}}
+    \centerline{\includegraphics[width=86mm]{NEWcategory.png}}
     \caption{Two categories of the deep learning models used in sgRNA related task. 
@@
     \item Methods in spatial domain. 
-    Some previous studies have used model based CNN to predict gRNA on-target activity or off-target effects \citep{lin2018off-target,kim2018deep,chuai2018deepcrispr}. 
+    Some previous studies have used model based CNN to predict gRNA on-target activity or off-target effect \citep{lin2018off-target,kim2018deep,chuai2018deepcrispr}. 
     They process sgRNA base sequence inputs with the help of one-hot encoding idea. 
@@
 Then follow the Equation~(\ref{eq:20}) to achieve the final prediction value. 
-AttCRISPR (with the hand-crafted biological features) performs better on all three data sets than DeepHF, the current state-of-the-art.
+AttCRISPR (with the hand-crafted biological features) performs better on all three datasets than DeepHF, the current state-of-the-art.
 
@@
 
-In the following content, when we use the word, global, we are referring to rules thats are common throughout the data set. 
+In the following content, when we use the word, global, we are referring to rules thats are common throughout the dataset. 
 If assumed the method with strong generalization ability, it might mean that these rules is common in the corresponding Cas9 system.
@@
     \caption{Preference for each position-dependent nucleotide on the sgRNA sequence. 
-(a)-(c) Bars show the score of preference after standardization, and the higher the number, the more positive it is for activity of sgRAN. 
+(a)-(c) Bars show the score of preference after standardization, and the higher the number, the more positive it is for activity of sgRNA. 
 The numbers below indicated the position of the nucleotides on-target DNA. 
@@
 The coordinates of the control points on the vertical axis represent the degree of preference, 
-and the higher the position-dependent nucleotide corresponding to the control point is, the more positive it is for the activity of sgRAN.
+and the higher the position-dependent nucleotide corresponding to the control point is, the more positive it is for the activity of sgRNA.
 The contour plots at the bottom show the area of position-dependent nucleotides which have different contribution to the activity of sgRNA. 
@@
 
+\section*{Funding}
+
+This work was partially supported by grants from the National Key R\&D Program of China (2019YFA0110802 and 2019YFA0802800).
+\\\\\emph{Conflict of Interest}: none declared.\vspace*{-12pt}
+
 \bibliographystyle{natbib}

### 2020-11-06 Paper/main.tex
11-6 paper

@@
 
-Clustered regularly interspaced short palindromic repeats (CRISPR) / CRIPSR associated protein 9 (Cas9) systems is preferred over other biological research and human medicine technologies now, 
+Clustered regularly interspaced short palindromic repeats (CRISPR) / CRIPSR associated protein 9 (Cas9) systems are preferred over other biological research and human medicine technologies now, 
 beacuse of it's efficiency, robustness and programmability. 
 Cas9 nucleases can be directed by short guide RNAs (sgRNAs) to introduce site-specific DNA double-stranded breaks in target, 
-so to enable editing site-specific regions within the mammalian genome \citep{jinek2012a,cong2013multiplex,mali2013rnaguided}. 
+so to enable editing site-specific regions within genome \citep{jinek2012a,cong2013multiplex,mali2013rnaguided}. 
 CRISPR/Cas9, to a large extent, has developed genetic therapies at the cellular level, 
 while there are still severe medical disadvantages even now which has greatly hindered the further clinical application of the CRISPR/Cas9 systems. 
-One of these disadvantages is due to point mutations caused by off-target effect \citep{rubeis2018risks,kang2016introducing,ishii2017reproductive,liang2015crispr/cas9-mediated}. 
+One of these disadvantages is due to unexpected insertion and deletion caused by off-target effect \citep{rubeis2018risks,kang2016introducing,ishii2017reproductive,liang2015crispr/cas9-mediated}. 
 To overcome this disadvantage, a solution is to engineer CRISPR / Cas9 with higher specificities. 
@@
         \botrule
-    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{
-\emph{Index} represents its index in the source data (Supplementary Data 1), 
-\emph{Activity} represents its activity reported in WT-SpCas9 dataset. }
+    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: 
+    \emph{Activity} of sgRNA represents the activity reported in WT-SpCas9 dataset (Supplementary Data 1). }
 \end{table}

### 2020-11-11 Paper/main.tex
11-11 paper

@@
 
-\title[short Title]{AttCRISPR : a spacetime interpretable model for prediction of sgRNA on-target activity}
+\title[sgRNA on-target activity]{AttCRISPR : a spacetime interpretable model for prediction of sgRNA on-target activity}
 \author[Xiao \textit{et~al}.]{Liming Xiao\,$^{\text{\sfb 1}}$, Yunqi Wan\,$^{\text{\sfb 1}}$ and Zhenran Jiang\,$^{\text{\sfb 1,}*}$}
-\address{$^{\text{\sf 1}}$Department of Computer Science \& Technology, East China Normal University, Shanghai, 200062, China.}
+\address{$^{\text{\sf 1}}$School of Computer Science \& Technology, East China Normal University, Shanghai, 200062, China.}
 
@@
 \abstract{\textbf{Motivation:} More and more Cas9 variants with higher specificities are developed to avoid the off-target effect, which bring a significant volume of experimental data. 
-Conventional machine learning performs poorly on these datasets, while model based on deep learning are often lack of interpretability, which makes it difficult for researchers to understand its decisions,
+Conventional machine learning performs poorly on these datasets, while the models based on deep learning are often lack of interpretability, which makes it difficult for researchers to understand its decisions,
 not to mention to design high-activity sgRNA with the insights brought by the model. 
-Moreover, neither the deep learning based model with existing structure can not satisfy enough precision at such huge datasets.\\
-\textbf{Results:} To overcome these, we design and implement AttCRISPR, a intrinsic interpretable method based on deep learning to predict the on-target activity. 
+Moreover, neither of the deep learning based model with existing structure can not satisfy enough precision at such huge datasets.\\
+\textbf{Results:} To overcome these problems, we design and implement AttCRISPR, an intrinsic interpretable method based on deep learning to predict the on-target activity. 
 In this paper, we find that based on the preprocessing of the input base sequence, the deep learning models can be divided into two categories, 
@@
 
-In practice, there have been a number of application and toolkit applied in this task. In the earlier studies, methods in silico are categorized into three types: 
+In practice, there have been a number of application and toolkits applied in this task. In the earlier studies, the methods \emph{in silico} are categorized into three types: 
 (1) alignment-based, (2) hypothesis-driven and (3) learning-based \citep{chuai2018deepcrispr}. 
-Recently we noticed that the last type of method seems to be getting more attention because of huger and huger datasets \citep{liu2019computational}.
+Recently, we noticed that the last type of method seems to be getting more attention because of huger and huger datasets \citep{liu2019computational}.
 
 Learning-based method, which designed to predict the on-target activity (or off-target probability) of sgRNAs, 
-is essentially a computational model built by machine learning algorithm, not only conventional machine learning but also deep learning algorithm. 
+is essentially a computational model built by machine learning algorithms, not only conventional machine learning but also deep learning. 
 In general, the single or multiple base sequences (vary according to the task) and biological features are represented as a multi-dimensional vector $X\in\mathbb{R}^d$, 
@@
 
- Beyond that, existing analysis of the models interpretability are all at global level, and result is a general pattern in the datasets. 
+ In addition, existing analysis of the models interpretability are all at global level, and result is a general pattern in the datasets. 
 For example, which position has a great impact on the final decision of the model and which position-dependent nucleotide has a positive impact on the activity. 
@@
 
-Deep neural network has shown its power in the study of CRISPR/Cas9 and its improved Systems \citep{liu2019computational}. 
- Most of the deep neural network existing are the combination of recurrent neural network (RNN), convolutional neural network (CNN), fully connected neural network (FNN), and their variants. 
+Deep neural network has shown its power in the study of CRISPR/Cas9 and its improved systems \citep{liu2019computational}. 
+ Most of the deep neural networks existing are the combination of recurrent neural network (RNN), convolutional neural network (CNN), fully connected neural network (FNN), and their variants. 
  As Figure~\ref{fig:category} show,  
@@
     \item Methods in spatial domain. 
-    Some previous studies have used model based CNN to predict gRNA on-target activity or off-target effect \citep{lin2018off-target,kim2018deep,chuai2018deepcrispr}. 
+    Some previous studies have used model based CNN to predict sgRNA on-target activity or off-target effect \citep{lin2018off-target,kim2018deep,chuai2018deepcrispr}. 
     They process sgRNA base sequence inputs with the help of one-hot encoding idea. 
@@
 
-\subsubsection{Method and attention in spatial domain}
+\subsubsection{Method in spatial domain}
 
@@
 \end{figure}
-As Figure~\ref{fig:CNN} show, method in spatial domain relies on the convolutional neural network. 
+As Figure~\ref{fig:CNN} demonstrated, the method in spatial domain relies on the convolutional neural network. 
 As previously mentioned, sgRNA sequence has been encoded into a $21\times 4$ one-hot matrix $X_{oh}$, and we regard $X_{oh}$ as a binary image. 
 Then, convolution kernels with different size are used to extract potential spatial features just like what other do in computer vision. 
-According to the foregoing, the Spatial Attention Module proposed by \citeauthor{woo2018cbam:} can be applied in our method in spatial domain, 
-which was used to improve the performance of CNN in vision tasks.
+According to the foregoing, the spatial attention Module proposed by \citeauthor{woo2018cbam:} can be applied in our method, 
+which has been used to improve the performance of CNN in vision tasks.
 
@@
 
-As Figure~\ref{fig:spatialmodule} show, Given an one-hot map $X_{oh}$, spatial attention module generating spatial attention matrix 
+As shown in Figure~\ref{fig:spatialmodule}, given an one-hot map $X_{oh}$, spatial attention module generating spatial attention matrix 
 $A_s\in\mathbb{R}^{l\times 4}$ with the same as $X_{oh}$ in shape. 
@@
 
-\subsubsection{Method and attention in temporal domain}
+\subsubsection{Method in temporal domain}
 As Figure~\ref{fig:04} show, temporal domain part of AttCRISPR relies on the recurrent neural network (or its variant). 
@@
 On this basis, we apply the idea of attention mechanism which has been widely used in natural language processing tasks to AttCRISPR in the method of temporal domain, 
-and name it Temporal Attention Module \citep{vaswani2017attention,luong2015effective}.
-As the idea of \citeauthor{vaswani2017attention}, Temporal Attention Module satisfies the following equation
+and name it temporal attention module \citep{vaswani2017attention,luong2015effective}.
+As the idea of \citeauthor{vaswani2017attention}, temporal attention module satisfies the following equation
 \begin{equation}
@@
 
-\subsection{Experiments}
+\subsection{Experiment design}
 
@@
 Then follow the Equation~(\ref{eq:20}) to achieve the final prediction value. 
-AttCRISPR (with the hand-crafted biological features) performs better on all three datasets than DeepHF, the current state-of-the-art.
+AttCRISPR (with the hand-crafted biological features) performs better on all three datasets than DeepHF.
 
@@
 In Table~\ref{Tab:baseline}, we annotate some properties of these baselines (is/isn't neural models, is/isn't end2end models)
-All the experiments were carried out in Python 3.6 using Keras 2.2.4 and one GeForce RTX 2080Ti Super was used for training and testing if needed.
+All of the experiments were carried out in Python 3.6 using Keras 2.2.4 and one GeForce RTX 2080Ti Super was used for training and testing if needed.
 
@@
     \item 
-    How can researcher understand the decisions make by AttCRISPR locally and globally, based on attention mechanisms? 
+    How can researcher understand the decisions made by AttCRISPR locally and globally, based on attention mechanisms? 
     $\rightarrow$ Section~\ref{section:interpretability}
@@
 In Table~\ref{Tab:withoutbiofeature}, we list the performance of methods in spatial or temporal domain and the stacking of methods. 
-Temporal AttCRISPR, TAC for short, achieved Spearman correlation coefficients of 0.857, 0.844, 0.851 in above three dataset. 
+Temporal AttCRISPR, TAC for short, achieved Spearman correlation coefficients of 0.857, 0.844, 0.851 respectively in above three dataset. 
 Spatial AttCRISPR, SpAC for short, corresponds to 0.862, 0.854, 0.857. In the absence of hand-crafted biological features. 
@@
 is the most predictive with Spearman correlation coefficients of 0.856, 0.849, 0.851. 
-It's obvious that the ensemble AttCRISPR is better at prediction (Figure~\ref{fig:06} a-c). 
+It's obvious that the ensemble AttCRISPR is better at prediction (Figure~\ref{fig:06} (a-c)). 
 Furthermore, the prediction ability of models could be boosted by addition of other hand-crafted biological features, which can't be obtained directly by sequence information.
 
-Hence, the second experiment is designed to compare the performance of standard AttCRISPR (hand-crafted biological features are used to improve performance of ensemble AttCRISPR)
- and current state-of-the-art method, DeepHF (the RNN mentioned above integrated with hand-crafted biological features).
+Further experiment is designed to compare the performance of standard AttCRISPR (hand-crafted biological features are used to improve performance of ensemble AttCRISPR)
+ and DeepHF, which is current state-of-the-art method.
 \begin{table}[!tpb]
@@
 The method with superscript of $^*$ and $^{\#}$ is reported by \citeauthor{wang2019optimized} and \citeauthor{MuhammadRafid2020} respectively. 
-In the tables, we use the results reported in the relevant paper as the performance of the method directly.}
+In the tables, we use the results reported in the relevant papers as the performance of the method directly.}
 \end{table}
 
-\subsection{Comparison to current methods}\label{section:comparison}
+\subsection{Performance comparison with current methods}\label{section:comparison}
 
@@
 we follow Equation~(\ref{eq:20}) to modify the ensemble method and design the control experiment using the same strategy to validate the conclusion that integrating with hand-crafted biological features can improve the predictive performance of methods.
-What's more, we compare the standard AttCRISPR and current state-of-the-art method, DeepHF, and show the results in Table~\ref{Tab:withbiofeature}.
+What's more, we compare the standard AttCRISPR and DeepHF (Table~\ref{Tab:withbiofeature}).
 
@@
 Further, integration with the hand-crafted biological features can also improve the performance of AttCRISPR, and achieve Spearman correlation coefficients of 0.872, 0.867 and 0.867 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively.
-Meanwhile, current state-of-the-art method, DeepHF achieve 0.867, 0.862 and 0.860 respectively.
+Meanwhile, DeepHF achieve 0.867, 0.862 and 0.860 respectively.
 After integrating with biological features, the performance gap between AttCRISPR and DeepHF is shortened, while AttCRISPR still has better performance.
@@
     \caption{
-Performance comparisons for methods before and after integrating with hand-crafted biological features, 
+Performance comparisons for the methods before and after integrating with hand-crafted biological features, 
 where DeepHF is the RNN integrated with hand-crafted biological features, 
@@
 
-To some extent, the attention module in the AttCRISPR can help us to understand the decisions it makes. 
-In the following sections, we will analyze the insight into activity of sgRNA bring through the attention mechanism at both global and local levels.
-
-In the following content, when we use the word, global, we are referring to rules thats are common throughout the dataset. 
-If assumed the method with strong generalization ability, it might mean that these rules is common in the corresponding Cas9 system.
-On the other hand, local refers to the rules applicable to a certain sgRNA. 
-We believe that the local interpretability is very helpful in the design and optimization of sgRNA.
+In the following sections, we will analyze the insight into activity of sgRNA bring through the attention mechanism at both global and local levels 
+to validate the attention module in the AttCRISPR can help us to understand the decisions. 
 \begin{figure*}[!tpb]
@@
 
-At global level, a important question we want AttCRISPR to answer is which nucleotide it prefers at each position on the sequence. 
+At global level, a important question we expect AttCRISPR to answer is which nucleotide it prefers at each position on the sequence. 
 In fact, \citeauthor{wang2019optimized} has already answered this question in detail with the DeepSHAP method.
@@
 attention mechanism can help us understand the decision made by AttCRISPR and reveal the insight into activity of sgRNA. 
-Some of them are consistent with the conclusion accepted current.
+Some of them are consistent with the current accepted conclusion.
 
@@
 
-At local level, we will analyze a case (consisting of three sgRNAs as Table~\ref{Tab:optimum} show), then answer two imortant question based on the local interpretability. 
-First, how to optimize a sgRNA with local interpretability to make it have more on-target activity. 
-Second, in the eyes of AttCRISPR, what are the reasons for the low activity of the sgRNA.
+At local level, we analyze a case (consisting of three sgRNAs as Table~\ref{Tab:optimum} show), 
+then we expect AttCRISPR to answer two imortant questions based on the local interpretability. 
+First, how can we optimize a sgRNA to have more on-target activity. 
+Second, what are the reasons for the low activity of the sgRNA.
 
@@
 
-The second question we want AttCRISPR to answer is why it give two low scores at position 14 and 16. 
+The second question we expect AttCRISPR to answer is why it give two low scores at position 14 and 16. 
 In practice, we will try to answer this question with second-order preference. 
@@
 It is obvious that a few unusual bright spots appear in the red box in Figure~\ref{fig:heatmap}. 
-We believe that tells us the nucleotide at position 15 has a great effect on the score of position 14 andd 16 (instead of position 13 or 17, which corresponding position are relatively dim in color). 
+We believe that tells us the nucleotide at position 15 has a great effect on the score of position 14 and 16 (instead of position 13 or 17, which corresponding position are relatively dim in color). 
 As shown in Table~\ref{Tab:optimum}, in source sgRNA there are three consecutive Ts at position 14, 15 and 16, and this may reveal that multiple consecutive Us on sgRNA would leads to low on-target activity of sgRNA, which is consistent with earlier report \citep{wu2014genome-wide}.
@@
 
-In this article, we have introduced a new prediction methods, called AttCRISPR for the activity of sgRNA. 
-For the first time, we take the ensemble of both spatial and temporal domain to predict the on-target activity of sgRNA. 
+In this article, we have introduced a new prediction method, called AttCRISPR for the activity of sgRNA. 
+We take the ensemble of both spatial and temporal domain to predict the on-target activity of sgRNA. 
 Throught ablation analysis and testing a series of possible network structure, we demonstrate that the ensemble method performs better than other methods on this task. 
@@
 One is that attention modules can significantly improve the performance of the model, which is short of experimental validation, 
-and the other is the performance of the method in spatial domain is underestimated.
+and the other is that the performance of the method in spatial domain is underestimated.
 
@@
 
-In Figure~\ref{fig:heatmap} of Section~\ref{section:local}, we note that the brightness at coordinates (14, 15) and (16, 15) exceeds (14, 13) and (16, 17). 
+As shown in Figure~\ref{fig:heatmap}, we note that the brightness at coordinates (14, 15) and (16, 15) exceeds (14, 13) and (16, 17). 
 In other words, there are two unusual bright spots at coordinates (14, 15) and (16, 15). 
@@
 in order to find all kind of nucleotide trimer that have a great influence on the decision made by AttCRISPR. 
-However, due to the lack of validation method, we don't implement it in our work.
+Further experiments may be need to validate.
 
@@
 
-In this paper, all the existing prediction method of sgRNA on-target activity are categorized as encoding-based spatial domain method and embedding-based temporal domain method, 
-according to the processing method of input sgRNA. 
-Then, we develop AttCRISPR, a ensemble method of both spatial method and temporal method follow the stacking strategy with strong interpretability. 
+In this paper, we develop AttCRISPR, a ensemble method of both spatial method and temporal method follow the stacking strategy with strong interpretability. 
 AttCRISPR prove that the ensemble method have a better performance in the datasets of DeepHF
@@
 and we explain the decisions made by AttCRISPR through the attention module which is consistent with earlier reports. 
-Further, we also point out that the output of the attention module can be used to optimize the low-activity sgRNA without exhaustively search, 
+Further, we also discovered that the output of the attention module can be used to optimize the low-activity sgRNA without exhaustively search, 
 and our optimization results are verified with available experimental data. 

### 2020-11-12 Paper/main.tex
paper

@@
 Cas9-High Fidelity (SpCas9-HF1) \citep{ishii2017reproductive,slaymaker2016rationally}, hyper-accurate Cas9 (HypaCas9) \citep{kleinstiver2016high-fidelity}, 
-been developed and bring a significant volume of experimental data, that is to say researchers have to face the difficulty of analyzing such huge and heterogeneous data.
+been developed and bring a significant volume of experimental data, which means that researchers have to face the difficulty of analyzing such huge and heterogeneous data.
 
@@
  where $Score(\cdot)$ depends on the algorithm being selected, and $y$ denotes the predicted value.
- Some studies on HT\_ABE and HT\_CBE (two gene editing tools grew out of CRISPR) have shown that deep learning based models often outperformed conventional machine learning, when the number of sgRNAs in the dataset reached a certain level \citep{Song2020,kim2018deep,kim2019spcas9}.
+ Some studies on HT\_ABE and HT\_CBE (two gene editing tools grew out of CRISPR) have shown that deep learning based models often outperformed conventional machine learning, when the number of sgRNAs in the dataset reached a certain level \citep{kim2018deep,kim2019spcas9,Song2020}.
  Per contra, conventional machine learning algorithms, such as linear regression, logistic regression and the decision tree, are often more interpretable due to the fewer parameters and clearer mathematical assumptions.
@@
  \citeauthor{MuhammadRafid2020} consider deep-learning models as black boxs and believe they lack interpretability, 
- motivated by the empirical assertion, they turn to build a model based conventional machine learning to compete with state-of-the-art deep learning models \citep{MuhammadRafid2020}. 
+ motivated by the empirical assertion, they turn to build a model based on conventional machine learning to compete with state-of-the-art deep learning models \citep{MuhammadRafid2020}. 
  On the other hand, input perturbation based feature importance analysis become a preferred components to reveal the importance of features in deep learning models. 
@@
     In temporal domain, the base sequence (represented by the binary matrix) is embedded into a sequance of high-dimensional vector, 
-    in which the recurrent neural network perform better.
+    in which the RNN perform better.
     In addition, we note that the last layers of neural network are usually full connection structure (not necessarily), 
@@
 As Figure~\ref{fig:category} show,  
- We found that the deep learning models used in sgRNA on-target activity (even for off-target effect) prediction tasks in recent years can be divided into the following two categories according to the encoding approach of the sgRNA sequence (sgRNA-DNA sequence pair, for off-target effect prediction):
+we found that the deep learning models used in sgRNA on-target activity (even for off-target effect) prediction tasks in recent years can be divided into the following two categories according to the encoding approach of the sgRNA sequence (sgRNA-DNA sequence pair, for off-target effect prediction):
 
@@
     \item Methods in spatial domain. 
-    Some previous studies have used model based CNN to predict sgRNA on-target activity or off-target effect \citep{lin2018off-target,kim2018deep,chuai2018deepcrispr}. 
+    Some previous studies have used model based CNN to predict sgRNA on-target activity or off-target effect \citep{chuai2018deepcrispr,kim2018deep,lin2018off-target}. 
     They process sgRNA base sequence inputs with the help of one-hot encoding idea. 
@@
     \item Methods in temporal domain. 
-    Although RNN-based network have been shown effective to improve the performance of the model with temporal sequential input, especially in natural language processing and sequential recommendation,
-    RNN be not used for gRNA activity prediction, until recently \citep{wang2019optimized,liu2020deep,Liu2019}. 
+    Although RNN-based network have been shown effective to improve the performance of the model with temporal sequential input, especially in Natural Language Processing(NLP) and sequential recommendation,
+    RNN be not used for gRNA activity prediction, until recently \citep{Liu2019,wang2019optimized,liu2020deep}. 
     They consider the nucleotides(can also dimer or polymer) in the sgRNA sequence as word, and the sgRNA sequence itself as a sentence (from 5' to 3'), then a trainable matrix (could be either supervised or unsupervised) is used to project the word to the dense real-valued space.
@@
     However, base embedding is not spatially interpretable (different from one-hot encode), and they have no way to further explore the correlation between CNN and RNN output. 
-    Almost all RNN based models used in sgRNA on-target activity or off-target effect flatten the hidden state vector into a one-dimensional vector as the input of the fully connected layer. 
+    Almost all of the RNN based models used in sgRNA on-target activity or off-target effect flatten the hidden state vector into a one-dimensional vector as the input of the fully connected layer. 
     It is a pity that the temporal sequential dependency of hidden state vector are rarely noticed. 
-    To summarise, RNN has limited representation power in capturing spatial feature. Furthermore, hidden state vector representation is usually hard to understand and explain.
+    In summarize, RNN has limited representation power in capturing spatial feature. 
+    Furthermore, the hidden state vector representation is usually hard to understand.
 \end{enumerate}
 
-Attention mechanism has demonstrated its power in Natural Language Processing, Statistical Learning, Speech and Computer Vision. 
- It makes model tends to focus selectively on parts of the input which is help in performing the task effectively. 
+Attention mechanism has demonstrated its power in NLP, Statistical Learning, Speech and Computer Vision. 
+ It makes model tends to focus selectively on parts of the input, which is help in performing the task effectively. 
  Previous observation have shown that Cas9 preferentially binds sgRNAs containing purines but not pyrimidines \citep{wang2014genetic} and multiple thymine in the spacer impairing sgRNA activity \citep{wu2014genome-wide},
- that is to say some specific nucleotide and base position need more attention compared to others. 
+ that is to say some specific nucleotides and base position need more attention compared to others. 
  The above is the premise of introducing attention mechanism. Strictly speaking, we are not the first to bring attention mechanisms into this field. 
@@
  In our work,the interpretability benefit from attention mechanism is more focused. 
- In this paper, our main contributions are as follows:\vspace*{1pt}
+ Our main contributions are as follows:\vspace*{1pt}
 \begin{itemize}
     \item Present a novel deep-learning model, which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
-    Finally, the ensemble learning method is used to combine the two to achieve better performance than other models.
-    It doesn't belong to any of the above categories of existing approaches.
+    Finally, the ensemble learning method is used to combine the two to achieve better performance than current state-of-the-art models. 
     \item Introduce attention mechanism into our model. 
-    As a result, It does not need post hoc explanations techniques based on input perturbation to explain itself. 
+    As a result, it does not need post hoc explanations techniques based on input perturbation to explain itself. 
     It is intrinsic interpretable in both temporal and spatial domains.
@@
     Thus, it is transformed from a black box to an intrinsically interpretable model with the performance of deep learning based model. 
-    \item Throught ablation analysis and testing a series of possible network structure, 
+    \item Throught ablation analysis and testing a series of possible network structures, 
     we find there are multiple components and strategy can improve the performance of our model and constructed AttCRISPR, 
-    which could outperform the current state-of-the-art tool on DeepHF dataset.\vspace*{1pt}
+    which could outperform current state-of-the-art tools on DeepHF dataset.\vspace*{1pt}
 \end{itemize}
@@
 We believe it is also meaningful to regard nucleotides in the sgRNA sequence as word, and the sgRNA sequence itself as a sentence, 
-Guided by this belief $E_m$ is the word embedding matrix and $X_e$ is the sentence embedding in natural language processing (NLP).
-Therefore, $X_e$ is used as an input of recurrent neural network (or its variant), which performs well in the NLP field.
-In the area of NLP, there have been many methods based on pre-training and unsupervised learning been developed to determine the $E_m$. 
-However, we believe that sgRNA sequence is not a natural language in the true sense, the method above does not apply to it. 
-So $E_m$ will be trained along with the model as a whole.
+Guided by this belief $E_m$ is the word embedding matrix and $X_e$ is the sentence embedding in NLP.
+Therefore, $X_e$ is used as an input of RNN (or its variant), which performs well in the NLP field.
 
@@
 and embedding vector is difficult for humans to understand. 
-That's why we call $X_e$ the temporal input, and the recurrent neural network (or its variant) work on $X_e$ is method in temporal domain.
+That's why we call $X_e$ the temporal input, and the RNN (or its variant) work on $X_e$ is method in temporal domain.
 
@@
 
-Based on the categorization above, we assume that method in spatial domain and in temporal domain are heterogeneous, 
+Based on the categorization above, we assume that the method in spatial domain and in temporal domain are heterogeneous, 
 which can satisfy the diversity premise of ensemble learning. 
@@
 which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
-Further, we apply attention mechanisms in both spatial and temporal domain respectively to enhance the interpretability of AttCRISPR.
+Further, we apply attention mechanisms in both spatial and temporal domain to enhance the interpretability of AttCRISPR.
 
@@
     Then refine it through a spatial attention module, which could tell us the importance of a specific matrix element (or just say, pixel).
-    A simple convolutional neural network followed is applied to extract potential feature representation of sgRNA sequence.
-    In the last step, we flatten the output of convolutional neural network into a one dimensional vector and 
+    A simple CNN followed is applied to extract potential feature representation of sgRNA sequence.
+    In the last step, we flatten the output of CNN network into a one dimensional vector and 
     use a multilayer perceptron with sigmoid activation function to achieve the spatial output $y_s$.}\label{fig:CNN}
@@
 Spatial attention matrix $A_s$ formally conforms to our proposed definition of first-order preference (each element of $X_{oh}$ is multiplied by the corresponding element of $A_s$), 
-in other word, element of $A_s$ reveal how important the corresponding elements in $X_{oh}$ is. 
+in other words, element of $A_s$ reveal how important the corresponding elements in $X_{oh}$ is. 
 We think it can reveal the preference of the scoring function at each position. 
-For instance, follow the encoding rules above, train spatial domain part of AttCRISPR with the WT-SpCas9 dataset. 
+For instance, follow the encoding rules above, we train spatial domain part of AttCRISPR with the WT-SpCas9 dataset. 
 Then take the average of all spatial attention matrix, and the element in the first row and third column are closer to 1, which means when calculate the final score, 
@@
 \subsubsection{Method in temporal domain}
-As Figure~\ref{fig:04} show, temporal domain part of AttCRISPR relies on the recurrent neural network (or its variant). 
+As Figure~\ref{fig:04} show, temporal domain part of AttCRISPR relies on the RNN (or its variant). 
 As previously mentioned, we mapping each one-hot vector into a dense real-valued high-dimensional space follow the Equation~(\ref{eq:08}), which generates the embedded matrix $X_e$.
 And we regard $X_{e}$ as a sequential data, or temporal data.
-Recurrent neural network (or its variant) has showed outstanding performance in the tasks with temporal data (for instance, natural language processing, sequential recommendation). 
+RNN (or its variant) has showed outstanding performance in the tasks with temporal data (for instance, NLP, sequential recommendation). 
 That's why we prefer to use it to extract potential temporal features. 
@@
 
-On this basis, we apply the idea of attention mechanism which has been widely used in natural language processing tasks to AttCRISPR in the method of temporal domain, 
-and name it temporal attention module \citep{vaswani2017attention,luong2015effective}.
-As the idea of \citeauthor{vaswani2017attention}, temporal attention module satisfies the following equation
+On this basis, we apply the idea of attention mechanism which has been widely used in NLP tasks to AttCRISPR in the method of temporal domain, 
+and name it temporal attention module \citep{luong2015effective,vaswani2017attention}.
+According to the idea of \citeauthor{vaswani2017attention}, temporal attention module satisfies the following equation
 \begin{equation}
@@
 \end{equation}
-according to above, values matrix $V$ comes from the hidden states of a bidirectional GRU networks, which is usually hard to understand and explain.
-While $B$ is the second-order preference matrix obtained by the attention mechanism, in our belief, the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in the biological sense.
+according to above, values matrix $V$ comes from the hidden states of a bidirectional GRU networks, which is usually hard to understand.
+While $B$ is the second-order preference matrix obtained by the attention mechanism. 
+We believe that the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in the biological sense. 
 \begin{figure}[!tpb]%figure4
@@
 
-As \citeauthor{wang2019optimized,Wang2016ProteinSS} have shown, some indirect sgRNA features, which can't be obtained directly by deep learning, including position accessibilities of secondary structure, stem–loop of secondary structure, melting temperature, and GC content are strongly associated with sgRNA activity.
+Some indirect sgRNA features, which can't be obtained directly by deep learning, 
+including position accessibilities of secondary structure, stem–loop of secondary structure, melting temperature, 
+and GC content are strongly associated with sgRNA activity \citep{Wang2016ProteinSS,wang2019optimized}. 
 It's worth noting that in the work of \citeauthor{wang2019optimized}, hand-crafted biological features didn't be normalized. 
@@
 Then we use a simple full connection network to extract the indirect features, and call the output of fully connection network $y_{bio}$. 
-As mentioned above, we assume that method in spatial domain and in temporal domain are heterogeneous, which can satisfy the diversity premise of ensemble learning.
-That's why we follow the stacking strategy, integrate the methods in time domain and space domain. 
+As mentioned above, we assume that the method in spatial domain and in temporal domain are heterogeneous, which can satisfy the diversity premise of ensemble learning.
+That's why we follow the stacking strategy, to integrate the methods in time domain and space domain. 
 Specifically, the $y_{bio}$, the spatial output $y_{s}$ and the temporal output $y_{t}$ we got earlier are concatenated and then weighted averaging is performed through a full connection layer as follow
@@
 where, $y$ is the final prediction value of AttCRISPR, $W$ is the weight learned by the full connection network. 
-In the actual implementation, we freeze the network in the spatial domain and temporal domain at first, in order to make our network focused on learning the weight $W$.
-Later in the process, in the fine tuning of AttCRISPR, the parameters of the entire network are adjusted.
+In the actual implementation, we freeze the network in the spatial domain and temporal domain firstly, in order to make our network focused on learning the weight $W$.
+Then the parameters of the entire network are adjusted in the fine tuning of AttCRISPR.
 
@@
 The dataset we used for training, validation and testing is built by \citeauthor{wang2019optimized} \citep{wang2019optimized}. 
-We extracted 55604, 58617, 56888 sgRNAs with activity (represented by insertion/deletion (indel)) for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively, from its source data. 
-As far as we know, the best performance on this dataset is the DeepHF of \citeauthor{wang2019optimized} currently, which base on deep learning and bidirectional LSTM architecture. 
-DeepHF achieved Spearman correlation coefficients of 0.867, 0.862 and 0.860 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively.
+We extracted 55604, 58617, 56888 sgRNAs with activity (represented by insertion/deletion (indel)) for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively, from its source data. 
+As far as we know, the best performance on this dataset is the DeepHF of \citeauthor{wang2019optimized} currently, which is based on deep learning and bidirectional LSTM architecture. 
+DeepHF achieved Spearman correlation coefficients of 0.867, 0.862 and 0.860 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively.
 
 Another tool worth noting is CRISPRpred(SEQ), which is based on conventional machine learning and need complicated human feature engineering exercise \citep{MuhammadRafid2020}. 
-They also test their tool with this dataset and achieved Spearman correlation coefficients of 0.838, 0.830 and 0.821 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively (without any hyperparameter tuning).
+They also test their tool with this dataset and achieved Spearman correlation coefficients of 0.838, 0.830 and 0.821 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively (without any hyperparameter tuning).
 
@@
 We compare the performance of end2end method (without any hand-crafted biological features) in both spatial and temporal domain. 
-Furthermore, we test the ensemble method based on the same strategy, which proved that the ensemble of method in both spatial and temporal domain can significantly improve the performance.
+Furthermore, we test the ensemble method based on the same strategy to prove that the ensemble of method in both spatial and temporal domain can significantly improve the performance.
 
@@
 As shown in Table~\ref{Tab:withbiofeature}, in the absence of hand-crafted biological features, AttCRISPR has significant advantages over DeepHF in predictability. 
-Further, integration with the hand-crafted biological features can also improve the performance of AttCRISPR, and achieve Spearman correlation coefficients of 0.872, 0.867 and 0.867 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1 respectively.
+Further, integration with the hand-crafted biological features can also improve the performance of AttCRISPR, and achieve Spearman correlation coefficients of 0.872, 0.867 and 0.867 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively.
 Meanwhile, DeepHF achieve 0.867, 0.862 and 0.860 respectively.

### 2020-11-12 Paper/main.tex
11-12 paper

@@
 \abstract{\textbf{Motivation:} More and more Cas9 variants with higher specificities are developed to avoid the off-target effect, which bring a significant volume of experimental data. 
-Conventional machine learning performs poorly on these datasets, while the models based on deep learning are often lack of interpretability, which makes it difficult for researchers to understand its decisions,
-not to mention to design high-activity sgRNA with the insights brought by the model. 
-Moreover, neither of the deep learning based model with existing structure can not satisfy enough precision at such huge datasets.\\
+Conventional machine learning performs poorly on these datasets, while the models based on deep learning are often lack of interpretability, 
+which makes researchers have to trade-off accuracy and interpretability. 
+We believe it is necessary to develope a model which can not only match deep learning based model in performance, 
+but also with strong interpretability that can be comparable to conventional machine learning method.\\
 \textbf{Results:} To overcome these problems, we design and implement AttCRISPR, an intrinsic interpretable method based on deep learning to predict the on-target activity. 
 In this paper, we find that based on the preprocessing of the input base sequence, the deep learning models can be divided into two categories, 
-methods in spatial domain with the input of encoded base sequence and in temporal domain with the input of embedded base sequence. 
-Based on the categorization above, we assume that spatial and temporal method are heterogeneous, and use a full connection layer to stack them, which achieve a better performance. 
-Our model was trained and tested on the biggest dataset, the same dataset as DeepHF used, as far as we know for performance evaluation. 
+encoded-based methods and embedded-based methods. 
+Based on the categorization above, we assume encoded-based methods and embedded-based methods are heterogeneous, and use a full connection layer to stack them, which achieve a better performance. 
+Our model is trained and tested on the DeepHF dataset for performance evaluation. 
+AttCRISPR can compete with state-of-the-art method in these datasets, and achieves an average spearman value of 0.872, 0.867, 0.867 (corresponding to WT-SpCas9, eSpCas9(1.1), SpCas9-HF1) with the same evaluation strategy.
 In addition, benefits from two attention modules, spatial and temporal attention modules, AttCRISPR has strong interpretability. 
 Through them, we can understand the decisions made by AttCRISPR at both global and local levels without other post hoc explanations techniques. 
-Further, interpretability AttCRISPR can be used to guide researcher to design sgRNA with higher activity, in order to reduce the experimental cost. 
-AttCRISPR can compete with state-of-the-art method in these datasets, and achieves an average spearman value of 0.872, 0.867, 0.867 (corresponding to WT-SpCas9, eSpCas9(1.1), SpCas9-HF1) under tenfold shuffled validation.
+With the trained model, we reveal the preference for each position-dependent nucleotide on the sgRNA sequence in each dataset at global level. 
+And at local level, we prove that interpretability of AttCRISPR can be used to guide researcher to design sgRNA with higher activity, in order to reduce the experimental cost. 
 \\
@@
 That's why more and more higher specificities Cas9 variants, such as enhanced SpCas9 (eSpCas9(1.1)), 
-Cas9-High Fidelity (SpCas9-HF1) \citep{ishii2017reproductive,slaymaker2016rationally}, hyper-accurate Cas9 (HypaCas9) \citep{kleinstiver2016high-fidelity}, 
+Cas9-High Fidelity (SpCas9-HF1) \citep{slaymaker2016rationally,ishii2017reproductive}, hyper-accurate Cas9 (HypaCas9) \citep{kleinstiver2016high-fidelity}, 
 been developed and bring a significant volume of experimental data, which means that researchers have to face the difficulty of analyzing such huge and heterogeneous data.
@@
 
- In addition, existing analysis of the models interpretability are all at global level, and result is a general pattern in the datasets. 
+ In addition, the interpretability of existing models are all at global level, and result is a general pattern in the datasets. 
 For example, which position has a great impact on the final decision of the model and which position-dependent nucleotide has a positive impact on the activity. 
@@
 For example, which structure causes the low activity of a certain nucleotide sequence and how to improve its activity with a few modification. 
-In light of the above, we believe it is essential to develope a model which can not only match deep learning based model in performance, 
+In light of the above, we believe it is necessary to develope a model which can not only match deep learning based model in performance, 
 but also with strong interpretability that can be comparable to conventional machine learning method.
@@
  They use transformer, a components based on attention mechanism, instead of RNN to improve the ability of temporal feature extraction, 
- hence, enhance the performance of their model \citep{Liu2019,vaswani2017attention}. 
+ hence, enhance the performance of their model \citep{vaswani2017attention,Liu2019}. 
  In our work,the interpretability benefit from attention mechanism is more focused. 
@@
     \item Throught ablation analysis and testing a series of possible network structures, 
-    we find there are multiple components and strategy can improve the performance of our model and constructed AttCRISPR, 
+    we find there are multiple components and strategy can improve the performance of AttCRISPR, 
     which could outperform current state-of-the-art tools on DeepHF dataset.\vspace*{1pt}
@@
 \section{Materials and methods}
+\subsection{Datasets}
+
+The dataset we used for training, validation and testing is built by \citeauthor{wang2019optimized}. 
+We extracted 55604, 58617, 56888 sgRNAs with activity (represented by insertion/deletion (indel)) for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively, from its source data.
 
@@
 
-For encoding process, we use the complementary base to represent the original base in sgRNA, as others do. 
-Further, we use one-hot encode strategy, which's is to say, we encoding each base in sgRNA into a four-dimensional vector 
+For encoding process, we use the complementary base to represent the original base in sgRNA. 
+Further, we use one-hot encode strategy, that is to say, we encoding each base in sgRNA into a four-dimensional vector 
 (encode A,T,G,C into [1,0,0,0], [0,1,0,0], [0,0,1,0], [0,0,0,1], respectively), called one-hot vector. 
@@
 To facilitate the training process, we can mapping each one-hot vector into a dense real-valued high-dimensional space, which is called embedding. 
-Concretely speaking, at the matrix level, the formula is as follows
+In summarized, at the matrix level, the formula is as follows
 \begin{equation}
@@
 Due to each element of $X_{oh}$ is interpretable (representing whether there is a corresponding nucleotide type at the corresponding location), 
-we call $X_{oh}$ the spatial input, and the convolutional neural network work on $X_{oh}$ is method in spatial domain. 
+we call $X_{oh}$ the spatial input, and the CNN work on $X_{oh}$ is method in spatial domain. 
 In other hand, different from $X_{oh}$, $X_e$ can only be explained in the first dimension (representing the embedding vector of corresponding nucleotide type), 
 and embedding vector is difficult for humans to understand. 
-That's why we call $X_e$ the temporal input, and the RNN (or its variant) work on $X_e$ is method in temporal domain.
+That's why we call $X_e$ the temporal input, and the RNN (or its variant) work on $X_e$ belongs to the method in temporal domain.
 
@@
 
-Before introducing the neural network architecture of AttCRISPR, Let's define first-order preference and second-order preference for convenience. 
+In order to introduce the neural network architecture of AttCRISPR, Let's define first-order preference and second-order preference for convenience. 
 Taking a simple linear regression model as an example, for input $X$ in Equation~(\ref{eq:01}), $y$ in Equation~(\ref{eq:01}) is as following
@@
 G typically may have a important contribution at first position within sgRNA sequence. 
-In fact, this corresponds to some early studies concerning the Human (hU6) promoter, which is believed to require G as the first nucleotide of its transcript \citep{cong2013multiplex,jinek2012a,mali2013rnaguided}.
+In fact, this corresponds to some early studies concerning the Human (hU6) promoter, which is believed to require G as the first nucleotide of its transcript \citep{jinek2012a,cong2013multiplex,mali2013rnaguided}.
 
@@
 So the first-order preference matrix $\tilde{A}$ come from the product of $B$ and values matrix $V$.
-    Although it's not shown above, it is also worth noting that, a full connection layer with L2 constraints is used to generates a transformation matrix in order to ensure $\tilde{A}_i$ and ${X_e} _i$ are in the same vector space.
     Temporal attention module generates the temporal first-order preference matrix $\tilde{A}$ and the temporal second-order preference matrix $B$.
@@
 Then we use a simple full connection network to extract the indirect features, and call the output of fully connection network $y_{bio}$. 
-As mentioned above, we assume that the method in spatial domain and in temporal domain are heterogeneous, which can satisfy the diversity premise of ensemble learning.
+As mentioned above, we assume that the method in spatial domain and in temporal domain can satisfy the diversity premise of ensemble learning.
 That's why we follow the stacking strategy, to integrate the methods in time domain and space domain. 
@@
 
-\subsection{Datasets and current prediction method}
+\subsection{Current prediction method}
 
-The dataset we used for training, validation and testing is built by \citeauthor{wang2019optimized} \citep{wang2019optimized}. 
-We extracted 55604, 58617, 56888 sgRNAs with activity (represented by insertion/deletion (indel)) for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively, from its source data. 
-As far as we know, the best performance on this dataset is the DeepHF of \citeauthor{wang2019optimized} currently, which is based on deep learning and bidirectional LSTM architecture. 
-DeepHF achieved Spearman correlation coefficients of 0.867, 0.862 and 0.860 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively.
-
+As far as we know, DeepHF, the state-of-the-art method, 
+achieved Spearman correlation coefficients of 0.867, 0.862 and 0.860 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively \citep{wang2019optimized}. 
 Another tool worth noting is CRISPRpred(SEQ), which is based on conventional machine learning and need complicated human feature engineering exercise \citep{MuhammadRafid2020}. 
@@
 
-\citeauthor{wang2019optimized} implemente a tenfold shuffled validation to evaluate the stability of the performance of DeepHF.
+In order to make the comparison apples to apples, we follow the same strategy as \citeauthor{wang2019optimized} to design our experiments.
 To be more specific, each set is shuffled and divided into three parts, 76.5\%, 15\% and 8.5\% of the relevant data was used as the training, test and validation set respectively in a single experiment.
 The experiment is repeated ten times with the results recorded and averaged finally.
-In order to make the comparison apples to apples, we will follow this strategy to design experiments.
 
@@
 \end{figure}
+
+\begin{figure}[!tpb]%figure4
+    \centerline{\includegraphics[width=86mm]{baselinewithbiofeat.eps}}
+    \caption{
+Performance comparisons for the methods before and after integrating with hand-crafted biological features, 
+where DeepHF is the RNN integrated with hand-crafted biological features, 
+and StAC is the EnAC integrated with hand-crafted biological features. 
+The box plot show the mean and distribution of Spearman correlation coefficient between predicted and measured sgRNA activity scores over all tests.
+}\label{fig:07}
+\end{figure}
+
 We designed experiments to address the following questions:
@@
 
-In order to make the comparison apples to apples, 
-we follow Equation~(\ref{eq:20}) to modify the ensemble method and design the control experiment using the same strategy to validate the conclusion that integrating with hand-crafted biological features can improve the predictive performance of methods.
-What's more, we compare the standard AttCRISPR and DeepHF (Table~\ref{Tab:withbiofeature}).
-
-As shown in Table~\ref{Tab:withbiofeature}, in the absence of hand-crafted biological features, AttCRISPR has significant advantages over DeepHF in predictability. 
-Further, integration with the hand-crafted biological features can also improve the performance of AttCRISPR, and achieve Spearman correlation coefficients of 0.872, 0.867 and 0.867 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively.
-Meanwhile, DeepHF achieve 0.867, 0.862 and 0.860 respectively.
-After integrating with biological features, the performance gap between AttCRISPR and DeepHF is shortened, while AttCRISPR still has better performance.
-In addition, we also compare the standard deviation of data obtained in ten tests, which are also shown in Table~\ref{Tab:withbiofeature}.
-It reveal that AttCRISPR is more stable than DeepHF.
-
-\begin{figure}[!tpb]%figure4
-    \centerline{\includegraphics[width=86mm]{baselinewithbiofeat.eps}}
-    \caption{
-Performance comparisons for the methods before and after integrating with hand-crafted biological features, 
-where DeepHF is the RNN integrated with hand-crafted biological features, 
-and StAC is the EnAC integrated with hand-crafted biological features. 
-The box plot show the mean and distribution of Spearman correlation coefficient between predicted and measured sgRNA activity scores over all tests.
-}\label{fig:07}
-\end{figure}
-
-\subsection{Interpretability of the AttCRISPR}\label{section:interpretability}
-
-In the following sections, we will analyze the insight into activity of sgRNA bring through the attention mechanism at both global and local levels 
-to validate the attention module in the AttCRISPR can help us to understand the decisions. 
 \begin{figure*}[!tpb]
@@
 
+In order to make the comparison apples to apples, 
+we follow Equation~(\ref{eq:20}) to modify the ensemble method and design the control experiment using the same strategy to validate the conclusion that integrating with hand-crafted biological features can improve the predictive performance of methods.
+What's more, we compare the standard AttCRISPR and DeepHF (Table~\ref{Tab:withbiofeature}).
+
+As shown in Table~\ref{Tab:withbiofeature}, in the absence of hand-crafted biological features, AttCRISPR has significant advantages over DeepHF in predictability. 
+Further, integration with the hand-crafted biological features can also improve the performance of AttCRISPR, and achieve Spearman correlation coefficients of 0.872, 0.867 and 0.867 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively.
+Meanwhile, DeepHF achieve 0.867, 0.862 and 0.860 respectively.
+After integrating with biological features, the performance gap between AttCRISPR and DeepHF is shortened, while AttCRISPR still has better performance.
+In addition, we also compare the standard deviation of data obtained in ten tests, which are also shown in Table~\ref{Tab:withbiofeature}.
+It reveal that AttCRISPR is more stable than DeepHF.
+
+\subsection{Interpretability of the AttCRISPR}\label{section:interpretability}
+
+In the following sections, we will analyze the insight into activity of sgRNA bring through the attention mechanism at both global and local levels 
+to validate the attention module in the AttCRISPR can help us to understand the decisions. 
 \subsubsection{Global interpretability}
@@
 
-\begin{table}[!tpb]
-    \processtable{Three sgRNA and their activity \label{Tab:optimum}} 
-    {\begin{tabular}{@{}lll@{}}\toprule
-        Index & sgRNA & Activity \\\midrule
-        8493 & ACATGACTTTGGATTTCCCCAGG & 0.831\\
-        8492 & ACATGACTTTGGATTCCCCCAGG & 0.869\\
-        8491 & ACATGACTTTGGACTTCCCCAGG & 0.861\\
-        \botrule
-    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: 
-    \emph{Activity} of sgRNA represents the activity reported in WT-SpCas9 dataset (Supplementary Data 1). }
-\end{table}
-\begin{figure}[!tpb]
-    \centerline{\includegraphics[width=86mm]{local0.eps}}
-    \caption{
-The scores of sgRNA with index of 8493 obtained by the temporal AttCRISPR. 
-The bar plot reveals the score at each position at local level, while the line of dashes reveals the scores at global level. 
-At global level we calculated the scores of all sgRNA, then average the scores at each position to obtain the global level which can be used as base line and is helpful to judge the relative height of the scores.
-}\label{fig:opt}
-\end{figure}
-
 The second question we expect AttCRISPR to answer is why it give two low scores at position 14 and 16. 
@@
 As shown in Table~\ref{Tab:optimum}, in source sgRNA there are three consecutive Ts at position 14, 15 and 16, and this may reveal that multiple consecutive Us on sgRNA would leads to low on-target activity of sgRNA, which is consistent with earlier report \citep{wu2014genome-wide}.
-
-\begin{figure}[!tpb]
-    \centerline{\includegraphics[width=86mm]{secondorder.eps}}
-    \caption{The visualization of second-order preference matrix $B$, 
-the elements in the $i$-th row and the $j$-th column represent the influence of nucleotide at position $j$ when generate the first-order preference $\tilde{A}$ at position $i$. 
-The warmer the color, the more important it is. 
-In the red box, a few unusual bright spots appear. 
-To be more specific, the nucleotide at position 15 has a great effect on the first-order preference at positon 14 and 16.
-}\label{fig:heatmap}
-\end{figure}
 
@@
 
+\begin{table}[!tpb]
+    \processtable{Three sgRNA and their activity \label{Tab:optimum}} 
+    {\begin{tabular}{@{}lll@{}}\toprule
+        Index & sgRNA & Activity \\\midrule
+        8493 & ACATGACTTTGGATTTCCCCAGG & 0.831\\
+        8492 & ACATGACTTTGGATTCCCCCAGG & 0.869\\
+        8491 & ACATGACTTTGGACTTCCCCAGG & 0.861\\
+        \botrule
+    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: 
+    \emph{Activity} of sgRNA represents the activity reported in WT-SpCas9 dataset (Supplementary Data 1). }
+\end{table}
+\begin{figure}[!tpb]
+    \centerline{\includegraphics[width=86mm]{local0.eps}}
+    \caption{
+The scores of sgRNA with index of 8493 obtained by the temporal AttCRISPR. 
+The bar plot reveals the score at each position at local level, while the line of dashes reveals the scores at global level. 
+At global level we calculated the scores of all sgRNA, then average the scores at each position to obtain the global level which can be used as base line and is helpful to judge the relative height of the scores.
+}\label{fig:opt}
+\end{figure}
+
+\begin{figure}[!tpb]
+    \centerline{\includegraphics[width=86mm]{secondorder.eps}}
+    \caption{The visualization of second-order preference matrix $B$, 
+the elements in the $i$-th row and the $j$-th column represent the influence of nucleotide at position $j$ when generate the first-order preference $\tilde{A}$ at position $i$. 
+The warmer the color, the more important it is. 
+In the red box, a few unusual bright spots appear. 
+To be more specific, the nucleotide at position 15 has a great effect on the first-order preference at positon 14 and 16.
+}\label{fig:heatmap}
+\end{figure}
 In this paper, we develop AttCRISPR, a ensemble method of both spatial method and temporal method follow the stacking strategy with strong interpretability. 

### 2020-11-13 Paper/main.tex
11-13 paper

@@
 \abstract{\textbf{Motivation:} More and more Cas9 variants with higher specificities are developed to avoid the off-target effect, which bring a significant volume of experimental data. 
-Conventional machine learning performs poorly on these datasets, while the models based on deep learning are often lack of interpretability, 
+Conventional machine learning performs poorly on these datasets, while the methods based on deep learning are often lack of interpretability, 
 which makes researchers have to trade-off accuracy and interpretability. 
-We believe it is necessary to develope a model which can not only match deep learning based model in performance, 
-but also with strong interpretability that can be comparable to conventional machine learning method.\\
+It is necessary to develope a method which can not only match deep learning based methods in performance, 
+but also with strong interpretability that can be comparable to conventional machine learning methods.\\
 \textbf{Results:} To overcome these problems, we design and implement AttCRISPR, an intrinsic interpretable method based on deep learning to predict the on-target activity. 
-In this paper, we find that based on the preprocessing of the input base sequence, the deep learning models can be divided into two categories, 
-encoded-based methods and embedded-based methods. 
-Based on the categorization above, we assume encoded-based methods and embedded-based methods are heterogeneous, and use a full connection layer to stack them, which achieve a better performance. 
-Our model is trained and tested on the DeepHF dataset for performance evaluation. 
-AttCRISPR can compete with state-of-the-art method in these datasets, and achieves an average spearman value of 0.872, 0.867, 0.867 (corresponding to WT-SpCas9, eSpCas9(1.1), SpCas9-HF1) with the same evaluation strategy.
-In addition, benefits from two attention modules, spatial and temporal attention modules, AttCRISPR has strong interpretability. 
+The advantage of AttCRISPR lies in using the ensemble learning strategy to stack available encoded-based methods and embedded-based methods with strong interpretability. 
+Comparison with the state-of-the-art methods (WT-SpCas9, eSpCas9(1.1), SpCas9-HF1), AttCRISPR can achieve an average spearman value of 0.872, 0.867, 0.867, respectively on several public datasets, which is superior to these methods.
+Furthermore, AttCRISPR has strong interpretability benefits from two attention modules, spatial and temporal attention modules. 
 Through them, we can understand the decisions made by AttCRISPR at both global and local levels without other post hoc explanations techniques. 
-With the trained model, we reveal the preference for each position-dependent nucleotide on the sgRNA sequence in each dataset at global level. 
-And at local level, we prove that interpretability of AttCRISPR can be used to guide researcher to design sgRNA with higher activity, in order to reduce the experimental cost. 
-\\
+With the trained model, we reveal the preference for each position-dependent nucleotide on the sgRNA (small guide RNA) sequence in each dataset at global level. 
+And at local level, we prove that interpretability of AttCRISPR can be used to guide researcher to design sgRNA with higher activity. \\
 \textbf{Availability:} The example code are available at \href{https://github.com/South-Walker/AttCRISPR}{https://github.com/South-Walker/AttCRISPR}\\
@@
 
-In practice, there have been a number of application and toolkits applied in this task. In the earlier studies, the methods \emph{in silico} are categorized into three types: 
+In practice, there have been a number of applications and toolkits applied in this task. In the earlier studies, the methods \emph{in silico} are categorized into three types: 
 (1) alignment-based, (2) hypothesis-driven and (3) learning-based \citep{chuai2018deepcrispr}. 
@@
 For example, which structure causes the low activity of a certain nucleotide sequence and how to improve its activity with a few modification. 
-In light of the above, we believe it is necessary to develope a model which can not only match deep learning based model in performance, 
-but also with strong interpretability that can be comparable to conventional machine learning method.
+In light of the above, we believe it is critical to develop an effective model which can not only have good performance, but also with strong interpretability.
 
@@
     In spatial domain, the base sequence is encoded into a binary matrix (or a binary image). 
-    Since convolution has great advantages in extracting spatial features, the convolutional neural network is an excellent tool in spatial domain. 
+    Since convolution has great advantages in extracting spatial features, the CNN is an excellent tool in spatial domain. 
     (b) Model work in temporal domain. 
@@
     \item Methods in spatial domain. 
-    Some previous studies have used model based CNN to predict sgRNA on-target activity or off-target effect \citep{chuai2018deepcrispr,kim2018deep,lin2018off-target}. 
+    Some previous studies have used the methods based CNN to predict sgRNA on-target activity or off-target effect \citep{chuai2018deepcrispr,kim2018deep,lin2018off-target}. 
     They process sgRNA base sequence inputs with the help of one-hot encoding idea. 
@@
     \item Throught ablation analysis and testing a series of possible network structures, 
-    we find there are multiple components and strategy can improve the performance of AttCRISPR, 
+    we find there are multiple components and strategies can improve the performance of AttCRISPR, 
     which could outperform current state-of-the-art tools on DeepHF dataset.\vspace*{1pt}
@@
 We believe it is meaningful to regard $X_{oh}$ as a binary image, 
-therefore, it is used as an input of convolutional neural network, which performs well in the image field.
+therefore, it is used as an input of CNN, which performs well in the image field.
 Meanwhile, as mentioned above, one-hot matrix is a little sparse.
@@
 Due to each element of $X_{oh}$ is interpretable (representing whether there is a corresponding nucleotide type at the corresponding location), 
-we call $X_{oh}$ the spatial input, and the CNN work on $X_{oh}$ is method in spatial domain. 
+we call $X_{oh}$ the spatial input, and the CNN work on $X_{oh}$ is the method in spatial domain. 
 In other hand, different from $X_{oh}$, $X_e$ can only be explained in the first dimension (representing the embedding vector of corresponding nucleotide type), 
@@
 which can satisfy the diversity premise of ensemble learning. 
-Based on assumption above and ensemble learning, we follow the stacking strategy to develop AttCRISPR 
+Based on the assumption above and ensemble learning, we follow the stacking strategy to develop AttCRISPR 
 which can extract potential feature representation of sgRNA sequence in both spatial and temporal domain parallelly. 
@@
 $A_i$ indicates how dramatically the function changes as $X_i$ changes in a neighborhood of $X$, 
-in other word, the importance of $X_i$. 
+in other words, the importance of $X_i$. 
 That's why we'll call $A$ first-order preference in our paper. 
@@
 \end{figure}
-As Figure~\ref{fig:CNN} demonstrated, the method in spatial domain relies on the convolutional neural network. 
+As Figure~\ref{fig:CNN} demonstrated, the method in spatial domain relies on the CNN. 
 As previously mentioned, sgRNA sequence has been encoded into a $21\times 4$ one-hot matrix $X_{oh}$, and we regard $X_{oh}$ as a binary image. 
 Then, convolution kernels with different size are used to extract potential spatial features just like what other do in computer vision. 
-According to the foregoing, the spatial attention Module proposed by \citeauthor{woo2018cbam:} can be applied in our method, 
+According to the foregoing, the spatial attention module proposed by \citeauthor{woo2018cbam:} can be applied in our method, 
 which has been used to improve the performance of CNN in vision tasks.
@@
 
-\subsubsection{Model ensemble following stacking strategy}
+\subsubsection{Ensemble model following stacking strategy}
 
@@
 It's worth noting that in the work of \citeauthor{wang2019optimized}, hand-crafted biological features didn't be normalized. 
-Since the wide range of data distribution, we believe it makes sense to normalize it, and we preprocess they based on the standard score (Z-Score).
+Since the wide range of data distribution, we normalize it based on the standard score (Z-Score).
 
@@
 
-\subsection{Current prediction method}
+\subsection{Current prediction methods}
 
@@
 
-Two different sets of experiments are carried out in our work. 
+Two different experiments are carried out in our work. 
 The first one is designed for ablation analysis of AttCRISPR. 
 We compare the performance of end2end method (without any hand-crafted biological features) in both spatial and temporal domain. 
-Furthermore, we test the ensemble method based on the same strategy to prove that the ensemble of method in both spatial and temporal domain can significantly improve the performance.
+Furthermore, we test the ensemble method based on the same strategy to prove that the ensemble method in both spatial and temporal domain can significantly improve the performance.
 
-The second experiment is designed to compare the performance of AttCRISPR and other current prediction method. 
+The second experiment is designed to compare the performance of AttCRISPR with other current prediction methods. 
 In order to make the comparison apples to apples, we reduce the dimensionality of the same hand-crafted biological features as DeepHF's, 
@@
         Method & Neural & End2end & Description\\\midrule
-        CNN$^*$ & Yes & Yes & Naive convolutional neural network\\
+        CNN$^*$ & Yes & Yes & Naive CNN\\
         RNN$^*$ & Yes & Yes & Bidirectional long short-term memory neural network\\
@@
 
-We designed experiments to address the following questions:
+We design experiments to address the following questions:
 \begin{itemize}
@@
 Further experiment is designed to compare the performance of standard AttCRISPR (hand-crafted biological features are used to improve performance of ensemble AttCRISPR)
- and DeepHF, which is current state-of-the-art method.
+ and DeepHF, which is a current state-of-the-art method.
 \begin{table}[!tpb]
@@
     \processtable{
-    Performance comparisons for methods before and after integrating with hand-crafted biological features
+    Performance comparisons for the methods before and after integrating with hand-crafted biological features
 (take Spearman correlation coefficient as evaluation index)\label{Tab:withbiofeature}} 
@@
 
-\subsection{Performance comparison with current methods}\label{section:comparison}
+\subsection{Performance comparison}\label{section:comparison}
 
@@
 
-In order to make the comparison apples to apples, 
-we follow Equation~(\ref{eq:20}) to modify the ensemble method and design the control experiment using the same strategy to validate the conclusion that integrating with hand-crafted biological features can improve the predictive performance of methods.
+In order to validate the conclusion that integrating with hand-crafted biological features can improve the predictive performance of methods, 
+we follow Equation~(\ref{eq:20}) to modify the ensemble method and design the control experiment using the same strategy. 
 What's more, we compare the standard AttCRISPR and DeepHF (Table~\ref{Tab:withbiofeature}).
@@
 Further, integration with the hand-crafted biological features can also improve the performance of AttCRISPR, and achieve Spearman correlation coefficients of 0.872, 0.867 and 0.867 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively.
-Meanwhile, DeepHF achieve 0.867, 0.862 and 0.860 respectively.
+Meanwhile, DeepHF achieve 0.867, 0.862 and 0.860, respectively.
 After integrating with biological features, the performance gap between AttCRISPR and DeepHF is shortened, while AttCRISPR still has better performance.
@@
 
-At global level, a important question we expect AttCRISPR to answer is which nucleotide it prefers at each position on the sequence. 
+At global level, an important question we expect AttCRISPR to answer is which nucleotide it prefers at each position on the sequence. 
 In fact, \citeauthor{wang2019optimized} has already answered this question in detail with the DeepSHAP method.
@@
 The result revealed that A and G typically have a positive contribution to the activity of sgRNA, while T typically have a negative contribution. 
-It is agree with the previous conlusion that when Cas9 is binding sgRNA, it prefer the one containing purines to pyrimidines \citep{wang2014genetic}. 
+It is agree with previous conlusion that when Cas9 is binding sgRNA, it prefer the one containing purines to pyrimidines \citep{wang2014genetic}. 
 In addition, global interpretability also pointed out that distinct from other nucleotides, G is strongly favored at position 20. 
@@
 while we still notice that compared with the other two datasets, 
-C makes a more positive contribution to the activity of sgRNA with the SpCas9-HF1 especially in the position 5, which is evident in Figure~\ref{fig:spatialattention} d-f.
+C makes a more positive contribution to the activity of sgRNA with the SpCas9-HF1 especially in the position 5, which is evident in Figure~\ref{fig:spatialattention} (d-f).
 
@@
 attention mechanism can help us understand the decision made by AttCRISPR and reveal the insight into activity of sgRNA.
-Some of them are consistent with the current accepted conclusion.
 
@@
 Let AttCRISPR output the second-order preference matrix $B$ corresponding to the source sgRNA, and show it in Figure~\ref{fig:heatmap}. 
-It is obvious that a few unusual bright spots appear in the red box in Figure~\ref{fig:heatmap}. 
-We believe that tells us the nucleotide at position 15 has a great effect on the score of position 14 and 16 (instead of position 13 or 17, which corresponding position are relatively dim in color). 
+It is obvious that a few unusual bright spots appear in the red box in Figure~\ref{fig:heatmap}, 
+which show that the nucleotide at position 15 has a great effect on the score of position 14 and 16 (instead of position 13 or 17, which corresponding position are relatively dim in color). 
 As shown in Table~\ref{Tab:optimum}, in source sgRNA there are three consecutive Ts at position 14, 15 and 16, and this may reveal that multiple consecutive Us on sgRNA would leads to low on-target activity of sgRNA, which is consistent with earlier report \citep{wu2014genome-wide}.
@@
 
-In this article, we have introduced a new prediction method, called AttCRISPR for the activity of sgRNA. 
+In this article, we have developed a new prediction method, called AttCRISPR for the activity of sgRNA. 
 We take the ensemble of both spatial and temporal domain to predict the on-target activity of sgRNA. 
@@
 This may be a natural belief that with the primary biological sequence we can predict the functional and structural information. 
-Therefore, there is a limit to the improvement of the performance by integrating with hand-srafed biological features.
+Therefore, there is a limit to the performance improvement by integrating with hand-srafed biological features.
 
@@
 
-The current architecture of AttCRISPR focuses on predicting the on-target activity of conventional sgRNA which have a PAM based on NGG. 
+Current architecture of AttCRISPR focuses on predicting the on-target activity of conventional sgRNA which have a PAM based on NGG. 
 However it can be extended to other Cas9 species, variants or off-target task easily.
@@
 AttCRISPR prove that the ensemble method have a better performance in the datasets of DeepHF
-and can compete with the current state-of-the-art method. 
+and can compete with current state-of-the-art methods. 
 In addition, AttCRISPR apply attention mechanisms in both the temporal and spatial part, 

### 2020-11-14 Paper/main.tex
11-14 paper

@@
 
-\title[sgRNA on-target activity]{AttCRISPR : a spacetime interpretable model for prediction of sgRNA on-target activity}
+\title[sgRNA on-target activity prediction]{AttCRISPR : a spacetime interpretable model for prediction of sgRNA on-target activity}
 \author[Xiao \textit{et~al}.]{Liming Xiao\,$^{\text{\sfb 1}}$, Yunqi Wan\,$^{\text{\sfb 1}}$ and Zhenran Jiang\,$^{\text{\sfb 1,}*}$}
@@
 which makes researchers have to trade-off accuracy and interpretability. 
-It is necessary to develope a method which can not only match deep learning based methods in performance, 
+It is necessary to develop a method which can not only match deep learning based methods in performance, 
 but also with strong interpretability that can be comparable to conventional machine learning methods.\\
@@
 Comparison with the state-of-the-art methods (WT-SpCas9, eSpCas9(1.1), SpCas9-HF1), AttCRISPR can achieve an average spearman value of 0.872, 0.867, 0.867, respectively on several public datasets, which is superior to these methods.
-Furthermore, AttCRISPR has strong interpretability benefits from two attention modules, spatial and temporal attention modules. 
+Furthermore, benefits from two attention modules, spatial and temporal attention modules, AttCRISPR has strong interpretability. 
 Through them, we can understand the decisions made by AttCRISPR at both global and local levels without other post hoc explanations techniques. 
@@
 \end{figure}
-In this paper, we develop AttCRISPR, a ensemble method of both spatial method and temporal method follow the stacking strategy with strong interpretability. 
-AttCRISPR prove that the ensemble method have a better performance in the datasets of DeepHF
+In this paper, we develop AttCRISPR, an ensemble method of both spatial method and temporal method follow the stacking strategy with strong interpretability. 
+AttCRISPR prove that the ensemble methods have a better performance in the datasets of DeepHF
 and can compete with current state-of-the-art methods. 

### 2020-11-17 Paper/main.tex
11-17 paper

@@
 Through them, we can understand the decisions made by AttCRISPR at both global and local levels without other post hoc explanations techniques. 
-With the trained model, we reveal the preference for each position-dependent nucleotide on the sgRNA (small guide RNA) sequence in each dataset at global level. 
+With the trained model, we reveal the preference for each position-dependent nucleotide on the sgRNA (short guide RNA) sequence in each dataset at global level. 
 And at local level, we prove that interpretability of AttCRISPR can be used to guide researcher to design sgRNA with higher activity. \\
@@
 beacuse of it's efficiency, robustness and programmability. 
-Cas9 nucleases can be directed by short guide RNAs (sgRNAs) to introduce site-specific DNA double-stranded breaks in target, 
+Cas9 nucleases can be directed by sgRNAs to introduce site-specific DNA double-stranded breaks in target, 
 so to enable editing site-specific regions within genome \citep{jinek2012a,cong2013multiplex,mali2013rnaguided}. 
@@
 been developed and bring a significant volume of experimental data, which means that researchers have to face the difficulty of analyzing such huge and heterogeneous data.
-
 The activity of chosen sgRNA sequence determines the efficiency of genome editing, 
-however distinctly fluctuant behaviors have been observed for the performance of different sgRNAs, even in the same Cas9 system. 
 This fact indicates that it's meaningful to explore an efficient approach to predict sgRNA activity and even guide sgRNA design.
@@
 Recently, we noticed that the last type of method seems to be getting more attention because of huger and huger datasets \citep{liu2019computational}. 
-
-Learning-based method, which designed to predict the on-target activity (or off-target probability) of sgRNAs, 
-is essentially a computational model built by machine learning algorithms, not only conventional machine learning but also deep learning. 
-In general, the single or multiple base sequences (vary according to the task) and biological features are represented as a multi-dimensional vector $X\in\mathbb{R}^d$, 
-and $d=l+b$, where $l$ refers to the length of base sequences and $b$ refers to the number of biological features, these methods can be represented as
-\begin{equation}
- y=Score( X)\label{eq:01}
-\end{equation}
- where $Score(\cdot)$ depends on the algorithm being selected, and $y$ denotes the predicted value.
+Learning-based method is essentially a computational model built by machine learning algorithms, not only conventional machine learning but also deep learning. 
 Some studies on HT\_ABE and HT\_CBE (two gene editing tools grew out of CRISPR) have shown that deep learning based models often outperformed conventional machine learning, when the number of sgRNAs in the dataset reached a certain level \citep{kim2018deep,kim2019spcas9,Song2020}.
@@
  On the other hand, input perturbation based feature importance analysis become a preferred components to reveal the importance of features in deep learning models. 
- \citeauthor{Liu2019} use a sliding window of length 2 to extract dimeric as input and rank the position of dimeric by contribution to final output \citep{Liu2019}. 
+ \citeauthor{Liu2019} use a sliding window of length 2 to extract dimeric as input and rank the position of dimeric by contribution to final output. 
  One regret is that subject to the processing of the input sgRNA sequence, their analysis can not exactly on the nucleotide class. 
  Further, SHAP, one of the most prominent of model explain techniques, has been widely used to understand the decision made by the model. 
- \citeauthor{wang2019optimized} develope DeepHF, a deep learning based model, and use Deep SHAP to revealed nucleotide contributions \citep{wang2019optimized}. 
- Deep SHAP is a compositional approximation of SHAP values since it is challenged to computate SHAP values exactly, especially for a complex deep neural networks. 
+ \citeauthor{wang2019optimized} develope DeepHF, a deep learning based model, and use Deep SHAP to revealed nucleotide contributions. 
  In our understanding, the method based on input perturbation often requires better generalization ability of the model (even for artificial ridiculous noise data).
-
- In addition, the interpretability of existing models are all at global level, and result is a general pattern in the datasets. 
-For example, which position has a great impact on the final decision of the model and which position-dependent nucleotide has a positive impact on the activity. 
-Lack of analysis at local level. 
-For example, which structure causes the low activity of a certain nucleotide sequence and how to improve its activity with a few modification. 
-In light of the above, we believe it is critical to develop an effective model which can not only have good performance, but also with strong interpretability.
 
@@
 
+ In addition, the interpretability of existing models are all at global level, and result is a general pattern in the datasets. 
+For example, which position has a great impact on the final decision of the model and which position-dependent nucleotide has a positive impact on the activity. 
+Lack of analysis at local level. 
+For instance, which structure causes the low activity of a certain nucleotide sequence and how to improve its activity with a few modification. 
+In light of the above, we believe it is critical to develop an effective model which can not only have good performance, but also with strong interpretability.
+
 Deep neural network has shown its power in the study of CRISPR/Cas9 and its improved systems \citep{liu2019computational}. 
@@
     \item Methods in temporal domain. 
-    Although RNN-based network have been shown effective to improve the performance of the model with temporal sequential input, especially in Natural Language Processing(NLP) and sequential recommendation,
-    RNN be not used for gRNA activity prediction, until recently \citep{Liu2019,wang2019optimized,liu2020deep}. 
-    They consider the nucleotides(can also dimer or polymer) in the sgRNA sequence as word, and the sgRNA sequence itself as a sentence (from 5' to 3'), then a trainable matrix (could be either supervised or unsupervised) is used to project the word to the dense real-valued space.
-    This technology is called embedding, which generates the base embedding. RNN further encoding the base embedding into a sequence of hidden state vector. 
-    Specially, \citeauthor{Liu2019} use RNN and CNN in parallel to extract features in base embedding \citep{Liu2019}. 
-    However, base embedding is not spatially interpretable (different from one-hot encode), and they have no way to further explore the correlation between CNN and RNN output. 
-    Almost all of the RNN based models used in sgRNA on-target activity or off-target effect flatten the hidden state vector into a one-dimensional vector as the input of the fully connected layer. 
+    These methods are not used for on-target activity or off-target effect prediction, until recently \citep{Liu2019,wang2019optimized,liu2020deep}. 
+    They consider the nucleotides (can also dimer or polymer) in the sgRNA sequence as a word, then a trainable matrix (could be either supervised or unsupervised) is used to project the word to the dense real-valued space.
+    This technology is called embedding, which generates the base embedding. 
+    However, base embedding is not spatially interpretable (different from one-hot encode). 
+    Almost all of the methods in temporal domain used in sgRNA on-target activity or off-target effect flatten the hidden state vector into a one-dimensional vector as the input of the fully connected layer.
     It is a pity that the temporal sequential dependency of hidden state vector are rarely noticed. 
-    In summarize, RNN has limited representation power in capturing spatial feature. 
-    Furthermore, the hidden state vector representation is usually hard to understand.
 \end{enumerate}
@@
     In the spatial domain it's at global level, while at local level in the temporal domain. 
-    Thus, it is transformed from a black box to an intrinsically interpretable model with the performance of deep learning based model. 
     \item Throught ablation analysis and testing a series of possible network structures, 
@@
 In order to introduce the neural network architecture of AttCRISPR, Let's define first-order preference and second-order preference for convenience. 
-Taking a simple linear regression model as an example, for input $X$ in Equation~(\ref{eq:01}), $y$ in Equation~(\ref{eq:01}) is as following
+Taking a simple linear regression model as an example, for input $X\in\mathbb{R}^l$, where $l$ refers to the length of base sequences, predicted activity $y$ is as following
 \begin{equation}
@@
 \end{figure}
-As Figure~\ref{fig:CNN} demonstrated, the method in spatial domain relies on the CNN. 
-As previously mentioned, sgRNA sequence has been encoded into a $21\times 4$ one-hot matrix $X_{oh}$, and we regard $X_{oh}$ as a binary image. 
-Then, convolution kernels with different size are used to extract potential spatial features just like what other do in computer vision. 
-According to the foregoing, the spatial attention module proposed by \citeauthor{woo2018cbam:} can be applied in our method, 
-which has been used to improve the performance of CNN in vision tasks.
 
@@
 \end{figure}
+
+As Figure~\ref{fig:CNN} demonstrated, the method in spatial domain relies on the CNN. 
+As previously mentioned, sgRNA sequence has been encoded into a $21\times 4$ one-hot matrix $X_{oh}$, and we regard $X_{oh}$ as a binary image. 
+Then, convolution kernels with different size are used to extract potential spatial features just like what other do in computer vision. 
+According to the foregoing, the spatial attention module proposed by \citeauthor{woo2018cbam:} can be applied in our method, 
+which has been used to improve the performance of CNN in vision tasks.
 
@@
 \subsubsection{Method in temporal domain}
+\begin{figure}[tpb]%figure4
+    \centerline{\includegraphics[width=86mm]{temporalmodule.png}}
+    \caption{The architecture of temporal domain method in AttCRISPR. 
+    The input of the method is embedding sgRNA sequence $X_e$. 
+    Then Keys $K$, Values $V$ and Queries $Q$ is generated through a classic encoder-decoder structure which is need for temporal attention module.
+    Next, the temporal attention module generates the first-order preference $\tilde{A}$. 
+    Each of the row vectors in matrix $\tilde{A}$ represents the base preference of sgRNA at the corresponding position, we use their dot product with the corresponding row vector in embedded $X_e$ to build the score of corresponding position.
+    Hence, a full connection layer is used to weighted average them and achieve the temporal output $y_t$.
+    }\label{fig:04}
+\end{figure}
+\begin{figure}[tpb]
+\centerline{\includegraphics[width=86mm]{temporalattentionmodule.png}}
+\caption{        
+    Details of temporal attention module. 
+    To generate the first order preference vector in the $i$ position of sgRNA $\tilde{A}_i$. 
+    First, the $i$-th row vector of the querys matrix $Q_i$ is multiplied by the transpose of the keys mateix $K^T$, and apply a softmax function to obtain a preliminary weights vector on the values. 
+    Second, to favor the alignment points near $i$, the weights vector obtained is multiplied element-by-element by the $i$-th row vector of the damping matrix $G$, as Equation~(\ref{eq:17}) has shown.
+    $G_{ij}$ can be regarded as the result of place a Gaussian distribution centered around $i$, then sampling the position $j$ (a scaling factor is used to ensure the sum of $G_I$ is $l$). 
+    Then we achieve the second-order preference matrix $B$, it is also a weights matrix on the values.
+So the first-order preference matrix $\tilde{A}$ come from the product of $B$ and values matrix $V$.
+    Temporal attention module generates the temporal first-order preference matrix $\tilde{A}$ and the temporal second-order preference matrix $B$.
+    }\label{fig:05}
+\end{figure}
+
 As Figure~\ref{fig:04} show, temporal domain part of AttCRISPR relies on the RNN (or its variant). 
@@
 We believe that the $j$-th dimension of $B_i$, denoted as $B_{ij}$, can reveal the effect of the base at position $j$ on position $i$ in the biological sense.
-\begin{figure}[!tpb]%figure4
-    \centerline{\includegraphics[width=86mm]{temporalmodule.png}}
-    \caption{The architecture of temporal domain method in AttCRISPR. 
-    The input of the method is embedding sgRNA sequence $X_e$, a $21\times e$ embedding matrix, where $e$ is the dimension of a nucleotide embedding vector. 
-    Then Keys $K$, Values $V$ and Queries $Q$ is generated through a classic encoder-decoder structure which is need for temporal attention module.
-    Next, the temporal attention module generates the first-order preference $\tilde{A}$, a $21\times e$ matrix (or a vector set). 
-    Each of the row vectors in matrix $\tilde{A}$ represents the base preference of sgRNA at the corresponding position, we use their dot product with the corresponding row vector in embedded $X_e$ to build the score of corresponding position.
-    Hence, a full connection layer is used to weighted average them and achieve the temporal output $y_t$.
-    }\label{fig:04}
-\end{figure}
-\begin{figure}[!tpb]
-\centerline{\includegraphics[width=86mm]{temporalattentionmodule.png}}
-\caption{        
-    Details of temporal attention module. 
-    To generate the first order preference vector in the $i$ position of sgRNA $\tilde{A}_i$. 
-    First, the $i$-th row vector of the querys matrix $Q_i$ is multiplied by the transpose of the keys mateix $K^T$, and apply a softmax function to obtain a preliminary weights vector on the values. 
-    Second, to favor the alignment points near $i$, the weights vector obtained is multiplied element-by-element by the $i$-th row vector of the damping matrix $G$, as Equation~(\ref{eq:17}) has shown.
-    $G_{ij}$ can be regarded as the result of place a Gaussian distribution centered around $i$, then sampling the position $j$ (a scaling factor is used to ensure the sum of $G_I$ is $l$). 
-    Then we achieve the second-order preference matrix $B$, it is also a weights matrix on the values.
-So the first-order preference matrix $\tilde{A}$ come from the product of $B$ and values matrix $V$.
-    Temporal attention module generates the temporal first-order preference matrix $\tilde{A}$ and the temporal second-order preference matrix $B$.
-    }\label{fig:05}
-\end{figure}
 
@@
 
-In Section~\ref{section:stacking}, we have tested both spatial and temporal domain AttCRISPR, and CNN (method in spatial domain), RNN (method in temporal domain) which reported by \citeauthor{wang2019optimized} in the absence of hand-crafted biological features.
-A worth noticing point is that there is a gap between spatial AttCRISPR and CNN, though the performance of temporal AttCRISPR is basically the same as that of RNN. 
-We suspect there are two possible reasons. 
-One is that attention modules can significantly improve the performance of the model, which is short of experimental validation, 
-and the other is that the performance of the method in spatial domain is underestimated.
-
-In Section~\ref{section:comparison}, also integrating with hand-srafted biological features to improve the predictive performance, the performance gap between AttCRISPR and DeepHF is shortened, while AttCRISPR still has better performance.
-This may be a natural belief that with the primary biological sequence we can predict the functional and structural information. 
-Therefore, there is a limit to the performance improvement by integrating with hand-srafed biological features.
-
 As shown in Figure~\ref{fig:heatmap}, we note that the brightness at coordinates (14, 15) and (16, 15) exceeds (14, 13) and (16, 17). 

### 2020-11-18 Paper/main.tex
11-18 paper

@@
 
-\begin{figure}[!tpb]%figure3
-    \centerline{\includegraphics[width=86mm]{spatialmodule.png}}
-    \caption{Details of spatial attention module. A convolution layer is used to generate multi-channel map from $X_{oh}$.
-    Then concatenated the output of both max-pooling and average-pooling method and forward it to the last convolution layer.
-    A sigmoid function is used to map the final result to a range of zero to one at last, 
-    which generates the spatial first-order preference matrix $A_s$.
-    }\label{fig:spatialmodule}
-\end{figure}
-
 As Figure~\ref{fig:CNN} demonstrated, the method in spatial domain relies on the CNN. 
@@
 
-As shown in Figure~\ref{fig:spatialmodule}, given an one-hot map $X_{oh}$, spatial attention module generating spatial attention matrix 
+As shown in Supplementary Fig. S1, given an one-hot map $X_{oh}$, spatial attention module generating spatial attention matrix 
 $A_s\in\mathbb{R}^{l\times 4}$ with the same as $X_{oh}$ in shape. 
@@
 \end{figure}
-\begin{figure}[tpb]
-\centerline{\includegraphics[width=86mm]{temporalattentionmodule.png}}
-\caption{        
-    Details of temporal attention module. 
-    To generate the first order preference vector in the $i$ position of sgRNA $\tilde{A}_i$. 
-    First, the $i$-th row vector of the querys matrix $Q_i$ is multiplied by the transpose of the keys mateix $K^T$, and apply a softmax function to obtain a preliminary weights vector on the values. 
-    Second, to favor the alignment points near $i$, the weights vector obtained is multiplied element-by-element by the $i$-th row vector of the damping matrix $G$, as Equation~(\ref{eq:17}) has shown.
-    $G_{ij}$ can be regarded as the result of place a Gaussian distribution centered around $i$, then sampling the position $j$ (a scaling factor is used to ensure the sum of $G_I$ is $l$). 
-    Then we achieve the second-order preference matrix $B$, it is also a weights matrix on the values.
-So the first-order preference matrix $\tilde{A}$ come from the product of $B$ and values matrix $V$.
-    Temporal attention module generates the temporal first-order preference matrix $\tilde{A}$ and the temporal second-order preference matrix $B$.
-    }\label{fig:05}
-\end{figure}
 
@@
 
-As Figure~\ref{fig:05} show, in our attention module they are calculated by the following equation
+As Supplementary Fig. S2 show, in our attention module they are calculated by the following equation
 \begin{equation}
@@
 
-\subsection{Current prediction methods}
+\subsection{Experiment design}
 
-As far as we know, DeepHF, the state-of-the-art method, 
-achieved Spearman correlation coefficients of 0.867, 0.862 and 0.860 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively \citep{wang2019optimized}. 
-Another tool worth noting is CRISPRpred(SEQ), which is based on conventional machine learning and need complicated human feature engineering exercise \citep{MuhammadRafid2020}. 
-They also test their tool with this dataset and achieved Spearman correlation coefficients of 0.838, 0.830 and 0.821 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively (without any hyperparameter tuning).
-
-In order to make the comparison apples to apples, we follow the same strategy as \citeauthor{wang2019optimized} to design our experiments.
+Two different experiments are carried out in our work, which follow the same strategy as \citeauthor{wang2019optimized} to design.
 To be more specific, each set is shuffled and divided into three parts, 76.5\%, 15\% and 8.5\% of the relevant data was used as the training, test and validation set respectively in a single experiment.
@@
 
-\subsection{Experiment design}
-
-Two different experiments are carried out in our work. 
 The first one is designed for ablation analysis of AttCRISPR. 
@@
 
-\section{Results}
-\begin{figure}[!tpb]
-    \centerline{\includegraphics[width=86mm]{baselinewithoutbiofeat.eps}}
-    \caption{In the absence of hand-crafted biological features, performance of different algorithms for sgRNA activity prediction. 
-    (a)-(c) The performance of Temporal AttCRISPR, Spatial AttCRISPR and Ensemble AttCRISPR. 
-    The half-violin plots show the mean and distribution of the Spearman correlation coefficient between predicted and measured sgRNA activity scores over all tests. 
-    (d)-(f) In the absence of hand-crafted biological features, the performance of all prediction methods in these datasets as far as we know. 
-    The $mean \pm s.d.$ of the Spearman correlation coefficient between predicted and measured sgRNA activity scores are shown in the bar plots.}\label{fig:06}
-\end{figure}
-
-\begin{figure}[!tpb]%figure4
-    \centerline{\includegraphics[width=86mm]{baselinewithbiofeat.eps}}
-    \caption{
-Performance comparisons for the methods before and after integrating with hand-crafted biological features, 
-where DeepHF is the RNN integrated with hand-crafted biological features, 
-and StAC is the EnAC integrated with hand-crafted biological features. 
-The box plot show the mean and distribution of Spearman correlation coefficient between predicted and measured sgRNA activity scores over all tests.
-}\label{fig:07}
-\end{figure}
-
-We design experiments to address the following questions:
-\begin{itemize}
-    \item 
-    In the absence of hand-crafted biological features, whether the stacking of method in spatial domain and temporal domain can get better performance then use these method alone? 
-    $\rightarrow$ Section~\ref{section:stacking}
-    \item 
-    How does AttCRISPR perform compared to current state-of-the-art methods, covering both conventional machine learning and deep-learning models? 
-    $\rightarrow$ Section~\ref{section:comparison}
-    \item 
-    How can researcher understand the decisions made by AttCRISPR locally and globally, based on attention mechanisms? 
-    $\rightarrow$ Section~\ref{section:interpretability}
-    \vspace*{1pt}
-\end{itemize}
-
-\subsection{Model building and stacking}\label{section:stacking}
-
-In Table~\ref{Tab:withoutbiofeature}, we list the performance of methods in spatial or temporal domain and the stacking of methods. 
-Temporal AttCRISPR, TAC for short, achieved Spearman correlation coefficients of 0.857, 0.844, 0.851 respectively in above three dataset. 
-Spatial AttCRISPR, SpAC for short, corresponds to 0.862, 0.854, 0.857. In the absence of hand-crafted biological features. 
-Ensemble AttCRISPR achieve the best performance of our knowledge, corresponds to 0.868, 0.859, 0.862.
-
-In addition, in Table~\ref{Tab:withoutbiofeature}, the performance of other methods without using hand-crafted biological features, are also recorded. 
-Regardless of the method we developed, RNN reported by \citeauthor{wang2019optimized}, which can be categorized as the method in temporal domain, 
-is the most predictive with Spearman correlation coefficients of 0.856, 0.849, 0.851. 
-It's obvious that the ensemble AttCRISPR is better at prediction (Figure~\ref{fig:06} (a-c)). 
-Furthermore, the prediction ability of models could be boosted by addition of other hand-crafted biological features, which can't be obtained directly by sequence information.
-
-Further experiment is designed to compare the performance of standard AttCRISPR (hand-crafted biological features are used to improve performance of ensemble AttCRISPR)
- and DeepHF, which is a current state-of-the-art method.
 \begin{table}[!tpb]
@@
 
+\section{Results}
+
+We design experiments to address the following questions:
+\begin{itemize}
+    \item 
+    In the absence of hand-crafted biological features, whether the stacking of method in spatial domain and temporal domain can get better performance then use these method alone? 
+    $\rightarrow$ Section~\ref{section:stacking}
+    \item 
+    How does AttCRISPR perform compared to current state-of-the-art methods, covering both conventional machine learning and deep-learning models? 
+    $\rightarrow$ Section~\ref{section:comparison}
+    \item 
+    How can researcher understand the decisions made by AttCRISPR locally and globally, based on attention mechanisms? 
+    $\rightarrow$ Section~\ref{section:interpretability}
+    \vspace*{1pt}
+\end{itemize}
+
+\subsection{Model building and stacking}\label{section:stacking}
+
+In Table~\ref{Tab:withoutbiofeature}, we list the performance of methods in spatial or temporal domain and the stacking of methods. 
+Temporal AttCRISPR, TAC for short, achieved Spearman correlation coefficients of 0.857, 0.844, 0.851 respectively in above three dataset. 
+Spatial AttCRISPR, SpAC for short, corresponds to 0.862, 0.854, 0.857. In the absence of hand-crafted biological features. 
+Ensemble AttCRISPR achieve the best performance of our knowledge, corresponds to 0.868, 0.859, 0.862.
+
+In addition, in Table~\ref{Tab:withoutbiofeature}, the performance of other methods without using hand-crafted biological features, are also recorded. 
+Regardless of the method we developed, RNN reported by \citeauthor{wang2019optimized}, which can be categorized as the method in temporal domain, 
+is the most predictive with Spearman correlation coefficients of 0.856, 0.849, 0.851. 
+It's obvious that the ensemble AttCRISPR is better at prediction (Supplementary Fig. S3(a-c)). 
+Furthermore, the prediction ability of models could be boosted by addition of other hand-crafted biological features, which can't be obtained directly by sequence information.
+
+Further experiment is designed to compare the performance of standard AttCRISPR (hand-crafted biological features are used to improve performance of ensemble AttCRISPR)
+ and DeepHF, which is a current state-of-the-art method.
+
 \subsection{Performance comparison}\label{section:comparison}
+
+In order to validate the conclusion that integrating with hand-crafted biological features can improve the predictive performance of methods, 
+we follow Equation~(\ref{eq:20}) to modify the ensemble method and design the control experiment using the same strategy. 
+What's more, we compare the standard AttCRISPR and DeepHF (Table~\ref{Tab:withbiofeature}).
+
+As shown in Table~\ref{Tab:withbiofeature}, in the absence of hand-crafted biological features, AttCRISPR has significant advantages over DeepHF in predictability. 
+Further, integration with the hand-crafted biological features can also improve the performance of AttCRISPR, 
+and achieve Spearman correlation coefficients of 0.872, 0.867 and 0.867 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively. 
+Meanwhile, DeepHF achieve 0.867, 0.862 and 0.860, respectively. 
+After integrating with biological features, the performance gap between AttCRISPR and DeepHF is shortened, while AttCRISPR still has better performance (Supplementary Fig. S4). 
+In addition, we also compare the standard deviation of data obtained in ten tests, which are also shown in Table~\ref{Tab:withbiofeature}. 
+It reveal that AttCRISPR is more stable than DeepHF.
+
+\subsection{Interpretability of the AttCRISPR}\label{section:interpretability}
+
+In the following sections, we will analyze the insight into activity of sgRNA bring through the attention mechanism at both global and local levels 
+to validate the attention module in the AttCRISPR can help us to understand the decisions.
+
+\subsubsection{Global interpretability}
 
@@
 \end{figure*}
-
-In order to validate the conclusion that integrating with hand-crafted biological features can improve the predictive performance of methods, 
-we follow Equation~(\ref{eq:20}) to modify the ensemble method and design the control experiment using the same strategy. 
-What's more, we compare the standard AttCRISPR and DeepHF (Table~\ref{Tab:withbiofeature}).
-
-As shown in Table~\ref{Tab:withbiofeature}, in the absence of hand-crafted biological features, AttCRISPR has significant advantages over DeepHF in predictability. 
-Further, integration with the hand-crafted biological features can also improve the performance of AttCRISPR, and achieve Spearman correlation coefficients of 0.872, 0.867 and 0.867 for WT-SpCas9, eSpCas9(1.1) and SpCas9-HF1, respectively.
-Meanwhile, DeepHF achieve 0.867, 0.862 and 0.860, respectively.
-After integrating with biological features, the performance gap between AttCRISPR and DeepHF is shortened, while AttCRISPR still has better performance.
-In addition, we also compare the standard deviation of data obtained in ten tests, which are also shown in Table~\ref{Tab:withbiofeature}.
-It reveal that AttCRISPR is more stable than DeepHF.
-
-\subsection{Interpretability of the AttCRISPR}\label{section:interpretability}
-
-In the following sections, we will analyze the insight into activity of sgRNA bring through the attention mechanism at both global and local levels 
-to validate the attention module in the AttCRISPR can help us to understand the decisions. 
-\subsubsection{Global interpretability}
 
@@
 
-At local level, we analyze a case (consisting of three sgRNAs as Table~\ref{Tab:optimum} show), 
+At local level, we analyze a case (consisting of three sgRNAs as Supplementary Tab. S1 show), 
 then we expect AttCRISPR to answer two imortant questions based on the local interpretability. 
@@
 
-For the first question, we input the least-active sgRNA in Table~\ref{Tab:optimum} (with the index of 8493 and the activity of 0.831, call source sgRNA for convenience) into the temporal AttCRISPR. 
+For the first question, we input the least-active sgRNA in Supplementary Tab. S1 (with the index of 8493 and the activity of 0.831, call source sgRNA for convenience) into the temporal AttCRISPR. 
 The score of each position is obtained based on Equation~(\ref{eq:05}) (the calculated symbol with $W$ is Hadamard product instead of dot product, in order to achieve the result in vector form), 
@@
 which show that the nucleotide at position 15 has a great effect on the score of position 14 and 16 (instead of position 13 or 17, which corresponding position are relatively dim in color). 
-As shown in Table~\ref{Tab:optimum}, in source sgRNA there are three consecutive Ts at position 14, 15 and 16, and this may reveal that multiple consecutive Us on sgRNA would leads to low on-target activity of sgRNA, which is consistent with earlier report \citep{wu2014genome-wide}.
+As shown in Supplementary Tab.
+S1, in source sgRNA there are three consecutive Ts at position 14, 15 and 16, and this may reveal that multiple consecutive Us on sgRNA would leads to low on-target activity of sgRNA, which is consistent with earlier report \citep{wu2014genome-wide}.
 
@@
 
-\begin{table}[!tpb]
-    \processtable{Three sgRNA and their activity \label{Tab:optimum}} 
-    {\begin{tabular}{@{}lll@{}}\toprule
-        Index & sgRNA & Activity \\\midrule
-        8493 & ACATGACTTTGGATTTCCCCAGG & 0.831\\
-        8492 & ACATGACTTTGGATTCCCCCAGG & 0.869\\
-        8491 & ACATGACTTTGGACTTCCCCAGG & 0.861\\
-        \botrule
-    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: 
-    \emph{Activity} of sgRNA represents the activity reported in WT-SpCas9 dataset (Supplementary Data 1). }
-\end{table}
 \begin{figure}[!tpb]

### 2020-11-18 Paper/temp/main.tex
11-18 paper

\documentclass{bioinfo}
\copyrightyear{2015} \pubyear{2015}

\access{Advance Access Publication Date: Day Month Year}
\appnotes{Manuscript Category}

\begin{document}
\firstpage{1}

\subtitle{Subject Section}

\title[short Title]{This is a title}
\author[Sample \textit{et~al}.]{Corresponding Author\,$^{\text{\sfb 1,}*}$, Co-Author\,$^{\text{\sfb 2}}$ and Co-Author\,$^{\text{\sfb 2,}*}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
$^{\text{\sf 2}}$Department, Institution, City, Post Code,
Country.}

\corresp{$^\ast$To whom correspondence should be addressed.}

\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

\editor{Associate Editor: XXXXXXX}

\abstract{\textbf{Motivation:} Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Textdsds Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text
Text Text Text Text Text.\\
\textbf{Results:} Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text\\
\textbf{Availability:} Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text Text  Text\\
\textbf{Contact:} \href{name@bio.com}{name@bio.com}\\
\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}
online.}

\maketitle

\section{Introduction}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text. Figure~\ref{fig:01}
shows that the above method  Text Text Text Text  Text Text Text
Text Text Text  Text Text.  \citep{Bag01} wants to know about
{\ldots}{\ldots} text follows.
\begin{equation}
\sum \text{\it x}+ \text{\it y} =\text{\it Z}\label{eq:01}\vspace*{-10pt}
\end{equation}

%\enlargethispage{12pt}

\section{Approach}

Equation~(\ref{eq:01}) Text Text Text Text Text Text  Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
.....

\begin{methods}
\section{Methods}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text
text\vspace*{1pt}

\begin{itemize}
\item for bulleted list, use itemize
\item for bulleted list, use itemize
\item for bulleted list, use itemize\vspace*{1pt}
\end{itemize}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text Text Text Text Text Text Text Text Text Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text\vadjust{\newpage}.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text Text Text Text Text Text Text Text Text Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\subsection{This is subheading}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text
text. Text Text Text Text Text Text  Text Text Text Text Text Text
Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\subsubsection{This is subsubheading}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text\break
text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text
textText Text Text Text Text Text  Text Text Text Text Text Text
Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\enlargethispage{6pt}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\begin{table}[!t]
\processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}\toprule head1 &
head2 & head3 & head4\\\midrule
row1 & row1 & row1 & row1\\
row2 & row2 & row2 & row2\\
row3 & row3 & row3 & row3\\
row4 & row4 & row4 & row4\\\botrule
\end{tabular}}{This is a footnote}
\end{table}

\end{methods}

\begin{figure}[!tpb]%figure1
\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{235pt} \vbox to 100pt{\vfill\hbox to
235pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
\end{minipage}}
%\centerline{\includegraphics{fig01.eps}}
\caption{Caption, caption.}\label{fig:01}
\end{figure}

%\begin{figure}[!tpb]%figure2
%%\centerline{\includegraphics{fig02.eps}}
%\caption{Caption, caption.}\label{fig:02}
%\end{figure}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\subsection{Test1}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\section{Discussion}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text.

Table~\ref{Tab:01} shows that Text Text Text Text Text  Text Text
Text Text Text Text. Figure~2\vphantom{\ref{fig:02}} shows that
the above method Text Text. Text Text Text  Text Text Text Text
Text Text. Figure~2\vphantom{\ref{fig:02}} shows that the above
method Text Text. Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     please remove the " % " symbol from \centerline{\includegraphics{fig01.eps}}
%     as it may ignore the figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

(Table~\ref{Tab:01}) Text Text Text Text Text Text  Text Text Text
Text Text Text Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\begin{enumerate}
\item this is item, use enumerate
\item this is item, use enumerate
\item this is item, use enumerate
\end{enumerate}

Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows\vadjust{\pagebreak} that the
above method  Text Text Text Text Text Text Text Text Text Text
Text Text.  \citealp{Boffelli03} might want to know about text
text text text Text Text Text Text Text Text  Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text\break Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text\vspace*{-10pt}

\section*{Acknowledgements}

Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text
text text text\vspace*{-12pt}

\section*{Funding}

This work has been supported by the... Text Text  Text Text.\vspace*{-12pt}

%\bibliographystyle{natbib}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{bioinformatics}
%
%\bibliographystyle{plain}
%
%\bibliography{Document}

\begin{thebibliography}{}

\bibitem[Bofelli {\it et~al}., 2000]{Boffelli03}
Bofelli,F., Name2, Name3 (2003) Article title, {\it Journal Name}, {\bf 199}, 133-154.

\bibitem[Bag {\it et~al}., 2001]{Bag01}
Bag,M., Name2, Name3 (2001) Article title, {\it Journal Name}, {\bf 99}, 33-54.

\bibitem[Yoo \textit{et~al}., 2003]{Yoo03}
Yoo,M.S. \textit{et~al}. (2003) Oxidative stress regulated genes
in nigral dopaminergic neurnol cell: correlation with the known
pathology in Parkinson's disease. \textit{Brain Res. Mol. Brain
Res.}, \textbf{110}(Suppl. 1), 76--84.

\bibitem[Lehmann, 1986]{Leh86}
Lehmann,E.L. (1986) Chapter title. \textit{Book Title}. Vol.~1, 2nd edn. Springer-Verlag, New York.

\bibitem[Crenshaw and Jones, 2003]{Cre03}
Crenshaw, B.,III, and Jones, W.B.,Jr (2003) The future of clinical
cancer management: one tumor, one chip. \textit{Bioinformatics},
doi:10.1093/bioinformatics/btn000.

\bibitem[Auhtor \textit{et~al}. (2000)]{Aut00}
Auhtor,A.B. \textit{et~al}. (2000) Chapter title. In Smith, A.C.
(ed.), \textit{Book Title}, 2nd edn. Publisher, Location, Vol. 1, pp.
???--???.

\bibitem[Bardet, 1920]{Bar20}
Bardet, G. (1920) Sur un syndrome d'obesite infantile avec
polydactylie et retinite pigmentaire (contribution a l'etude des
formes cliniques de l'obesite hypophysaire). PhD Thesis, name of
institution, Paris, France.

\end{thebibliography}
\end{document}

### 2020-11-18 Paper/main.tex
11-18 paper

@@
  It makes model tends to focus selectively on parts of the input, which is help in performing the task effectively. 
- Previous observation have shown that Cas9 preferentially binds sgRNAs containing purines but not pyrimidines \citep{wang2014genetic} and multiple thymine in the spacer impairing sgRNA activity \citep{wu2014genome-wide},
- that is to say some specific nucleotides and base position need more attention compared to others. 
- The above is the premise of introducing attention mechanism. Strictly speaking, we are not the first to bring attention mechanisms into this field. 
+ Strictly speaking, we are not the first to bring attention mechanisms into this field. 
  The most similar approach to ours is the work based on transformer by \citeauthor{Liu2019}. 
@@
 \begin{figure}[tpb]%figure4
-    \centerline{\includegraphics[width=86mm]{temporalmodule.png}}
+    \centerline{\includegraphics[width=86mm,height=100mm]{temporalmodule.png}}
     \caption{The architecture of temporal domain method in AttCRISPR. 
@@
 
+\section{Results}
+
 \begin{table}[!tpb]
@@
 
-\section{Results}
+\begin{figure*}[!tb]
+    \centerline{\includegraphics[width=178mm,height=160mm]{spatialattention.eps}}
+    \caption{Preference for each position-dependent nucleotide on the sgRNA sequence. 
+(a)-(c) Bars show the score of preference after standardization, and the higher the number, the more positive it is for activity of sgRNA. 
+The numbers below indicated the position of the nucleotides on-target DNA. 
+(d)-(f) Preference surfaces for each position-dependent nucleotide fitted with Bézier surfaces. 
+Each position-dependent nucleotide is a control point. 
+The coordinates of the control points on the vertical axis represent the degree of preference, 
+and the higher the position-dependent nucleotide corresponding to the control point is, the more positive it is for the activity of sgRNA.
+The contour plots at the bottom show the area of position-dependent nucleotides which have different contribution to the activity of sgRNA. 
+}\label{fig:spatialattention}
+\end{figure*}
 
@@
 Further experiment is designed to compare the performance of standard AttCRISPR (hand-crafted biological features are used to improve performance of ensemble AttCRISPR)
- and DeepHF, which is a current state-of-the-art method.
+ and DeepHF, which is a current state-of-the-art method.\vspace*{-10pt}
 
@@
 
+\begin{figure}[!tpb]
+    \centerline{\includegraphics[width=86mm,height=60mm]{local0.eps}}
+    \caption{
+The scores of sgRNA with index of 8493 obtained by the temporal AttCRISPR. 
+The bar plot reveals the score at each position, while the line of dashes reveals the average scores which can be used as a base line. 
+}\label{fig:opt}
+\end{figure}
+
 In the following sections, we will analyze the insight into activity of sgRNA bring through the attention mechanism at both global and local levels 
@@
 \subsubsection{Global interpretability}
-
-\begin{figure*}[!tpb]
-    \centerline{\includegraphics[width=178mm]{spatialattention.eps}}
-    \caption{Preference for each position-dependent nucleotide on the sgRNA sequence. 
-(a)-(c) Bars show the score of preference after standardization, and the higher the number, the more positive it is for activity of sgRNA. 
-The numbers below indicated the position of the nucleotides on-target DNA. 
-(d)-(f) Preference surfaces for each position-dependent nucleotide fitted with Bézier surfaces. 
-Each position-dependent nucleotide is a control point. 
-The coordinates of the control points on the vertical axis represent the degree of preference, 
-and the higher the position-dependent nucleotide corresponding to the control point is, the more positive it is for the activity of sgRNA.
-The contour plots at the bottom show the area of position-dependent nucleotides which have different contribution to the activity of sgRNA. 
-}\label{fig:spatialattention}
-\end{figure*}
 
@@
 
+\begin{figure}[!tpb]
+    \centerline{\includegraphics[width=86mm,height=60mm]{secondorder.eps}}
+    \caption{The visualization of second-order preference matrix $B$, 
+the elements in the $i$-th row and the $j$-th column represent the influence of nucleotide at position $j$ when generate the first-order preference $\tilde{A}$ at position $i$. 
+The warmer the color, the more important it is. 
+In the red box, a few unusual bright spots appear. 
+To be more specific, the nucleotide at position 15 has a great effect on the first-order preference at positon 14 and 16.
+}\label{fig:heatmap}
+\end{figure}
 At local level, we analyze a case (consisting of three sgRNAs as Supplementary Tab. S1 show), 
@@
 which show that the nucleotide at position 15 has a great effect on the score of position 14 and 16 (instead of position 13 or 17, which corresponding position are relatively dim in color). 
-As shown in Supplementary Tab.
-S1, in source sgRNA there are three consecutive Ts at position 14, 15 and 16, and this may reveal that multiple consecutive Us on sgRNA would leads to low on-target activity of sgRNA, which is consistent with earlier report \citep{wu2014genome-wide}.
+As shown in Supplementary Tab. S1, in source sgRNA there are three consecutive Ts at position 14, 15 and 16, 
+and this may reveal that multiple consecutive Us on sgRNA would leads to low on-target activity of sgRNA, 
+which is consistent with earlier report \citep{wu2014genome-wide}.\vspace*{-19pt}
 
@@
 As shown in Figure~\ref{fig:heatmap}, we note that the brightness at coordinates (14, 15) and (16, 15) exceeds (14, 13) and (16, 17). 
-In other words, there are two unusual bright spots at coordinates (14, 15) and (16, 15). 
 This could explain that the nucleotide trimer at position 14, 15, 16 has a great influence on the decision made by AttCRISPR. 
@@
 Current architecture of AttCRISPR focuses on predicting the on-target activity of conventional sgRNA which have a PAM based on NGG. 
-However it can be extended to other Cas9 species, variants or off-target task easily.
+However it can be extended to other Cas9 species, variants or off-target task easily.\vspace*{-19pt}
 
@@
 
-\begin{figure}[!tpb]
-    \centerline{\includegraphics[width=86mm]{local0.eps}}
-    \caption{
-The scores of sgRNA with index of 8493 obtained by the temporal AttCRISPR. 
-The bar plot reveals the score at each position at local level, while the line of dashes reveals the scores at global level. 
-At global level we calculated the scores of all sgRNA, then average the scores at each position to obtain the global level which can be used as base line and is helpful to judge the relative height of the scores.
-}\label{fig:opt}
-\end{figure}
-
-\begin{figure}[!tpb]
-    \centerline{\includegraphics[width=86mm]{secondorder.eps}}
-    \caption{The visualization of second-order preference matrix $B$, 
-the elements in the $i$-th row and the $j$-th column represent the influence of nucleotide at position $j$ when generate the first-order preference $\tilde{A}$ at position $i$. 
-The warmer the color, the more important it is. 
-In the red box, a few unusual bright spots appear. 
-To be more specific, the nucleotide at position 15 has a great effect on the first-order preference at positon 14 and 16.
-}\label{fig:heatmap}
-\end{figure}
 In this paper, we develop AttCRISPR, an ensemble method of both spatial method and temporal method follow the stacking strategy with strong interpretability. 
@@
 and our optimization results are verified with available experimental data. 
-To our knowledge, this is the first time that the attentional mechanim is used to reveal the reasons influencing on-target activity of sgRNA, and assist sgRNA design.
+To our knowledge, this is the first time that the attentional mechanim is used to reveal the reasons influencing on-target activity of sgRNA, and assist sgRNA design.\vspace*{-20pt}
 

### 2020-11-18 Paper/main.tex
11-18 paper

@@
 With the trained model, we reveal the preference for each position-dependent nucleotide on the sgRNA (short guide RNA) sequence in each dataset at global level. 
-And at local level, we prove that interpretability of AttCRISPR can be used to guide researcher to design sgRNA with higher activity. \\
+And at local level, we prove that the interpretability of AttCRISPR can be used to guide researcher to design sgRNA with higher activity. \\
 \textbf{Availability:} The example code are available at \href{https://github.com/South-Walker/AttCRISPR}{https://github.com/South-Walker/AttCRISPR}\\
@@
 In fact, \citeauthor{wang2019optimized} has already answered this question in detail with the DeepSHAP method.
-Leaving aside nucleotides, just consider the importance of each position, the method of \citeauthor{Liu2019} have gone some way too. 
+Leaving aside nucleotides, just consider the importance of each position, the method of \citeauthor{Liu2019} has gone some way too. 
 While our method is not based on the post hoc explanations techniques and input perturbations, the only work we need to do is to get the first-order preference $A$ generated by the attention module.
@@
 In practice, we input every sgRNA into the spatial AttCRISPR, in order to obtain the $A_s$ from the spatial attention module and take its mean value. 
-Then we rescale it through Z-score to obtain a standardization value and the final result is shown in Figure~\ref{fig:spatialattention}.
+Then we rescale it through Z-score to obtain a standardization value and the final result is shown in Figure~\ref{fig:spatialattention} and Supplementary Data S3.
 
@@
 The score of each position is obtained based on Equation~(\ref{eq:05}) (the calculated symbol with $W$ is Hadamard product instead of dot product, in order to achieve the result in vector form), 
-and the results are shown in Figure~\ref{fig:opt}. 
-Acording to Figure~\ref{fig:opt}, scores at position 14 and 16 of source sgRNA are significantly below the base line 
+and the results are shown in Figure~\ref{fig:opt} and Supplementary Data S4, in which scores at position 14 and 16 of source sgRNA are significantly below the base line 
 (in fact, the scores at position 6 and 11 is also noteworthy, however, we don't find sgRNA in the dataset for comparison). 

### 2021-04-04 Train/Pipeline.py
fix bug

@@ -23,12 +23,12 @@ def Pipeline(dataset,pretrainCNN=False,pretrainRNN=False,ensemble=False,fineTuni
         r = Ensemble(params['EnsembleParams'],
                  input['train']['onehot'],input['train']['biofeat'],label['train'],
                  input['test']['onehot'],input['test']['biofeat'],label['test'],
-                 cnn_trainable=False,rnn_trainable=False)
+                 withbiofeature=True,cnn_trainable=False,rnn_trainable=False)
     if fineTuning:
         r = Ensemble(params['FineTuning'],
                 input['train']['onehot'],input['train']['biofeat'],label['train'],
                 input['test']['onehot'],input['test']['biofeat'],label['test'],
-                cnn_trainable=True,rnn_trainable=True,load_weight=True)
+                withbiofeature=True,cnn_trainable=True,rnn_trainable=True,load_weight=True)
     return r
 if __name__ == "__main__":
     Pipeline('WT',pretrainCNN=False,pretrainRNN=False,ensemble=False,fineTuning=True) 
